### 2022-07-30 ms/porn.tex
base commit

\documentclass[12pt, letterpaper]{article}
\usepackage[titletoc,title]{appendix}
\usepackage{color}
\usepackage{booktabs}
\usepackage{caption}
\newcommand\fnote[1]{\captionsetup{font=small}\caption*{#1}}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{dark-red}{rgb}{0.75,0.10,0.10} 
\usepackage[margin=1in]{geometry}
\usepackage[linkcolor=dark-red,
			colorlinks=true,
			urlcolor=blue,
			pdfstartview={XYZ null null 1.00},
			pdfpagemode=UseNone,
			citecolor={dark-red},
			pdftitle={Consumption of Pornography Online}]{hyperref}
\usepackage{multibib}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{letterpaper}               % This is 8.5x11 paper. Options are a4paper or a5paper or other... 
\usepackage{graphicx}                % Handles inclusion of major graphics formats and allows use of 
\usepackage{amsfonts,amssymb,amsbsy}
\usepackage{amsxtra}
\usepackage{natbib}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{verbatim}
\setcitestyle{round,semicolon,aysep={},yysep={;}}
\usepackage{setspace}		     % Permits line spacing control. Options are \doublespacing, \onehalfspace
\usepackage{sectsty}		     % Permits control of section header styles
\usepackage{lscape}
\usepackage{fancyhdr}		     % Permits header customization. See header section below.
\usepackage{url}                 % Correctly formats URLs with the \url{} tag
\usepackage{fullpage}		     %1-inch margins
\usepackage{multirow}
\usepackage{rotating}
\setlength{\parindent}{3em}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{bm}
\usepackage{libertine}

\usepackage{chngcntr}

\title{\Large{Consumption of Pornography Online}\footnote{Data and scripts behind the analysis presented here can be downloaded at: \href{http://github.com/soodoku/porn}{http://github.com/soodoku/porn.}}}

\author{Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}} \and Andrew Guess\thanks{New York University, \href{mailto:guess@nyu.edu}{\footnotesize{\texttt{guess@nyu.edu}}}}\vspace{.5cm}}

\date{\vspace{.5cm}\normalsize{\today}}

\begin{document}
\maketitle

\begin{center}
\vspace{.5cm}\textbf{NB:} Preliminary draft. Please do not cite without permission.\vspace{1.5cm}
\end{center}

\begin{comment}

setwd(paste0(basedir, "adult/ms"))
tools::texi2dvi("porn.tex", pdf=TRUE, clean=TRUE) 
setwd(basedir)

\end{comment}

\begin{abstract}
\noindent Consumption of pornography has been blamed for a variety of societal ills, including, rise in misogyny, sex crimes, and coarsening of the culture. In this paper, using passive browsing data from comScore and YouGov, we investigate how much pornography Americans consume online, how consumption of pornography online has changed over time, and shed light on who consumes pornography. We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and many consuming small amounts. The median Internet user today spends X\% of time consuming pornography, and visits Y sites per year. Between 2002 and 2014, the consumption of pornography online increased by between XX and YY\%. Lastly, we find that, unlike previous data, relying on ecological inference, liberals consume more pornography than conservatives \citep{macinnis2015american, edelman2009markets}.
\end{abstract} 
\clearpage
\doublespace

Consumption of pornography is associated with a variety of disturbing attitudes, beliefs, emotions, and behaviors. Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, greater gender role conflict and lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex, and having extramarital sex \citep{wright2012internet}. A lot of popular pornography also contains a healthy dose of violence. One analysis of popular pornography revealed that 88.2\% of the analyzed scenes contained physical aggression, and 48.7\% verbal aggression \citep{bridges2010aggression}. In all, there exist good reasons to be worried about rise in consumption of pornography.

In this paper, using passive browsing data from comScore and a YouGov sample, we investigate how much pornography do Americans consume online, how consumption of pornography online has changed over time, and shed light on who consumes pornography. We find that there is sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography. The median Internet user today spends X\% of time consuming pornography, and visits Y sites per year. Between 2002 and 2014, the consumption of pornography online has increased by between XX and YY\%. Lastly, we find that, unlike previous data, relying on ecological inference, liberals consume more pornography than conservatives \citep{macinnis2015american, edelman2009markets}.

\citep{lykke2015widening}
\citep{boik2016empirical}

\section*{Data}
We exploit data from comScore and a YouGov survey to measure the consumption of adult content.

comScore maintains a panel of around 100,000 households, offering small rewards in exchange for monitoring all Internet data from a machine. There are multiple notable biases in the sample. See \ref{si1_comscore} for comparison between demographics and population benchmarks on some key variables.

YouGov maintains a large online panel recruited through a variety of methods. It uses matched sampling to survey respondents: The provider first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey. For details and validation, see \citet{rivers2009}. For this particular sample, panelists also provided de-identified access to their web browsing activity via passive metering software installed voluntarily on their computers. The software, called Wakoopa, can be uninstalled at any point and captures visited web URLs independent of the type of browser or browser-specific privacy settings.\footnote{Wakoopa does not save passwords or financial transactions, and personally identifying information is screened out by the survey provider.} At the time this data was made available in March 2015, YouGov had recruited 1,392 individuals to the web tracking panel, which is currently marketed as YouGov Pulse. Our data comes from \citet{guess2016}. See \ref{si2_yougov} for a comparison between demographics and population benchmarks on some key variables.

The passive metering component of this particular opt-in panel adds a layer of selectivity to the sampling process. Thus, to address concerns about the non-probability sampling procedure, we use raking weights to account for under- or overrepresentation along the following dimensions: age, gender, race, party identification, and region. We obtain population benchmark estimates from the U.S. Census (resident population, 2014) and proportions of party identifiers from Pew (2014). Raking takes into account the marginal, not the joint, distribution of the relevant demographic variables used to estimate the weights.

\section*{Measuring Consumption of Adult Content}
For both comScore and YouGov, we only observe data from a single machine per person. Our analyses should hold if people exhibit similar consumption patterns across devices. If that is too implausible an assumption, then we must decide on the direction of error and how it affects our analyses. We think it is likely that people would be less likely to search for pornography from machines on which they have installed these passive monitoring software (though the data are de-identified). If that is so, our estimates are a lower bound of net consumption of pornography per machine. As number of devices per person are increasing, all these numbers need to be adjusted. Next, is measurement error correlated with ideology? We have little reason to expect that, but we have no capacity to check if it is true. Thus, for current purposes, we assume that it is so.

We code pornographic content at the domain level. For both YouGov and comScore, we measure ideology using shallalist, DMOZ, and two machine learning classifiers. For YouGov data, we also present data based on classification from Wakoopa.

Our first classifier is based on just the domain name and domain suffix. In particular, we use a calibrated keyword classifier. The features of the model are whether any of the following keywords are present in the domain name:

\begin{quote}
cumshot, dildo, anal, adult, porn, mature, sex, xx, bbw, slut, whore, tits, titty, titties, pussy, sperm, gay, cheat, booty, ebony, asian, brazilian, fuck, cock, cunt, lesbian, shemale, boob, naughty, fatty, bitch, granny, jizz, faggot, horny, bukakke, bdsm, vagina, smut, x-rated, lusty, erotic, cunnilingus, blowjob, panty, hentai, latex, fetisch, fetish, erotik, bondage, naked, strip, teen, stocking, coitus, deprav, tube, perverse 
\end{quote}

For the 2004 comScore data, this gave about 140k domains that potentially carry pornographic content. We compare this list to the approximately 850k porn domains in the shallalist. This leaves us with a list of 68k domains with uncertain status. Use one of the many URL classification APIs. Using Trusted Source API, we get about 20k porn, and 48k non-porn. This gives us the lower bound of adult domains.

To estimate the false positives, we take a large random sample of 10,000 unique domains and compare results from our classifier to results from a commercial API by McAfee. This serves are our estimate of the false positive rate. For comScore data, our false negative rate is 5\%. False positive rate is close to 0. All of this ignores pornography available via more conventional channels. For instance, a large amount of pornography is consumed on sites like Tumblr.

\subsection{Measuring Partisan Identification}
With the YouGov survey, we measured ideology and partisanship using the conventional survey measures. In the comScore data, we do have data on partisan identification. We substitute with a validated model. We train our model on the YouGov data, predicting partisan identification using socio-demographics coded to match comScore (3-point party identification, gender, education, income, age, race, and ideology), and passively observed visits to site domains (excluding adult, rewards, and social networking sites). We aggregate the number of visits to each domain in the data by individual respondent, excluding domains with more than 100 visits total in the data. We estimate a cross-validated ridge (L2 penalized) regression with a total of 5,651 features. The model has a high degree of accuracy (92\%). %Interestingly, the features most predictive of Democratic partisan affiliation are not demographic variables but rather

\section*{Results}

\input{../tabs/models.tex}

\begin{figure}[h]
\centering
\caption{Consumption of Pornography by Ideology}
\includegraphics[scale=.75]{../figs/ideo_boxplot_shalla.pdf}
\label{fig:summary}
\end{figure}

\section*{Discussion}

\clearpage
\bibliographystyle{apsr}
\bibliography{porn_bib}
\clearpage
\appendix
\renewcommand{\thesection}{SI \arabic{section}}
\renewcommand\thetable{\thesection.\arabic{table}}  
\renewcommand\thefigure{\thesection.\arabic{figure}}
\counterwithin{figure}{section}
\counterwithin{table}{section}

\begin{center}
\Large{Supporting Information}
\end{center}

\section{Comparing comScore Sample to Population Benchmarks}
\label{si1_comscore}
\input{../tabs/cs_dem.tex}

\clearpage
\section{Comparing YouGov Sample to Population Benchmarks}
\label{si2_yougov}

\input{../tabs/app_table.tex}

\end{document}

### 2022-07-30 scripts/01_pred_porn/01_shalla_ip_to_host.R

@@ -1,0 +1,31 @@
+"
+
+Aim: Convert Shalla from IP/Cat to Domain/Cat
+Author: Gaurav Sood
+
+"
+
+# Set Global Options
+options(stringsAsFactors=FALSE)
+
+# Set working dir.
+setwd(basedir)
+setwd("domain_classifier/")
+
+# Load shalla data
+shalla     <- read.csv("shallalist_agg.csv")
+
+# Create a domain name level dataset
+dat <- data.frame(category=NULL, hostname=NULL)
+
+# Loop over shalla
+for (i in 1:nrow(shalla)) {
+    dat <- rbind(dat, cbind(category=shalla$shallalist.category[i], hostname=unlist(strsplit(shalla$shallalist.hostname[i], ","))))
+}
+
+# Only unique domain names
+shalla_s  <- subset(dat, !duplicated(hostname))
+
+# Write out the file
+write.csv(shalla_s, file="shalla_cat_unique_host.csv", row.names=F)
+ 

### 2022-07-30 scripts/01_pred_porn/02_shalla_model_porn.R

@@ -1,0 +1,82 @@
+"
+
+General Aim: Predict Category of Content Hosted by Domain Using Shallalist data
+In particular: Calibrated keyword classifier for porn
+Author: Gaurav Sood
+
+"
+# Global options
+options(StringsAsFactors=FALSE)
+
+# Load libs 
+library(urltools)
+library(goji)
+library(glmnet)
+
+# Load the data
+shalla <- read.csv("data/shalla/shalla_cat_unique_host.csv")
+
+# Featurize for calibrated porn keywords
+knotty_file <- file("data/knotty_words.txt", "r")
+knotty      <- readLines(knotty_file, warn=F)
+close(knotty_file)
+knotty      <- unlist(strsplit(knotty, ", "))
+
+# Let us just initialize new cols for each of the knotty words
+shalla[, knotty] <- NA
+
+for (j in knotty) {
+
+	shalla[, j] <- grepl(j, shalla$hostname)
+}
+
+# Code for IP
+#sum(grepl("^[0-9]*.[0-9]*.[0-9]*.[0-9]", shalla$hostname[shalla$cat==0]))/sum(length(shalla$hostname[shalla$cat==0]))
+shalla$num <- grepl("^[0-9]*.[0-9]*.[0-9]*.[0-9]", shalla$hostname)
+
+# Numerics
+shalla[,3:length(shalla)] <- shalla[,3:length(shalla)]*1
+shalla$porn_cat <- as.numeric(shalla$category=="porn")
+
+# Code for TLDs
+split_url <- suffix_extract(shalla$hostname)
+shallam   <- merge(shalla, split_url, by.x="hostname", by.y="host", all.x=T, all.y=F)
+
+shallam$subdomain <- nona(shallam$subdomain)
+shallam$suffix    <- nona(shallam$suffix)
+
+# Create dummies
+unique_cats <- unique(shallam$suffix)
+
+for(t in unique_cats) {
+  shallam[, t] <- grepl(t, shallam$suffix)
+}
+
+# Take out sparse cols.
+col_sums     <- colSums(shallam[, unique_cats])
+dispose_cats <- unique_cats[which(unique_cats %in% names(col_sums)[col_sums <= 100])]
+shallams     <- shallam[,- which(names(shallam) %in% dispose_cats)]
+remain_cats  <- unique_cats[!(unique_cats %in% dispose_cats)]
+
+# Split into train and test 
+set.seed(31415)
[…]

### 2022-07-30 scripts/01_pred_porn/03_shalla_pred_porn.R

@@ -1,0 +1,89 @@
+"
+
+Aim: 
+Predict YG Domains using saved model
+Author: Gaurav Sood
+
+"
+
+# Load libs 
+# devtools::install_github("soodoku/domain_classifier/rdomains")
+# devtools::install_github("soodoku/goji")
+
+library(goji)
+library(rdomains)
+
+# Set dir
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+setwd("web_analysis/")
+
+# YG Dat
+# -----------------
+# Load YG Data
+load("data/yg/unique_domains/unique_domains.Rdata")
+
+# Get ML cat
+ml_cat <- name_suffix_cat(unique.domains)
+ml_cat$ml_porn <- (ml_cat$category > .5)*1
+
+# Get shalla cat
+sh_cat <-  shalla_cat(unique.domains)
+sh_cat$shalla_porn <- (sh_cat$shalla_category == "porn")*1
+sh_cat$shalla_porn <- nona(sh_cat$shalla_porn)
+
+# Add shalla cat
+ml_cat$shalla_porn <- sh_cat$shalla_porn[match(ml_cat$domain_name, sh_cat$domain_name)]
+
+# Subset
+ml_cat <- subset(ml_cat, select=c("domains", "ml_porn", "shalla_porn")) 
+
+write.csv(ml_cat, file="data/yg/unique_domains/unique_domains_category_shalla_ml.csv", row.names=F)
+
+# ComScore 2013
+# ---------------------
+
+# Load YG Data
+load("data/comscore/unique_domains/cs13_unique_domain_names.rda")
+
+# Get ML cat
+#ml_cat <- name_suffix_cat(cs13_unique_domain_names)
+#ml_cat$ml_porn <- (ml_cat$category > .5)*1
+
+# Get shalla cat
+sh_cat <-  shalla_cat(cs13_unique_domain_names)
+sh_cat$shalla_porn <- (sh_cat$shalla_category == "porn")*1
+sh_cat$shalla_porn <- nona(sh_cat$shalla_porn)
+
+# Add shalla cat
+#ml_cat$shalla_porn <- sh_cat$shalla_porn[match(ml_cat$domains, sh_cat$domain_name)]
+
+# Subset
+#ml_cat <- subset(ml_cat, select=c("domains", "ml_porn", "shalla_porn")) 
+
[…]

### 2022-07-30 scripts/01_pred_porn/ag_shalla/shalla_recode.R

@@ -1,0 +1,57 @@
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+setwd("web analysis/")
+
+porn.indiv <- select(wakoopa, category, pmxid, duration, domain, used_at) %>%
+  mutate(porn = ifelse(category == "Adult", 1, 0)) %>%
+  group_by(pmxid) %>%
+  arrange(pmxid)
+
+# load data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
+indiv <- read.csv("ind_level_with_weights_2016.csv", stringsAsFactors = FALSE)
+
+# load porn domains from Shallalist
+library(readr)
+shalla <- read_csv("shallalist_agg.csv")
+head(shalla)
+head(shalla$shallalist.hostname)
+
+# grab labeled porn domains
+shalla <- select(shalla, shallalist.category, shallalist.hostname) %>%
+  filter(shallalist.category == "porn")
+
+# DON'T RUN!
+#shalla_domains <- as.vector(unlist(sapply(shalla$shallalist.hostname, function(x) strsplit(x, ","))))
+
+# split list into separate unique domains
+shalla_domains <- NULL
+for(i in 1:nrow(shalla)) {
+  
+  tmp <- as.vector(unlist(strsplit(shalla$shallalist.hostname[i], ",")))
+  shalla_domains <- c(shalla_domains, tmp)
+  
+}
+shalla_domains <- unique(shalla_domains)
+head(shalla_domains)
+
+length(which(porn.indiv$porn == 1)) # 79045
+
+table(porn.indiv$porn, useNA = "always")
+#   0       1    <NA> 
+#   4501651   79045 1738745 
+
+
+# now recode individual site visits matching shalla domain list
+# BEWARE: takes ~3 days to run
+for(i in 1:length(shalla_domains)) {
+  
+  try(porn.indiv[which(porn.indiv$domain %in% shalla_domains[i]),]$porn <- 1, silent = TRUE)
+  
+}
+
+table(porn.indiv$porn, useNA = "always")
+#   0       1    <NA> 
+#   4500520  104454 1714467 
+
+length(which(porn.indiv$porn == 1)) # 104454
+
+## NOW REMAKE OUTCOME MEASURES

### 2022-07-30 scripts/02_yg_survey/00_prep_data.R

@@ -1,0 +1,35 @@
+# rm(list=ls(all=TRUE))
+
+library(dplyr)
+
+names(indiv)
+names(s)
+head(s)
+
+### 1. LOAD INDIVIDUAL-LEVEL DATA WITH WEIGHTS (see raking_weights.R) ###
+
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+setwd("web analysis/")
+
+porn.indiv <- select(wakoopa, category, pmxid, duration, domain, used_at) %>%
+  mutate(porn = ifelse(category == "Adult", 1, 0)) %>%
+  group_by(pmxid) %>%
+  arrange(pmxid)
+
+# load data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
+indiv <- read.csv("data/yg/indiv_level_weighted_2016.csv", stringsAsFactors = FALSE)
+
+# load porn domains from Shallalist
+shalla <- readLines("data/measure_porn/shalla_porn_list/domains.txt")
+length(shalla)
+
+#sapply(shalla, function(x) { if(length(which(porn.indiv$domain %in% x)) > 0) { porn.indiv[which(porn.indiv$domain %in% x),]$porn <- 1 }})
+
+### 2. GENERATE DVs ###
+
+# Visited any porn? 1/0
+porn.indiv.1 <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) max(x, na.rm = TRUE))))
+porn.indiv.1 <- ifelse(porn.indiv.1 < 0, 0, porn.indiv.1)
+
+# Number of porn sites visited
+porn.indiv.n <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) sum(x, na.rm = TRUE))))

### 2022-07-30 scripts/02_yg_survey/01_app_table.R

@@ -1,0 +1,72 @@
+library(weights)
+library(xtable)
+
+wpct(s$age)
+wpct(s$gender)
+wpct(s$race5)
+wpct(s$pid3)
+wpct(s$region)
+wpct(s$income)
+
+wpct(s$age, weight = s$weights)
+wpct(s$gender, weight = s$weights)
+wpct(s$race5, weight = s$weights)
+wpct(s$pid3, weight = s$weights)
+wpct(s$region, weight = s$weights)
+wpct(s$income, weight = s$weights)
+
+
+round(c(wpct(s$age), wpct(s$gender), wpct(s$race5), wpct(s$pid3), wpct(s$region), wpct(s$income)), digits = 3)
+
+app_table <- as.data.frame(
+  cbind(round(c(wpct(s$age), wpct(s$gender), wpct(s$race5), wpct(s$pid3), wpct(s$region), wpct(s$income)), digits = 3),
+      round(c(wpct(s$age, weight = s$weights), wpct(s$gender, weight = s$weights), wpct(s$race5, weight = s$weights), 
+        wpct(s$pid3, weight = s$weights), wpct(s$region, weight = s$weights), wpct(s$income, weight = s$weights)), digits = 3))
+  )
+
+names(app_table) <- c("Unweighted", "Weighted")
+
+setwd("../../figs")
+print(xtable(app_table), file = "app_table.tex")
+
+### APP TABLE REVISED ###
+
+## first load indiv from 02_results.R (step 0)
+
+app_table <- as.data.frame(
+  cbind(round(c(wpct(indiv$age), wpct(indiv$gender), wpct(indiv$race5), wpct(indiv$pid3), wpct(indiv$region), wpct(indiv$income)), digits = 3),
+        round(c(wpct(indiv$age, weight = indiv$weights), wpct(indiv$gender, weight = indiv$weights), wpct(indiv$race5, weight = indiv$weights), 
+                wpct(indiv$pid3, weight = indiv$weights), wpct(indiv$region, weight = indiv$weights), wpct(indiv$income, weight = indiv$weights)), digits = 3))
+)
+
+names(app_table) <- c("Unweighted", "Weighted")
+
+## now add pop marginals from benchmarks
+
+# From 2010 Census: https://www.census.gov/popest/data/national/asrh/2014/index.html -- U.S. residents vintage 2014
+age <- round(c(31464158/245273438,
+               84029637/245273438,
+               83536432/245273438,
[…]

### 2022-07-30 scripts/02_yg_survey/01a_raking_weights.R

@@ -1,0 +1,147 @@
+# YouGov UK weights Wakoopa data by age, gender, region (by Internet representativeness)
+# see: http://sebadaza.com/survey/2012/08/25/raking/
+
+library(dplyr)
+library(weights)
+library(anesrake)
+
+setwd("~/Dropbox/web analysis/data/yg/wakoopa/")
+demos <- read.csv("wakoopa_demos.csv", stringsAsFactors = FALSE)
+load("wakoopa_fullcat.RData")
+head(wakoopa)
+
+s <- distinct(select(wakoopa, pmxid, birthyr, gender, educ, race5, ideo5, pid3))
+s <- merge(s, demos, by = "pmxid", all.x = TRUE)
+head(s)
+
+# YouGov codes, direct from Q wording:
+state.names <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "District of Columbia", "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina",
+                "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", "American Samoa", "Federated States of Micronesia", "Guam", "Marshall Islands", "Northern Mariana Islands", "Palau", "Puerto Rico", "U.S. Minor Outlying Islands", "Virgin Islands", "Alberta", "British Columbia", "Manitoba", "New Brunswick", "Newfoundland", "Northwest Territories", "Nova Scotia", "Nunavut", "Ontario", "Prince Edward Island", "Quebec", "Saskatchewan", "Yukon Territory", "Not in the U.S. or Canada")
[…]

### 2022-07-30 scripts/02_yg_survey/02_results.R

@@ -1,0 +1,241 @@
+# rm(list=ls(all=TRUE))
+library(dplyr)
+
+### THIS FILE: Run models & report tables + graphs.
+
+#############################################
+### 0. PREP #################################
+#############################################
+
+# Set dir
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+setwd("web analysis/")
+
+# load data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
+# DVs already coded in code/yg/porn_analysis.R
+indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode2.csv", stringsAsFactors = FALSE) # latest coding 3/29/16
+indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode_shalla1.csv", stringsAsFactors = FALSE) # latest coding 4/4/16 using Shallalist
+
+# relevel as needed:
+indiv$ideo5 <- factor(indiv$ideo5) # factorize
+indiv$ideo5 <- relevel(indiv$ideo5, "moderate") # moderate = base category
+indiv$ideo5 <- relevel(indiv$ideo5, "dk") # "dk" = base category
+#indiv$ideo5 <- relevel(indiv$ideo5, "liberal")
+
+indiv$pid3 <- factor(indiv$pid3)
+indiv$pid3 <- relevel(indiv$pid3, "ind") # independent = base category
+#indiv$pid3 <- relevel(indiv$pid3, "dem")
+head(indiv)
+
+
+
+#################################################
+### 1. MODELS ###################################
+#################################################
+
+### Test for overdispersion ###
+library(qcc)
+qcc.overdispersion.test(indiv$porn.indiv.n) # definitely overdispersed; use quasi-Poisson for count data
+
+### Dichotomous DV (visited porn 1/0) ###
+
+# ideology predictor
+summary(lm(porn.indiv.1 ~ ideo5 + age + gender, data = indiv, weights = weights))
+summary(lm(porn.indiv.1 ~ ideo5 + age + gender - 1, data = indiv, weights = weights)) # sans intercept
+summary(lm(porn.indiv.1 ~ ideo5 + age + gender + married, data = indiv, weights = weights))
+summary(lm(porn.indiv.1 ~ ideo5 + age + gender + married - 1, data = indiv, weights = weights))
[…]

### 2022-07-30 scripts/02_yg_survey/porn_analysis.R

@@ -1,0 +1,278 @@
+# rm(list=ls(all=TRUE))
+# porn.indiv <- select(wakoopa, category, duration, pmxid) %>%
+#   mutate(porn = ifelse(category == "Adult", 1, 0)) %>%
+#   group_by(pmxid) %>%
+#   arrange(pmxid)
+#   #ungroup() %>%
+#   #group_by(pmxid) %>%
+#   #summarise(numporn = sum())
+# 
+# porn.indiv.1 <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) max(x, na.rm = TRUE))))
+# porn.indiv.1 <- ifelse(porn.indiv.1 < 0, 0, porn.indiv.1)
+# porn.indiv.n <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) sum(x, na.rm = TRUE))))
+# pct_visits_on_porn <- round(as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) mean(x, na.rm = TRUE)))), digits = 2)
+
+# 
+# head(porn.indiv)
+# head(porn.indiv.1)
+# head(porn.indiv.n)
+# head(s)
+# 
+# indiv <- cbind(s, porn.indiv.1, porn.indiv.n, pct_visits_on_porn)
+# write.csv(indiv, "data/indiv_level_weighted.csv")
+
+### ADDING DURATION MEASURES -ag ###
+# 
+# porn.indiv$porn <- ifelse(is.na(porn.indiv$porn), 0, porn.indiv$porn)
+# 
+# porn.duration <- select(porn.indiv, pmxid, porn, duration) %>%
+#   group_by(pmxid, porn) %>%
+#   summarize(total_duration = sum(duration))
+# porn.duration <- filter(porn.duration, porn == 1) # this gives us the total duration of porn visits, if exist
+# 
+# porn.denom <- select(porn.indiv, pmxid, duration) %>%
+#   group_by(pmxid) %>%
+#   summarize(denom = sum(duration)) # total duration of ALL visits for each pmxid
+# 
+# total_time_on_porn <- sapply(indiv$pmxid, function(x) ifelse(x %in% porn.duration$pmxid, porn.duration[which(porn.duration$pmxid %in% x),]$total_duration, 0))
+# pct_time_on_porn <- round(total_time_on_porn/porn.denom$denom, digits = 2)
+# 
[…]

### 2022-07-30 scripts/02_yg_survey/top_domains.R

@@ -1,0 +1,33 @@
+names(porn.indiv)
+unique_prn <- select(porn.indiv, domain, porn) %>%
+  distinct(domain) %>%
+  group_by(porn) %>%
+  summarise(num_domains = n())
+2911/(262485+2911)
+# 1.1% unique domains = porn
+
+99415/(99415+6220026)
+# 1.57% all visits = porn
+
+top_domains <- select(porn.indiv, domain, porn) %>%
+  filter(porn == 1) %>%
+  group_by(domain) %>%
+  mutate(visits = n()) %>%
+  distinct(domain) #%>%
+#arrange(desc(visits))
+
+top_domains <- top_domains[order(top_domains$visits, decreasing = TRUE),]
+
+# pmxid                domain porn visits
+# 1  46799653        g.e-hentai.org    1  12672
+# 2       937           pornhub.com    1   8099
+# 3   2061741           xvideos.com    1   5587
+# 4   2009176          xhamster.com    1   4974
+# 5   2598004        myfreecams.com    1   4147
+# 6   2397958 adultfriendfinder.com    1   3733
+# 7       937         adam4adam.com    1   3404
+# 8       937           manhunt.net    1   3028
+# 9   2061741        literotica.com    1   2513
+# 10  2412386         streamate.com    1   2297
+
+

### 2022-07-30 scripts/03_pred_pid/01 predict_pid.R

@@ -1,0 +1,196 @@
+# rm(list=ls(all=TRUE))
+
+"
+
+Predicting PID
+
+1. Limit yourself to political domains + sociodem. categorized in same way as comScore (see data/cs)
+2. Aggregate domain level visitation up to person level
+3. PID_3 ~ agg_domain + sociodem.
+
+AG DETAILS:
+
+Comparing models:
+1) include non-political sites (filtering out mail, facebook, porn, points/benefits sites) + demos
+2) filter using only sites predicted to be political/news-related (predicted to be political using ML based on Shallalist & comScore)
+3) both of above using proportions (% total visits per respondent) rather than counts
+4) demos only for comparison
+5) web visits only (counts)
+
+"
+
+# Set dir
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+setwd("web analysis/")
+
+## Load packages
+library(dplyr)
+
+## Load indiv-level data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
+indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode_shalla1.csv", stringsAsFactors = FALSE)
+load("data/yg/wakoopa/wakoopa_fullcat.RData")
+
+
+## Remove URLs for email, FB, porn
+
+# Code for email/FB visits (Is this sufficient?)
+wakoopa$mail <- (grepl("hotmail", wakoopa$url, fixed = TRUE) | grepl("mail.yahoo", wakoopa$url, fixed = TRUE) | grepl("gmail", wakoopa$url, fixed = TRUE) | grepl("mail.google", wakoopa$url, fixed = TRUE) | grepl("outlook.com", wakoopa$url, fixed = TRUE) | grepl("email.", wakoopa$url, fixed = TRUE)) * 1
+wakoopa$fb <- grepl("facebook.com", wakoopa$url, fixed = TRUE) * 1
+
+# If filtering by politics: Get news_domains -- predicted political/news domains using both shalla & comScore data
+news_domains <- read.csv("data/yg/predict_pid/keep_domains_shalla_cs.csv", stringsAsFactors = FALSE)
+news_domains <- news_domains$x
+
+visits <- select(wakoopa, pmxid, pid3, domain, category, subcategory, mail, fb) %>%
+  filter(category != "Adult") %>%
[…]

### 2022-07-30 scripts/03_pred_pid/02 predict_pid_run_model.R

@@ -1,0 +1,161 @@
+## Ridge regression -- multiclass dem/rep/ind ##
+
+# run 01 predict_pid.R first
+# need x of features and visits_agg from 01 predict_pid.R
+
+library(glmnet) 
+library(caret)
+
+setwd("data/yg/predict_pid")
+load("web_classify_nofilter.RData")
+load("web_classify_filter.RData")
+load("web_classify_nofilter_props.RData")
+load("web_classify_filter_props.RData")
+
+# y is respondent-level pid
+y <- visits_agg$pid3
+y <- y[!seq(1, length(y)) %in% as.vector(attr(x, which = "na.action"))]
+y <- ifelse(!y %in% c("dem", "ind", "rep"), "ind", y) # set other categories to "ind"
+
+## OUT OF SAMPLE (test set)
+
+train_set <- createDataPartition(y, p = 0.8, list = FALSE)
+train_predictors <- x[train_set,]
+test_predictors <- x[-train_set,]
+train_classes <- y[train_set]
+test_classes <- y[-train_set]
+
+set.seed(9382)
+glmnet_grid <- expand.grid(alpha = c(0,  .5, 1), # c(0,  .1,  .2, .4, .6, .8, 1)
+                           lambda = seq(.01, .2, length = 10))
+glmnet_ctrl <- trainControl(method = "cv", number = 10)
+glmnet_fit <- train(train_classes ~ ., data = train_predictors,
+                    method = "glmnet",
+                    #preProcess = c("center", "scale"),
+                    tuneGrid = glmnet_grid,
+                    trControl = glmnet_ctrl)
+
+glmnet_fit
+plot(glmnet_fit)
+saveRDS(glmnet_fit, "glmnet_trainmodel_nofilter.rds")
+saveRDS(glmnet_fit, "glmnet_trainmodel_filter.rds")
+saveRDS(glmnet_fit, "glmnet_trainmodel_nofilter_props.rds")
+saveRDS(glmnet_fit, "glmnet_trainmodel_filter_props.rds")
+saveRDS(glmnet_fit, "glmnet_trainmodel_justvisits_nofilter_counts.rds")
+
+pred_classes <- predict(glmnet_fit, newdata = test_predictors)
+table(pred_classes)
+length(which(pred_classes == test_classes))/length(test_classes) # 0.576 out of sample for nofilter, 0.584 for filter
+# .567 for filter with proportions
[…]

### 2022-07-30 scripts/03_pred_pid/archive/01 predict_pid.R

@@ -1,0 +1,230 @@
+# rm(list=ls(all=TRUE))
+
+"
+
+Predicting PID
+
+1. Limit yourself to political domains + sociodem. categorized in same way as comScore (see data/cs)
+2. Aggregate domain level visitation up to person level
+3. PID_3 ~ agg_domain + sociodem.
+
+DETAILS:
+
+
+
+
+"
+
+# Set dir
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+setwd("web analysis/")
+
+## Load packages
+library(dplyr)
+library(glmnet) 
+library(caret)
+
+## Load indiv-level data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
+indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode_shalla1.csv", stringsAsFactors = FALSE)
+load("data/yg/wakoopa/wakoopa_fullcat.RData")
+
+
+## Remove URLs for email, FB, porn
+
+# Code for email/FB visits (Is this sufficient?)
+wakoopa$mail <- (grepl("hotmail", wakoopa$url, fixed = TRUE) | grepl("mail.yahoo", wakoopa$url, fixed = TRUE) | grepl("gmail", wakoopa$url, fixed = TRUE) | grepl("mail.google", wakoopa$url, fixed = TRUE) | grepl("outlook.com", wakoopa$url, fixed = TRUE) | grepl("email.", wakoopa$url, fixed = TRUE)) * 1
+wakoopa$fb <- grepl("facebook.com", wakoopa$url, fixed = TRUE) * 1
+#wakoopa$deals <- (grepl("bucks", wakoopa$url, fixed = TRUE) | grepl("deals", wakoopa$url, fixed = TRUE)) * 1
+
+# check URLs
+wakoopa$url[which(head(wakoopa$mail, 10000) == 1)]
+wakoopa$url[which(head(wakoopa$fb, 10000) == 1)]
+
+# Get news_domains -- predicted political/news domains using both shalla & comScore data
+news_domains <- read.csv("data/yg/predict_pid/keep_domains_shalla_cs.csv", stringsAsFactors = FALSE)
+news_domains <- news_domains$x
+
+visits <- select(wakoopa, pmxid, pid3, domain, category, subcategory, mail, fb) %>%
+            filter(category != "Adult") %>%
+            filter(subcategory != "Benefits/Points") %>%
[…]

### 2022-07-30 scripts/03_pred_pid/archive/__old_predict_pid.R

@@ -1,0 +1,236 @@
+"
+
+Predicting PID
+
+1. Limit yourself to political domains + sociodem. categorized in same way as comScore (see data/cs)
+2. Aggregate domain level visitation up to person level
+3. PID_3 ~ agg_domain + sociodem.
+
+"
+
+# Set dir
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+setwd("web analysis/")
+
+## Load packages
+library(dplyr)
+library(glmnet) 
+library(caret)
+
+## Load indiv-level data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
+indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode_shalla1.csv", stringsAsFactors = FALSE)
+
+load("data/yg/wakoopa/wakoopa_fullcat.RData")
+
+
+## Remove URLs for email, FB, porn
+
+# Code for email/FB visits (Is this sufficient?)
+wakoopa$mail <- (grepl("hotmail", wakoopa$url, fixed = TRUE) | grepl("mail.yahoo", wakoopa$url, fixed = TRUE) | grepl("gmail", wakoopa$url, fixed = TRUE) | grepl("mail.google", wakoopa$url, fixed = TRUE) | grepl("outlook.com", wakoopa$url, fixed = TRUE) | grepl("email.", wakoopa$url, fixed = TRUE)) * 1
+wakoopa$fb <- grepl("facebook.com", wakoopa$url, fixed = TRUE) * 1
+#wakoopa$deals <- (grepl("bucks", wakoopa$url, fixed = TRUE) | grepl("deals", wakoopa$url, fixed = TRUE)) * 1
+
+# check URLs
+wakoopa$url[which(head(wakoopa$mail, 10000) == 1)]
+wakoopa$url[which(head(wakoopa$fb, 10000) == 1)]
+
+visits <- select(wakoopa, pmxid, pid3, domain, category, subcategory, mail, fb) %>%
+            filter(category != "Adult") %>%
+            filter(subcategory != "Benefits/Points") %>%
+            filter(mail == 0 & fb == 0) # cuts down 6.3 --> 3 million URLs!
+
+rm(wakoopa)
+
+#visit_domain <- select(visits, pmxid, pid3, domain) %>%
+#                  distinct(domain) # 8339 unique domains
+
[…]

### 2022-07-30 scripts/04_comscore/by_domain_cat/script_for_each_machineid_date_base_on_category.py

@@ -1,0 +1,104 @@
+import time
+
+URL_CATEGORY_FILE = "url_category.csv"
+CATEGORY="Pornography"
+INTERNET_USAGE_FILE = "../../../web_browsing_2004" #"8bdff911e30b975c.csv"#
+FINAL_OUTPUT_FILE = "final_output_by_machineid_date.csv"
+
+
+FINAL_OUTPUT_HEADER = "machine_id, date, total_pages_viewed, total_time_spent, total_domain_category_pages_viewed, total_domain_category_time_spent"
+
+#############################READ DOMAIN LIST FILE#######################################
+DOMAIN_LIST = []
+print "Read the url category file %s" %(URL_CATEGORY_FILE,)
+with open(URL_CATEGORY_FILE) as myfile:
+        firstline = True
+        for line in myfile:
+            if firstline:
+                firstline = False
+                continue
+            line = line.strip().replace("\n","")
+            domain = line.split(',')[0]
+            category = line.split(',')[1]
+            if (len(domain)!=0 and category.lower()==CATEGORY.lower()):
+                DOMAIN_LIST.append(domain)
+print "Lengnth domain list  = %s\n" %(len(DOMAIN_LIST),) 
+
+###############################START PROCESSING DATA#####################################
+print "Start processing the data file %s" %(INTERNET_USAGE_FILE,)
+
+my_output_file = open(FINAL_OUTPUT_FILE,"w")
+my_output_file.write(FINAL_OUTPUT_HEADER + "\n")
+    
+fist_line = True
+prev_machine_id = -1
+DATA_BY_DATE = {}
+count = 0
+prev_timer = time.time()
+DOMAIN_LIST = set(DOMAIN_LIST)
+with open(INTERNET_USAGE_FILE) as myfile:
+    for line in myfile:
+        # Monitor the progress
+        count = count + 1
+        if (count%1000000==0):
+            now = time.time()
+            difference = int(now - prev_timer)
+            print "   + Processing line %s.000.000th time_till_now=%s(s)"%(count/1000000,difference,)
+        
+        if fist_line: # Skip the first row
+            fist_line = False
+        else:
+            # Extract data in a row
+            datas = line.split(",")
+            domain = datas[1]
+            if len(datas)==9:
+                machine_id = datas[3]
+                pages_viewed = int(float(datas[6]))
+                duration = int(float(datas[5]))
+                date =  datas[7]
+            elif len(datas)==8:
+                machine_id = datas[2]
[…]

### 2022-07-30 scripts/04_comscore/by_domain_list/script_for_each_machineid_date.py

@@ -1,0 +1,98 @@
+import time
+
+USE_DOMAIN_LIST_FILE = True
+DOMAIN_LIST_FILE = "porn_domains_list.txt" #"website_list_gentzkow_shapiro.txt"#
+INTERNET_USAGE_FILE = "../../../web_browsing_2004" #"8bdff911e30b975c.csv"#
+FINAL_OUTPUT_FILE = "final_output_each_machineid_date.csv"
+
+FINAL_OUTPUT_HEADER = "machine_id, date, total_pages_viewed, total_time_spent, total_pages_viewed_porn_domains, total_time_spent_porn_domains"
+
+#############################READ DOMAIN LIST FILE#######################################
+DOMAIN_LIST = []
+if USE_DOMAIN_LIST_FILE and len(DOMAIN_LIST_FILE)>0:
+    print "Read the domain list file %s" %(DOMAIN_LIST_FILE,)
+    with open(DOMAIN_LIST_FILE) as myfile:
+        for line in myfile:
+            line = line.strip().replace("\n","")
+            if (len(line)!=0):
+                DOMAIN_LIST.append(line)
+    print "Lengnth domain list  = %s\n" %(len(DOMAIN_LIST),) 
+
+###############################START PROCESSING DATA#####################################
+print "Start processing the data file %s" %(INTERNET_USAGE_FILE,)
+
+my_output_file = open(FINAL_OUTPUT_FILE,"w")
+my_output_file.write(FINAL_OUTPUT_HEADER + "\n")
+    
+fist_line = True
+prev_machine_id = -1
+DATA_BY_DATE = {}
+count = 0
+prev_timer = time.time()
+DOMAIN_LIST = set(DOMAIN_LIST)
+with open(INTERNET_USAGE_FILE) as myfile:
+    for line in myfile:
+        # Monitor the progress
+        count = count + 1
+        if (count%1000000==0):
+            now = time.time()
+            difference = int(now - prev_timer)
+            print "   + Processing line %s.000.000th time_till_now=%s(s)"%(count/1000000,difference,)
+        
+        if fist_line: # Skip the first row
+            fist_line = False
+        else:
+            # Extract data in a row
+            datas = line.split(",")
+            domain = datas[1]
+            if len(datas)==9:
+                machine_id = datas[3]
+                pages_viewed = int(float(datas[6]))
+                duration = int(float(datas[5]))
+                date =  datas[7]
+            elif len(datas)==8:
+                machine_id = datas[2]
+                pages_viewed = int(float(datas[5]))
[…]

### 2022-07-30 scripts/04_comscore/by_domain_list/script_for_each_machineid_date_domain.py

@@ -1,0 +1,119 @@
+import time
+
+DOMAIN_LIST_FILE = "porn_domains_list.txt" #"website_list_gentzkow_shapiro.txt"#
+INTERNET_USAGE_FILE = "../../web_browsing_2004" #"8bdff911e30b975c.csv"#
+FINAL_OUTPUT_FILE = "final_output_each_machineid_date_domain.csv"
+
+FINAL_OUTPUT_HEADER = "machine_id, date, total_pages_viewed, total_time_spent, total_pages_viewed_porn_domains, total_time_spent_porn_domains"
+USE_DOMAIN_LIST_FILE = True
+
+#############################READ DOMAIN LIST FILE#######################################
+DOMAIN_LIST = []
+if USE_DOMAIN_LIST_FILE and len(DOMAIN_LIST_FILE)>0:
+    print "Read the domain list file %s" %(DOMAIN_LIST_FILE,)
+    with open(DOMAIN_LIST_FILE) as myfile:
+        for line in myfile:
+            DOMAIN_LIST.append(line.strip().replace("\n",""))
+    print "Lengnth domain list  = %s\n" %(len(DOMAIN_LIST),)
+        
+# Add additional column into FINAL_OUTPUT_HEADER 
+for i in range(len(DOMAIN_LIST)):
+    FINAL_OUTPUT_HEADER = FINAL_OUTPUT_HEADER + ", domain_%s_pages_viewed, domain_%s_time_spent"%(i+1,i+1,)
+
+my_output_file = open(FINAL_OUTPUT_FILE,"w")
+my_output_file.write(FINAL_OUTPUT_HEADER + "\n")
+
+###############################START PROCESSING DATA#####################################
+print "Start processing the data file %s" %(INTERNET_USAGE_FILE,)
+    
+fist_line = True
+prev_machine_id = -1
+DATA_BY_DATE = {}
+count = 0
+prev_timer = time.time()
+usage_each_date_domain={}
+with open(INTERNET_USAGE_FILE) as myfile:
+    for line in myfile:
+        # Monitor the progress
+        count = count + 1
+        if (count%100000==0):
+            now = time.time()
+            difference = int(now - prev_timer)
+            print "   + Processing line %s00.000th time_till_now=%s(s)"%(count/100000,difference,)
+            
+        if fist_line: # Skip the first row
+            fist_line = False
+        else:
+            # Extract data in a row
+            datas = line.split(",")
+            domain = datas[1]
+            if len(datas)==9:
[…]

### 2022-07-30 scripts/05_classify_urls/classify_pages.R

@@ -1,0 +1,279 @@
+# rm(list=ls(all=TRUE))
+
+## Load packages
+library(quanteda)
+library(dplyr)
+library(glmnet) # for lasso/ridge regression
+
+## Load dfm of all texts in Wakoopa data
+setwd("~/Dropbox/web analysis/data/yg/urls_text/")
+load("urls_dfm_all.RData")
+
+## remove stopwords, single letters as features
+urls_dfm <- selectFeatures(urls_dfm, unique(c(stopwords("english"), letters)), "remove")
+topfeatures(urls_dfm, 50)
+urls_dfm
+
+## take random sample of 10,000 features
+urls_dfm <- trim(urls_dfm, minCount = 20, nsample = 10000)
+
+## Load URL list, set ordering, grab labels
+
+#urls <- readLines("../unique_urls.txt")
+#urls <- gsub("\"", "", urls)
+#head(urls)
+
+wakoopa <- select(wakoopa, domain, url, category, subcategory) %>%
+                  distinct(url)
+wakoopa <- rbind(c(NA, "url", NA, NA), wakoopa) # to match irrelevant first row of urls which I accidentally "scraped"
+
+text_order <- docnames(urls_dfm[1:100000])
+head(text_order, 20)
+text_order <- gsub(".txt", "", as.vector(unlist(sapply(strsplit(text_order, "_"), function(x) x[2]))))
+text_order <- as.numeric(text_order)
+head(text_order[order(text_order)])
+head(order(text_order))
+#urls[head(order(text_order))]
+
+wakoopa[1:100000,] <- wakoopa[1:100000,][text_order,]
+wakoopa[100001:200000,] <- wakoopa[100001:200000,][text_order,]
+wakoopa[200001:300000,] <- wakoopa[200001:300000,][text_order,]
+wakoopa[300001:400000,] <- wakoopa[300001:400000,][text_order,]
+wakoopa[400001:500000,] <- wakoopa[400001:500000,][text_order,]
+wakoopa[500001:600000,] <- wakoopa[500001:600000,][text_order,]
+wakoopa[600001:700000,] <- wakoopa[600001:700000,][text_order,]
+wakoopa[700001:800000,] <- wakoopa[700001:800000,][text_order,]
+wakoopa[800001:900000,] <- wakoopa[800001:900000,][text_order,]
[…]

### 2022-07-30 scripts/05_classify_urls/scrape_urls/python_scraper.py

@@ -1,0 +1,71 @@
+import urllib2
+import requests
+#import re
+import BeautifulSoup
+#import newspaper
+
+# def remove_html_tags(data):
+#      p = re.compile(r'<.*?>')
+#      return p.sub('', data)
+
+num = 0
+with open("unique_urls_100k.txt") as f: #urls_10.txt
+    for url in f:
+    	if num == 6:
+    		break
+    	num = num + 1
+    	url = url.strip("\"\r\n")
+        #print(url)
+        try:
+        	page = requests.get('http://' + url, timeout=1)
+        	page_content = page.text.encode("utf-8")
+        	#page_content = remove_html_tags(page_content) # remove tags
+        	# http://stackoverflow.com/questions/2977893/best-way-to-strip-out-everything-but-text-from-a-webpage
+        	page_content = ''.join(BeautifulSoup.BeautifulSoup(page_content).findAll(text=lambda 
+        		text: text.parent.name != "script" and 
+        		text.parent.name != "style")).encode("utf-8")
+        	with open('text/url'+str(num)+'.txt', 'w') as fid:
+    			fid.write(page_content)
+        except (urllib2.URLError, requests.exceptions.ConnectionError, requests.exceptions.ReadTimeout):
+        	print "Bad URL (" + str(num) + "): " + url
+        
+
+## newspaper test
+
+from newspaper import Article
+article = Article('http://' + url, keep_article_html=True, fetch_images=False)
+
+article.download()
+article.parse()
+
+article.html
+article.text
+
+from newspaper import fulltext
+
+html = requests.get('http://' + url, timeout=1).text.encode("utf-8")
+text = fulltext(html)
+
+## using newspaper (1)
+
+import urllib2
+import requests
+from newspaper import fulltext
+
+num = 0
+with open("unique_urls_100k.txt") as f: #urls_10.txt
+    for url in f:
+        if num == 50:
+            break
+        num = num + 1
+        url = url.strip("\"\r\n")
+        #print(url)
+        try:
+            page = requests.get('http://' + url, timeout=1)
+            page_content = page.text.encode("utf-8")
+            text = fulltext(page_content)
+            with open('text/url'+str(num)+'.txt', 'w') as fid:
+                fid.write(text)
+        except: # (urllib2.URLError, requests.exceptions.ConnectionError, requests.exceptions.ReadTimeout): #, requests.exceptions.ReadTimeout
+            print "Bad URL (" + str(num) + "): " + url
+        

### 2022-07-30 scripts/05_classify_urls/scrape_urls/scrape_pages_scratch.R

@@ -1,0 +1,52 @@
+setwd("/Users/aguess/Dropbox/web analysis/data/yg")
+load("unique_urls.RData")
+urls100 <- read.csv("unique_urls_100k.txt", stringsAsFactors = FALSE)
+urls100 <- urls100$us.mg6.mail.yahoo.com.neo.launch..rand.7hej9u1h3rnn2.6463884649
+
+writeLines(urls100[1:10,1], "urls_10.txt")
+
+head(urls100)
+urls100[1,1]
+urls100[10,1]
+
+dim(unique.urls)
+head(unique.urls)
+unique.urls$unique.urls[2200000]
+
+
+library(RCurl)
+library(rvest)
+
+#page <- readLines(paste0("http://", urls100[1,1]))
+page <- getURL(paste0("http://", urls100[1,1]), .opts=curlOptions(followlocation=TRUE))
+writeLines(page, "url.txt")
+
+page <- html_session(paste0("http://", urls100[1,1]))
+page %>% html_nodes("p") %>% html_text()
+
+download.file()
+
+# https://cran.r-project.org/web/packages/boilerpipeR/index.html
+library(boilerpipeR)
+
+url <- "blog.rstudio.org/2014/05/09/reshape2-1-4/"
+page <- getURL(paste0("http://", url), .opts=curlOptions(followlocation=TRUE))
+maintext <- ArticleExtractor(page, asText = TRUE)
+
+sink()
+cat(maintext)
+sink()
+
+writeLines(maintext, "text/urltest.txt")
+
+setwd("/Users/aguess/Documents/Columbia/Dissertation/jmp2/scrape_pages/text")
+for(i in 44:100) { #length(urls100)
+  
+  page <- ""
+  url <- urls100[i]
+  try(page <- getURL(paste0("http://", url), .opts=curlOptions(followlocation=TRUE, timeout=1, maxredirs=20)), silent = TRUE)
+  try(maintext <- ArticleExtractor(page, asText = TRUE), silent = TRUE)
+  
+  writeLines(maintext, paste0("url_", i, ".txt"))
+  
+}

### 2022-07-30 scripts/05_classify_urls/scrape_urls/scrape_urls.R

@@ -1,0 +1,31 @@
+#!/usr/bin/env Rscript
+args = commandArgs(trailingOnly=TRUE)
+
+library(boilerpipeR)
+library(RCurl)
+
+setwd("~/scrape_urls")
+
+a1 <- as.numeric(args[1])
+a2 <- as.numeric(args[2])
+a3 <- args[3]
+
+urls100 <- readLines("unique_urls.txt") # , stringsAsFactors = FALSE
+urls100 <- urls100[a1:a2]
+urls100 <- gsub("\"", "", urls100)
+#print(dim(urls100))
+
+setwd(a3)
+for(i in 1:length(urls100)) { #length(urls100)  11655 23069 33000 34176
+  
+  page <- ""
+  url <- urls100[i]
+  try(page <- getURLContent(paste0("http://", url), .opts=curlOptions(followlocation=TRUE, timeout=2, maxredirs=20)), silent = TRUE)
+  try(maintext <- ArticleExtractor(page, asText = TRUE), silent = TRUE)
+  
+  writeLines(maintext, paste0("url_", i, ".txt"))
+  
+}
+
+print(i)
+

### 2022-07-30 scripts/05_classify_urls/scrape_urls/scraper.R

@@ -1,0 +1,23 @@
+library(boilerpipeR)
+library(RCurl)
+
+setwd("~/Documents/prn_project/data")
+#load("unique_urls.RData")
+urls100 <- readLines("unique_urls_100k.txt") # , stringsAsFactors = FALSE
+#urls100 <- urls100$us.mg6.mail.yahoo.com.neo.launch..rand.7hej9u1h3rnn2.6463884649
+head(urls100)
+tail(urls100)
+
+urls100 <- gsub("\"", "", urls100)
+
+setwd("text_try3")
+for(i in 1:34175) { #length(urls100)  11655 23069 33000 34176
+  
+  page <- ""
+  url <- urls100[i]
+  try(page <- getURLContent(paste0("http://", url), .opts=curlOptions(followlocation=TRUE, timeout=2, maxredirs=20)), silent = TRUE)
+  try(maintext <- ArticleExtractor(page, asText = TRUE), silent = TRUE)
+  
+  writeLines(maintext, paste0("url_", i, ".txt"))
+  
+}

### 2022-07-30 scripts/05_classify_urls/unique_domains_urls.R

@@ -1,0 +1,41 @@
+"
+Produce a file with Unique Domain Names, URLs
+
+"
+# Set dir
+ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
+
+
+# From AG
+unique.urls <- unique(wakoopa$url)
+unique.urls <- as.data.frame(unique.urls)
+unique.domains <- unique(wakoopa$domain)
+
+save(unique.urls, file = "unique_urls.RData")
+save(unique.domains, file = "unique_domains.RData")
+
+# Convert Rdata files to one domain/url per line
+# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+# Load domain data
+load("web analysis/data/yg/unique_domains.RData")
+
+# Output: one domain per line
+fileConn<-file("web analysis/data/unique_domains.txt")
+writeLines(unique.domains[1:length(unique.domains)], fileConn)
+close(fileConn)
+
+# Load url data
+load("web analysis/data/yg/unique_urls.RData")
+
+# Output: one url per line
+fileConn<-file("web analysis/data/yg/unique_urls.txt")
+writeLines(as.name(as.character(unique.urls[,1])), fileConn)
+close(fileConn)
+
+# Take large random sample
+set.seed(31415)
+fileConn<-file("web analysis/data/yg/unique_urls_100k.txt")
+temp <- as.character(unique.urls[sample(nrow(unique.urls),100000),1])
+writeLines(noquote(temp), fileConn)
+close(fileConn)

### 2022-07-30 scripts/05_classify_urls/url_dfm/create_dfm.R

@@ -1,0 +1,26 @@
+#devtools::install_github("kbenoit/quanteda")
+library(quanteda)
+
+# Create corpus from multiple text files
+text1 <- textfile("~/Documents/Columbia/Dissertation/jmp2/scrape_pages/text/u1/*.txt", cache = FALSE,
+                  docvarsfrom = "filenames", docvarnames = c("whichdoc", "urlnum"))
+summary(corpus(text1), 5)
+texts(text1)[1]
+# ~ 5 mins x 22 = 110 min = 1 hour 50 mins
+
+# Create document-feature matrix from corpus
+urls_dfm <- dfm(corpus(text1), ignoredFeatures = stopwords("english"), stem = TRUE) #[1:99999]
+# 66 sec
+
+setwd("/Users/aguess/Dropbox/web analysis/data/yg/urls_text")
+#save(urls_dfm, file = "dfm_1.RData")
+load("dfm_1.RData")
+
+text2 <- textfile("~/Documents/Columbia/Dissertation/jmp2/scrape_pages/text/u2/*.txt", cache = FALSE,
+                  docvarsfrom = "filenames", docvarnames = c("whichdoc", "urlnum"))
+urls_dfm2 <- dfm(corpus(text2), ignoredFeatures = stopwords("english"), stem = TRUE) #[1:99999]
+
+corpus_1_2 <- corpus(text1) + corpus(text2) # docvars = data.frame(corpus = rep("Text1", 100000))
+summary(corpus_1_2, 5)
+
+paste0("u", seq(1, 22))

### 2022-07-30 scripts/05_classify_urls/url_dfm/create_dfm_parallel_cluster.R

@@ -1,0 +1,38 @@
+#devtools::install_github("kbenoit/quanteda")
+library(quanteda)
+library(methods)
+library(parallel)
+
+setwd("~/scrape_urls")
+
+# Calculate the number of cores
+no_cores <- detectCores() - 1
+
+# Initiate cluster
+cl <- makeCluster(no_cores)
+clusterEvalQ(cl, library(quanteda))
+
+u <- parLapply(cl, paste0("u", seq(1, 22)), function(d) {
+
+  # Create corpus from multiple text files
+  corpus(textfile(paste0(d, "/*.txt"), cache = FALSE, docvarsfrom = "filenames", docvarnames = c("batch", "url")))
+
+})
+
+stopCluster(cl)
+
+corpus_all <- u[[1]] + u[[2]] + u[[3]] + u[[4]] + u[[5]] + u[[6]] + u[[7]] + u[[8]] + u[[9]] + u[[10]]
+corpus_all <- corpus_all + u[[11]] + u[[12]] + u[[13]] + u[[14]] + u[[15]] + u[[16]] + u[[17]] + u[[18]] + u[[19]] + u[[20]]
+corpus_all <- corpus_all + u[[21]] + u[[22]]
+
+print("done combining, now dfm")
+
+# Create document-feature matrix from corpus
+urls_dfm <- dfm(corpus_all, ignoredFeatures = stopwords("english"), stem = TRUE) #[1:99999]
+
+print("done with dfm!")
+
+save(urls_dfm, file = "urls_dfm_all.RData")
+
+print("SAVED")
+

### 2022-07-30 scripts/cat_domains.R

@@ -1,0 +1,48 @@
+"
+
+Get category of domains
+"
+
+# Load the libs 
+library(data.table)
+library(rdomains)
+library(dplyr)
+
+# general function
+
+gen_cat <- function(file_name = NULL ) {
+
+	domains          <- fread(file_name)
+	domains_shalla   <- shalla_cat(domains$x)
+	domains_ml1_porn <- adult_ml1_cat(domains$x)
+
+	# Join 
+	domains_cat      <- inner_join(domains_shalla, domains_ml1_porn)
+	domains_cat
+}
+
+# 2002
+# ---------------------
+cs2002_cat <- gen_cat("cs2002_unique_domains")
+write.csv(cs2002_cat, file="cs2002_unique_domains_shalla_ml1_porn.csv", row.names=F)
+
+cs2004_cat <- gen_cat("cs2004_unique_domains")
+write.csv(cs2004_cat, file="cs2004_unique_domains_shalla_ml1_porn.csv", row.names=F)
+
+cs2008_cat <- gen_cat("cs2008_unique_domains")
+write.csv(cs2008_cat, file="cs2008_unique_domains_shalla_ml1_porn.csv", row.names=F)
+
+cs2009_cat <- gen_cat("cs2009_unique_domains")
+write.csv(cs2009_cat, file="cs2009_unique_domains_shalla_ml1_porn.csv", row.names=F)
+
+cs2010_cat <- gen_cat("cs2010_unique_domains")
+write.csv(cs2010_cat, file="cs2010_unique_domains_shalla_ml1_porn.csv", row.names=F)
+
+cs2011_cat <- gen_cat("cs2011_unique_domains")
+write.csv(cs2011_cat, file="cs2011_unique_domains_shalla_ml1_porn.csv", row.names=F)
+
+cs2012_cat <- gen_cat("cs2012_unique_domains")
+write.csv(cs2012_cat, file="cs2012_unique_domains_shalla_ml1_porn.csv", row.names=F)
+
+cs2013_cat <- gen_cat("cs2013_unique_domains")
+write.csv(cs2013_cat, file="cs2013_unique_domains_shalla_ml1_porn.csv", row.names=F)

### 2022-07-30 scripts/comscore_demographics_summarize.R

@@ -1,0 +1,85 @@
+"
+Summarize comscore demographic data
+
+"
+
+# Set dir. 
+setwd(basedir)
+setwd("adult")
+
+# Recode Function
+# ---------------
+cs_recoder <- function(dat=NULL) {
+
+	dat$hoh_most_education_r <- factor(car::recode(dat$hoh_most_education, 
+												  "0='Less than HS'; 1='HS Diploma or Equivalent'; 2='Some college but no degree'; 3='Associate';4='BS';5='Grad. Degree or Above';c(99, '**')=NA"),
+												  c('Less than HS', 'HS Diploma or Equivalent', 'Some college but no degree', 'Associate', 'BS', 'Grad. Degree or Above'))
+	dat$household_income_r   <- factor(car::recode(dat$household_income,   
+													"1='less Than 15k'; 2='15k--25k'; 3='25k--35k';4='35k--50k';5='50k--75k'; 6= '75k--100k';7 = '100k+'"),
+													c('less Than 15k', '15k--25k', '25k--35k', '35k--50k', '50k--75k', '75k--100k', '100k+'))
+
+	dat$connection_speed_r   <- factor(car::recode(dat$connection_speed,   "1='Broadband'; 0='Not Broadband'"), c('Broadband', 'Not Broadband'))
+	dat$racial_background_r  <- factor(car::recode(dat$racial_background,  "1='White'; 2='Black'; 3='Asian';5='Other';'*'=NA"), c('White', 'Black', 'Asian', 'Other'))
+
+	dat$census_region_r      <- factor(car::recode(dat$census_region,      "'*'=NA; 1='Northeast'; 2='North Central'; 3='South';4='West'"), c('Northeast', 'North Central', 'South', 'West'))
+	dat$country_of_origin_r  <- factor(car::recode(dat$country_of_origin,  "1='Hispanic'; 0='Non-Hispanic'"), c('Hispanic', 'Non-Hispanic'))
+	dat$hoh_oldest_age_r     <- factor(car::recode(dat$hoh_oldest_age,     "1='18--20'; 2='21--24'; 3='25--29';4='30--34';5='35-39'; 6= '40-44';7 = '45-49'; 8 = '50-54'; 9 ='55-59'; 10 ='60-64'; 11='65+'; 99=NA"))
[…]

### 2022-07-30 scripts/comscore_summarize.R

@@ -1,0 +1,158 @@
+"
+
+summarize by machine, domain
+	: total_page_views, total_duration, n_unique_days_machine_visited_site
+
+"
+
+# Set dir. 
+setwd(basedir)
+
+# Load libs 
+library(data.table)
+library(dplyr)
+
+# 2002 --- we have data starting July  (20020701 20021231)
+# -----------------------------------------------------------
+
+# Read in the data 
+cs2002 <- fread("cs2002_by_machine_date_domain.csv")
+
+# Summarize data > per machine_id > per domain > total_time, total_page_views, n_unique_days 
+by_machine_domain <- 
+cs2002 %>%
+group_by(machine_id, domain_name) %>%
+summarise(total_duration=sum(total_duration, na.rm=T), total_pages=sum(total_pages, na.rm=T), site_category_id = mean(site_category_id), n_dates = length(unique(date)))
+
+# Write out
+write.csv(by_machine_domain, file="cs2002_by_machine_domain.csv", row.names=F)
+
+# 2004
+# -----------
+
+# Read in the data
+cs2004 <- fread("cs2004_by_machine_date_domain.csv")
+
+by_machine_domain <- 
+cs2004 %>%
+group_by(machine_id, domain_name) %>%
+summarise(total_duration=sum(total_duration, na.rm=T), total_pages=sum(total_pages, na.rm=T), n_dates = length(unique(event_date)))
+
+# Write out
+write.csv(by_machine_domain, file="cs2004_by_machine_domain.csv", row.names=F)
+
+# 2006
+# -----------
+
+# Read in the data
+cs2006 <- fread("cs2006_by_machine_date_domain.csv")
+
+by_machine_domain <- 
+cs2006 %>%
+group_by(machine_id, domain_name) %>%
+summarise(total_duration=sum(total_duration, na.rm=T), total_pages=sum(total_pages, na.rm=T), n_dates = length(unique(event_date)))
+
+# Write out
+write.csv(by_machine_domain, file="cs2006_by_machine_domain.csv", row.names=F)
+
+# 2007
+# -----------
+
+# Read in the data
+cs2007 <- fread("cs2007_by_machine_date_domain.csv")
+
+by_machine_domain <- 
+cs2007 %>%
+group_by(machine_id, domain_name) %>%
[…]

### 2022-07-30 scripts/cs_join_domain_cat_summarized_dat.R

@@ -1,0 +1,80 @@
+"
+join  unique_domain_cat + 
+summarized by machine, domain
+	: total_page_views, total_duration, n_unique_days_machine_visited_site
+
+"
+
+# Set dir. 
+setwd(basedir)
+
+# Load libs 
+library(data.table)
+library(dplyr)
+
+# 2002 --- we have data starting July  (20020701 20021231)
+# -----------------------------------------------------------
+
+# Read in the data 
+cs2002_machine_domain  <- fread("data/media/comScore/views_duration_by_machine_id_domain/cs2002_by_machine_domain.csv")
+cs2002_domain_cat      <- fread("data/media/comScore/unique_domain_cat/cs2002_unique_domains_shalla_ml1_porn.csv")
+#cs2002_dem <- fread("data/comscore/dem/demographics2002.csv")
+
+cs2002_t <- inner_join(cs2002_machine_domain, cs2002_domain_cat)
+
+cs2002_porn <- 
+cs2002_t %>%
+group_by(machine_id) %>%
+summarise(porn_time = sum(as.numeric(shalla_category=='porn')*as.numeric(total_duration), na.rm=T), porn_views = sum(as.numeric(shalla_category=='porn')*as.numeric(total_pages), na.rm=T))
+
+mean(cs2002_t$shalla_category=='porn', na.rm=T)
+#[1] 0.3929881
+
+median(cs2002_porn$porn_time)
+median(cs2002_porn$porn_views)
+
+
+# Read in the data 
+cs2008_machine_domain  <- fread("data/media/comScore/views_duration_by_machine_id_domain/cs2008_by_machine_domain.csv")
+cs2008_domain_cat      <- fread("data/media/comScore/unique_domain_cat/cs2008_unique_domains_shalla_ml1_porn.csv")
+#cs2002_dem <- fread("data/comscore/dem/demographics2002.csv")
+
+cs2008_t <- inner_join(cs2008_machine_domain, cs2008_domain_cat)
+mean(cs2008_t$shalla_category=='porn', na.rm=T)
+
+cs2008_porn <- 
+cs2008_t %>%
+group_by(machine_id) %>%
+summarise(porn_time = sum(as.numeric(shalla_category=='porn')*as.numeric(total_duration), na.rm=T), porn_views = sum(as.numeric(shalla_category=='porn')*as.numeric(total_pages), na.rm=T))
+
+median(cs2008_porn$porn_time)
[…]

### 2022-07-30 scripts/grab_domains.R

@@ -1,0 +1,11 @@
+rm(list=ls(all=TRUE))
+
+library(tidyverse)
+
+setwd("~/Dropbox/MediaChoiceModeration/data")
+load("pulse_merged.RData") # full data
+
+domains <- wakoopa %>% select(domain) %>% unique()
+
+# setwd("")
+# write_csv(domains, "web_domains.csv")

### 2022-07-30 scripts/misc_pctwhite.R

@@ -1,0 +1,16 @@
+library(dplyr)
+
+# load wakoopa data
+load("wakoopa_fullcat.RData")
+
+channels <- paste0(c("cnn", "msnbc", "foxnews", "abcnews.go", "nbc", "cbs"), ".com")
+
+pct_white <- select(wakoopa, domain, race5, weights) %>%
+                filter(domain %in% channels) %>%
+                group_by(domain) %>%
+                dplyr::summarize(num_white = length(which(race5 == "white")),
+                                 avg_white_unweighted = num_white/n(),
+                                 avg_white_weighted = weighted.mean(race5 == "white", weights, na.rm = TRUE))
+
+setwd("~/Dropbox/issue_ideology/data/media")
+write.csv(pct_white, "pctwhite_channels.csv")

### 2022-12-10 ms/porn.tex
remove old files

@@
 \usepackage{booktabs}
-\usepackage{caption}
-\newcommand\fnote[1]{\captionsetup{font=small}\caption*{#1}}
-
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
 \definecolor{dark-red}{rgb}{0.75,0.10,0.10}
+\definecolor{bluish}{rgb}{0.05,0.05,0.85}
+
 \usepackage[margin=1in]{geometry}
-\usepackage[linkcolor=dark-red,
+\usepackage[linkcolor=blue,
 			colorlinks=true,
@@
 			pdfpagemode=UseNone,
-			citecolor={dark-red},
-			pdftitle={Consumption of Pornography Online}]{hyperref}
-\usepackage{multibib}
+			citecolor={bluish},
+			pdftitle={partisan_gap}]{hyperref}
+
+\usepackage[resetlabels,labeled]{multibib}
+\newcites{SI}{SI References}
+\usepackage{natbib}
+
+\usepackage{float}
+
 \usepackage{geometry}  % see geometry.pdf on how to lay out the page. There's lots.
@@
 \usepackage{amsxtra}
-\usepackage{natbib}
-\usepackage{dcolumn}
-\usepackage{longtable}
 \usepackage{verbatim}
 \setcitestyle{round,semicolon,aysep={},yysep={;}}
-\usepackage{setspace}		     % Permits line spacing control. Options are \doublespacing, \onehalfspace
+\usepackage{setspace} % Permits line spacing control. Options are:
+%\doublespacing
+%\onehalfspace
 \usepackage{sectsty}    % Permits control of section header styles
-\usepackage{lscape}
+\usepackage{pdflscape}
 \usepackage{fancyhdr}   % Permits header customization. See header section below.
@@
 \usepackage{multirow}
+\usepackage{verbatim}
 \usepackage{rotating}
 \setlength{\parindent}{3em}
-\usepackage{subcaption}
+
 \usepackage[T1]{fontenc}
-\usepackage{bm}
-\usepackage{libertine}
+\usepackage[bitstream-charter]{mathdesign}
 
 \usepackage{chngcntr}
+\usepackage{longtable}
+\usepackage{adjustbox}
+\usepackage{dcolumn}
+
+\usepackage[nameinlink, capitalize, noabbrev]{cleveref}
+
+\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
+
+\makeatother
+
+\usepackage{footmisc}
+\setlength{\footnotesep}{\baselineskip}
+\makeatother
+\renewcommand{\footnotelayout}{\normalsize \doublespacing}
+
+% Colors
+\usepackage{color}
+
+\newcommand{\bch}{\color{blue}\em  }   % begin change
+\newcommand{\ying} {\color{orange}\em  }   % begin change
+\newcommand{\bgcd} {\color{purple}\em }
+\newcommand{\ech}{\color{black}\rm  }    % end change
+
+% Caption
+\usepackage[hang, font=small,skip=0pt, labelfont={bf}]{caption}
+%\captionsetup[subtable]{font=small,skip=0pt}
+\usepackage{subcaption}
+
+% tt font issues
+% \renewcommand*{\ttdefault}{qcr}
+\renewcommand{\ttdefault}{pcr}
+
+\setcounter{page}{0}
+
+\usepackage{lscape}
+\renewcommand{\textfraction}{0}
+\renewcommand{\topfraction}{0.95}
+\renewcommand{\bottomfraction}{0.95}
+\renewcommand{\floatpagefraction}{0.40}
+\setcounter{totalnumber}{5}
+\makeatletter
+\providecommand\phantomcaption{\caption@refstepcounter\@captype}
+\makeatother
 
@@
 
-\author{Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}} \and Andrew Guess\thanks{New York University, \href{mailto:guess@nyu.edu}{\footnotesize{\texttt{guess@nyu.edu}}}}\vspace{.5cm}}
+\author{Lucas Shen\thanks{Lucas is a Research Fellow at Asia Competitiveness Institute, Lee Kuan Yew School of Public Policy, at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
 
@@
 \begin{abstract}
-\noindent Consumption of pornography has been blamed for a variety of societal ills, including, rise in misogyny, sex crimes, and coarsening of the culture.
-In this paper, using passive browsing data from comScore and YouGov, we investigate how much pornography Americans consume online, how consumption of pornography online has changed over time, and shed light on who consumes pornography.
-We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and many consuming small amounts.
-The median Internet user today spends X\% of time consuming pornography, and visits Y sites per year.
-Between 2002 and 2014, the consumption of pornography online increased by between XX and YY\%.
-Lastly, we find that, unlike previous data, relying on ecological inference, liberals consume more pornography than conservatives \citep{macinnis2015american, edelman2009markets}.
+\noindent Consumption of pornography has been blamed for a variety of societal ills, including, the rise in misogyny, sex crimes, and coarsening of the culture.
+Using passive browsing data from YouGov, we investigate how much pornography Americans consume online.
+We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography with most consuming small amounts.
+The median American Internet user today spends X\% of time-consuming pornography, visiting Y sites per month.
+Lastly, we find that, unlike previous research, relying on ecological inference, liberals consume slightly more pornography than conservatives \citep{macinnis2015american, edelman2009markets}.
 \end{abstract} 
@@
 
-\section{Comparing comScore Sample to Population Benchmarks}
-\label{si1_comscore}
-\input{../tabs/cs_dem.tex}
-
 \clearpage

### 2022-12-10 ms/porn.tex
revise ms

@@
 \definecolor{bluish}{rgb}{0.05,0.05,0.85}
-
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{naturalnames}{hyperref}
 \usepackage[margin=1in]{geometry}
@@
 			citecolor={bluish},
-			pdftitle={partisan_gap}]{hyperref}
+			pdftitle={partisan}]{hyperref}
 
-\usepackage[resetlabels,labeled]{multibib}
-\newcites{SI}{SI References}
+%\newcites{SI}{SI References}
 \usepackage{natbib}
@@
 \usepackage{verbatim}
-\setcitestyle{round,semicolon,aysep={},yysep={;}}
+%\setcitestyle{round,semicolon,aysep={},yysep={;}}
 \usepackage{setspace} % Permits line spacing control. Options are:
@@
 %\onehalfspace
-\usepackage{sectsty}    % Permits control of section header styles
+%\usepackage{sectsty}    % Permits control of section header styles
 \usepackage{pdflscape}
@@
 
-\usepackage[T1]{fontenc}
-\usepackage[bitstream-charter]{mathdesign}
+%\usepackage[T1]{fontenc}
+%\usepackage[bitstream-charter]{mathdesign}
 
@@
 
-\title{\Large{Consumption of Pornography Online}\footnote{Data and scripts behind the analysis presented here can be downloaded at: \href{http://github.com/soodoku/porn}{http://github.com/soodoku/porn.}}}
+\title{\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}}
 
@@
 
-\date{\vspace{.5cm}\normalsize{\today}}
+\date{\today}
 
@@
 
-\begin{center}
-\vspace{.5cm}\textbf{NB:} Preliminary draft. Please do not cite without permission.\vspace{1.5cm}
-\end{center}
-
 \begin{comment}
 
-setwd(paste0(basedir, "adult/ms"))
+setwd("Documents/Github/adult/ms/")
 tools::texi2dvi("porn.tex", pdf=TRUE, clean=TRUE) 
@@
 \begin{abstract}
-\noindent Consumption of pornography has been blamed for a variety of societal ills, including, the rise in misogyny, sex crimes, and coarsening of the culture.
-Using passive browsing data from YouGov, we investigate how much pornography Americans consume online.
-We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography with most consuming small amounts.
-The median American Internet user today spends X\% of time-consuming pornography, visiting Y sites per month.
-Lastly, we find that, unlike previous research, relying on ecological inference, liberals consume slightly more pornography than conservatives \citep{macinnis2015american, edelman2009markets}.
+\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture.
+Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online.
+We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts.
+The median American Internet user today spends X minutes per month consuming pornography, visiting Y sites per month; the 95th percentile is X and Y respectively.
+Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume slightly more pornography than Republicans.
 \end{abstract} 
@@
 Consumption of pornography is associated with a variety of disturbing attitudes, beliefs, emotions, and behaviors.
-Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, greater gender role conflict and lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex, and having extramarital sex \citep{wright2012internet}.
+Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex, and having extramarital sex \citep{wright2012internet}.
 A lot of popular pornography also contains a healthy dose of violence.
-One analysis of popular pornography revealed that 88.2\% of the analyzed scenes contained physical aggression, and 48.7\% verbal aggression \citep{bridges2010aggression}.
-In all, there exist good reasons to be worried about rise in consumption of pornography.
+An analysis of popular pornography revealed that 88.2\% of the scenes contained physical aggression, and 48.7\% verbal aggression \citep{bridges2010aggression}.
+For all these reasons, there are serious concerns about consumption of pornography.
 
-In this paper, using passive browsing data from comScore and a YouGov sample, we investigate how much pornography do Americans consume online, how consumption of pornography online has changed over time, and shed light on who consumes pornography.
-We find that there is sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
-The median Internet user today spends X\% of time consuming pornography, and visits Y sites per year.
-Between 2002 and 2014, the consumption of pornography online has increased by between XX and YY\%.
-Lastly, we find that, unlike previous data, relying on ecological inference, liberals consume more pornography than conservatives \citep{macinnis2015american, edelman2009markets}.
+In this paper, using passive browsing data from YouGov, we investigate how much pornography Americans consume online.
+We find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
+The median American Internet user spends X minutes per month (Y\% of their time online) consuming pornography, visiting Y unique sites; the 95th percentile for time spent consuming pornography online is YY minutes.
 
-\citep{lykke2015widening}
-\citep{boik2016empirical}
+We also use the data to shed light on an age-old debate --- whether Democrats consume more pornography than Republicans or vice versa.
+Both parties claim the higher moral ground.
+And in surveys both parties think consumption of pornography is abhorrent, plausibly for different reasons.
+Unlike previous research, which relied on ecological inference, we find that Democrats consume slightly more pornography online than Republicans \citep{macinnis2015american, edelman2009markets}.
+Adjusting for background covariates like age, gender etc., further mutes the differences.
 
 \section*{Data}
-We exploit data from comScore and a YouGov survey to measure the consumption of adult content.
-
-comScore maintains a panel of around 100,000 households, offering small rewards in exchange for monitoring all Internet data from a machine.
-There are multiple notable biases in the sample.
-See \ref{si1_comscore} for comparison between demographics and population benchmarks on some key variables.
-
+We use passively observed browsing data from a YouGov survey to measure the consumption of adult content.
 YouGov maintains a large online panel recruited through a variety of methods.
@@
 For this particular sample, panelists also provided de-identified access to their web browsing activity via passive metering software installed voluntarily on their computers.
-The software, called Wakoopa, can be uninstalled at any point and captures visited web URLs independent of the type of browser or browser-specific privacy settings.\footnote{Wakoopa does not save passwords or financial transactions, and personally identifying information is screened out by the survey provider.} At the time this data was made available in March 2015, YouGov had recruited 1,392 individuals to the web tracking panel, which is currently marketed as YouGov Pulse.
-Our data comes from \citet{guess2016}.
-See \ref{si2_yougov} for a comparison between demographics and population benchmarks on some key variables.
-
+The software, called RealityMine, can be uninstalled at any point and captures visited web URLs independent of the type of browser or browser-specific privacy settings.\footnote{RealityMine does not save passwords or financial transactions, and personally identifying information is screened out by the survey provider.} At the time this data was made available in June, 2022, YouGov had recruited 1,200 individuals to the web tracking panel, which is currently marketed as YouGov Pulse.
 The passive metering component of this particular opt-in panel adds a layer of selectivity to the sampling process.
-Thus, to address concerns about the non-probability sampling procedure, we use raking weights to account for under- or overrepresentation along the following dimensions: age, gender, race, party identification, and region.
-We obtain population benchmark estimates from the U.S.
-Census (resident population, 2014) and proportions of party identifiers from Pew (2014).
-Raking takes into account the marginal, not the joint, distribution of the relevant demographic variables used to estimate the weights.
 
 \section*{Measuring Consumption of Adult Content}
-For both comScore and YouGov, we only observe data from a single machine per person.
+For YouGov, we only observe data from a single machine per person.
 Our analyses should hold if people exhibit similar consumption patterns across devices.
 If that is too implausible an assumption, then we must decide on the direction of error and how it affects our analyses.
-We think it is likely that people would be less likely to search for pornography from machines on which they have installed these passive monitoring software (though the data are de-identified).
+We think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified).
 If that is so, our estimates are a lower bound of net consumption of pornography per machine.
-As number of devices per person are increasing, all these numbers need to be adjusted.
+As the number of devices per person is increasing, all these numbers need to be adjusted.
 Next, is measurement error correlated with ideology?
@@
 We code pornographic content at the domain level.
-For both YouGov and comScore, we measure ideology using shallalist, DMOZ, and two machine learning classifiers.
-For YouGov data, we also present data based on classification from Wakoopa.
-
-Our first classifier is based on just the domain name and domain suffix.
-In particular, we use a calibrated keyword classifier.
-The features of the model are whether any of the following keywords are present in the domain name:
-
-\begin{quote}
-cumshot, dildo, anal, adult, porn, mature, sex, xx, bbw, slut, whore, tits, titty, titties, pussy, sperm, gay, cheat, booty, ebony, asian, brazilian, fuck, cock, cunt, lesbian, shemale, boob, naughty, fatty, bitch, granny, jizz, faggot, horny, bukakke, bdsm, vagina, smut, x-rated, lusty, erotic, cunnilingus, blowjob, panty, hentai, latex, fetisch, fetish, erotik, bondage, naked, strip, teen, stocking, coitus, deprav, tube, perverse
-\end{quote}
-
-For the 2004 comScore data, this gave about 140k domains that potentially carry pornographic content.
-We compare this list to the approximately 850k porn domains in the shallalist.
-This leaves us with a list of 68k domains with uncertain status.
-Use one of the many URL classification APIs.
-Using Trusted Source API, we get about 20k porn, and 48k non-porn.
-This gives us the lower bound of adult domains.
-
-To estimate the false positives, we take a large random sample of 10,000 unique domains and compare results from our classifier to results from a commercial API by McAfee.
-This serves are our estimate of the false positive rate.
-For comScore data, our false negative rate is 5\%.
-False positive rate is close to 0.
+Our main analysis depends on the domain classifications that come with YouGov data.
+In the Appendix, we use a keyword classifier and a machine learning classifier.
+As you will see, all of these methods consistently show the same thing.
 All of this ignores pornography available via more conventional channels.
-For instance, a large amount of pornography is consumed on sites like Tumblr.
-
-\subsection{Measuring Partisan Identification}
-With the YouGov survey, we measured ideology and partisanship using the conventional survey measures.
-In the comScore data, we do have data on partisan identification.
-We substitute with a validated model.
-We train our model on the YouGov data, predicting partisan identification using socio-demographics coded to match comScore (3-point party identification, gender, education, income, age, race, and ideology), and passively observed visits to site domains (excluding adult, rewards, and social networking sites).
-We aggregate the number of visits to each domain in the data by individual respondent, excluding domains with more than 100 visits total in the data.
-We estimate a cross-validated ridge (L2 penalized) regression with a total of 5,651 features.
-The model has a high degree of accuracy (92\%).
-%Interestingly, the features most predictive of Democratic partisan affiliation are not demographic variables but rather
+For instance, some pornography is consumed on sites like Tumblr.
 
@@
 
-\input{../tabs/models.tex}
+Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites. (In the appendix, we show similar analysis for visits.)
 
@@
 \centering
-\caption{Consumption of Pornography by Ideology}
-\includegraphics[scale=.75]{../figs/ideo_boxplot_shalla.pdf}
-\label{fig:summary}
+\caption{Distribution of Consumption of Pornography Online}
+\includegraphics[scale=.75]{figs/distribution_duration_on_adultsites.pdf}
+\label{fig:distribution_duration}
 \end{figure}
 
+\begin{figure}[h]
+\centering
+\caption{Proportion of Visits to Pornographic Sites}
+\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_duration.pdf}
+\label{fig:distribution_prop_duration}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\caption{Distribution of Consumption of Pornography Online by Party}
+\includegraphics[scale=.75]{figs/distribution_duration_on_adultsites_by_party.pdf}
+\label{fig:distribution_duration}
+\end{figure}
+
+These minor differences (or lack of differences) could be because of the demographic differences we see across the party.
+Next, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much.
+Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find.
+
+\input{tabs/models.tex}
+
 \section*{Discussion}
-
+Consumption of pornography is also problematic from a religious perspective.
+Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}.
 \clearpage
 \bibliographystyle{apsr}
-\bibliography{porn_bib}
+\bibliography{porn}
 \clearpage
@@
 \clearpage
-\section{Comparing YouGov Sample to Population Benchmarks}
-\label{si2_yougov}
+\section{Consequence of Using Alternate Ways of Measuring Pornography}
+\subsection{Keyword Classifier}
+Our first classifier is based on just the domain name and domain suffix.
+In particular, we use a calibrated keyword classifier.
+The features of the model are whether any of the following keywords are present in the domain name:
 
-\input{../tabs/app_table.tex}
+\begin{quote}
+
+cumshot, dildo, anal, adult, porn, mature, sex, xx, bbw, slut, whore, tits, titty, titties, pussy, sperm, gay, cheat, booty, ebony, asian, brazilian, fuck, cock, cunt, lesbian, shemale, boob, naughty, fatty, bitch, granny, jizz, faggot, horny, bukakke, bdsm, vagina, smut, x-rated, lusty, erotic, cunnilingus, blowjob, panty, hentai, latex, fetisch, fetish, erotik, bondage, naked, strip, teen, stocking, coitus, deprav, tube, perverse
+
+\end{quote}
+\subsection{Machine Learning Classifier}
+
+\section{Analysis of Visits}
+
+\begin{figure}[h]
+\centering
+\caption{Distribution of Consumption of Pornography Online}
+\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_visits.pdf}
+\label{fig:distribution_visits}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\caption{Proportion of Visits to Pornographic Sites}
+\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_visits_by_party.pdf}
+\label{fig:distribution_prop_visits}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\caption{Distribution of Consumption of Pornography Online by Party}
+\includegraphics[scale=.75]{figs/distribution_visits_to_adultsites_by_party.pdf}
+\label{fig:distribution_visits_party}
+\end{figure}
 

### 2022-12-16 ms/adult.tex
revise ms
Update ms

--- 2022-12-10 ms/porn.tex
@@
 \caption{Distribution of Consumption of Pornography Online}
-\includegraphics[scale=.75]{figs/distribution_duration_on_adultsites.pdf}
+\includegraphics[width=.55\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
+\caption*{\footnotesize \emph{Notes:} 
+	Hours spent on adult sites by individuals who consumed pornography in the sample period.
+	Individuals are split into deciles with each bin containing approximately the same number of individuals.
+	Height of bars indicate mean of each bin.
+	Capped vertical bars are 95\% confidence intervals.
+	See \cref{tab:distribution_duration} for the more tabulated values.
+}
 \label{fig:distribution_duration}
@@
 \caption{Proportion of Visits to Pornographic Sites}
-\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_duration.pdf}
+\includegraphics[scale=.75]{../figs/distribution_proportion_duration_on_adultsites.pdf}
 \label{fig:distribution_prop_duration}
@@
 \caption{Distribution of Consumption of Pornography Online by Party}
-\includegraphics[scale=.75]{figs/distribution_duration_on_adultsites_by_party.pdf}
-\label{fig:distribution_duration}
+\includegraphics[scale=.75]{../figs/distribution_duration_on_adultsites_by_party.pdf}
+\label{fig:distribution_duration_party}
+\end{figure}
+
+To formally test for these differences, we ran quantile regression, regressing the duration on party.
+
+\begin{figure}[h]
+\centering
+\caption{Distribution of Consumption of Pornography Online by Party}
+\includegraphics[scale=.75]{../figs/quantile_reg_nonzero_duration_adult.pdf}
+\label{fig:quantile_regression_duration}
 \end{figure}
@@
 
-\input{tabs/models.tex}
+\input{../tabs/models.tex}
 
@@
 
+\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+	\caption{Distribution of Consumption of Pornography Online}
+	\label{tab:distribution_duration}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
+			\toprule
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
+			\midrule
+			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		See \cref{fig:distribution_duration} for the plot.
+	}
+\end{table}
+
 \clearpage
+\section{Top 25 Adult Domains}
+
+\begin{figure}[h]
+\centering
+\caption{Proportion of Visits to Pornographic Sites}
+\includegraphics[scale=.75]{../figs/top_25_adultsites.pdf}
+\label{fig:top25}
+\end{figure}
+
 \section{Consequence of Using Alternate Ways of Measuring Pornography}
@@
 \caption{Distribution of Consumption of Pornography Online}
-\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_visits.pdf}
+\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits.pdf}
 \label{fig:distribution_visits}
@@
 \caption{Proportion of Visits to Pornographic Sites}
-\includegraphics[scale=.75]{figs/distribution_proportion_adultsites_visits_by_party.pdf}
+\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits_by_party.pdf}
 \label{fig:distribution_prop_visits}
@@
 \caption{Distribution of Consumption of Pornography Online by Party}
-\includegraphics[scale=.75]{figs/distribution_visits_to_adultsites_by_party.pdf}
+\includegraphics[scale=.75]{../figs/distribution_visits_to_adultsites_by_party.pdf}
 \label{fig:distribution_visits_party}

### 2022-12-17 ms/adult.tex
Update
Update top 25 sites
Minor formatting. Also added top 25 non-adult sites

@@
 \caption{Distribution of Consumption of Pornography Online}
-\includegraphics[width=.55\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
+\includegraphics[width=.5\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
 \caption*{\footnotesize \emph{Notes:} 
@@
 
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
 	\caption{Distribution of Consumption of Pornography Online}
@@
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
+			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex} \\
 			\bottomrule
@@
 	\centering
-\caption{Proportion of Visits to Pornographic Sites}
-\includegraphics[scale=.75]{../figs/top_25_adultsites.pdf}
-\label{fig:top25}
+	\caption{Top 25 Adult Domains}
+	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
+		\caption*{\footnotesize \emph{Notes:} 
+			Table shows the top 25 adult sites that panelists visit in the sample period.
+			Adult sites are categorized by YouGov.
+			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
+			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
+			Sites to the right of the vertical dashed are the top 1 percent.
+		}
+	\label{fig:top25_adult}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\caption{Top 25 (Non-Adult) Domains}
+	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
+		\caption*{\footnotesize \emph{Notes:} 
+			Table shows the top 25 non-adult sites that panelists visit in the sample period.
+			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
+			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
+			Sites to the right of the vertical dashed are the top 1 percent.
+		}
+	\label{fig:top25_nonadult}
 \end{figure}

### 2022-12-17 scripts/utils/data_utils.py
Update data utils
Add line to remove the annoying trailing // for TeX

@@ -9,6 +9,10 @@ def pandas_to_tex(df, texfile):
         
     tex_table = df.to_latex(index=False, header=False)
     tex_table_fragment = "\n".join(tex_table.split("\n")[2:-3])
+    # Remove the last \\ in the tex fragment to prevent the annoying
+    # "Misplaced \noalign" LaTeX error when I use \bottomrule
+    tex_table_fragment = tex_table_fragment[:-2]
+
     
     with open(texfile, "w") as tf:
         tf.write(tex_table_fragment)

### 2022-12-17 ms/adult.tex
Update ms
fixing formatting. Changing proportion to percentages

@@
 \usepackage{float}
+\usepackage{placeins}
 
@@
 We code pornographic content at the domain level.
-Our main analysis depends on the domain classifications that come with YouGov data.
+Our main analysis depends on the domain classifications that come with YouGov data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the most visited domains).
 In the Appendix, we use a keyword classifier and a machine learning classifier.
@@
 
+\FloatBarrier
 \section*{Results}
@@
 
-\begin{figure}[h]
+%======================================================
+% Figure for Distribution of Hours spent on adult sites
+%======================================================
+\begin{figure}[ht]
 \centering
@@
 \caption*{\footnotesize \emph{Notes:} 
-	Hours spent on adult sites by individuals who consumed pornography in the sample period.
+	Figure shows the number of hours spent on adult sites by individuals who consumed pornography in the sample period.
 	Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 
-\begin{figure}[h]
+%===================================================================
+% Figure for Distribution of proportion of time spent on adult sites
+%===================================================================
+\begin{figure}[ht]
 	\centering
-\caption{Proportion of Visits to Pornographic Sites}
-\includegraphics[scale=.75]{../figs/distribution_proportion_duration_on_adultsites.pdf}
+	\caption{Percentage of Time Spent on Pornographic Sites}
+	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_duration_on_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows the proportion of time spent on adult sites by individuals who consumed pornography in the sample period.
+		Individuals are split into deciles with each bin containing approximately the same number of individuals.
+		Height of bars indicate mean of each bin.
+		Capped vertical bars are 95\% confidence intervals.
+		See \cref{tab:distribution_prop_duration} for the more tabulated values.
+	}
 	\label{fig:distribution_prop_duration}
@@
 
-\begin{figure}[h]
+%===============================================
+% Splits by party for hours spent on adult sites
+%===============================================
+\begin{figure}[ht]
 	\centering
 	\caption{Distribution of Consumption of Pornography Online by Party}
-\includegraphics[scale=.75]{../figs/distribution_duration_on_adultsites_by_party.pdf}
+	\includegraphics[width=.6\linewidth]{../figs/distribution_duration_on_adultsites_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows splits by party and by percentiles for the total time spent on adult sites for panelists in the sample who consumed pornography in the sample period.
+		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
+		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		See \cref{tab:distribution_duration_party} for the more tabulated values.
+	}
 	\label{fig:distribution_duration_party}
 \end{figure}
+
+%============================================================
+% Splits by party for proportion of time spent on adult sites
+%============================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Percentage of Time Spent on Pornographic Sites by Party}
+	\includegraphics[width=.6\linewidth]{../figs/distribution_proportion_duration_on_adultsites_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows splits by party and by percentiles for the proportion of time spent on adult sites for panelists in the sample who consumed pornography in the sample period.
+		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
+		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		See \cref{tab:distribution_prop_duration_party} for the more tabulated values.
+	}
+	\label{fig:distribution_prop_duration_party}
+\end{figure}
+
+\newpage
 
@@
 \clearpage
+
+%===============================================================================
+%===============================================================================
+% Appendix
+%===============================================================================
+%===============================================================================
 \appendix
@@
 \counterwithin{table}{section}
-
 \begin{center}
@@
 
+%====================================================
+% Tabulated percentiles of hours spent on adult sites
+%====================================================
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
@@
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex} \\
+			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
 			\bottomrule
@@
 		See \cref{fig:distribution_duration} for the plot.
+	}
+\end{table}
+
+%=====================================================================
+% Tabulated percentiles of proportion of duration spent on adult sites
+%=====================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites}
+	\label{tab:distribution_prop_duration}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
+			\toprule
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
+			\midrule
+			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		See \cref{fig:distribution_prop_duration} for the plot.
+	}
+\end{table}
+
+%===========================================================================
+% Tabulated splits by party and by percentiles for hours spent on adultsites
+%===========================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Consumption of Pornography Online by Party}
+	\label{tab:distribution_duration_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
+			\toprule
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+			Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+See \cref{fig:distribution_duration_party} for the plot.
+	}
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
+%===============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party}
+	\label{tab:distribution_prop_duration_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
+			\toprule
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+See \cref{fig:distribution_prop_duration_party} for the plot.
 	}

### 2022-12-17 ms/adult.tex
Update
Added quantile results for duration and proportion duration. Also tidied up SI a little.

@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
-\caption{Distribution of Consumption of Pornography Online by Party}
-\includegraphics[scale=.75]{../figs/quantile_reg_nonzero_duration_adult.pdf}
+\caption{Quantile Estimates--Hours Spent on Adult Sites by Party}
+\includegraphics[width=.6\linewidth]{../figs/quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+}
 \label{fig:quantile_regression_duration}
 \end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party}
+	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:quantile_regression_prop_duration}
+\end{figure}
+
+\newpage
 
@@
 \end{center}
+
+\FloatBarrier
+%===============================================================================
+% Supplementary Descriptives for sense of landscape of porn consumption
+%===============================================================================
+\section{Supplementary Descriptive Figures and Tables}
+\begin{figure}[ht]
+	\centering
+	\caption{Top 25 Adult Domains}
+	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows the top 25 adult sites that panelists visit in the sample period.
+		Adult sites are categorized by YouGov.
+		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
+		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
+		Sites to the right of the vertical dashed are the top 1 percent.
+	}
+	\label{fig:top25_adult}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\caption{Top 25 (Non-Adult) Domains}
+	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows the top 25 non-adult sites that panelists visit in the sample period.
+		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
+		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
+		Sites to the right of the vertical dashed are the top 1 percent.
+	}
+	\label{fig:top25_nonadult}
+\end{figure}
 
@@
 
-\clearpage
-\section{Top 25 Adult Domains}
-
-\begin{figure}[h]
-	\centering
-	\caption{Top 25 Adult Domains}
-	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
-		\caption*{\footnotesize \emph{Notes:} 
-			Table shows the top 25 adult sites that panelists visit in the sample period.
-			Adult sites are categorized by YouGov.
-			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
-			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
-			Sites to the right of the vertical dashed are the top 1 percent.
-		}
-	\label{fig:top25_adult}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\caption{Top 25 (Non-Adult) Domains}
-	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
-		\caption*{\footnotesize \emph{Notes:} 
-			Table shows the top 25 non-adult sites that panelists visit in the sample period.
-			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
-			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
-			Sites to the right of the vertical dashed are the top 1 percent.
-		}
-	\label{fig:top25_nonadult}
-\end{figure}
-
-\section{Consequence of Using Alternate Ways of Measuring Pornography}
+\FloatBarrier
+%===============================================================================
+% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
+%===============================================================================
+\section{Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography}
 \subsection{Keyword Classifier}
@@
 
+\subsection{Alternative Analyses of Time Spent on Pornography}
+
+%=====================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (with covariates) 
+%=====================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
+	}
+	\label{fig:quantile_regression_duration_covariates}
+\end{figure}
+
+%==============================================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (for individuals who consumed pornography)
+%==============================================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_duration} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_duration_nonzeroes}
+\end{figure}
+
+%==============================================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
+%==============================================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_duration_covariates} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_duration_nonzeroes}
+\end{figure}
+
+%================================================================
+% Fig of quantile regression estimates
+% Percentage Time Spent on Adult Sites by Party (with covariates) 
+%================================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
+	}
+	\label{fig:quantile_regression_prop_duration_covariates}
+\end{figure}
+
+%==============================================================================
+% Fig of quantile regression estimates
+% Percentage Time Spent on Adult Sites by Party (for individuals who consumed pornography)
+%==============================================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_duration} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_prop_duration_nonzeroes}
+\end{figure}
+
+%==============================================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
+%==============================================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_duration_nonzeroes_covariates}
+\end{figure}
+\FloatBarrier
+%===============================================================================
+% Analogous results for visits to adult sites
+%===============================================================================
 \section{Analysis of Visits}
 
-\begin{figure}[h]
-\centering
-\caption{Distribution of Consumption of Pornography Online}
-\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits.pdf}
-\label{fig:distribution_visits}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\caption{Proportion of Visits to Pornographic Sites}
-\includegraphics[scale=.75]{../figs/distribution_proportion_adultsites_visits_by_party.pdf}
-\label{fig:distribution_prop_visits}
-\end{figure}
-
-\begin{figure}[h]
-\centering
-\caption{Distribution of Consumption of Pornography Online by Party}
-\includegraphics[scale=.75]{../figs/distribution_visits_to_adultsites_by_party.pdf}
-\label{fig:distribution_visits_party}
-\end{figure}
-
 \end{document}

### 2022-12-17 ms/adult.tex
Fix multiply-defined fig labels
Add barplot for tendency to consume porn
Add barplot for tendency to consume porn, split by party.

@@
 
+%===========================
+% Quantile regressions
+% Hours spent on adult sites
+%===========================
 \begin{figure}[ht]
@@
 
+%========================================
+% Quantile regressions
+% Proportion of time spent on adult sites
+%========================================
 \begin{figure}[ht]
@@
 These minor differences (or lack of differences) could be because of the demographic differences we see across the party.
+This lack of difference also partly stems from a lack of difference in the tendency to consume pornography (see \cref{fig:consume_porn_yes_no}).
 Next, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much.
@@
 	\label{fig:top25_nonadult}
+\end{figure}
+
+%===============================================================================
+\begin{figure}
+	\centering
+	\caption{Porn Consumption by Party}
+	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows proportion of panelists in the sample who ever consumed pornography in the sample period by party.
+		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
+	}
+	\label{fig:consume_porn_yes_no}
 \end{figure}
@@
 	}
-	\label{fig:quantile_regression_duration_nonzeroes}
+	\label{fig:quantile_regression_duration_nonzeroes_covariates}
 \end{figure}
@@
 	}
-	\label{fig:quantile_regression_duration_nonzeroes_covariates}
+	\label{fig:quantile_regression_prop_duration_nonzeroes_covariates}
 \end{figure}

### 2022-12-17 ms/adult.tex
Update
Minor update to push all current local changes

@@
 We code pornographic content at the domain level.
-Our main analysis depends on the domain classifications that come with YouGov data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the most visited domains).
+Our main analysis depends on the domain classifications that come with YouGov data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains).
 In the Appendix, we use a keyword classifier and a machine learning classifier.
@@
 %===============================================================================
-\section{Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography}
+\section{Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses}
 \subsection{Keyword Classifier}
@@
 %===============================================================================
-\section{Analysis of Visits}
+\section{Analyses of Visits}
 

### 2022-12-18 ms/adult.tex
Add concentration of porn consumption
Some figures to show that certain adult sites get the most traffic and that most individuals' porn consumption is heavily concentrated on a single adult site.
Update ms
Add figures and some writeup for concentration of porn consumption.

@@
 
+The consumption of pornography is concentrated.
+Traffic to the top 10 most frequented porn sites ten times that of traffic to all other porn sites outside the top 10 (approximately 120 minutes vs 12 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}).
+For panelists who consume porn, close to 80 percent of their traffic to adult sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}).
+This behavior does not differ substantially party.
+
 \FloatBarrier
@@
 
-\input{../tabs/models.tex}
-
 \section*{Discussion}
@@
 \section{Supplementary Descriptive Figures and Tables}
+%============================
+% Figure of top 25 adultsites
+%============================
 \begin{figure}[ht]
@@
 
+%================================
+% Figure of top 25 non-adultsites
+%================================
 \begin{figure}
@@
 
-%===============================================================================
+%=============================================
+% Figure for concentration of porn consumption
+%=============================================
+\begin{figure}
+	\centering
+	\caption{Traffic to Top 10 Porn Sites}
+	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
+		Time units is hours.
+		Data is at the panelist-domain level.
+		Others indicate traffic to all other adult sites outside of the top 10.
+		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
+	}
+	\label{fig:concentration_porn_consumption}
+\end{figure}
+
+%======================================================
+% Figure for concentration of porn consumption by party
+%======================================================
+\begin{figure}
+	\centering
+	\caption{Traffic to Top 10 Porn Sites by Party}
+	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
+		Time units is hours.
+		Data is at the panelist-domain level.
+		Others indicate traffic to all other adult sites outside of the top 10.
+		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
+	}
+	\label{fig:concentration_porn_consumption_by_party}
+\end{figure}
+
+%====================================
+% Figure of traffic to top x websites
+%====================================
+\begin{figure}
+	\centering
+	\caption{Traffic to Top x Porn Sites by Party}
+	\includegraphics[width=.7\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
+		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
+	}
+	\label{fig:concentration_porn_consumption_topX_by_party}
+\end{figure}
+
+%============================================================================
+% Figure of porn consumption by party
+% Y-axis = proportion of individuals that ever consumed porn in sample period
+%============================================================================
 \begin{figure}

### 2022-12-20 ms/adult.tex
Update quantile regressions
Updating quantile regressions using the new data removing obvious false positives of porn sites.

@@
 The consumption of pornography is concentrated.
-Traffic to the top 10 most frequented porn sites ten times that of traffic to all other porn sites outside the top 10 (approximately 120 minutes vs 12 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}).
+Traffic to the top 10 most frequented porn sites more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}).
 For panelists who consume porn, close to 80 percent of their traffic to adult sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}).

### 2022-12-20 ms/adult.tex
Update data writeup + visits results

@@
 
+Overall, we have over 6 million web browsing records by the 1,200 individuals over the one-month period of June 2022. 
+For each web browsing activity, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
+Individuals are spread out over the US states and regions (see \cref{fig:map_duration}).
+Our data also comes with characteristics for the 1,200 individuals.
+We have information on their party identification, which we use to code their partisanship.
+We verify this using information on whether they voted for the Republican or Democratic candidate in the 2020 presidential election.
+Most individuals reported their party identification, with 120 individuals who did not respond or say not sure/don't know.
+Out of the 1,080 individuals who report party identification, the majority 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.
+In the analyses focusing on splits by party, we use only those who lean either Republican or Democrat.
+We also have information on birth year, gender, race, and education level.
+\cref{tab:characteristics_split_by_party} shows differences in gender, and race(?) by party. 
+Hence, our analyses below for differences in porn consumption includes these characteristics in the estimation.
+
 \section*{Measuring Consumption of Adult Content}
@@
 We code pornographic content at the domain level. 
-Our main analysis depends on the domain classifications that come with YouGov data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains).
+Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as porn sites. 
+These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). 
+A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.
+See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains.
+Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites.
+For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We manually check the top adult domains in our sample to remove obvious false positives.
+Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}
 In the Appendix, we use a keyword classifier and a machine learning classifier.
@@
 	\caption{Traffic to Top 10 Porn Sites}
-	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption.pdf}
+	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\caption{Traffic to Top x Porn Sites by Party}
-	\includegraphics[width=.7\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
+	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
+		\begin{tabular}{cr}
 			\toprule
@@
 	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
+		\begin{tabular}{crr}
 			\toprule
@@
 \FloatBarrier
+
+%===============================================================================
 %===============================================================================
@@
 %===============================================================================
+%===============================================================================
 \section{Analyses of Visits}
+%=================================================
+% Figure for Distribution of visits to adult sites
+%=================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Distribution of Traffic to Pornography Online}
+	\includegraphics[width=.5\linewidth]{../figs/distribution_visits_to_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows the number of visits to adult sites by individuals who consumed pornography in the sample period.
+		Individuals are split into deciles with each bin containing approximately the same number of individuals.
+		Height of bars indicate mean of each bin.
+		Capped vertical bars are 95\% confidence intervals.
+		See \cref{tab:distribution_visits} for the more tabulated values.
+	}
+	\label{fig:distribution_visits}
+\end{figure}
+
+%===============================================================
+% Figure for Distribution of proportion of visits to adult sites
+%===============================================================
+\begin{figure}
+	\centering
+	\caption{Percentage of Traffic to Pornography Online}
+	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_visits_to_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows the proportion of visits to adult sites by individuals who consumed pornography in the sample period.
+		Individuals are split into deciles with each bin containing approximately the same number of individuals.
+		Height of bars indicate mean of each bin.
+		Capped vertical bars are 95\% confidence intervals.
+		See \cref{tab:distribution_prop_visits} for the more tabulated values.
+	}
+	\label{fig:distribution_prop_visits}
+\end{figure}
+
+%==========================================
+% Splits by party for visits to adult sites
+%==========================================
+\begin{figure}
+	\centering
+	\caption{Distribution of Traffic to Pornography Online by Party}
+	\includegraphics[width=.55\linewidth]{../figs/distribution_visits_to_adultsites_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows splits by party and by percentiles for visits to adult sites for panelists in the sample who consumed pornography in the sample period.
+		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
+		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		See \cref{tab:distribution_visits_party} for the more tabulated values.
+	}
+	\label{fig:distribution_visits_party}
+\end{figure}
+
+%========================================================
+% Splits by party for proportion of visits to adult sites
+%========================================================
+\begin{figure}
+	\centering
+	\caption{Percentage of Traffic to Pornographic Sites by Party}
+	\includegraphics[width=.55\linewidth]{../figs/distribution_proportion_visits_to_adultsites_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows splits by party and by percentiles for visits to adult sites for panelists in the sample who consumed pornography in the sample period.
+		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
+		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		See \cref{tab:distribution_prop_visits_party} for the more tabulated values.
+	}
+	\label{fig:distribution_prop_visits_party}
+\end{figure}
+
+%===============================================
+% Tabulated percentiles of visits to adult sites
+%===============================================
+\begin{table} \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Traffic to Pornography Online}
+	\label{tab:distribution_visits}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{cr}
+			\toprule
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
+			\midrule
+			\input{../tabs/percentiles_visits_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period.
+		See \cref{fig:distribution_visits} for the plot.
+	}
+\end{table}
+
+%=============================================================
+% Tabulated percentiles of proportion of visits to adult sites
+%=============================================================
+\begin{table} \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Traffic to Pornographic Sites}
+	\label{tab:distribution_prop_visits}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{cr}
+			\toprule
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
+			\midrule
+			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period.
+		See \cref{fig:distribution_prop_visits} for the plot.
+	}
+\end{table}
+
+%======================================================================
+% Tabulated splits by party and by percentiles for visits to adultsites
+%======================================================================
+\begin{table} \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Traffic to Pornography Online by Party}
+	\label{tab:distribution_visits_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/percentiles_visits_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period.
+See \cref{fig:distribution_visits_party} for the plot.
+	}
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
+%===============================================================================
+\begin{table} \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Traffic to Pornographic Sites by Party}
+	\label{tab:distribution_prop_visits_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
+			\toprule
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period.
+See \cref{fig:distribution_prop_visits_party} for the plot.
+	}
+\end{table}
+
+%=======================
+% Quantile regressions
+% Traffic to adult sites
+%=======================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Traffic to Adult Sites by Party}
+	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of visits to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_visits_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:quantile_regression_visits}
+\end{figure}
+
+%=====================================
+% Quantile regressions
+% Proportion of traffic to adult sites
+%=====================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party}
+	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:quantile_regression_prop_visits}
+\end{figure}
+
+%==================================================
+% Fig of quantile regression estimates
+% Traffic to Adult Sites by Party (with covariates) 
+%==================================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Traffic to Porn Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of visits to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_visits} for the same plot without covariates.
+	}
+	\label{fig:quantile_regression_visits_covariates}
+\end{figure}
+
+%===========================================================================
+% Fig of quantile regression estimates
+% Traffic to Adult Sites by Party (for individuals who consumed pornography)
+%===========================================================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of visits to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_visits} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_visits_nonzeroes}
+\end{figure}
+
+%==============================================================================
+% Fig of quantile regression estimates
+% Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
+%==============================================================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography and with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of visits to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_visits_covariates} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_visits_nonzeroes_covariates}
+\end{figure}
+
+%=============================================================
+% Fig of quantile regression estimates
+% Percentage Traffic to Adult Sites by Party (with covariates) 
+%=============================================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_visits} for the same plot without covariates.
+	}
+	\label{fig:quantile_regression_prop_visits_covariates}
+\end{figure}
+
+%==============================================================================
+% Fig of quantile regression estimates
+% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography)
+%==============================================================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (for individuals who consumed pornography)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_visits} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_prop_visits_nonzeroes}
+\end{figure}
+
+%==============================================================================
+% Fig of quantile regression estimates
+% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
+%==============================================================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes panelists who consumed pornography in the sample period.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from robust standard errors.
+		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot for the full sample.
+	}
+	\label{fig:quantile_regression_prop_visits_nonzeroes_covariates}
+\end{figure}
 

### 2022-12-20 scripts/utils/data_utils.py
Table for differences by party
Add table for splits by party for key porn consumption measures and individual characteristics.

@@ -3,7 +3,7 @@ import pandas as pd
 import statsmodels.api as sm
 import statsmodels.formula.api as smf
 
-def pandas_to_tex(df, texfile):
+def pandas_to_tex(df, texfile, index=False):
     if texfile.split(".")[-1] != ".tex":
         texfile += ".tex"
         

### 2022-12-21 ms/adult.tex
Add tables for splits by party and porn consumption
Add tables of means and differences in means for splits by party and porn consumption for measurs of porn consumption and individual characteristics.

@@
 
+%==============================================================================
+% Table for balance of porn consumption and individual characteristics by party
+%==============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+	\caption{Differences in Porn Consumption and Individual Characteristics by Party}
+	\label{tab:characteristics_split_by_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
+			\toprule
+			&\multicolumn{7}{c}{\underline{Panel A. Measures of porn consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{../tabs/balance_outcomes_by_party.tex}\\
+			%-------------------------------------------------------------------
+			\cmidrule{2-8}
+			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{../tabs/balance_covariates_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:}
+		Table shows splits by party for porn consumption and for individual characteristics for the 1,200 individuals.
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) shows subgroups for categorical variables.
+		Column (2) indicates the count of missing variables, if any.
+		Columns (3)--(5) show mean and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
+		Standard deviations and percentages in parentheses.
+		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
+	}
+\end{table}
+
+%==============================================================================
+% Table for balance of porn consumption and individual characteristics by party
+%==============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+	\caption{Differences in Porn Consumption and Individual Characteristics by Porn Consumers}
+	\label{tab:characteristics_split_by_porn_consumers}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
+			\toprule
+			&\multicolumn{7}{c}{\underline{Panel A. Measures of porn consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
+			%-------------------------------------------------------------------
+			\cmidrule{2-8}
+			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:}
+		Table shows splits by consumers of porn for porn consumption and for individual characteristics for the 1,200 individuals.
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) shows subgroups for categorical variables.
+		Column (2) indicates the count of missing variables, if any.
+		Columns (3)--(5) show mean and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of porn, and consumers of porn.
+		Standard deviations and percentages in parentheses.
+		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
+	}
+\end{table}
+
 \FloatBarrier

### 2022-12-21 scripts/utils/data_utils.py

@@ -1,23 +1,40 @@
-
 import pandas as pd
 import statsmodels.api as sm
 import statsmodels.formula.api as smf
 
+
 def pandas_to_tex(df, texfile, index=False):
     if texfile.split(".")[-1] != ".tex":
         texfile += ".tex"
-        
-    tex_table = df.to_latex(index=False, header=False)
+
+    tex_table = df.to_latex(index=index, header=False)
     tex_table_fragment = "\n".join(tex_table.split("\n")[2:-3])
     # Remove the last \\ in the tex fragment to prevent the annoying
     # "Misplaced \noalign" LaTeX error when I use \bottomrule
     tex_table_fragment = tex_table_fragment[:-2]
 
-    
     with open(texfile, "w") as tf:
         tf.write(tex_table_fragment)
     return None
 
+
+def tableone_to_texfrag(tableone, texfile):
+    tex_table = tableone.tabulate(tablefmt="latex")
+    # line #1 = \begin{tabular}...
+    # line #2 = headers..
+    # line #3 = \hline
+    # last line = \end{tabular}
+    # 2nd last line = \hline
+    tex_table_fragment = "\n".join(tex_table.split("\n")[4:-2])
+    # Remove the last \\ in the tex fragment to prevent the annoying
+    # "Misplaced \noalign" LaTeX error when I use \bottomrule
+    tex_table_fragment = tex_table_fragment[:-2]
+    # Save
+    if texfile.split(".")[-1] != ".tex":
+        texfile += ".tex"
+    with open(texfile, "w") as tf:
+        tf.write(tex_table_fragment)
+    return None
 
 
 def fit_quantile_reg(y, x, quantile, df, z=None):
@@ -39,7 +56,6 @@ def fit_quantile_reg(y, x, quantile, df, z=None):
     return coef_list
 
 
-
 def fit_ols_reg(y, x, df, z=None):
     if z is None:
         ols_model = smf.ols(f"{y} ~ {x}", df)
@@ -55,6 +71,5 @@ def fit_ols_reg(y, x, df, z=None):
         tstat=ols_results.tvalues[x],
         pval=ols_results.pvalues[x],
         obs=ols_results.nobs,
-
     )
-    return ols_results    
+    return ols_results

### 2022-12-21 ms/adult.tex
Minor update

@@
 		Table shows the top 25 adult sites that panelists visit in the sample period.
-		Adult sites are categorized by YouGov.
+		Adult sites are categorized by YouGov (see \textbf{subsection xx} discussion).
 		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
 		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
-		Sites to the right of the vertical dashed are the top 1 percent.
+		Sites to the right of the vertical dashed are the top 1 percent of porn sites.
 	}
@@
 	\centering
-	\caption{Top 25 (Non-Adult) Domains}
+	\caption{Top 25 (Non-Porn) Domains}
 	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
@@
 		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
-		Sites to the right of the vertical dashed are the top 1 percent.
+		Sites to the right of the vertical dashed are the top 1 percent (of non-porn sites).
 	}
@@
 		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
+		The Others bar indicates traffic to all other adult sites outside of the top 10.
+		The y-axis is the total time spent on porn sites, averaged across individuals.
 		Time units is hours.
-		Data is at the panelist-domain level.
-		Others indicate traffic to all other adult sites outside of the top 10.
 		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).

### 2022-12-21 ms/adult.tex
Add map porn
Add map of party identification and porn consumtpion by US states.

@@
 For each web browsing activity, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
-Individuals are spread out over the US states and regions (see \cref{fig:map_duration}).
+Individuals are spread out over the US states and regions (see \cref{fig:map_porn}).
 Our data also comes with characteristics for the 1,200 individuals.
@@
 We also have information on birth year, gender, race, and education level.
-\cref{tab:characteristics_split_by_party} shows differences in gender, and race(?) by party. 
+\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.
+Republicans in the sample are, on average, older, less likely to be female, and much more likely to be White.
 Hence, our analyses below for differences in porn consumption includes these characteristics in the estimation.
@@
 
+%============================================================================
+% Map of party identification
+%============================================================================
+\begin{figure}
+	\centering
+	\caption{Party Identification by States}
+	\begin{subfigure}[t]{0.7\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../figs/map_pid7.pdf}
+		\caption{Partisanship}
+	\end{subfigure}
+	\caption*{\footnotesize \emph{Notes:} 
+		Redder colors indicate stronger identification to the Republican party.
+		Bluer colors indicate stronger identification to the Democratic party.
+		North Dakota and Vermont have no data (shaded out).
+	}
+	\label{fig:map_pid7}
+\end{figure}
+
+\begin{figure}[t]
+	\caption{Porn Consumption by State}
+	\label{fig:map_porn}
+	\centering
+	\begin{subfigure}[t]{0.8\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../figs/map_visits.pdf}
+		\caption{Percentage of visits to porn sites}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.8\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{../figs/map_duration.pdf}
+		\caption{Percentage of duration on porn sites}
+	\end{subfigure}
+	\caption*{\footnotesize \emph{Notes:} 
+		Darker shades indicate higher values.
+		Values for each state are percentage of visits to and time spent on porn sites averaged across individuals of the states.
+		Baseline values are for all web browsing activity.
+		North Dakota and Vermont have no data (shaded out).}
+\end{figure}
+
 \FloatBarrier

### 2022-12-21 scripts/utils/utils.py

@@ -27,3 +27,194 @@ def fit_exp(x , y, w=None):
 def save_mpl_fig(savepath):
     plt.savefig(f"{savepath}.pdf", dpi=None, bbox_inches="tight", pad_inches=0)
     plt.savefig(f"{savepath}.png", dpi=120, bbox_inches="tight", pad_inches=0)
+
+
+def annotate_states_on_map(gdf_states):
+    ANNOT_SIZE = 21
+    for statecode, lat, long in zip(
+        gdf_states["STUSPS"], gdf_states["centroid"].x, gdf_states["centroid"].y
+    ):
+        if statecode == "RI":
+            plt.annotate(
+                statecode,
+                xy=(lat, long),
+                fontweight="bold",
+                size=ANNOT_SIZE,
+                xytext=(lat + 2.5, long),
+                arrowprops=dict(arrowstyle="->", lw=0.5),
+            )
+        elif statecode == "DE":
+            plt.annotate(
+                statecode,
+                xy=(lat, long),
+                fontweight="bold",
+                size=ANNOT_SIZE,
+                xytext=(lat + 2.5, long),
+                arrowprops=dict(arrowstyle="->", lw=0.5),
+            )
+        elif statecode == "MD":
+            plt.annotate(
+                statecode,
+                xy=(lat, long),
+                fontweight="bold",
+                size=ANNOT_SIZE,
+                xytext=(lat + 2.5, long - 1),
+                arrowprops=dict(arrowstyle="->", lw=0.5),
+            )
+        elif statecode == "DC":
+            plt.annotate(
+                statecode,
+                xy=(lat, long),
+                fontweight="bold",
+                size=ANNOT_SIZE,
+                xytext=(lat + 2.5, long - 2),
+                arrowprops=dict(arrowstyle="->", lw=0.5),
+            )
+        elif statecode == "FL":
+            plt.annotate(
+                statecode,
+                xy=(lat, long),
+                fontweight="bold",
+                size=ANNOT_SIZE,
+                xytext=(lat + 0.1, long - 0.5),
+            )
+        elif statecode == "LA":
+            plt.annotate(
+                statecode,
+                xy=(lat, long),
+                fontweight="bold",
+                size=ANNOT_SIZE,
+                xytext=(lat - 1.5, long),
+            )
+        elif statecode == "CA":
+            plt.annotate(
+                statecode,
[…]

### 2022-12-21 ms/adult.tex
'Adult sites' --> 'Porn sites'
Fixing terms from 'adult sites' to 'porn sites' in the ms.

@@
 
-\section*{Data}
+\section*{Data}\label{sec:data}
 We use passively observed browsing data from a YouGov survey to measure the consumption of adult content.
@@
 
-\section*{Measuring Consumption of Adult Content}
+\section*{Measuring Consumption of Porn Online}
 For YouGov, we only observe data from a single machine per person.
@@
 Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites.
-For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We manually check the top adult domains in our sample to remove obvious false positives.
+For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We manually check the top adult domains in our sample to remove obvious false positives of porn sites.
 Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}
@@
 Traffic to the top 10 most frequented porn sites more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}).
-For panelists who consume porn, close to 80 percent of their traffic to adult sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}).
+For individuals who consume porn, close to 80 percent of their traffic to porn sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}).
 This behavior does not differ substantially party.
@@
 \caption*{\footnotesize \emph{Notes:} 
-	Figure shows the number of hours spent on adult sites by individuals who consumed pornography in the sample period.
+	Figure shows the number of hours spent on porn sites by individuals who consumed pornography in the sample period.
 	Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of time spent on adult sites by individuals who consumed pornography in the sample period.
+		Figure shows the proportion of time spent on porn sites by individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for the total time spent on adult sites for panelists in the sample who consumed pornography in the sample period.
+		Figure shows splits by party and by percentiles for the total time spent on porn sites for panelists in the sample who consumed pornography in the sample period.
 		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for the proportion of time spent on adult sites for panelists in the sample who consumed pornography in the sample period.
+		Figure shows splits by party and by percentiles for the proportion of time spent on porn sites for panelists in the sample who consumed pornography in the sample period.
 		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
@@
 \centering
-\caption{Quantile Estimates--Hours Spent on Adult Sites by Party}
+\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
 \includegraphics[width=.6\linewidth]{../figs/quantile_reg_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Dependent variable is the number of hours panelists in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party}
+	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party}
 	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Dependent variable is the percentage of time panelists in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Top 25 Adult Domains}
+	\caption{Top 25 Porn Sites}
 	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 adult sites that panelists visit in the sample period.
-		Adult sites are categorized by YouGov (see \textbf{subsection xx} discussion).
+		Table shows the top 25 porn sites that panelists visit in the sample period.
+		Porn sites are as categorized by YouGov (see the \nameref{sec:data} section).
 		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 non-adult sites that panelists visit in the sample period.
+		Table shows the top 25 non-porn sites that individuals visit in the sample period.
 		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The Top 10 bar indicates traffic to the top 10 adult sites in the data (see \cref{fig:top25_adult}).
-		The Others bar indicates traffic to all other adult sites outside of the top 10.
+		The Top 10 bar indicates traffic to the top 10 porn sites in the data (see \cref{fig:top25_adult}).
+		The Others bar indicates traffic to all other porn sites outside of the top 10.
 		The y-axis is the total time spent on porn sites, averaged across individuals.
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (with covariates)}
+	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Dependent variable is the number of hours panelists in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography)}
+	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (for individuals who consumed pornography)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Dependent variable is the number of hours panelists in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
+	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (for individuals who consumed pornography and with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours panelists in our sample spent on adult sites.
+		Dependent variable is the number of hours panelists in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (with covariates)}
+	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Dependent variable is the percentage of time panelists in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography)}
+	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (for individuals who consumed pornography)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)}
+	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (for individuals who consumed pornography and with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time panelists in our sample spent on adult sites.
+		Dependent variable is the percentage of time panelists in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the number of visits to adult sites by individuals who consumed pornography in the sample period.
+		Figure shows the number of visits to porn sites by individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of visits to adult sites by individuals who consumed pornography in the sample period.
+		Figure shows the proportion of visits to porn sites by individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for visits to adult sites for panelists in the sample who consumed pornography in the sample period.
+		Figure shows splits by party and by percentiles for visits to porn sites for panelists in the sample who consumed pornography in the sample period.
 		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
@@
 	\centering
-	\caption{Quantile Estimates--Traffic to Adult Sites by Party}
+	\caption{Quantile Estimates--Traffic to Porn Sites by Party}
 	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party}
+	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party}
 	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (with covariates)}
+	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (for individuals who consumed pornography)}
+	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (for individuals who consumed pornography)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_visits_adult.pdf}
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)}
+	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (for individuals who consumed pornography and with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_visits_adult.pdf}

### 2022-12-21 scripts/utils/utils.py

@@ -164,7 +164,10 @@ def annotate_states_on_map(gdf_states):
     return None    
 
 import cmasher as cmr
-from mapclassify import Quantiles
+try:
+    from mapclassify import Quantiles
+except ModuleNotFoundError:
+    pass
 import matplotlib as mpl
 
 def plot_map(y, gdf):

### 2022-12-21 ms/adult.tex
Add difference in medians
Add difference in medians for porn consumption by party. Currently Table SI 1.7.

@@
 		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show mean and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
+		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
 		Standard deviations and percentages in parentheses.
 		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
+		Given the skew in porn consumption, we also performed tests for difference in means medians for the measures of porn consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
 	}
@@
 		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show mean and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of porn, and consumers of porn.
+		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of porn, and consumers of porn.
 		Standard deviations and percentages in parentheses.
 		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
+	}
+\end{table}
+
+%==============================================================================
+% Table for balance of porn consumption and individual characteristics by party
+% Difference in medians
+%==============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+	\caption{Differences (in Medians) in Porn Consumption and Individual Characteristics by Party}
+	\label{tab:characteristics_split_by_party_medians}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
+			\toprule
+			&\multicolumn{7}{c}{\underline{Measures of porn consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:}
+		Table shows splits by party for porn consumption and for individual characteristics for the 1,200 individuals.
+		This table focuses on differences in medians.
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) shows subgroups for categorical variables.
+		Column (2) indicates the count of missing variables, if any.
+		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles, for the full sample, Democrats, and Republicans.
+		Standard deviations and percentages in parentheses.
+		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
 	}

### 2022-12-22 ms/adult.tex
Add difference in medians
Add difference in medians for porn consumption by party. Currently Table SI 1.7.
'Panelists' --> 'Individuals'
Fixing terms from 'panelists' to 'individuals' in the ms.

@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for the total time spent on porn sites for panelists in the sample who consumed pornography in the sample period.
+		Figure shows splits by party and by percentiles for the total time spent on porn sites for individuals in the sample who consumed pornography in the sample period.
 		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		The \emph{x} symbols indicate actual individuals based on their percentiles.
 		See \cref{tab:distribution_duration_party} for the more tabulated values.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for the proportion of time spent on porn sites for panelists in the sample who consumed pornography in the sample period.
+		Figure shows splits by party and by percentiles for the proportion of time spent on porn sites for individuals in the sample who consumed pornography in the sample period.
 		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		The \emph{x} symbols indicate actual individuals based on their percentiles.
 		See \cref{tab:distribution_prop_duration_party} for the more tabulated values.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours panelists in our sample spent on porn sites.
+		Dependent variable is the number of hours individuals in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time panelists in our sample spent on porn sites.
+		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 porn sites that panelists visit in the sample period.
+		Table shows the top 25 porn sites that individuals visit in the sample period.
 		Porn sites are as categorized by YouGov (see the \nameref{sec:data} section).
-		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
+		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
+		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
 		Sites to the right of the vertical dashed are the top 1 percent of porn sites.
@@
 		Table shows the top 25 non-porn sites that individuals visit in the sample period.
-		The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
+		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
+		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
 		Sites to the right of the vertical dashed are the top 1 percent (of non-porn sites).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows proportion of panelists in the sample who ever consumed pornography in the sample period by party.
+		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
 		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
 		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles, for the full sample, Democrats, and Republicans.
-		Standard deviations and percentages in parentheses.
-		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
+		1st and 3rd quartiles in brackets.
+		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
+		See \cref{tab:characteristics_split_by_party} for differences in means.
 	}
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours panelists in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Dependent variable is the number of hours individuals in our sample spent on porn sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes individuals who consumed pornography in the sample period.
 		95\% confidence intervals constructed from robust standard errors.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours panelists in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Dependent variable is the number of hours individuals in our sample spent on porn sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes individuals who consumed pornography in the sample period.
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Only includes individuals who consumed pornography in the sample period.
 		95\% confidence intervals constructed from robust standard errors.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time panelists in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes individuals who consumed pornography in the sample period.
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for visits to porn sites for panelists in the sample who consumed pornography in the sample period.
+		Figure shows splits by party and by percentiles for visits to porn sites for individuals in the sample who consumed pornography in the sample period.
 		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		The \emph{x} symbols indicate actual individuals based on their percentiles.
 		See \cref{tab:distribution_visits_party} for the more tabulated values.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for visits to porn sites for panelists in the sample who consumed pornography in the sample period.
+		Figure shows splits by party and by percentiles for visits to porn sites for individuals in the sample who consumed pornography in the sample period.
 		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual panelists based on their percentiles.
+		The \emph{x} symbols indicate actual individuals based on their percentiles.
 		See \cref{tab:distribution_prop_visits_party} for the more tabulated values.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to porn sites by panelists in our sample.
+		Dependent variable is the number of visits to porn sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
+		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to porn sites by panelists in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Dependent variable is the number of visits to porn sites by individuals in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes individuals who consumed pornography in the sample period.
 		95\% confidence intervals constructed from robust standard errors.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to porn sites by panelists in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Dependent variable is the number of visits to porn sites by individuals in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes individuals who consumed pornography in the sample period.
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes individuals who consumed pornography in the sample period.
 		95\% confidence intervals constructed from robust standard errors.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to porn sites by panelists in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes panelists who consumed pornography in the sample period.
+		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Only includes individuals who consumed pornography in the sample period.
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).

### 2022-12-30 ms/adult.tex
Update ms
- Fix Figures SI 1.3/1.4 figure notes to 'average time spent on pornographic sites'.

- Fix headers in the percentiles/distributions tables.

- Removed Figure SI 1.7 - map of pid7 across states.
Update Figure SI 1.6
Remove independents from graph
Report numbers from Table SI 1.6 in main text
Report numbers from Table SI SI 1.6 (and similar tables) in the main text. Reporting key differences in consumers and non-consumers of porn online. Key differences are age and gender---consumers are younger and more likely to be male.

@@
 We have information on their party identification, which we use to code their partisanship.
-We verify this using information on whether they voted for the Republican or Democratic candidate in the 2020 presidential election.
+We verify this using information on whether they voted for the Republican or Democratic candidate in the 2020 presidential election (see \cref{tab:characteristics_split_by_party}).
 Most individuals reported their party identification, with 120 individuals who did not respond or say not sure/don't know.
@@
 \cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.
-Republicans in the sample are, on average, older, less likely to be female, and much more likely to be White.
-Hence, our analyses below for differences in porn consumption includes these characteristics in the estimation.
+We use these information in our analyses of pornography consumption below.
+
+In supplementary analyses, we leverage the \texttt{piedomains} package to classify which domains are pornographic sites using \textbf{what goes under-the-hood here}.
+We show that our results do not change using the alternative classifiers..\footnote{We also supplement our analyses using other open-source packages like }
 
@@
 For individuals who consume porn, close to 80 percent of their traffic to porn sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}). 
+The next most frequented pornographic site constitutes less than 20 percent of total traffic.
 This behavior does not differ substantially party.
 
+The majority of individuals do not consume pornography online. 
+On average, approximately 32 percent of individuals consumed pornography online---these are individuals who consumed visited any pornography site in the sample period.
+In \cref{fig:consume_porn_yes_no}, splitting by party does not reveal any substantial differences.
+We confirm this in \cref{tab:characteristics_split_by_porn_consumers}, which reports differences in characteristics between individuals who do and do not consume pornography online.
+The average consumer of pornography online spends about approximately 230 minutes (standard deviation of 576 minutes), which is 10.6 percent of total browsing activity (standard deviation of 17.9 percent).
+These come from 233 visits to pornographic sites (standard deviation of 550), which is 6.9 percent of visits to all sites (standard deviation of 11.2 percent).
+
+Based on individual characteristics, the key differences between consumers and non-consumers of pornography online is age and gender. 
+Consumers of pornography online are younger and are more likely to be male.
+In addition to splits by pornography consumption, these differences can also be observed in the splits by party.
+\cref{tab:characteristics_split_by_party} reports that individuals identifying as Republicans tend to be older and more likely to be male, in addition to some differences by regions in which they reside.
+In the regression analyses (\textbf{?in SI or main text?}) where we estimate whether pornography consumption differs by party, we account for these individual characteristics.
+
 \FloatBarrier
-\section*{Results}
+\section*{Regression Estimates for Porn Consumption by Party}
 
@@
 			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
 			\midrule
@@
 			\toprule
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
 			\midrule
@@
 			\toprule
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
 			\midrule
@@
 		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in porn consumption, we also performed tests for difference in means medians for the measures of porn consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
+		Given the skew in porn consumption, we also performed tests for difference in means for the measures of porn consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
 	}
@@
 		Table shows splits by consumers of porn for porn consumption and for individual characteristics for the 1,200 individuals.
+		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
+		These 65 individuals are not substantially different in characteristics than those included in the sample (see \textbf{TABLE ??}).
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences (in Medians) in Porn Consumption and Individual Characteristics by Party}
+	\caption{Differences (in Medians) in Porn Consumption}
 	\label{tab:characteristics_split_by_party_medians}
@@
 		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
-		See \cref{tab:characteristics_split_by_party} for differences in means.
+		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
 	}
@@
 %============================================================================
-% Map of party identification
+% Map of porn consumption (visits and duration)
 %============================================================================
-\begin{figure}
-	\centering
-	\caption{Party Identification by States}
-	\begin{subfigure}[t]{0.7\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../figs/map_pid7.pdf}
-		\caption{Partisanship}
-	\end{subfigure}
-	\caption*{\footnotesize \emph{Notes:} 
-		Redder colors indicate stronger identification to the Republican party.
-		Bluer colors indicate stronger identification to the Democratic party.
-		North Dakota and Vermont have no data (shaded out).
-	}
-	\label{fig:map_pid7}
-\end{figure}
-
 \begin{figure}[t]
@@
 			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Visits}}\\
 			\midrule
@@
 			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% visits}}\\
 			\midrule
@@
 			\toprule
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Visits}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\			
 			\midrule
@@
 			\toprule
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% visits}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\	
 			\midrule

### 2023-01-02 ms/adult.tex
revised ms

--- 2022-12-22 ms/adult.tex
@@
 			citecolor={bluish},
-			pdftitle={partisan}]{hyperref}
+			pdftitle={partisan adult}]{hyperref}
 
@@
 
-\title{\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}}
+\title{\Large{Holier Than Thou?
+No Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}}
 
@@
 
-setwd("Documents/Github/adult/ms/")
-tools::texi2dvi("porn.tex", pdf=TRUE, clean=TRUE) 
-setwd(basedir)
+setwd("~/Documents/Github/adult/ms/")
+tools::texi2dvi("adult.tex", pdf=TRUE, clean=TRUE)
 
@@
 The median American Internet user today spends X minutes per month consuming pornography, visiting Y sites per month; the 95th percentile is X and Y respectively.
-Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume slightly more pornography than Republicans.
+Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume about as much pornography online as Republicans.
 \end{abstract} 
@@
 
-In this paper, using passive browsing data from YouGov, we investigate how much pornography Americans consume online.
-We find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
+In this paper, we investigate how much pornography Americans consume online.
+Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
 The median American Internet user spends X minutes per month (Y\% of their time online) consuming pornography, visiting Y unique sites; the 95th percentile for time spent consuming pornography online is YY minutes.
@@
 And in surveys both parties think consumption of pornography is abhorrent, plausibly for different reasons.
-Unlike previous research, which relied on ecological inference, we find that Democrats consume slightly more pornography online than Republicans \citep{macinnis2015american, edelman2009markets}.
-Adjusting for background covariates like age, gender etc., further mutes the differences.
+Unlike previous research, which relied on ecological inference, we find that Democrats consume about as much pornography online as Republicans \citep{macinnis2015american, edelman2009markets}.
+Adjusting for background attributes like age, gender etc., makes little difference.
 
@@
 For this particular sample, panelists also provided de-identified access to their web browsing activity via passive metering software installed voluntarily on their computers.
-The software, called RealityMine, can be uninstalled at any point and captures visited web URLs independent of the type of browser or browser-specific privacy settings.\footnote{RealityMine does not save passwords or financial transactions, and personally identifying information is screened out by the survey provider.} At the time this data was made available in June, 2022, YouGov had recruited 1,200 individuals to the web tracking panel, which is currently marketed as YouGov Pulse.
-The passive metering component of this particular opt-in panel adds a layer of selectivity to the sampling process.
+The software, called RealityMine, captures visited web URLs independent of the type of browser or browser-specific privacy settings.
 
-Overall, we have over 6 million web browsing records by the 1,200 individuals over the one-month period of June 2022. 
-For each web browsing activity, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
-Individuals are spread out over the US states and regions (see \cref{fig:map_porn}).
+The data are from 1,200 respondents and contains a month of data from June, 2022.
+We have data on visits to domains, which are about 6 million in total.
+For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
+
 Our data also comes with characteristics for the 1,200 individuals.
-We have information on their party identification, which we use to code their partisanship.
-We verify this using information on whether they voted for the Republican or Democratic candidate in the 2020 presidential election.
-Most individuals reported their party identification, with 120 individuals who did not respond or say not sure/don't know.
-Out of the 1,080 individuals who report party identification, the majority 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.
-In the analyses focusing on splits by party, we use only those who lean either Republican or Democrat.
-We also have information on birth year, gender, race, and education level.
-\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.
-Republicans in the sample are, on average, older, less likely to be female, and much more likely to be White.
-Hence, our analyses below for differences in porn consumption includes these characteristics in the estimation.
+We have data on demographic characterists like birth year, state, gender, race, and education level.
+We also have information on their party identification.
+Except for 120 respondents  who did not respond or picked not sure/don't know, the rest stated the party they identified with.
+Of the 1,080 individuals who report party identification, 82 percent lean either Republican or Democrat.
+The remaining 18 percent identify as independent.
 
-\section*{Measuring Consumption of Porn Online}
-For YouGov, we only observe data from a single machine per person.
-Our analyses should hold if people exhibit similar consumption patterns across devices.
-If that is too implausible an assumption, then we must decide on the direction of error and how it affects our analyses.
-We think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified).
-If that is so, our estimates are a lower bound of net consumption of pornography per machine.
-As the number of devices per person is increasing, all these numbers need to be adjusted.
-Next, is measurement error correlated with ideology?
-We have little reason to expect that, but we have no capacity to check if it is true.
-Thus, for current purposes, we assume that it is so.
-
+\section*{Measuring Pornographic Content}
 We code pornographic content at the domain level.
-Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as porn sites. 
+Our main analysis depends on the domain classifications that come with YouGov data.
+We code domains that YouGov categorizes as ``Adult'' as porn sites.
 These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com).
-A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.
-See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains.
+A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains.
 Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites.
@@
 Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}
-In the Appendix, we use a keyword classifier and a machine learning classifier.
-As you will see, all of these methods consistently show the same thing.
-All of this ignores pornography available via more conventional channels.
-For instance, some pornography is consumed on sites like Tumblr.
 
-The consumption of pornography is concentrated.
-Traffic to the top 10 most frequented porn sites more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}).
-For individuals who consume porn, close to 80 percent of their traffic to porn sites is concentrated in just one porn site (\cref{fig:concentration_porn_consumption_topX_by_party}).
-This behavior does not differ substantially party.
+In \ref{si:alternate_ways}, we leverage the \texttt{piedomains} package to classify which domains are pornographic sites using machine learning \citep{Chintalapati_piedomains_Predict_the_2022}.
+We leverage the probability estimates to produce a low false negative and low false positive version.
+The key results remain unchanged.
 
-\FloatBarrier
-\section*{Results}
+\section{Results}
 
-Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites. (In the appendix, we show similar analysis for visits.)
+\subsection{Consumption of Pornography}
+The consumption of pornography is highly concentrated.
+Traffic to the top 10 most frequented porn sites is more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}).
+Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site (\cref{fig:concentration_porn_consumption}).
+The next most frequented pornographic site constitutes less than 20 percent of total traffic.
 
-%======================================================
-% Figure for Distribution of Hours spent on adult sites
-%======================================================
-\begin{figure}[ht]
-\centering
-\caption{Distribution of Consumption of Pornography Online}
-\includegraphics[width=.5\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
-\caption*{\footnotesize \emph{Notes:} 
-	Figure shows the number of hours spent on porn sites by individuals who consumed pornography in the sample period.
-	Individuals are split into deciles with each bin containing approximately the same number of individuals.
-	Height of bars indicate mean of each bin.
-	Capped vertical bars are 95\% confidence intervals.
-	See \cref{tab:distribution_duration} for the more tabulated values.
-}
-\label{fig:distribution_duration}
-\end{figure}
+The consumption of pornography online is also limited to a minority of respondents.
+Only about 32 percent of the respondents visited at least one pornography online during the sample period.
+The average consumer of pornography online spends approximately 230 minutes (standard deviation of 576 minutes), which is 10.6 percent of total browsing activity (standard deviation of 17.9 percent).
+These come from 233 visits to pornographic sites (standard deviation of 550), which is 6.9 percent of visits to all sites (standard deviation of 11.2 percent).
 
-%===================================================================
-% Figure for Distribution of proportion of time spent on adult sites
-%===================================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Percentage of Time Spent on Pornographic Sites}
-	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_duration_on_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of time spent on porn sites by individuals who consumed pornography in the sample period.
-		Individuals are split into deciles with each bin containing approximately the same number of individuals.
-		Height of bars indicate mean of each bin.
-		Capped vertical bars are 95\% confidence intervals.
-		See \cref{tab:distribution_prop_duration} for the more tabulated values.
-	}
-	\label{fig:distribution_prop_duration}
-\end{figure}
+The key differences between consumers and non-consumers of pornography online are age and gender. Consumers of pornography online are younger and are more likely to be male.
 
-%===============================================
-% Splits by party for hours spent on adult sites
-%===============================================
-\begin{figure}[ht]
-	\centering
-	\caption{Distribution of Consumption of Pornography Online by Party}
-	\includegraphics[width=.6\linewidth]{../figs/distribution_duration_on_adultsites_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for the total time spent on porn sites for individuals in the sample who consumed pornography in the sample period.
-		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual individuals based on their percentiles.
-		See \cref{tab:distribution_duration_party} for the more tabulated values.
-	}
-	\label{fig:distribution_duration_party}
-\end{figure}
+\subsection{Partisan Differences in Consumption of Pornography Online}
 
-%============================================================
-% Splits by party for proportion of time spent on adult sites
-%============================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Percentage of Time Spent on Pornographic Sites by Party}
-	\includegraphics[width=.6\linewidth]{../figs/distribution_proportion_duration_on_adultsites_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for the proportion of time spent on porn sites for individuals in the sample who consumed pornography in the sample period.
-		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual individuals based on their percentiles.
-		See \cref{tab:distribution_prop_duration_party} for the more tabulated values.
-	}
-	\label{fig:distribution_prop_duration_party}
-\end{figure}
+Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+(In \ref{si:visits}, we show similar analysis for visits.)
 
-\newpage
-
-To formally test for these differences, we ran quantile regression, regressing the duration on party.
+Given the skew in the data, we ran a quantile regression, regressing the duration on party.
+As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties.
+To account for the possibility that these non-differences may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much.
+Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.
 
@@
 
-\newpage
+\section*{Discussion}
 
-These minor differences (or lack of differences) could be because of the demographic differences we see across the party.
-This lack of difference also partly stems from a lack of difference in the tendency to consume pornography (see \cref{fig:consume_porn_yes_no}).
-Next, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much.
-Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find.
+Consumption of pornography has been attributed to a variety of ills.
+It is also considered problematic from a religious perspective.
+Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}.
+The Internet has dramatically increased access to pornography.
+This leads to the concern that pornography consumption has become very widespread.
+Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornograpghy and most people consuming very little.
 
-\section*{Discussion}
-Consumption of pornography is also problematic from a religious perspective.
-Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}.
+The second contribution of our paper is estimates of partisan differences in consumption of pornography online.
+Both the parties claim the higher ground when it comes to women--- one's case for morality is steeped in religion, the other's in enduring concern for women.
+Our data suggest that the partisan differences are likely very small.
+
+Our research has two major limitations.
+The first concern with our data is that we may not have data from all the machines that the respondent uses to visit online.
+If the respondent changes their behavior in response to the knowledge that their data is being collected (even if it is de-identified), for e.g., they may modify their behavior on the machine or figure out ways to evade detection, it may bias our results.
+In fact, we think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified).
+If that is so, our estimates are a lower bound of net consumption of pornography per machine.
+If this bias varies by party, our estimates of partisan differences will also be biased.
+
+The second concern with our measurement is that we code content at a domain level.
+This runs the risk of incurring some ecological fallacy.
+For instance, our classification would code websites like Tumblr as not carrying pornographic content but some of Tumblr content is pornographic.
+
 \clearpage
@@
 %===============================================================================
-\section{Supplementary Descriptive Figures and Tables}
+\section{Descriptive Analysis}
+
+\subsection{Skew in Website Visits}
 %============================
@@
 		Table shows the top 25 porn sites that individuals visit in the sample period.
-		Porn sites are as categorized by YouGov (see the \nameref{sec:data} section).
+		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
 		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 non-porn sites that individuals visit in the sample period.
+		Table shows the top 25 non-pornographic sites that individuals visit in the sample period.
 		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
@@
 	\centering
-	\caption{Traffic to Top 10 Porn Sites}
+	\caption{Traffic to Top 10 Pornographic Sites}
 	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		The Top 10 bar indicates traffic to the top 10 porn sites in the data (see \cref{fig:top25_adult}).
-		The Others bar indicates traffic to all other porn sites outside of the top 10.
-		The y-axis is the total time spent on porn sites, averaged across individuals.
+		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
+		The Others bar indicates traffic to all other pornographic sites outside of the top 10.
+		The y-axis is the total time spent on pornographic sites, averaged across individuals.
 		Time units is hours.
@@
 
-%======================================================
-% Figure for concentration of porn consumption by party
-%======================================================
-\begin{figure}
-	\centering
-	\caption{Traffic to Top 10 Porn Sites by Party}
-	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		The Top 10 bar indicates traffic to the top 10 porn sites in the data (see \cref{fig:top25_adult}).
-		The Others bar indicates traffic to all other porn sites outside of the top 10.
-		The y-axis is the total time spent on porn sites, averaged across individuals.
-		Time units is hours.
-		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:concentration_porn_consumption_by_party}
-\end{figure}
-
-%====================================
-% Figure of traffic to top x websites
-%====================================
-\begin{figure}
-	\centering
-	\caption{Traffic to Top x Porn Sites by Party}
-	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
-		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:concentration_porn_consumption_topX_by_party}
-\end{figure}
-
-%============================================================================
-% Figure of porn consumption by party
-% Y-axis = proportion of individuals that ever consumed porn in sample period
-%============================================================================
-\begin{figure}
-	\centering
-	\caption{Porn Consumption by Party}
-	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
-		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:consume_porn_yes_no}
-\end{figure}
+\subsection{Skew in Consumption of Pornographic Content}
 
@@
 
+\section{Partisan Differences}
+\subsection{Distribution of Differences}
 %===========================================================================
@@
 
+\subsection{Accounting for Confounders}
+
 %==============================================================================
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences in Porn Consumption and Individual Characteristics by Party}
+	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
 	\label{tab:characteristics_split_by_party}
@@
 			\toprule
-			&\multicolumn{7}{c}{\underline{Panel A. Measures of porn consumption}}\\
+			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
 			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for porn consumption and for individual characteristics for the 1,200 individuals.
+		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in porn consumption, we also performed tests for difference in means medians for the measures of porn consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
+		Given the skew in consumption of pornography, we also performed tests for difference in means for the measures of pornography consumption by party.
+See \cref{tab:characteristics_split_by_party_medians}.
 	}
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences in Porn Consumption and Individual Characteristics by Porn Consumers}
+	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
 	\label{tab:characteristics_split_by_porn_consumers}
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by consumers of porn for porn consumption and for individual characteristics for the 1,200 individuals.
+		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
+		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
+		These 65 individuals are not substantially different in characteristics than those included in the sample (see \textbf{TABLE ??}).
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of porn, and consumers of porn.
+		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
 		Standard deviations and percentages in parentheses.
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences (in Medians) in Porn Consumption and Individual Characteristics by Party}
+	\caption{Differences (in Medians) in Pornography Consumption}
 	\label{tab:characteristics_split_by_party_medians}
@@
 			\toprule
-			&\multicolumn{7}{c}{\underline{Measures of porn consumption}}\\
+			&\multicolumn{7}{c}{\underline{Measures of pornography consumption}}\\
 			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for porn consumption and for individual characteristics for the 1,200 individuals.
+		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
 		This table focuses on differences in medians.
@@
 		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
-		See \cref{tab:characteristics_split_by_party} for differences in means.
+		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
 	}
 \end{table}
-
-%============================================================================
-% Map of party identification
-%============================================================================
-\begin{figure}
-	\centering
-	\caption{Party Identification by States}
-	\begin{subfigure}[t]{0.7\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../figs/map_pid7.pdf}
-		\caption{Partisanship}
-	\end{subfigure}
-	\caption*{\footnotesize \emph{Notes:} 
-		Redder colors indicate stronger identification to the Republican party.
-		Bluer colors indicate stronger identification to the Democratic party.
-		North Dakota and Vermont have no data (shaded out).
-	}
-	\label{fig:map_pid7}
-\end{figure}
-
-\begin{figure}[t]
-	\caption{Porn Consumption by State}
-	\label{fig:map_porn}
-	\centering
-	\begin{subfigure}[t]{0.8\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../figs/map_visits.pdf}
-		\caption{Percentage of visits to porn sites}
-	\end{subfigure}
-	\begin{subfigure}[t]{0.8\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{../figs/map_duration.pdf}
-		\caption{Percentage of duration on porn sites}
-	\end{subfigure}
-	\caption*{\footnotesize \emph{Notes:} 
-		Darker shades indicate higher values.
-		Values for each state are percentage of visits to and time spent on porn sites averaged across individuals of the states.
-		Baseline values are for all web browsing activity.
-		North Dakota and Vermont have no data (shaded out).}
-\end{figure}
-
-\FloatBarrier
-%===============================================================================
-% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
-%===============================================================================
-\section{Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses}
-\subsection{Keyword Classifier}
-Our first classifier is based on just the domain name and domain suffix.
-In particular, we use a calibrated keyword classifier.
-The features of the model are whether any of the following keywords are present in the domain name:
-
-\begin{quote}
-
-cumshot, dildo, anal, adult, porn, mature, sex, xx, bbw, slut, whore, tits, titty, titties, pussy, sperm, gay, cheat, booty, ebony, asian, brazilian, fuck, cock, cunt, lesbian, shemale, boob, naughty, fatty, bitch, granny, jizz, faggot, horny, bukakke, bdsm, vagina, smut, x-rated, lusty, erotic, cunnilingus, blowjob, panty, hentai, latex, fetisch, fetish, erotik, bondage, naked, strip, teen, stocking, coitus, deprav, tube, perverse
-
-\end{quote}
-\subsection{Machine Learning Classifier}
-
-\subsection{Alternative Analyses of Time Spent on Pornography}
-
 %=====================================================
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (with covariates)}
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on porn sites.
+		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 
-%==============================================================================
-% Fig of quantile regression estimates
-% Time Spent on Adult Sites by Party (for individuals who consumed pornography)
-%==============================================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (for individuals who consumed pornography)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_duration} for the same plot for the full sample.
-	}
-	\label{fig:quantile_regression_duration_nonzeroes}
-\end{figure}
-
-%==============================================================================
-% Fig of quantile regression estimates
-% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
-%==============================================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (for individuals who consumed pornography and with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_duration_covariates} for the same plot for the full sample.
-	}
-	\label{fig:quantile_regression_duration_nonzeroes_covariates}
-\end{figure}
-
 %================================================================
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (with covariates)}
+	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
+		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 \end{figure}
+\clearpage
+%===============================================================================
+% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
+%===============================================================================
+\section{Alternate Ways of Measuring Pornography}
+\label{si:alternate_ways}
+\clearpage
 
-%==============================================================================
-% Fig of quantile regression estimates
-% Percentage Time Spent on Adult Sites by Party (for individuals who consumed pornography)
-%==============================================================================
-\begin{figure}[ht]
+\section{Consumption of Pornography Among Independents}
+
+\section{Alternate Measures}
+%============================================================================
+% Figure of porn consumption by party
+% Y-axis = proportion of individuals that ever consumed porn in sample period
+%============================================================================
+
+\subsection{Proportion of Partisans Who Consumed Any Pornography}
+\begin{figure}
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (for individuals who consumed pornography)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_duration_adult.pdf}
+	\caption{Pornography Consumption by Party}
+	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_prop_duration} for the same plot for the full sample.
+		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
+		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
 	}
-	\label{fig:quantile_regression_prop_duration_nonzeroes}
+	\label{fig:consume_porn_yes_no}
 \end{figure}
-
-%==============================================================================
-% Fig of quantile regression estimates
-% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
-%==============================================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (for individuals who consumed pornography and with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
-	}
-	\label{fig:quantile_regression_prop_duration_nonzeroes_covariates}
-\end{figure}
-\FloatBarrier
-
+\clearpage
 %===============================================================================
@@
 %===============================================================================
-\section{Analyses of Visits}
+\subsection{Analyses of Visits}
+\label{si:visits}
 %=================================================
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the number of visits to porn sites by individuals who consumed pornography in the sample period.
+		Figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of visits to porn sites by individuals who consumed pornography in the sample period.
+		Figure shows the proportion of visits to pornography sites by individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 
-%==========================================
-% Splits by party for visits to adult sites
-%==========================================
-\begin{figure}
-	\centering
-	\caption{Distribution of Traffic to Pornography Online by Party}
-	\includegraphics[width=.55\linewidth]{../figs/distribution_visits_to_adultsites_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for visits to porn sites for individuals in the sample who consumed pornography in the sample period.
-		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual individuals based on their percentiles.
-		See \cref{tab:distribution_visits_party} for the more tabulated values.
-	}
-	\label{fig:distribution_visits_party}
-\end{figure}
-
-%========================================================
-% Splits by party for proportion of visits to adult sites
-%========================================================
-\begin{figure}
-	\centering
-	\caption{Percentage of Traffic to Pornographic Sites by Party}
-	\includegraphics[width=.55\linewidth]{../figs/distribution_proportion_visits_to_adultsites_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows splits by party and by percentiles for visits to porn sites for individuals in the sample who consumed pornography in the sample period.
-		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
-		The \emph{x} symbols indicate actual individuals based on their percentiles.
-		See \cref{tab:distribution_prop_visits_party} for the more tabulated values.
-	}
-	\label{fig:distribution_prop_visits_party}
-\end{figure}
-
-%===============================================
-% Tabulated percentiles of visits to adult sites
-%===============================================
-\begin{table} \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Traffic to Pornography Online}
-	\label{tab:distribution_visits}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{cr}
-			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
-			\midrule
-			\input{../tabs/percentiles_visits_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period.
-		See \cref{fig:distribution_visits} for the plot.
-	}
-\end{table}
-
-%=============================================================
-% Tabulated percentiles of proportion of visits to adult sites
-%=============================================================
-\begin{table} \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Traffic to Pornographic Sites}
-	\label{tab:distribution_prop_visits}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{cr}
-			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
-			\midrule
-			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period.
-		See \cref{fig:distribution_prop_visits} for the plot.
-	}
-\end{table}
-
-%======================================================================
-% Tabulated splits by party and by percentiles for visits to adultsites
-%======================================================================
-\begin{table} \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Traffic to Pornography Online by Party}
-	\label{tab:distribution_visits_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_visits_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period.
-See \cref{fig:distribution_visits_party} for the plot.
-	}
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
-%===============================================================================
-\begin{table} \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Traffic to Pornographic Sites by Party}
-	\label{tab:distribution_prop_visits_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
-			\toprule
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{r}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period.
-See \cref{fig:distribution_prop_visits_party} for the plot.
-	}
-\end{table}
-
 %=======================
@@
 	\centering
-	\caption{Quantile Estimates--Traffic to Porn Sites by Party}
+	\caption{Quantile Estimates--Traffic to Pornography Sites by Party}
 	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to porn sites by individuals in our sample.
+		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party}
+	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party}
 	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
+		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Traffic to Porn Sites by Party (with covariates)}
+	\caption{Quantile Estimates--Traffic to Pornographic Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_visits_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to porn sites by individuals in our sample.
+		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 
-%===========================================================================
-% Fig of quantile regression estimates
-% Traffic to Adult Sites by Party (for individuals who consumed pornography)
-%===========================================================================
-\begin{figure}
-	\centering
-	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to porn sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_visits} for the same plot for the full sample.
-	}
-	\label{fig:quantile_regression_visits_nonzeroes}
-\end{figure}
-
-%==============================================================================
-% Fig of quantile regression estimates
-% Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
-%==============================================================================
-\begin{figure}
-	\centering
-	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography and with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to porn sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_visits_covariates} for the same plot for the full sample.
-	}
-	\label{fig:quantile_regression_visits_nonzeroes_covariates}
-\end{figure}
-
 %=============================================================
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (with covariates)}
+	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
+		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 
-%==============================================================================
-% Fig of quantile regression estimates
-% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography)
-%==============================================================================
-\begin{figure}
-	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (for individuals who consumed pornography)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_prop_visits} for the same plot for the full sample.
-	}
-	\label{fig:quantile_regression_prop_visits_nonzeroes}
-\end{figure}
-
-%==============================================================================
-% Fig of quantile regression estimates
-% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
-%==============================================================================
-\begin{figure}
-	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (for individuals who consumed pornography and with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Only includes individuals who consumed pornography in the sample period.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot for the full sample.
-	}
-	\label{fig:quantile_regression_prop_visits_nonzeroes_covariates}
-\end{figure}
-
 \end{document}

### 2023-01-04 ms/adult.tex
Updates from Overleaf

@@
 \title{\Large{Holier Than Thou?
-No Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}}
+No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}}
 
@@
 
-\section{Results}
+\section*{Results}
 
-\subsection{Consumption of Pornography}
+\subsection*{Consumption of Pornography}
 The consumption of pornography is highly concentrated.
@@
 
-\subsection{Partisan Differences in Consumption of Pornography Online}
+\subsection*{Partisan Differences in Consumption of Pornography Online}
 
@@
 To account for the possibility that these non-differences may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much.
+\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.
+We use these variables in our analyses of pornography consumption below.
 Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.
@@
 This leads to the concern that pornography consumption has become very widespread.
-Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornograpghy and most people consuming very little.
+Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little.
 

### 2023-01-04 ms/scrap_yard.tex
Updates from Overleaf

%% given sample size, probably misleading so I propose scraping it for now

%============================================================================
% Map of porn consumption (visits and duration)
%============================================================================
\begin{figure}[t]
	\caption{Porn Consumption by State}
	\label{fig:map_porn}
	\centering
	\begin{subfigure}[t]{0.8\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../figs/map_visits.pdf}
		\caption{Percentage of visits to porn sites}
	\end{subfigure}
	\begin{subfigure}[t]{0.8\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../figs/map_duration.pdf}
		\caption{Percentage of duration on porn sites}
	\end{subfigure}
	\caption*{\footnotesize \emph{Notes:} 
		Darker shades indicate higher values.
		Values for each state are percentage of visits to and time spent on porn sites averaged across individuals of the states.
		Baseline values are for all web browsing activity.
		North Dakota and Vermont have no data (shaded out).}
\end{figure}

\FloatBarrier

%% i didn't get the point of this so removing it for now

%======================================================
% Figure for concentration of porn consumption by party
%======================================================
\begin{figure}
	\centering
	\caption{Traffic to Top 10 Porn Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The Top 10 bar indicates traffic to the top 10 porn sites in the data (see \cref{fig:top25_adult}).
		The Others bar indicates traffic to all other porn sites outside of the top 10.
		The y-axis is the total time spent on porn sites, averaged across individuals.
		Time units is hours.
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_by_party}
\end{figure}

%======================================================
% Figure for Distribution of Hours spent on adult sites
%======================================================
\begin{figure}[ht]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[width=.5\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
\caption*{\footnotesize \emph{Notes:} 
	Figure shows the number of hours spent on pornographic sites by individuals who consumed pornography in the sample period.
	Individuals are split into deciles with each bin containing approximately the same number of individuals.
	Height of bars indicate mean of each bin.
	Capped vertical bars are 95\% confidence intervals.
	See \cref{tab:distribution_duration} for the more tabulated values.
}
\label{fig:distribution_duration}
\end{figure}

%===================================================================
% Figure for Distribution of proportion of time spent on adult sites
%===================================================================
\begin{figure}[ht]
	\centering
	\caption{Percentage of Time Spent on Pornographic Sites}
	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_duration_on_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows the proportion of time spent on pornographic sites by individuals who consumed pornography in the sample period.
		Individuals are split into deciles with each bin containing approximately the same number of individuals.
		Height of bars indicate mean of each bin.
		Capped vertical bars are 95\% confidence intervals.
		See \cref{tab:distribution_prop_duration} for the more tabulated values.
	}
	\label{fig:distribution_prop_duration}
\end{figure}

%===============================================
% Splits by party for hours spent on adult sites
%===============================================
\begin{figure}[ht]
	\centering
	\caption{Distribution of Consumption of Pornography Online by Party}
	\includegraphics[width=.6\linewidth]{../figs/distribution_duration_on_adultsites_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows splits by party and by percentiles for the total time spent on porn sites for individuals in the sample who consumed pornography in the sample period.
		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
		The \emph{x} symbols indicate actual individuals based on their percentiles.
		See \cref{tab:distribution_duration_party} for the more tabulated values.
	}
	\label{fig:distribution_duration_party}
\end{figure}

%============================================================
% Splits by party for proportion of time spent on adult sites
%============================================================
\begin{figure}[ht]
	\centering
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\includegraphics[width=.6\linewidth]{../figs/distribution_proportion_duration_on_adultsites_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows splits by party and by percentiles for the proportion of time spent on porn sites for individuals in the sample who consumed pornography in the sample period.
		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
		The \emph{x} symbols indicate actual individuals based on their percentiles.
		See \cref{tab:distribution_prop_duration_party} for the more tabulated values.
	}
	\label{fig:distribution_prop_duration_party}
\end{figure}

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Porn Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_duration_nonzeroes_covariates}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (for individuals who consumed pornography)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_duration_nonzeroes}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}[ht]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_duration_nonzeroes_covariates}
\end{figure}
\FloatBarrier

%==========================================
% Splits by party for visits to adult sites
%==========================================
\begin{figure}
	\centering
	\caption{Distribution of Traffic to Pornography Online by Party}
	\includegraphics[width=.55\linewidth]{../figs/distribution_visits_to_adultsites_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows splits by party and by percentiles for visits to porn sites for individuals in the sample who consumed pornography in the sample period.
		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
		The \emph{x} symbols indicate actual individuals based on their percentiles.
		See \cref{tab:distribution_visits_party} for the more tabulated values.
	}
	\label{fig:distribution_visits_party}
\end{figure}

%========================================================
% Splits by party for proportion of visits to adult sites
%========================================================
\begin{figure}
	\centering
	\caption{Percentage of Traffic to Pornographic Sites by Party}
	\includegraphics[width=.55\linewidth]{../figs/distribution_proportion_visits_to_adultsites_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows splits by party and by percentiles for visits to porn sites for individuals in the sample who consumed pornography in the sample period.
		Round markers and the corresponding vertical lines indicate the mean and 95\% confidence intervals for each bin.
		The \emph{x} symbols indicate actual individuals based on their percentiles.
		See \cref{tab:distribution_prop_visits_party} for the more tabulated values.
	}
	\label{fig:distribution_prop_visits_party}
\end{figure}

%===============================================
% Tabulated percentiles of visits to adult sites
%===============================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Traffic to Pornography Online}
	\label{tab:distribution_visits}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Visits}}\\
			\midrule
			\input{../tabs/percentiles_visits_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_visits} for the plot.
	}
\end{table}

%=============================================================
% Tabulated percentiles of proportion of visits to adult sites
%=============================================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Traffic to Pornographic Sites}
	\label{tab:distribution_prop_visits}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% visits}}\\
			\midrule
			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for traffic to porn sites by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_prop_visits} for the plot.
	}
\end{table}

%======================================================================
% Tabulated splits by party and by percentiles for visits to adultsites
%======================================================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Traffic to Pornography Online by Party}
	\label{tab:distribution_visits_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Visits}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\			
			\midrule
			\input{../tabs/percentiles_visits_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period. See \cref{fig:distribution_visits_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table} \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Traffic to Pornographic Sites by Party}
	\label{tab:distribution_prop_visits_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}ccc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% visits}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\	
			\midrule
			\input{../tabs/percentiles_proportion_visits_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for traffic to porn sites by individuals who consumed pornography in the sample period. See \cref{fig:distribution_prop_visits_party} for the plot.
	}
\end{table}

%==============================================================================
% Fig of quantile regression estimates
% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography)
%==============================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_proportion_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_visits} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_visits_nonzeroes}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Percentage Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Percentage of Traffic to Porn Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_proportion_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of traffic to porn sites by individuals in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_prop_visits_nonzeroes_covariates}
\end{figure}

%==============================================================================
% Fig of quantile regression estimates
% Traffic to Adult Sites by Party (for individuals who consumed pornography and with covariates)
%==============================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography and with covariates)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_covariates_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of visits to porn sites by individuals in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_visits_covariates} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_visits_nonzeroes_covariates}
\end{figure}

%===========================================================================
% Fig of quantile regression estimates
% Traffic to Adult Sites by Party (for individuals who consumed pornography)
%===========================================================================
\begin{figure}
	\centering
	\caption{Quantile Estimates--Traffic to Porn Sites by Party (for individuals who consumed pornography)}
	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_nonzero_visits_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of visits to porn sites by individuals in our sample.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Only includes individuals who consumed pornography in the sample period.
		95\% confidence intervals constructed from robust standard errors.
		See \cref{fig:quantile_regression_visits} for the same plot for the full sample.
	}
	\label{fig:quantile_regression_visits_nonzeroes}
\end{figure}

### 2023-01-04 ms/adult.tex
Update ms

@@
 
-\setcounter{page}{0}
-
 \usepackage{lscape}
@@
 
+\thispagestyle{empty}
 \begin{abstract}
@@
 \clearpage
+\setcounter{page}{1}
 \doublespace
@@
 Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
-The median American Internet user spends X minutes per month (Y\% of their time online) consuming pornography, visiting Y unique sites; the 95th percentile for time spent consuming pornography online is YY minutes.
+Most individuals in the sample do not consumer pornography.
+The median American Internet user spends 0 minutes per month consuming pornography (0\% of their time online), visiting 122 unique sites. 
+The median American consumer of pornography spends about 44 minutes per month consuming pornography (3\% of their time online), visiting three unique pornographic sites. 
+The 95th percentile for time spent consuming pornography online is 337 minutes (about 21\% of their time online).
 
@@
 \section*{Data}\label{sec:data}
-We use passively observed browsing data from a YouGov survey to measure the consumption of adult content.
+We use passively observed browsing data from a YouGov survey to measure the consumption of adult content \citep{data-dataverse}.
 YouGov maintains a large online panel recruited through a variety of methods.
@@
 For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
+We capture about 64k unique sites, of which 900 are pornographic sites (1.4\$ of sites).
 
@@
 These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com).
-A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains.
+A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.
+See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains.
 Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites.
-For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We manually check the top adult domains in our sample to remove obvious false positives of porn sites.
+For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.} \footnote{We manually check the top adult domains in our sample to remove obvious false positives of porn sites.
 Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}
@@
 The consumption of pornography is highly concentrated.
-Traffic to the top 10 most frequented porn sites is more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \crefrange{fig:concentration_porn_consumption}{fig:concentration_porn_consumption_by_party}).
-Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site (\cref{fig:concentration_porn_consumption}).
+Traffic to the top 10 most frequented porn sites is more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \cref{fig:concentration_porn_consumption}).
+Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site, a behavior that is fairly consistent across parties (\cref{fig:concentration_porn_consumption_topX_by_party}).
 The next most frequented pornographic site constitutes less than 20 percent of total traffic.
@@
 \subsection*{Partisan Differences in Consumption of Pornography Online}
+%===========================
+% Quantile regressions
+% Hours spent on adult sites
+%===========================
+\begin{figure}[t]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
+	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours individuals in our sample spent on porn sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:quantile_regression_duration}
+\end{figure}
+
+%========================================
+% Quantile regressions
+% Proportion of time spent on adult sites
+%========================================
+\begin{figure}[t]
+	\centering
+	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party}
+	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:quantile_regression_prop_duration}
+\end{figure}
 
@@
 
-%===========================
-% Quantile regressions
-% Hours spent on adult sites
-%===========================
-\begin{figure}[ht]
-\centering
-\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
-\includegraphics[width=.6\linewidth]{../figs/quantile_reg_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
-}
-\label{fig:quantile_regression_duration}
-\end{figure}
-
-%========================================
-% Quantile regressions
-% Proportion of time spent on adult sites
-%========================================
-\begin{figure}[ht]
-	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party}
-	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
-	}
-	\label{fig:quantile_regression_prop_duration}
-\end{figure}
-
 \section*{Discussion}
@@
 This leads to the concern that pornography consumption has become very widespread.
-Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little.
+Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.
 
 The second contribution of our paper is estimates of partisan differences in consumption of pornography online.
-Both the parties claim the higher ground when it comes to women--- one's case for morality is steeped in religion, the other's in enduring concern for women.
+Both the parties claim the higher ground when it comes to women---one's case for morality is steeped in religion, the other's in enduring concern for women.
 Our data suggest that the partisan differences are likely very small.
@@
 
+%====================================
+% Figure of traffic to top x websites
+%====================================
+\begin{figure}
+	\centering
+	\caption{Traffic to Top x Porn Sites by Party}
+	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
+		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
+	}
+	\label{fig:concentration_porn_consumption_topX_by_party}
+\end{figure}
+
+\FloatBarrier
 \subsection{Skew in Consumption of Pornographic Content}
-
 %====================================================
@@
 		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		See \cref{fig:distribution_duration} for the plot.
+		%See \cref{fig:distribution_duration} for the plot.
 	}
@@
 		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		See \cref{fig:distribution_prop_duration} for the plot.
+		%See \cref{fig:distribution_prop_duration} for the plot.
 	}
@@
 
+\FloatBarrier
 \section{Partisan Differences}
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-See \cref{fig:distribution_duration_party} for the plot.
+		%See \cref{fig:distribution_duration_party} for the plot.
 	}
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-See \cref{fig:distribution_prop_duration_party} for the plot.
+		%See \cref{fig:distribution_prop_duration_party} for the plot.
 	}
@@
 
+\FloatBarrier
 \subsection{Accounting for Confounders}
-
 %==============================================================================
@@
 		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
-		These 65 individuals are not substantially different in characteristics than those included in the sample (see \textbf{TABLE ??}).
+		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
+		95\% confidence intervals constructed from standard errors.
 		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
@@
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
+		95\% confidence intervals constructed from standard errors.
 		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
@@
 \clearpage
+
+\FloatBarrier
 %===============================================================================
@@
 
+\FloatBarrier
 \section{Alternate Measures}
@@
 		Capped vertical bars are 95\% confidence intervals.
-		See \cref{tab:distribution_visits} for the more tabulated values.
+		%See \cref{tab:distribution_visits} for the more tabulated values.
 	}
@@
 		Capped vertical bars are 95\% confidence intervals.
-		See \cref{tab:distribution_prop_visits} for the more tabulated values.
+		%See \cref{tab:distribution_prop_visits} for the more tabulated values.
 	}
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_visits_covariates} for the same plot controlling for individual characteristics.
+		95\% confidence intervals constructed from standard errors.
+		%See \cref{fig:quantile_regression_visits_covariates} for the same plot controlling for individual characteristics.
 	}
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot controlling for individual characteristics.
+		95\% confidence intervals constructed from standard errors.
+		%See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot controlling for individual characteristics.
 	}
@@
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_visits} for the same plot without covariates.
+		95\% confidence intervals constructed from standard errors.
+		%See \cref{fig:quantile_regression_visits} for the same plot without covariates.
 	}
@@
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from robust standard errors.
-		See \cref{fig:quantile_regression_prop_visits} for the same plot without covariates.
+		95\% confidence intervals constructed from standard errors.
+		%See \cref{fig:quantile_regression_prop_visits} for the same plot without covariates.
 	}

### 2023-01-04 ms/scrap_yard.tex
Update ms

@@
 	\label{fig:distribution_prop_duration_party}
-\end{figure}
-
-%====================================
-% Figure of traffic to top x websites
-%====================================
-\begin{figure}
-	\centering
-	\caption{Traffic to Top x Porn Sites by Party}
-	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
-		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:concentration_porn_consumption_topX_by_party}
 \end{figure}

### 2023-01-04 ms/adult.tex
Update adult.tex

@@
 We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts.
-The median American Internet user today spends X minutes per month consuming pornography, visiting Y sites per month; the 95th percentile is X and Y respectively.
+Only about 32 percent of the respondents consumed pornography online during the month long observation period.
+Of the people who consumed pornography, the median consumer spent about 44 minutes  consuming pornography and 95 percent spent less than 337 minutes.
 Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume about as much pornography online as Republicans.
@@
 Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
-Most individuals in the sample do not consumer pornography.
-The median American Internet user spends 0 minutes per month consuming pornography (0\% of their time online), visiting 122 unique sites. 
-The median American consumer of pornography spends about 44 minutes per month consuming pornography (3\% of their time online), visiting three unique pornographic sites. 
-The 95th percentile for time spent consuming pornography online is 337 minutes (about 21\% of their time online).
+About 68 percent of the respondents abstained from  pornography online during the month long observation period.
+Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and the 95th percentile consumer spent 337 minutes.
 
-We also use the data to shed light on an age-old debate --- whether Democrats consume more pornography than Republicans or vice versa.
+We also use the data to shed light on an age-old debate---whether Democrats consume more pornography than Republicans or vice versa.
 Both parties claim the higher moral ground.
@@
 \subsection*{Consumption of Pornography}
-The consumption of pornography is highly concentrated.
-Traffic to the top 10 most frequented porn sites is more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \cref{fig:concentration_porn_consumption}).
-Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site, a behavior that is fairly consistent across parties (\cref{fig:concentration_porn_consumption_topX_by_party}).
-The next most frequented pornographic site constitutes less than 20 percent of total traffic.
-
-The consumption of pornography online is also limited to a minority of respondents.
-Only about 32 percent of the respondents visited at least one pornography online during the sample period.
-The average consumer of pornography online spends approximately 230 minutes (standard deviation of 576 minutes), which is 10.6 percent of total browsing activity (standard deviation of 17.9 percent).
-These come from 233 visits to pornographic sites (standard deviation of 550), which is 6.9 percent of visits to all sites (standard deviation of 11.2 percent).
-
-The key differences between consumers and non-consumers of pornography online are age and gender. Consumers of pornography online are younger and are more likely to be male.
+Only about 32 percent of the respondents consumed pornography online during the sample period.
+The average consumer of pornography online spent approximately 230 minutes (standard deviation of 576 minutes).
+The consumption of pornography was highly concentrated among a few sites with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs.
+9 minutes, see \cref{fig:concentration_porn_consumption}).
+Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site.
+Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male.
 
@@
 
-Our research has two major limitations.
-The first concern with our data is that we may not have data from all the machines that the respondent uses to visit online.
+Our research has three major limitations.
+The first concern with our data is that we may not have all the Internet visitation data from a user.
 If the respondent changes their behavior in response to the knowledge that their data is being collected (even if it is de-identified), for e.g., they may modify their behavior on the machine or figure out ways to evade detection, it may bias our results.
 In fact, we think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified).
-If that is so, our estimates are a lower bound of net consumption of pornography per machine.
+If that is so, our estimates are a lower bound of net consumption of pornography.
 If this bias varies by party, our estimates of partisan differences will also be biased.
@@
 For instance, our classification would code websites like Tumblr as not carrying pornographic content but some of Tumblr content is pornographic.
+
+The third concern is that our measures are a point in time.
+We have data from one month in one year---June, 2022.
+It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in preceding or following months.
 

### 2023-01-04 ms/adult.tex
revise ms

@@
 Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
-About 68 percent of the respondents abstained from  pornography online during the month long observation period.
+About 68 percent of the respondents abstained from consuming pornography online during the month long observation period.
 Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and the 95th percentile consumer spent 337 minutes.
@@
 Both parties claim the higher moral ground.
-And in surveys both parties think consumption of pornography is abhorrent, plausibly for different reasons.
+And in surveys both parties think consumption of pornography is abhorrent.
 Unlike previous research, which relied on ecological inference, we find that Democrats consume about as much pornography online as Republicans \citep{macinnis2015american, edelman2009markets}.
@@
 \section*{Data}\label{sec:data}
-We use passively observed browsing data from a YouGov survey to measure the consumption of adult content \citep{data-dataverse}.
-YouGov maintains a large online panel recruited through a variety of methods.
-It uses matched sampling to survey respondents: The provider first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
-For details and validation, see \citet{rivers2009}.
-For this particular sample, panelists also provided de-identified access to their web browsing activity via passive metering software installed voluntarily on their computers.
-The software, called RealityMine, captures visited web URLs independent of the type of browser or browser-specific privacy settings.
+We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}.
+YouGov maintains a large panel that is recruits using various methods.
+YouGov uses matched sampling to survey respondents: it first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
+For data on how well Yougov is able to approximate a random sample, see \citet{rivers2009}.
+For our sample, panelists also shared de-identified web browsing data tracked via passive metering software installed voluntarily on their computers.
+The software, called RealityMine, captures online visits independent of the type of browser or browser-specific privacy settings.
 
 The data are from 1,200 respondents and contains a month of data from June, 2022.
-We have data on visits to domains, which are about 6 million in total.
+In all, we have data on about 6 million visits.
 For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
-We capture about 64k unique sites, of which 900 are pornographic sites (1.4\$ of sites).
+The respondents visited about 64k unique sites, of which 900 are pornographic sites.
 
-Our data also comes with characteristics for the 1,200 individuals.
-We have data on demographic characterists like birth year, state, gender, race, and education level.
+Our data also includes characteristics of the 1,200 individuals.
+We have data on demographic characteristics like birth year, state, gender, race, and education level.
 We also have information on their party identification.

### 2023-01-04 ms/adult.tex
Update adult.tex

@@
 Our main analysis depends on the domain classifications that come with YouGov data.
-We code domains that YouGov categorizes as ``Adult'' as porn sites.
+We code domains that YouGov categorizes as ``Adult'' as pornographic sites.
 These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com).
-A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites.
-See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains.
-Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites.
-For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.} \footnote{We manually check the top adult domains in our sample to remove obvious false positives of porn sites.
-Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}
+Yougoc classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org .
+Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.}, we manually check the top adult domains to remove such sites.
+If there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a pornographic.
 
@@
 \subsection*{Consumption of Pornography}
+Across all respondents, only a small fraction of the web browsing visits, approximately 84,000 visits or 1.3 percent, are to pornographic sites.
+And these visits are concentrated among a few people.
 Only about 32 percent of the respondents consumed pornography online during the sample period.
 The average consumer of pornography online spent approximately 230 minutes (standard deviation of 576 minutes).
-The consumption of pornography was highly concentrated among a few sites with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs.
+
+The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs.
 9 minutes, see \cref{fig:concentration_porn_consumption}).
-Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site.
-Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male.
+Close to 80 percent of the traffic to pornographic sites is to just one pornographic site.
+Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male \cref{fig:} %TODO
 
 \subsection*{Partisan Differences in Consumption of Pornography Online}
+Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+(In \ref{si:visits}, we show similar analysis for visits.
+The upshot is that the key conclusions are unaffected.)
+
+Given the skew in the data, we ran a quantile regression, regressing the duration on party.
+As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties.
+To account for the possibility that this may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender.
+(\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
+Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.
 %===========================
@@
 
-Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites.
-(In \ref{si:visits}, we show similar analysis for visits.)
-
-Given the skew in the data, we ran a quantile regression, regressing the duration on party.
-As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties.
-To account for the possibility that these non-differences may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much.
-\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.
-We use these variables in our analyses of pornography consumption below.
-Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.
-
 \section*{Discussion}
@@
 It is also considered problematic from a religious perspective.
-Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}.
+For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}.
 The Internet has dramatically increased access to pornography.
-This leads to the concern that pornography consumption has become very widespread.
+This has led to the concern that pornography consumption has become very widespread and extensive.
 Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.

### 2023-01-04 ms/adult.tex
revise ms

@@
 
-The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs.
+The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites  (approximately 109 minutes vs.
 9 minutes, see \cref{fig:concentration_porn_consumption}).
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party}
 	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on porn sites.
+		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party}
+	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party}
 	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
+		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\centering
-	\caption{Top 25 Porn Sites}
+	\caption{Top 25 Pornography Sites}
 	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 porn sites that individuals visit in the sample period.
+		Table shows the top 25 pornographic sites that individuals visit in the sample period.
 		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
@@
 		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
-		Sites to the right of the vertical dashed are the top 1 percent of porn sites.
+		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
 	}
@@
 		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
-		Sites to the right of the vertical dashed are the top 1 percent (of non-porn sites).
+		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
 	}
@@
 	\centering
-	\caption{Traffic to Top x Porn Sites by Party}
+	\caption{Traffic to Top x Pornographic Sites by Party}
 	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
+		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
 		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).

### 2023-01-05 ms/adult.tex
Update ms
Add tables for pornography consumption for Independents vs partisans (D/R) in the SI. Also added the corresponding footnote into the main text. And some other minor formatting changes.

@@
 
+\usepackage{tocloft}
+
 \usepackage{lscape}
@@
 \title{\Large{Holier Than Thou?
-No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}}
+No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.
+		%We thank Alexander Marsolais (YouGov) and Rajashekar Chintalapati. 
+	}
+}
 
@@
 \section*{Data}\label{sec:data}
+\addcontentsline{toc}{section}{\nameref{sec:data}}
 We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}.
@@
 
-\section*{Measuring Pornographic Content}
+\section*{Measuring Pornographic Content}\label{sec:measuring_porn_content}
+\addcontentsline{toc}{section}{\nameref{sec:measuring_porn_content}}
+
 We code pornographic content at the domain level.
@@
 These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com).
-Yougoc classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org .
+Yougov classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org .
 Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.}, we manually check the top adult domains to remove such sites.
@@
 
-\section*{Results}
+\section*{Results}\label{sec:results}
+\addcontentsline{toc}{section}{\nameref{sec:results}}
 
@@
 Close to 80 percent of the traffic to pornographic sites is to just one pornographic site.
-Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male \cref{fig:} %TODO
+Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male (see, for instance, Panel B of \cref{tab:characteristics_split_by_porn_consumers}).
 
@@
 (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
-Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.
+Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.\footnote{
+	We also investigated consumption of pornography among independents in \cref{si:independents}.
+	At the median, Independents consume more pornography compared to partisans in terms of the amount of time spent and the percentage of time spent on pornography online (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
+	This difference is driven by the relatively higher consumption of pornography among Republicans.
+
+	This pattern reverses somewhat near the right tail  of the distribution.
+	Independents also consume more pornography at the right tail of the distribution. 
+	At the 95th percentile, Independents consume about 3.5 hours more and spend 13.9\% more of their internet browsing time on pornography online.
+	This behavior at the right tail is driven by the relatively higher consumption of pornography among the Democrats.
+}
+
 %===========================
@@
 
-\section*{Discussion}
-
+\section*{Discussion}\label{sec:discussion}
+\addcontentsline{toc}{section}{\nameref{sec:discussion}}
 Consumption of pornography has been attributed to a variety of ills.
 It is also considered problematic from a religious perspective.
-For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}.
-The Internet has dramatically increased access to pornography.
+For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}} The Internet has dramatically increased access to pornography.
 This has led to the concern that pornography consumption has become very widespread and extensive.
@@
 \counterwithin{table}{section}
-\begin{center}
-\Large{Supporting Information}
-\end{center}
+
+\section{Supporting Information}\label{si}
+%\begin{center}
+%\Large{Supporting Information}
+%\end{center}
 
@@
 %===============================================================================
-\section{Descriptive Analysis}
+\subsection{Descriptive Analysis}
 
-\subsection{Skew in Website Visits}
+\subsubsection{Skew in Website Visits}
 %============================
@@
 \FloatBarrier
-\subsection{Skew in Consumption of Pornographic Content}
+\subsubsection{Skew in Consumption of Pornographic Content}
 %====================================================
@@
 \FloatBarrier
-\section{Partisan Differences}
-\subsection{Distribution of Differences}
+\subsection{Partisan Differences}
+\subsubsection{Distribution of Differences}
 %===========================================================================
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
 		%See \cref{fig:distribution_prop_duration_party} for the plot.
@@
 \FloatBarrier
-\subsection{Accounting for Confounders}
+\subsubsection{Accounting for Confounders}
 %==============================================================================
@@
 %===============================================================================
-\section{Alternate Ways of Measuring Pornography}
+\subsection{Alternate Ways of Measuring Pornography}
 \label{si:alternate_ways}
@@
 
-\section{Consumption of Pornography Among Independents}
+\subsection{Consumption of Pornography Among Independents}
+\label{si:independents}
+%===========================================================================
+% Tabulated splits by party and by percentiles for hours spent on adultsites
+%===========================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
+	\caption{Distribution of Consumption of Pornography Online Among Independents}
+	\label{tab:percentiles_duration_adultsites_by_individuals_independents_partisans}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
+			\toprule		
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
+			\midrule
+			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Column (1) includes Democrats (n = 154).
+		Column (2) includes Republicans (n = 95).
+		Column (3) includes both Republicans and Democrats (n = 249).
+		Column (4) includes Independents (n = 67).
+		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
+		%See \cref{fig:distribution_duration_party} for the plot.
+	}
+\end{table}
+
+\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites Among Independents}
+	\label{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
+			\toprule		
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
+			\midrule
+			\input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		Column (1) includes Democrats (n = 154).
+		Column (2) includes Republicans (n = 95).
+		Column (3) includes both Republicans and Democrats (n = 249).
+		Column (4) includes Independents (n = 67).
+		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
+		%See \cref{fig:distribution_duration_party} for the plot.
+	}
+\end{table}
 
 \FloatBarrier
-\section{Alternate Measures}
+\subsection{Alternate Measures}
 %============================================================================
@@
 
-\subsection{Proportion of Partisans Who Consumed Any Pornography}
+\subsubsection{Proportion of Partisans Who Consumed Any Pornography}
 \begin{figure}
@@
 %===============================================================================
-\subsection{Analyses of Visits}
+\subsubsection{Analyses of Visits}
 \label{si:visits}

### 2023-01-06 ms/adult.tex
Update ms using piedomains classification
- Add Tables SI 1.8 and 1.9 for percentile splits by party using the piedomains classification

- Percentile tables decimal points --> 1 decimal precision

- Add KS tests to percentile tables

- plus some minor formatting updates

@@
 Yougov classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org .
-Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.}, we manually check the top adult domains to remove such sites.
+Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We also use various packages to derive key results \citep{tableone, statsmodels, forestplot, scipy}.}, we manually check the top adult domains to remove such sites.
 If there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a pornographic.
@@
 		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
 		%See \cref{fig:distribution_duration} for the plot.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
+		See \cref{tab:distribution_duration} for the distribution in terms of hours.
 		%See \cref{fig:distribution_prop_duration} for the plot.
@@
 \FloatBarrier
+\clearpage
 \subsection{Partisan Differences}
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
+		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.005, rejecting the null that the Republican and Democrat distributions are the same.
 		%See \cref{fig:distribution_duration_party} for the plot.
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
+		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.025, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
 		%See \cref{fig:distribution_prop_duration_party} for the plot.
@@
 \FloatBarrier
+\clearpage
 \subsubsection{Accounting for Confounders}
@@
 		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in consumption of pornography, we also performed tests for difference in means for the measures of pornography consumption by party.
-See \cref{tab:characteristics_split_by_party_medians}.
+		Given the skew in consumption of pornography, we also performed tests for difference in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
 	}
@@
 \label{si:alternate_ways}
+%===========================================================================
+% Tabulated splits by party and by percentiles for hours spent on adultsites
+%===========================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Consumption of Pornography Online by Party}
+	\label{tab:piedomains_distribution_duration_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/piedomains_percentiles_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Classificationo of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		See \cref{tab:piedomains_distribution_prop_duration_party} for the corresponding distribution in terms of percentage of time. 
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.0481, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
+		%See \cref{fig:distribution_duration_party} for the plot.
+	}
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
+%===============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party}
+	\label{tab:piedomains_distribution_prop_duration_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/piedomains_percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		Classificationo of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of percentage of time.
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.19, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
+		%See \cref{fig:distribution_prop_duration_party} for the plot.
+	}
+\end{table}
+
+\FloatBarrier
 \clearpage
-
 \subsection{Consumption of Pornography Among Independents}
@@
 
+\cleardoublepage
 \FloatBarrier
 \subsection{Alternate Measures}
+\subsubsection{Proportion of Partisans Who Consumed Any Pornography}
 %============================================================================
@@
 %============================================================================
-
-\subsubsection{Proportion of Partisans Who Consumed Any Pornography}
 \begin{figure}

### 2023-01-07 ms/adult.tex
Update adult.tex

@@
 
-\title{\Large{Holier Than Thou?
-No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.
-		%We thank Alexander Marsolais (YouGov) and Rajashekar Chintalapati. 
-	}
-}
+\title{Holier Than Thou: Partisan Gap in the Consumption\\ of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}}
 
@@
 We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts.
-Only about 32 percent of the respondents consumed pornography online during the month long observation period.
+Only about 32 percent of respondents consumed pornography online during the month-long observation period.
 Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and 95 percent spent less than 337 minutes.
-Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume about as much pornography online as Republicans.
+Lastly, we find that, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, Republicans consume somewhat more pornography online than Democrats.
 \end{abstract} 
@@
 Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
-About 68 percent of the respondents abstained from consuming pornography online during the month long observation period.
-Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and the 95th percentile consumer spent 337 minutes.
+About 68 percent of respondents abstained from consuming pornography online during the month-long observation period.
+Of the people who consumed pornography, the median consumer spent about 45 minutes consuming pornography and the 95th percentile consumer spent about five and a half hours.
 
@@
 And in surveys both parties think consumption of pornography is abhorrent.
-Unlike previous research, which relied on ecological inference, we find that Democrats consume about as much pornography online as Republicans \citep{macinnis2015american, edelman2009markets}.
-Adjusting for background attributes like age, gender etc., makes little difference.
+Unlike previous research, which relied on aggregated data, we find that Republicans consume somewhat more pornography online than Democrats \citep{macinnis2015american, edelman2009markets}.
+Adjusting for background attributes like age, gender etc., makes the differences go away.
 
@@
 We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}.
-YouGov maintains a large panel that is recruits using various methods.
-YouGov uses matched sampling to survey respondents: it first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
-For data on how well Yougov is able to approximate a random sample, see \citet{rivers2009}.
+YouGov maintains a large panel that it recruits through various methods.
+YouGov uses matched sampling to survey respondents: it draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
+For data on how well YouGov is able to approximate a random sample, see \citet{rivers2009}.
 For our sample, panelists also shared de-identified web browsing data tracked via passive metering software installed voluntarily on their computers.
@@
 
-The data are from 1,200 respondents and contains a month of data from June, 2022.
-In all, we have data on about 6 million visits.
+The data are from 1,200 respondents for June, 2022.
+We have data on about 6 million visits.
 For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
-The respondents visited about 64k unique sites, of which 900 are pornographic sites.
+The respondents visited about 64,000 unique domains.
 
-Our data also includes characteristics of the 1,200 individuals.
+Our data also includes characteristics of the respondents.
 We have data on demographic characteristics like birth year, state, gender, race, and education level.
 We also have information on their party identification.
-Except for 120 respondents  who did not respond or picked not sure/don't know, the rest stated the party they identified with.
-Of the 1,080 individuals who report party identification, 82 percent lean either Republican or Democrat.
+Except for 120 respondents who did not respond or picked not sure or don't know, the rest selected the party they identified with.
+Of the 1,080 individuals who reported party identification, 82 percent lean either Republican or Democrat.
 The remaining 18 percent identify as independent.
@@
 Yougov classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org .
-Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We also use various packages to derive key results \citep{tableone, statsmodels, forestplot, scipy}.}, we manually check the top adult domains to remove such sites.
-If there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a pornographic.
+Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use various statistical packages to compute key results \citep{tableone, statsmodels, forestplot, scipy}.}, we manually check the top adult domains to remove such sites.
+We code a domain as pornographic if there is nudity on the landing page or if the site is some form of erotica.
 
@@
 \subsection*{Partisan Differences in Consumption of Pornography Online}
-Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites.
-(In \ref{si:visits}, we show similar analysis for visits.
+Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+(In \ref{si:visits}, we analyze similar metrics for visits.
 The upshot is that the key conclusions are unaffected.)
@@
 Given the skew in the data, we ran a quantile regression, regressing the duration on party.
-As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties.
-To account for the possibility that this may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender.
-(\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
-Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.\footnote{
-	We also investigated consumption of pornography among independents in \cref{si:independents}.
+As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference at nearly XX hrs.
+To put this in context, the 80th and 90th percentile of time spent on pornographic sites online among Republicans is nearly XX hrs and YY respectively.
+In contrast, the corresponding numbers are KK and PP for Democrats.
+(%TODO See also SI TABLE FOR DISTRIBUTION OF TIME SPENT ON PORNOGRAPHIC SITES BY PARTY AMONG THE SUBSET OF PEOPLE WHO CONSUMED AT LEAST SOME PORNOGRAPHIC CONTENT.)\footnote{
+
+	We also investigated the consumption of pornography among independents in \cref{si:independents}.
+
 	At the median, Independents consume more pornography compared to partisans in terms of the amount of time spent and the percentage of time spent on pornography online (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
+
 	This difference is driven by the relatively higher consumption of pornography among Republicans.
@@
 	This pattern reverses somewhat near the right tail of the distribution.
-	Independents also consume more pornography at the right tail of the distribution. 
+
+	Independents also consume more pornography in the right tail of the distribution.
+
 	At the 95th percentile, Independents consume about 3.5 hours more and spend 13.9\% more of their internet browsing time on pornography online.
-	This behavior at the right tail is driven by the relatively higher consumption of pornography among the Democrats.
+
+	This behavior at the right tail is driven by the relatively higher consumption of pornography among Democrats.
+
 }
 
+Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites.
+The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10% at the 100th percentile (albeit the number is very imprecisely estimated).
+
+Looking at differences in the percentage of partisans who consume any pornographic content shows muted differences.
+YY percent of Democrats and KK percent of Republicans consumed at least some pornography online in June, 2022; the difference between the two is not statistically significant (see FIGURE SI BLAH).
+
+To what extent are the results "explained" by the confounding demographic differences between the parties?
+To learn that, we control for immutable characteristics like age and gender.
+(\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
+As Figure \ref{fig:quantile_regression_duration} shows, once you adjust for confounders, the partisan differences melt away.
 %===========================
@@
 The second contribution of our paper is estimates of partisan differences in consumption of pornography online.
-Both the parties claim the higher ground when it comes to women---one's case for morality is steeped in religion, the other's in enduring concern for women.
-Our data suggest that the partisan differences are likely very small.
+Both parties claim the higher ground when it comes to women---one's case for morality is steeped in religion, the other's in enduring concern for women.
+Our data suggest that partisan differences are likely small.
 
 Our research has three major limitations.
-The first concern with our data is that we may not have all the Internet visitation data from a user.
+The first concern with our data is that we may not have all the Internet visitation data of a user.
 If the respondent changes their behavior in response to the knowledge that their data is being collected (even if it is de-identified), for e.g., they may modify their behavior on the machine or figure out ways to evade detection, it may bias our results.
 In fact, we think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified).
-If that is so, our estimates are a lower bound of net consumption of pornography.
+If that is so, our estimates are a lower bound of consumption of online pornography.
 If this bias varies by party, our estimates of partisan differences will also be biased.
@@
 This runs the risk of incurring some ecological fallacy.
-For instance, our classification would code websites like Tumblr as not carrying pornographic content but some of Tumblr content is pornographic.
+For instance, our classification codes websites like Tumblr as not carrying pornographic content but some of Tumblr content is pornographic.
 
 The third concern is that our measures are a point in time.
-We have data from one month in one year---June, 2022.
-It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in preceding or following months.
+We have data from one month in one year - June, 2022.
+It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in the preceding or following months.
 

### 2023-01-07 scripts/utils/data_utils.py
Adding regression tables
Adding regression tables (for OLS and quantile regressions) for the key results.

@@ -1,6 +1,7 @@
 import pandas as pd
 import statsmodels.api as sm
 import statsmodels.formula.api as smf
+from stargazer.stargazer import Stargazer
 
 
 def pandas_to_tex(df, texfile, index=False):
@@ -73,3 +74,64 @@ def fit_ols_reg(y, x, df, z=None):
         obs=ols_results.nobs,
     )
     return ols_results
+
+
+def esttab_ols_quantile(y, x, quantiles, df, z=None):
+    ## Set up regression models (quantile & OLS)
+    if z is None:
+        quantile_model = smf.quantreg(f"{y} ~ {x}", df)
+        ols_model = smf.ols(f"{y} ~ {x}", df)
+    else:
+        quantile_model = smf.quantreg(f"{y} ~ {x} + {z}", df)
+        ols_model = smf.ols(f"{y} ~ {x} + {z}", df)
+
+    ## Fit and store estimates
+    reg_results = []
+    
+    # Store OLS estimates
+    reg_results.append(ols_model.fit(cov_type="HC3"))
+    
+    # Store quantile estimates
+    for quantile in quantiles:
+        result = quantile_model.fit(q=quantile, max_iter=10_000)
+        reg_results.append(result)
+    stargazer = Stargazer(reg_results)
+
+    ## Edit stargazer table (absent variables seem to be ignored)
+    coeflabels = {
+        "rep": "Republican", 
+        "C(gender)[T.2]": "Female",
+        "C(educ2)[T.2]": "Educ (HS)",
+        "C(educ2)[T.3]": "Educ (some college)",
+        "C(educ2)[T.4]": "Educ (college grad)",
+        "age": "Age",
+        "age2": "Age$^2$",        
+        "C(race2)[T.2]": "Race (Black)",
+        "C(race2)[T.3]": "Race (Hispanic)",
+        "C(race2)[T.4]": "Race (Asian)",
+        "C(race2)[T.5]": "Race (Other)",
+        "C(region)[T.2]": "Region (MW)",
+        "C(region)[T.3]": "Region (South)",
+        "C(region)[T.4]": "Region (West)",
+        "Intercept": "Constant", 
+    }
+    stargazer.rename_covariates(coeflabels)
+    if z is None:
+        stargazer.covariate_order(["rep", "Intercept"])
+    else:
+        stargazer.covariate_order(coeflabels.keys())
+    stargazer.significant_digits(2)
+
+    ## Pare down to get LaTeX *fragment*
[…]

### 2023-01-07 scripts/utils/data_utils.py
Adding quantile regressions for piedomains
Adding quantile regression results for classification of porn sites using piedomains---for duration and percentage of time spent on porn sites.

@@ -131,7 +131,7 @@ def esttab_ols_quantile(y, x, quantiles, df, z=None):
     
     ## Make sig stars compatible with downstream dcolumns in LaTeX
     latex_fragment_str = latex_fragment_str.replace("$^{}$", "")
-    latex_fragment_str = latex_fragment_str.replace("$^{*}$", "\sym{*}")
-    latex_fragment_str = latex_fragment_str.replace("$^{**}$", "\sym{**}")
-    latex_fragment_str = latex_fragment_str.replace("$^{***}$", "\sym{***}")
+    latex_fragment_str = latex_fragment_str.replace("$^{*}$", "\sym{c}")
+    latex_fragment_str = latex_fragment_str.replace("$^{**}$", "\sym{b}")
+    latex_fragment_str = latex_fragment_str.replace("$^{***}$", "\sym{a}")
     return latex_fragment_str, stargazer

### 2023-01-08 ms/adult.tex
update ms.

@@
 Only about 32 percent of respondents consumed pornography online during the month-long observation period.
-Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and 95 percent spent less than 337 minutes.
+Of the people who consumed pornography, the median consumer spent about three-quarters of an hour consuming pornography and 95 percent of the consumers spent less than five and a half hours.
 Lastly, we find that, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, Republicans consume somewhat more pornography online than Democrats.
+Adjusting for immutable characteristics like age and gender makes the differences go away.
 \end{abstract} 
@@
 An analysis of popular pornography revealed that 88.2\% of the scenes contained physical aggression, and 48.7\% verbal aggression \citep{bridges2010aggression}.
-For all these reasons, there are serious concerns about consumption of pornography.
+For all these reasons, there are serious concerns about the consumption of pornography.
 
@@
 And in surveys both parties think consumption of pornography is abhorrent.
-Unlike previous research, which relied on aggregated data, we find that Republicans consume somewhat more pornography online than Democrats \citep{macinnis2015american, edelman2009markets}.
+Like previous research, which relied on aggregated data, we find that Republicans consume somewhat more pornography online than Democrats \citep{macinnis2015american, edelman2009markets}.
 Adjusting for background attributes like age, gender etc., makes the differences go away.
@@
 We also have information on their party identification.
-Except for 120 respondents who did not respond or picked not sure or don't know, the rest selected the party they identified with.
-Of the 1,080 individuals who reported party identification, 82 percent lean either Republican or Democrat.
+Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents.
+Of those 1,080 individuals, 82 percent lean either Republican or Democrat.
 The remaining 18 percent identify as independent.
@@
 Our main analysis depends on the domain classifications that come with YouGov data.
-We code domains that YouGov categorizes as ``Adult'' as pornographic sites.
+We code domains that YouGov categorizes as ``Adult'' as pornographic.
 These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com).
-Yougov classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org .
-Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use various statistical packages to compute key results \citep{tableone, statsmodels, forestplot, scipy}.}, we manually check the top adult domains to remove such sites.
+Yougov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as `Adult.' Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We cite some of the statistical packages to compute key results \citep{tableone, statsmodels, forestplot, scipy}.}, we manually checked the top adult domains to remove such sites.
 We code a domain as pornographic if there is nudity on the landing page or if the site is some form of erotica.
 
-In \ref{si:alternate_ways}, we leverage the \texttt{piedomains} package to classify which domains are pornographic sites using machine learning \citep{Chintalapati_piedomains_Predict_the_2022}.
+In \ref{si:alternate_ways}, we leverage the \texttt{piedomains} package, which uses a machine learning model that uses the text of the website to classify the content of domains \citep{Chintalapati_piedomains_Predict_the_2022}.
 We leverage the probability estimates to produce a low false negative and low false positive version.
-The key results remain unchanged.
+The key conclusions remain unchanged.
 
@@
 
+Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+(In \ref{si:visits}, we analyze similar metrics for visits.
+The upshot is that the key conclusions are unaffected.)
+
 \subsection*{Consumption of Pornography}
-Across all respondents, only a small fraction of the web browsing visits, approximately 84,000 visits or 1.3 percent, are to pornographic sites.
-And these visits are concentrated among a few people.
-Only about 32 percent of the respondents consumed pornography online during the sample period.
-The average consumer of pornography online spent approximately 230 minutes (standard deviation of 576 minutes).
+Only about 32 percent of respondents consumed pornography online during the observation period.
+Of the 32\% of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile, nearly 20 hours (see \cref{tab:distribution_duration}).
+You see a similar picture when it comes to the proportion of time spent online consuming pornography-the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).
 
-The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites  (approximately 109 minutes vs.
+The consumption of pornography is also highly concentrated among a few sites, with the ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites (approximately 109 minutes vs.
 9 minutes, see \cref{fig:concentration_porn_consumption}).
@@
 \subsection*{Partisan Differences in Consumption of Pornography Online}
+
+\subsection*{Partisan Differences in Consumption of Pornography Online}
+
 Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
@@
 Given the skew in the data, we ran a quantile regression, regressing the duration on party.
-As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference at nearly XX hrs.
-To put this in context, the 80th and 90th percentile of time spent on pornographic sites online among Republicans is nearly XX hrs and YY respectively.
-In contrast, the corresponding numbers are KK and PP for Democrats.
-(%TODO See also SI TABLE FOR DISTRIBUTION OF TIME SPENT ON PORNOGRAPHIC SITES BY PARTY AMONG THE SUBSET OF PEOPLE WHO CONSUMED AT LEAST SOME PORNOGRAPHIC CONTENT.)\footnote{
+As Figures \ref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs.
+For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively.
+In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{
 
-	We also investigated the consumption of pornography among independents in \cref{si:independents}.
+	We analyze the consumption of pornography online among independents in \cref{si:independents}.
+The median independent consumes more pornography than partisans (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
+This pattern reverses somewhat near the right tail of the distribution.}
 
-	At the median, Independents consume more pornography compared to partisans in terms of the amount of time spent and the percentage of time spent on pornography online (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
-
-	This difference is driven by the relatively higher consumption of pornography among Republicans.
-
-	This pattern reverses somewhat near the right tail of the distribution.
-
-	Independents also consume more pornography in the right tail of the distribution.
-
-	At the 95th percentile, Independents consume about 3.5 hours more and spend 13.9\% more of their internet browsing time on pornography online.
-
-	This behavior at the right tail is driven by the relatively higher consumption of pornography among Democrats.
-
-}
-
-Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites.
-The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10% at the 100th percentile (albeit the number is very imprecisely estimated).
+Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \ref{fig:quantile_regression_prop_duration}).
+The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).
 
 Looking at differences in the percentage of partisans who consume any pornographic content shows muted differences.
-YY percent of Democrats and KK percent of Republicans consumed at least some pornography online in June, 2022; the difference between the two is not statistically significant (see FIGURE SI BLAH).
+Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June, 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
 
@@
 As Figure \ref{fig:quantile_regression_duration} shows, once you adjust for confounders, the partisan differences melt away.
+
 %===========================
+
 % Quantile regressions
+
 % Hours spent on adult sites
+
 %===========================
+
 \begin{figure}[t]
+
 	\centering
+
 	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party}
+
 	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
+
 	\caption*{\footnotesize \emph{Notes:}
+
 		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+
 		95\% confidence intervals constructed from standard errors.
+
 		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+
 	}
+
 	\label{fig:quantile_regression_duration}
+
 \end{figure}
@@
 %========================================
+
 % Quantile regressions
+
 % Proportion of time spent on adult sites
+
 %========================================
+
 \begin{figure}[t]
+
 	\centering
+
 	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party}
+
 	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
+
 	\caption*{\footnotesize \emph{Notes:}
+
 		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+
 		95\% confidence intervals constructed from standard errors.
+
 		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
+
 	}
+
 	\label{fig:quantile_regression_prop_duration}
+
 \end{figure}
@@
 This runs the risk of incurring some ecological fallacy.
-For instance, our classification codes websites like Tumblr as not carrying pornographic content but some of Tumblr content is pornographic.
+For instance, our classification codes websites like Tumblr as not carrying pornographic content but some of Tumblr's content is pornographic.
 

### 2023-01-08 ms/adult.tex
update ms.

@@
 
-\subsection*{Partisan Differences in Consumption of Pornography Online}
-
 Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
@@
 
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
 
@@
 
-	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
 

### 2023-01-08 ms/adult.tex
Update release
- Report sample sizes in results

- Add untruncated percentile splits by party for hours and percentage time spent on porn site

- Add regression tables for quantile and OLS regressions

- Add quantile regression results for piedomains classification

- Fix figures and tables caption

@@
 
-\author{Lucas Shen\thanks{Lucas is a Research Fellow at Asia Competitiveness Institute, Lee Kuan Yew School of Public Policy, at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
+\author{Lucas Shen\thanks{Lucas is a Research Fellow at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
 
@@
 The remaining 18 percent identify as independent.
+Column (3) of \cref{tab:characteristics_split_by_party} reports summary statistics.
 
@@
 Of the 32\% of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile, nearly 20 hours (see \cref{tab:distribution_duration}).
-You see a similar picture when it comes to the proportion of time spent online consuming pornography-the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).
+You see a similar picture when it comes to the proportion of time spent online consuming pornography---the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).
 
@@
 9 minutes, see \cref{fig:concentration_porn_consumption}).
-Close to 80 percent of the traffic to pornographic sites is to just one pornographic site.
-Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male (see, for instance, Panel B of \cref{tab:characteristics_split_by_porn_consumers}).
+Close to 80 percent of the traffic to pornographic sites is to just one pornographic site (\cref{fig:concentration_porn_consumption_topX_by_party}).
+
+Looking at the characteristics of consumers of pornography in Panel B of \cref{tab:characteristics_split_by_porn_consumers}, expectedly, consumers of pornography online are younger and are more likely to be male.
+In addition, consumers of pornography are no different in terms of party identification.
+The mean in the 7-point scale in party identification is identical, with a mean of 3.6 and a standard deviation of 2.2, for both consumers and non-consumers of pornography.
+Treating party identification as subgroups (Republicans, Independents, Democrats) does not change this lack of difference in party identification between consumers and non-consumers (see also \cref{fig:consume_porn_yes_no}).
+This foreshadows the systematic lack of partisan differences in consumption of pornography online we find below.
 
@@
 
-Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
-(In \ref{si:visits}, we analyze similar metrics for visits.
-The upshot is that the key conclusions are unaffected.)
+%===========================
+% Quantile regressions
+% Hours spent on adult sites
+%===========================
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
+	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+		See \cref{tab:regtab_quantile_reg_duration_adult} for a numerical report of the estimates.
+	}
+	\label{fig:quantile_regression_duration}
+\end{figure}
+
+%========================================
+% Quantile regressions
+% Proportion of time spent on adult sites
+%========================================
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
+	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
+		See \cref{tab:regtab_quantile_reg_proportion_duration_adult} for a numerical report of the estimates.
+	}
+	\label{fig:quantile_regression_prop_duration}
+\end{figure}
 
 Given the skew in the data, we ran a quantile regression, regressing the duration on party.
-As Figures \ref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs.
+As \cref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs.
 For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively.
 In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{
-
 We analyze the consumption of pornography online among independents in \cref{si:independents}.
@@
 
-Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \ref{fig:quantile_regression_prop_duration}).
+Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \cref{fig:quantile_regression_prop_duration}).
 The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).
@@
 To what extent are the results "explained" by the confounding demographic differences between the parties?
-To learn that, we control for immutable characteristics like age and gender.
+To learn that, we control for immutable characteristics like age, gender, level of education qualification, race, and region.
 (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
-As Figure \ref{fig:quantile_regression_duration} shows, once you adjust for confounders, the partisan differences melt away.
-
-%===========================
-
-% Quantile regressions
-
-% Hours spent on adult sites
-
-%===========================
-
-\begin{figure}[t]
-
-	\centering
-
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
-
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
-
-	\caption*{\footnotesize \emph{Notes:}
-
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-
-		95\% confidence intervals constructed from standard errors.
-
-		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
-
-	}
-
-	\label{fig:quantile_regression_duration}
-
-\end{figure}
-
-%========================================
-
-% Quantile regressions
-
-% Proportion of time spent on adult sites
-
-%========================================
-
-\begin{figure}[t]
-
-	\centering
-
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
-
-	\caption*{\footnotesize \emph{Notes:}
-
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-
-		95\% confidence intervals constructed from standard errors.
-
-		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
-
-	}
-
-	\label{fig:quantile_regression_prop_duration}
-
-\end{figure}
+As \cref{si:confounders} shows, once you adjust for confounders, the partisan differences melt away.\footnote{Using an alternative machine learning classifier of domains in \cref{si:alternate_ways} and alternative measures of pornography consumption (using traffic to pornographic sites) in \cref{si:visits} does little to change our conclusions.}
 
@@
 It is also considered problematic from a religious perspective.
-For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}} The Internet has dramatically increased access to pornography.
+For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}.} The Internet has dramatically increased access to pornography.
 This has led to the concern that pornography consumption has become very widespread and extensive.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 pornographic sites that individuals visit in the sample period.
+		Table shows the top 25 pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
 		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
@@
 		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
+		See \cref{fig:top25_nonadult} for top non-pornographic domains.
 	}
@@
 	\centering
-	\caption{Top 25 (Non-Porn) Domains}
+	\caption{Top 25 (Non-Pornographic) Domains}
 	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 non-pornographic sites that individuals visit in the sample period.
+		Table shows the top 25 non-pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
 		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
@@
 		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
+		See \cref{fig:top25_nonadult} for top non-pornographic domains.
 	}
@@
 		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
+		Observations are at the individual-domain level (N = 2,437) for pornography sites and individuals who consume pornography online.
 		The Others bar indicates traffic to all other pornographic sites outside of the top 10.
@@
 		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
+		Observations are from the 256 individuals with party identification (Republicans or Democrats) who consume pornography online.
 		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period (n = 353).
 		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
+		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period (n = 353).
 		See \cref{tab:distribution_duration} for the distribution in terms of hours.
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
 		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
+		See \cref{tab:distribution_duration_party_untruncated} including non-consumers of pornography.
 		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
 		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
+		See \cref{tab:distribution_prop_duration_party_untruncated} including non-consumers of pornography.
 		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
@@
 
+%===========================================================================
+% Tabulated splits by party and by percentiles for hours spent on adultsites
+% Full sample
+%===========================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Consumption of Pornography Online by Party\\ (Including non-consumers)}
+	\label{tab:distribution_duration_party_untruncated}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party_untruncated.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Sample includes 834 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
+		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
+		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.37, rejecting the null that the Republican and Democrat distributions are the same.
+		%See \cref{fig:distribution_duration_party} for the plot.
+	}
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
+% Full sample
+%===============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party \\(Including non-consumers)}
+	\label{tab:distribution_prop_duration_party_untruncated}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party_untruncated.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		Sample includes 834 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
+		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
+		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.6, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
+		%See \cref{fig:distribution_prop_duration_party} for the plot.
+	}
+\end{table}
+
 \FloatBarrier
 \clearpage
-\subsubsection{Accounting for Confounders}
+\subsubsection{Accounting for Confounders}\label{si:confounders}
 %==============================================================================
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
+		Table shows splits by party for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
+		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
+		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
+		52 of the 65 are partisans, so in later analyses the sample of partisans drop from the 886 to 834.
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
+		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
 		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel. 
 		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
+		52 of the 65 are partisans, so in later analyses the sample of partisans drop from the 886 to 834.
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
+		Table shows splits by party for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
 		This table focuses on differences in medians.
@@
 \end{table}
+
+%============================
+% Regression table
+% Dependent variable is hours
+%============================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in Hours Spent on Pornographic Sites}
+	\label{tab:regtab_quantile_reg_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_quantile_reg_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions. 
+		Dependent variable is the number of hours of pornography consumption online by individuals.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:quantile_regression_duration} for a plot of the quantile estimates for the Republican coefficient.
+		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for estimates controlling for individual characteristics.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
+	}
+\end{table}
+
+%======================================
+% Regression table
+% Dependent variable is percentage time
+%======================================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
+	\label{tab:regtab_quantile_reg_proportion_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_quantile_reg_proportion_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions. 
+		Dependent variable is the percentage of time individuals spend on pornography consumption online.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:quantile_regression_prop_duration} for a plot of the quantile estimates for the Republican coefficient.
+		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for estimates controlling for individual characteristics.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
+	}
+\end{table}
+
 %=====================================================
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
+		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for a numerical report of the estimates.
 	}
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
@@
 		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
+		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for a numerical report of the estimates.
 	}
@@
 \end{figure}
-\clearpage
+
+%============================
+% Regression table
+% Dependent variable is hours
+% w/ covariates
+%============================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
+	\label{tab:regtab_quantile_reg_covariates_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_quantile_reg_covariates_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions. 
+		Dependent variable is the number of hours of pornography consumption online by individuals.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:quantile_regression_duration_covariates} for a plot of the quantile estimates for the Republican coefficient.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
+	}
+\end{table}
+
+%======================================
+% Regression table
+% Dependent variable is percentage time
+% w/ covariates
+%======================================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
+	\label{tab:regtab_quantile_reg_covariates_proportion_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_quantile_reg_covariates_proportion_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions. 
+		Dependent variable is the percentage of time individuals spend on pornography consumption online.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:quantile_regression_prop_duration_covariates} for a plot of the quantile estimates for the Republican coefficient.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
+	}
+\end{table}
 
@@
 % Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
+% Piedomains classification
 %===============================================================================
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Classificationo of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
 		See \cref{tab:piedomains_distribution_prop_duration_party} for the corresponding distribution in terms of percentage of time. 
@@
 		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Classificationo of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of percentage of time.
+		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
+		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of hours.
 		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.19, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
 		%See \cref{fig:distribution_prop_duration_party} for the plot.
+	}
+\end{table}
+
+%===========================
+% Quantile regressions
+% Hours spent on adult sites
+% Piedomains
+%===========================
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
+	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:piedomains_quantile_reg_covariates_duration_adult} for the same plot controlling for individual characteristics.
+		See \cref{tab:regtab_piedomains_quantile_reg_duration_adult} for a numerical report of the estimates.
+	}
+	\label{fig:piedomains_quantile_reg_duration_adult}
+\end{figure}
+
+%========================================
+% Quantile regressions
+% Proportion of time spent on adult sites
+% Piedomains
+%========================================
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
+	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:piedomains_quantile_reg_covariates_proportion_duration_adult} for the same plot controlling for individual characteristics.
+		See \cref{tab:regtab_piedomains_quantile_reg_proportion_duration_adult} for a numerical report of the estimates.
+	}
+	\label{fig:piedomains_quantile_reg_proportion_duration_adult}
+\end{figure}
+
+%============================
+% Regression table
+% Dependent variable is hours
+% Piedomains
+%============================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in Hours Spent on Pornographic Sites}
+	\label{tab:regtab_piedomains_quantile_reg_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_piedomains_quantile_reg_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Dependent variable is the number of hours of pornography consumption online by individuals.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:piedomains_quantile_reg_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
+		See \cref{tab:regtab_quantile_reg_duration_adult} for estimates using the YouGov classification.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
+	}
+\end{table}
+
+%======================================
+% Regression table
+% Dependent variable is percentage time
+% Piedomains
+%======================================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
+	\label{tab:regtab_piedomains_quantile_reg_proportion_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_piedomains_quantile_reg_proportion_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Dependent variable is the percentage of time individuals spend on pornography consumption online.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:piedomains_quantile_reg_proportion_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
+		See \cref{tab:regtab_quantile_reg_proportion_duration_adult} for estimates using the YouGov classification.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
+	}
+\end{table}
+
+\FloatBarrier
+\subsubsection{Accounting for Confounders}
+%=====================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (with covariates) 
+% Piedomains
+% w/ covariates
+%=====================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{tab:regtab_piedomains_quantile_reg_covariates_duration_adult} for a numerical report of the estimates.
+	}
+	\label{fig:piedomains_quantile_reg_covariates_duration_adult}
+\end{figure}
+
+%========================================
+% Quantile regressions
+% Proportion of time spent on adult sites
+% Piedomains
+% w/ covariates
+%========================================
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
+	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{tab:regtab_piedomains_quantile_reg_covariates_proportion_duration_adult} for a numerical report of the estimates.
+	}
+	\label{fig:piedomains_quantile_reg_covariates_proportion_duration_adult}
+\end{figure}
+
+%============================
+% Regression table
+% Dependent variable is hours
+% Piedomains
+% \w covariates
+%============================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
+	\label{tab:regtab_piedomains_quantile_reg_covariates_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_piedomains_quantile_reg_covariates_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Dependent variable is the number of hours of pornography consumption online by individuals.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:piedomains_quantile_reg_covariates_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
+		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for estimates using the YouGov classification.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
+	}
+\end{table}
+
+%======================================
+% Regression table
+% Dependent variable is percentage time
+% Piedomains
+% w/ covariates
+%======================================
+\begin{table} \centering \small \setlength\tabcolsep{0 pt}
+	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
+	\label{tab:regtab_piedomains_quantile_reg_covariates_proportion_duration_adult}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
+			\toprule
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
+			\cmidrule{3-21}
+			&&\multicolumn{19}{c}{Quantile regressions}\\
+			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
+			\cmidrule(l){2-21}
+			\input{../tabs/regtab_piedomains_quantile_reg_covariates_proportion_duration_adult.tex}\\
+			\bottomrule
+		\end{tabular}{\tiny }
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:} 
+		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		Dependent variable is the percentage of time individuals spend on pornography consumption online.
+		All models have N = 834; only partisans are included in the sample.
+		Baseline category is Democrats.
+		See \cref{fig:piedomains_quantile_reg_covariates_proportion_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
+		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for estimates using the YouGov classification.
+		Standard errors in parentheses.
+		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
 	}
@@
 		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Column (1) includes Democrats (n = 154).
-		Column (2) includes Republicans (n = 95).
-		Column (3) includes both Republicans and Democrats (n = 249).
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) includes Republicans (n = 95).		
+		Column (2) includes Democrats (n = 154).
+		Column (3) includes both individuals from columns (1) and (2)---the Republicans and Democrats (n = 249).
 		Column (4) includes Independents (n = 67).
@@
 		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Column (1) includes Democrats (n = 154).
-		Column (2) includes Republicans (n = 95).
-		Column (3) includes both Republicans and Democrats (n = 249).
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) includes Republicans (n = 95).
+		Column (2) includes Democrats (n = 154).
+		Column (3) includes both individuals from columns (1) and (2)---the Republicans and Democrats (n = 249).
 		Column (4) includes Independents (n = 67).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
+		Figure shows the number of visits to pornography sites by the 361 individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of visits to pornography sites by individuals who consumed pornography in the sample period.
+		Figure shows the proportion of visits to pornography sites by the 361 individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
@@
 	\centering
-	\caption{Quantile Estimates--Traffic to Pornography Sites by Party}
+	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites}
 	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Sample includes 834 individuals identified as either Republicans or Democrats.
 		95\% confidence intervals constructed from standard errors.
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party}
+	\caption{Distribution of Partisan Differences in the Percentage of Visits to Pornographic Sites}
 	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
@@
 	\centering
-	\caption{Quantile Estimates--Traffic to Pornographic Sites by Party (with covariates)}
+	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites (Conditional on Covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_visits_adult.pdf}
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party (with covariates)}
+	\caption{Distribution of Partisan Differences in the Percentage of Visits to Pornographic Sites (Conditional on Covariates)}
 	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}

### 2023-01-08 ms/adult.tex
Fix typo
Fix typo with KS hypothesis test

@@
 		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.37, rejecting the null that the Republican and Democrat distributions are the same.
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.37, failing to reject the null that the Republican and Democrat distributions are the same.
 		%See \cref{fig:distribution_duration_party} for the plot.
@@
 		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.6, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.6, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
 		%See \cref{fig:distribution_prop_duration_party} for the plot.

### 2023-01-08 scripts/01_pred_porn/03_shalla_pred_porn.R
take out irrelevant scripts

@@ -1,89 +1,0 @@
-"
-
-Aim: 
-Predict YG Domains using saved model
-Author: Gaurav Sood
-
-"
-
-# Load libs 
-# devtools::install_github("soodoku/domain_classifier/rdomains")
-# devtools::install_github("soodoku/goji")
-
-library(goji)
-library(rdomains)
-
-# Set dir
-ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
-setwd("web_analysis/")
-
-# YG Dat
-# -----------------
-# Load YG Data
-load("data/yg/unique_domains/unique_domains.Rdata")
-
-# Get ML cat
-ml_cat <- name_suffix_cat(unique.domains)
-ml_cat$ml_porn <- (ml_cat$category > .5)*1
-
-# Get shalla cat
-sh_cat <-  shalla_cat(unique.domains)
-sh_cat$shalla_porn <- (sh_cat$shalla_category == "porn")*1
-sh_cat$shalla_porn <- nona(sh_cat$shalla_porn)
-
-# Add shalla cat
-ml_cat$shalla_porn <- sh_cat$shalla_porn[match(ml_cat$domain_name, sh_cat$domain_name)]
-
-# Subset
-ml_cat <- subset(ml_cat, select=c("domains", "ml_porn", "shalla_porn")) 
-
-write.csv(ml_cat, file="data/yg/unique_domains/unique_domains_category_shalla_ml.csv", row.names=F)
-
-# ComScore 2013
-# ---------------------
-
-# Load YG Data
-load("data/comscore/unique_domains/cs13_unique_domain_names.rda")
-
-# Get ML cat
-#ml_cat <- name_suffix_cat(cs13_unique_domain_names)
-#ml_cat$ml_porn <- (ml_cat$category > .5)*1
-
-# Get shalla cat
-sh_cat <-  shalla_cat(cs13_unique_domain_names)
-sh_cat$shalla_porn <- (sh_cat$shalla_category == "porn")*1
-sh_cat$shalla_porn <- nona(sh_cat$shalla_porn)
-
-# Add shalla cat
-#ml_cat$shalla_porn <- sh_cat$shalla_porn[match(ml_cat$domains, sh_cat$domain_name)]
-
-# Subset
-#ml_cat <- subset(ml_cat, select=c("domains", "ml_porn", "shalla_porn")) 
-
[…]

### 2023-01-08 scripts/02_yg_survey/00_prep_data.R

@@ -1,35 +1,0 @@
-# rm(list=ls(all=TRUE))
-
-library(dplyr)
-
-names(indiv)
-names(s)
-head(s)
-
-### 1. LOAD INDIVIDUAL-LEVEL DATA WITH WEIGHTS (see raking_weights.R) ###
-
-ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
-setwd("web analysis/")
-
-porn.indiv <- select(wakoopa, category, pmxid, duration, domain, used_at) %>%
-  mutate(porn = ifelse(category == "Adult", 1, 0)) %>%
-  group_by(pmxid) %>%
-  arrange(pmxid)
-
-# load data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
-indiv <- read.csv("data/yg/indiv_level_weighted_2016.csv", stringsAsFactors = FALSE)
-
-# load porn domains from Shallalist
-shalla <- readLines("data/measure_porn/shalla_porn_list/domains.txt")
-length(shalla)
-
-#sapply(shalla, function(x) { if(length(which(porn.indiv$domain %in% x)) > 0) { porn.indiv[which(porn.indiv$domain %in% x),]$porn <- 1 }})
-
-### 2. GENERATE DVs ###
-
-# Visited any porn? 1/0
-porn.indiv.1 <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) max(x, na.rm = TRUE))))
-porn.indiv.1 <- ifelse(porn.indiv.1 < 0, 0, porn.indiv.1)
-
-# Number of porn sites visited
-porn.indiv.n <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) sum(x, na.rm = TRUE))))

### 2023-01-08 scripts/02_yg_survey/01a_raking_weights.R

@@ -1,147 +1,0 @@
-# YouGov UK weights Wakoopa data by age, gender, region (by Internet representativeness)
-# see: http://sebadaza.com/survey/2012/08/25/raking/
-
-library(dplyr)
-library(weights)
-library(anesrake)
-
-setwd("~/Dropbox/web analysis/data/yg/wakoopa/")
-demos <- read.csv("wakoopa_demos.csv", stringsAsFactors = FALSE)
-load("wakoopa_fullcat.RData")
-head(wakoopa)
-
-s <- distinct(select(wakoopa, pmxid, birthyr, gender, educ, race5, ideo5, pid3))
-s <- merge(s, demos, by = "pmxid", all.x = TRUE)
-head(s)
-
-# YouGov codes, direct from Q wording:
-state.names <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "District of Columbia", "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina",
-                "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", "American Samoa", "Federated States of Micronesia", "Guam", "Marshall Islands", "Northern Mariana Islands", "Palau", "Puerto Rico", "U.S. Minor Outlying Islands", "Virgin Islands", "Alberta", "British Columbia", "Manitoba", "New Brunswick", "Newfoundland", "Northwest Territories", "Nova Scotia", "Nunavut", "Ontario", "Prince Edward Island", "Quebec", "Saskatchewan", "Yukon Territory", "Not in the U.S. or Canada")
[…]

### 2023-01-08 scripts/02_yg_survey/02_results.R

@@ -1,241 +1,0 @@
-# rm(list=ls(all=TRUE))
-library(dplyr)
-
-### THIS FILE: Run models & report tables + graphs.
-
-#############################################
-### 0. PREP #################################
-#############################################
-
-# Set dir
-ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
-setwd("web analysis/")
-
-# load data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
-# DVs already coded in code/yg/porn_analysis.R
-indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode2.csv", stringsAsFactors = FALSE) # latest coding 3/29/16
-indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode_shalla1.csv", stringsAsFactors = FALSE) # latest coding 4/4/16 using Shallalist
-
-# relevel as needed:
-indiv$ideo5 <- factor(indiv$ideo5) # factorize
-indiv$ideo5 <- relevel(indiv$ideo5, "moderate") # moderate = base category
-indiv$ideo5 <- relevel(indiv$ideo5, "dk") # "dk" = base category
-#indiv$ideo5 <- relevel(indiv$ideo5, "liberal")
-
-indiv$pid3 <- factor(indiv$pid3)
-indiv$pid3 <- relevel(indiv$pid3, "ind") # independent = base category
-#indiv$pid3 <- relevel(indiv$pid3, "dem")
-head(indiv)
-
-
-
-#################################################
-### 1. MODELS ###################################
-#################################################
-
-### Test for overdispersion ###
-library(qcc)
-qcc.overdispersion.test(indiv$porn.indiv.n) # definitely overdispersed; use quasi-Poisson for count data
-
-### Dichotomous DV (visited porn 1/0) ###
-
-# ideology predictor
-summary(lm(porn.indiv.1 ~ ideo5 + age + gender, data = indiv, weights = weights))
-summary(lm(porn.indiv.1 ~ ideo5 + age + gender - 1, data = indiv, weights = weights)) # sans intercept
-summary(lm(porn.indiv.1 ~ ideo5 + age + gender + married, data = indiv, weights = weights))
-summary(lm(porn.indiv.1 ~ ideo5 + age + gender + married - 1, data = indiv, weights = weights))
[…]

### 2023-01-08 scripts/02_yg_survey/porn_analysis.R

@@ -1,278 +1,0 @@
-# rm(list=ls(all=TRUE))
-# porn.indiv <- select(wakoopa, category, duration, pmxid) %>%
-#   mutate(porn = ifelse(category == "Adult", 1, 0)) %>%
-#   group_by(pmxid) %>%
-#   arrange(pmxid)
-#   #ungroup() %>%
-#   #group_by(pmxid) %>%
-#   #summarise(numporn = sum())
-# 
-# porn.indiv.1 <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) max(x, na.rm = TRUE))))
-# porn.indiv.1 <- ifelse(porn.indiv.1 < 0, 0, porn.indiv.1)
-# porn.indiv.n <- as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) sum(x, na.rm = TRUE))))
-# pct_visits_on_porn <- round(as.vector(with(porn.indiv, tapply(porn, pmxid, function(x) mean(x, na.rm = TRUE)))), digits = 2)
-
-# 
-# head(porn.indiv)
-# head(porn.indiv.1)
-# head(porn.indiv.n)
-# head(s)
-# 
-# indiv <- cbind(s, porn.indiv.1, porn.indiv.n, pct_visits_on_porn)
-# write.csv(indiv, "data/indiv_level_weighted.csv")
-
-### ADDING DURATION MEASURES -ag ###
-# 
-# porn.indiv$porn <- ifelse(is.na(porn.indiv$porn), 0, porn.indiv$porn)
-# 
-# porn.duration <- select(porn.indiv, pmxid, porn, duration) %>%
-#   group_by(pmxid, porn) %>%
-#   summarize(total_duration = sum(duration))
-# porn.duration <- filter(porn.duration, porn == 1) # this gives us the total duration of porn visits, if exist
-# 
-# porn.denom <- select(porn.indiv, pmxid, duration) %>%
-#   group_by(pmxid) %>%
-#   summarize(denom = sum(duration)) # total duration of ALL visits for each pmxid
-# 
-# total_time_on_porn <- sapply(indiv$pmxid, function(x) ifelse(x %in% porn.duration$pmxid, porn.duration[which(porn.duration$pmxid %in% x),]$total_duration, 0))
-# pct_time_on_porn <- round(total_time_on_porn/porn.denom$denom, digits = 2)
-# 
[…]

### 2023-01-08 scripts/03_pred_pid/01 predict_pid.R

@@ -1,196 +1,0 @@
-# rm(list=ls(all=TRUE))
-
-"
-
-Predicting PID
-
-1. Limit yourself to political domains + sociodem. categorized in same way as comScore (see data/cs)
-2. Aggregate domain level visitation up to person level
-3. PID_3 ~ agg_domain + sociodem.
-
-AG DETAILS:
-
-Comparing models:
-1) include non-political sites (filtering out mail, facebook, porn, points/benefits sites) + demos
-2) filter using only sites predicted to be political/news-related (predicted to be political using ML based on Shallalist & comScore)
-3) both of above using proportions (% total visits per respondent) rather than counts
-4) demos only for comparison
-5) web visits only (counts)
-
-"
-
-# Set dir
-ifelse(grepl("Gaurav", getwd()), setwd(basedir), setwd("/Users/aguess/Dropbox/"))
-setwd("web analysis/")
-
-## Load packages
-library(dplyr)
-
-## Load indiv-level data -- weights generated in code/yg/raking_weights.R -- raked using age, gender, race, PID, & region
-indiv <- read.csv("data/yg/porn_indiv_level_weighted_2016_recode_shalla1.csv", stringsAsFactors = FALSE)
-load("data/yg/wakoopa/wakoopa_fullcat.RData")
-
-
-## Remove URLs for email, FB, porn
-
-# Code for email/FB visits (Is this sufficient?)
-wakoopa$mail <- (grepl("hotmail", wakoopa$url, fixed = TRUE) | grepl("mail.yahoo", wakoopa$url, fixed = TRUE) | grepl("gmail", wakoopa$url, fixed = TRUE) | grepl("mail.google", wakoopa$url, fixed = TRUE) | grepl("outlook.com", wakoopa$url, fixed = TRUE) | grepl("email.", wakoopa$url, fixed = TRUE)) * 1
-wakoopa$fb <- grepl("facebook.com", wakoopa$url, fixed = TRUE) * 1
-
-# If filtering by politics: Get news_domains -- predicted political/news domains using both shalla & comScore data
-news_domains <- read.csv("data/yg/predict_pid/keep_domains_shalla_cs.csv", stringsAsFactors = FALSE)
-news_domains <- news_domains$x
-
-visits <- select(wakoopa, pmxid, pid3, domain, category, subcategory, mail, fb) %>%
-  filter(category != "Adult") %>%
[…]

### 2023-01-08 scripts/04_comscore/by_domain_cat/script_for_each_machineid_date_base_on_category.py

@@ -1,104 +1,0 @@
-import time
-
-URL_CATEGORY_FILE = "url_category.csv"
-CATEGORY="Pornography"
-INTERNET_USAGE_FILE = "../../../web_browsing_2004" #"8bdff911e30b975c.csv"#
-FINAL_OUTPUT_FILE = "final_output_by_machineid_date.csv"
-
-
-FINAL_OUTPUT_HEADER = "machine_id, date, total_pages_viewed, total_time_spent, total_domain_category_pages_viewed, total_domain_category_time_spent"
-
-#############################READ DOMAIN LIST FILE#######################################
-DOMAIN_LIST = []
-print "Read the url category file %s" %(URL_CATEGORY_FILE,)
-with open(URL_CATEGORY_FILE) as myfile:
-        firstline = True
-        for line in myfile:
-            if firstline:
-                firstline = False
-                continue
-            line = line.strip().replace("\n","")
-            domain = line.split(',')[0]
-            category = line.split(',')[1]
-            if (len(domain)!=0 and category.lower()==CATEGORY.lower()):
-                DOMAIN_LIST.append(domain)
-print "Lengnth domain list  = %s\n" %(len(DOMAIN_LIST),) 
-
-###############################START PROCESSING DATA#####################################
-print "Start processing the data file %s" %(INTERNET_USAGE_FILE,)
-
-my_output_file = open(FINAL_OUTPUT_FILE,"w")
-my_output_file.write(FINAL_OUTPUT_HEADER + "\n")
-    
-fist_line = True
-prev_machine_id = -1
-DATA_BY_DATE = {}
-count = 0
-prev_timer = time.time()
-DOMAIN_LIST = set(DOMAIN_LIST)
-with open(INTERNET_USAGE_FILE) as myfile:
-    for line in myfile:
-        # Monitor the progress
-        count = count + 1
-        if (count%1000000==0):
-            now = time.time()
-            difference = int(now - prev_timer)
-            print "   + Processing line %s.000.000th time_till_now=%s(s)"%(count/1000000,difference,)
-        
-        if fist_line: # Skip the first row
-            fist_line = False
-        else:
-            # Extract data in a row
-            datas = line.split(",")
-            domain = datas[1]
-            if len(datas)==9:
-                machine_id = datas[3]
-                pages_viewed = int(float(datas[6]))
-                duration = int(float(datas[5]))
-                date =  datas[7]
-            elif len(datas)==8:
-                machine_id = datas[2]
[…]

### 2023-01-08 scripts/04_comscore/by_domain_list/script_for_each_machineid_date_domain.py

@@ -1,119 +1,0 @@
-import time
-
-DOMAIN_LIST_FILE = "porn_domains_list.txt" #"website_list_gentzkow_shapiro.txt"#
-INTERNET_USAGE_FILE = "../../web_browsing_2004" #"8bdff911e30b975c.csv"#
-FINAL_OUTPUT_FILE = "final_output_each_machineid_date_domain.csv"
-
-FINAL_OUTPUT_HEADER = "machine_id, date, total_pages_viewed, total_time_spent, total_pages_viewed_porn_domains, total_time_spent_porn_domains"
-USE_DOMAIN_LIST_FILE = True
-
-#############################READ DOMAIN LIST FILE#######################################
-DOMAIN_LIST = []
-if USE_DOMAIN_LIST_FILE and len(DOMAIN_LIST_FILE)>0:
-    print "Read the domain list file %s" %(DOMAIN_LIST_FILE,)
-    with open(DOMAIN_LIST_FILE) as myfile:
-        for line in myfile:
-            DOMAIN_LIST.append(line.strip().replace("\n",""))
-    print "Lengnth domain list  = %s\n" %(len(DOMAIN_LIST),)
-        
-# Add additional column into FINAL_OUTPUT_HEADER 
-for i in range(len(DOMAIN_LIST)):
-    FINAL_OUTPUT_HEADER = FINAL_OUTPUT_HEADER + ", domain_%s_pages_viewed, domain_%s_time_spent"%(i+1,i+1,)
-
-my_output_file = open(FINAL_OUTPUT_FILE,"w")
-my_output_file.write(FINAL_OUTPUT_HEADER + "\n")
-
-###############################START PROCESSING DATA#####################################
-print "Start processing the data file %s" %(INTERNET_USAGE_FILE,)
-    
-fist_line = True
-prev_machine_id = -1
-DATA_BY_DATE = {}
-count = 0
-prev_timer = time.time()
-usage_each_date_domain={}
-with open(INTERNET_USAGE_FILE) as myfile:
-    for line in myfile:
-        # Monitor the progress
-        count = count + 1
-        if (count%100000==0):
-            now = time.time()
-            difference = int(now - prev_timer)
-            print "   + Processing line %s00.000th time_till_now=%s(s)"%(count/100000,difference,)
-            
-        if fist_line: # Skip the first row
-            fist_line = False
-        else:
-            # Extract data in a row
-            datas = line.split(",")
-            domain = datas[1]
-            if len(datas)==9:
[…]

### 2023-01-08 scripts/05_classify_urls/scrape_urls/python_scraper.py

@@ -1,71 +1,0 @@
-import urllib2
-import requests
-#import re
-import BeautifulSoup
-#import newspaper
-
-# def remove_html_tags(data):
-#      p = re.compile(r'<.*?>')
-#      return p.sub('', data)
-
-num = 0
-with open("unique_urls_100k.txt") as f: #urls_10.txt
-    for url in f:
-    	if num == 6:
-    		break
-    	num = num + 1
-    	url = url.strip("\"\r\n")
-        #print(url)
-        try:
-        	page = requests.get('http://' + url, timeout=1)
-        	page_content = page.text.encode("utf-8")
-        	#page_content = remove_html_tags(page_content) # remove tags
-        	# http://stackoverflow.com/questions/2977893/best-way-to-strip-out-everything-but-text-from-a-webpage
-        	page_content = ''.join(BeautifulSoup.BeautifulSoup(page_content).findAll(text=lambda 
-        		text: text.parent.name != "script" and 
-        		text.parent.name != "style")).encode("utf-8")
-        	with open('text/url'+str(num)+'.txt', 'w') as fid:
-    			fid.write(page_content)
-        except (urllib2.URLError, requests.exceptions.ConnectionError, requests.exceptions.ReadTimeout):
-        	print "Bad URL (" + str(num) + "): " + url
-        
-
-## newspaper test
-
-from newspaper import Article
-article = Article('http://' + url, keep_article_html=True, fetch_images=False)
-
-article.download()
-article.parse()
-
-article.html
-article.text
-
-from newspaper import fulltext
-
-html = requests.get('http://' + url, timeout=1).text.encode("utf-8")
-text = fulltext(html)
-
-## using newspaper (1)
-
-import urllib2
-import requests
-from newspaper import fulltext
-
-num = 0
-with open("unique_urls_100k.txt") as f: #urls_10.txt
-    for url in f:
-        if num == 50:
-            break
-        num = num + 1
-        url = url.strip("\"\r\n")
-        #print(url)
-        try:
-            page = requests.get('http://' + url, timeout=1)
-            page_content = page.text.encode("utf-8")
-            text = fulltext(page_content)
-            with open('text/url'+str(num)+'.txt', 'w') as fid:
-                fid.write(text)
-        except: # (urllib2.URLError, requests.exceptions.ConnectionError, requests.exceptions.ReadTimeout): #, requests.exceptions.ReadTimeout
-            print "Bad URL (" + str(num) + "): " + url
-        

### 2023-01-08 scripts/05_classify_urls/scrape_urls/scrape_pages_scratch.R

@@ -1,52 +1,0 @@
-setwd("/Users/aguess/Dropbox/web analysis/data/yg")
-load("unique_urls.RData")
-urls100 <- read.csv("unique_urls_100k.txt", stringsAsFactors = FALSE)
-urls100 <- urls100$us.mg6.mail.yahoo.com.neo.launch..rand.7hej9u1h3rnn2.6463884649
-
-writeLines(urls100[1:10,1], "urls_10.txt")
-
-head(urls100)
-urls100[1,1]
-urls100[10,1]
-
-dim(unique.urls)
-head(unique.urls)
-unique.urls$unique.urls[2200000]
-
-
-library(RCurl)
-library(rvest)
-
-#page <- readLines(paste0("http://", urls100[1,1]))
-page <- getURL(paste0("http://", urls100[1,1]), .opts=curlOptions(followlocation=TRUE))
-writeLines(page, "url.txt")
-
-page <- html_session(paste0("http://", urls100[1,1]))
-page %>% html_nodes("p") %>% html_text()
-
-download.file()
-
-# https://cran.r-project.org/web/packages/boilerpipeR/index.html
-library(boilerpipeR)
-
-url <- "blog.rstudio.org/2014/05/09/reshape2-1-4/"
-page <- getURL(paste0("http://", url), .opts=curlOptions(followlocation=TRUE))
-maintext <- ArticleExtractor(page, asText = TRUE)
-
-sink()
-cat(maintext)
-sink()
-
-writeLines(maintext, "text/urltest.txt")
-
-setwd("/Users/aguess/Documents/Columbia/Dissertation/jmp2/scrape_pages/text")
-for(i in 44:100) { #length(urls100)
-  
-  page <- ""
-  url <- urls100[i]
-  try(page <- getURL(paste0("http://", url), .opts=curlOptions(followlocation=TRUE, timeout=1, maxredirs=20)), silent = TRUE)
-  try(maintext <- ArticleExtractor(page, asText = TRUE), silent = TRUE)
-  
-  writeLines(maintext, paste0("url_", i, ".txt"))
-  
-}

### 2023-01-08 scripts/05_classify_urls/scrape_urls/scrape_urls.R

@@ -1,31 +1,0 @@
-#!/usr/bin/env Rscript
-args = commandArgs(trailingOnly=TRUE)
-
-library(boilerpipeR)
-library(RCurl)
-
-setwd("~/scrape_urls")
-
-a1 <- as.numeric(args[1])
-a2 <- as.numeric(args[2])
-a3 <- args[3]
-
-urls100 <- readLines("unique_urls.txt") # , stringsAsFactors = FALSE
-urls100 <- urls100[a1:a2]
-urls100 <- gsub("\"", "", urls100)
-#print(dim(urls100))
-
-setwd(a3)
-for(i in 1:length(urls100)) { #length(urls100)  11655 23069 33000 34176
-  
-  page <- ""
-  url <- urls100[i]
-  try(page <- getURLContent(paste0("http://", url), .opts=curlOptions(followlocation=TRUE, timeout=2, maxredirs=20)), silent = TRUE)
-  try(maintext <- ArticleExtractor(page, asText = TRUE), silent = TRUE)
-  
-  writeLines(maintext, paste0("url_", i, ".txt"))
-  
-}
-
-print(i)
-

### 2023-01-08 scripts/05_classify_urls/scrape_urls/scraper.R

@@ -1,23 +1,0 @@
-library(boilerpipeR)
-library(RCurl)
-
-setwd("~/Documents/prn_project/data")
-#load("unique_urls.RData")
-urls100 <- readLines("unique_urls_100k.txt") # , stringsAsFactors = FALSE
-#urls100 <- urls100$us.mg6.mail.yahoo.com.neo.launch..rand.7hej9u1h3rnn2.6463884649
-head(urls100)
-tail(urls100)
-
-urls100 <- gsub("\"", "", urls100)
-
-setwd("text_try3")
-for(i in 1:34175) { #length(urls100)  11655 23069 33000 34176
-  
-  page <- ""
-  url <- urls100[i]
-  try(page <- getURLContent(paste0("http://", url), .opts=curlOptions(followlocation=TRUE, timeout=2, maxredirs=20)), silent = TRUE)
-  try(maintext <- ArticleExtractor(page, asText = TRUE), silent = TRUE)
-  
-  writeLines(maintext, paste0("url_", i, ".txt"))
-  
-}

### 2023-01-08 scripts/cat_domains.R

@@ -1,48 +1,0 @@
-"
-
-Get category of domains
-"
-
-# Load the libs 
-library(data.table)
-library(rdomains)
-library(dplyr)
-
-# general function
-
-gen_cat <- function(file_name = NULL ) {
-
-	domains          <- fread(file_name)
-	domains_shalla   <- shalla_cat(domains$x)
-	domains_ml1_porn <- adult_ml1_cat(domains$x)
-
-	# Join 
-	domains_cat      <- inner_join(domains_shalla, domains_ml1_porn)
-	domains_cat
-}
-
-# 2002
-# ---------------------
-cs2002_cat <- gen_cat("cs2002_unique_domains")
-write.csv(cs2002_cat, file="cs2002_unique_domains_shalla_ml1_porn.csv", row.names=F)
-
-cs2004_cat <- gen_cat("cs2004_unique_domains")
-write.csv(cs2004_cat, file="cs2004_unique_domains_shalla_ml1_porn.csv", row.names=F)
-
-cs2008_cat <- gen_cat("cs2008_unique_domains")
-write.csv(cs2008_cat, file="cs2008_unique_domains_shalla_ml1_porn.csv", row.names=F)
-
-cs2009_cat <- gen_cat("cs2009_unique_domains")
-write.csv(cs2009_cat, file="cs2009_unique_domains_shalla_ml1_porn.csv", row.names=F)
-
-cs2010_cat <- gen_cat("cs2010_unique_domains")
-write.csv(cs2010_cat, file="cs2010_unique_domains_shalla_ml1_porn.csv", row.names=F)
-
-cs2011_cat <- gen_cat("cs2011_unique_domains")
-write.csv(cs2011_cat, file="cs2011_unique_domains_shalla_ml1_porn.csv", row.names=F)
-
-cs2012_cat <- gen_cat("cs2012_unique_domains")
-write.csv(cs2012_cat, file="cs2012_unique_domains_shalla_ml1_porn.csv", row.names=F)
-
-cs2013_cat <- gen_cat("cs2013_unique_domains")
-write.csv(cs2013_cat, file="cs2013_unique_domains_shalla_ml1_porn.csv", row.names=F)

### 2023-01-08 scripts/comscore_demographics_summarize.R

@@ -1,85 +1,0 @@
-"
-Summarize comscore demographic data
-
-"
-
-# Set dir. 
-setwd(basedir)
-setwd("adult")
-
-# Recode Function
-# ---------------
-cs_recoder <- function(dat=NULL) {
-
-	dat$hoh_most_education_r <- factor(car::recode(dat$hoh_most_education, 
-												  "0='Less than HS'; 1='HS Diploma or Equivalent'; 2='Some college but no degree'; 3='Associate';4='BS';5='Grad. Degree or Above';c(99, '**')=NA"),
-												  c('Less than HS', 'HS Diploma or Equivalent', 'Some college but no degree', 'Associate', 'BS', 'Grad. Degree or Above'))
-	dat$household_income_r   <- factor(car::recode(dat$household_income,   
-													"1='less Than 15k'; 2='15k--25k'; 3='25k--35k';4='35k--50k';5='50k--75k'; 6= '75k--100k';7 = '100k+'"),
-													c('less Than 15k', '15k--25k', '25k--35k', '35k--50k', '50k--75k', '75k--100k', '100k+'))
-
-	dat$connection_speed_r   <- factor(car::recode(dat$connection_speed,   "1='Broadband'; 0='Not Broadband'"), c('Broadband', 'Not Broadband'))
-	dat$racial_background_r  <- factor(car::recode(dat$racial_background,  "1='White'; 2='Black'; 3='Asian';5='Other';'*'=NA"), c('White', 'Black', 'Asian', 'Other'))
-
-	dat$census_region_r      <- factor(car::recode(dat$census_region,      "'*'=NA; 1='Northeast'; 2='North Central'; 3='South';4='West'"), c('Northeast', 'North Central', 'South', 'West'))
-	dat$country_of_origin_r  <- factor(car::recode(dat$country_of_origin,  "1='Hispanic'; 0='Non-Hispanic'"), c('Hispanic', 'Non-Hispanic'))
-	dat$hoh_oldest_age_r     <- factor(car::recode(dat$hoh_oldest_age,     "1='18--20'; 2='21--24'; 3='25--29';4='30--34';5='35-39'; 6= '40-44';7 = '45-49'; 8 = '50-54'; 9 ='55-59'; 10 ='60-64'; 11='65+'; 99=NA"))
[…]

### 2023-01-08 scripts/comscore_summarize.R

@@ -1,158 +1,0 @@
-"
-
-summarize by machine, domain
-	: total_page_views, total_duration, n_unique_days_machine_visited_site
-
-"
-
-# Set dir. 
-setwd(basedir)
-
-# Load libs 
-library(data.table)
-library(dplyr)
-
-# 2002 --- we have data starting July  (20020701 20021231)
-# -----------------------------------------------------------
-
-# Read in the data 
-cs2002 <- fread("cs2002_by_machine_date_domain.csv")
-
-# Summarize data > per machine_id > per domain > total_time, total_page_views, n_unique_days 
-by_machine_domain <- 
-cs2002 %>%
-group_by(machine_id, domain_name) %>%
-summarise(total_duration=sum(total_duration, na.rm=T), total_pages=sum(total_pages, na.rm=T), site_category_id = mean(site_category_id), n_dates = length(unique(date)))
-
-# Write out
-write.csv(by_machine_domain, file="cs2002_by_machine_domain.csv", row.names=F)
-
-# 2004
-# -----------
-
-# Read in the data
-cs2004 <- fread("cs2004_by_machine_date_domain.csv")
-
-by_machine_domain <- 
-cs2004 %>%
-group_by(machine_id, domain_name) %>%
-summarise(total_duration=sum(total_duration, na.rm=T), total_pages=sum(total_pages, na.rm=T), n_dates = length(unique(event_date)))
-
-# Write out
-write.csv(by_machine_domain, file="cs2004_by_machine_domain.csv", row.names=F)
-
-# 2006
-# -----------
-
-# Read in the data
-cs2006 <- fread("cs2006_by_machine_date_domain.csv")
-
-by_machine_domain <- 
-cs2006 %>%
-group_by(machine_id, domain_name) %>%
-summarise(total_duration=sum(total_duration, na.rm=T), total_pages=sum(total_pages, na.rm=T), n_dates = length(unique(event_date)))
-
-# Write out
-write.csv(by_machine_domain, file="cs2006_by_machine_domain.csv", row.names=F)
-
-# 2007
-# -----------
-
-# Read in the data
-cs2007 <- fread("cs2007_by_machine_date_domain.csv")
-
-by_machine_domain <- 
-cs2007 %>%
-group_by(machine_id, domain_name) %>%
[…]

### 2023-01-08 scripts/cs_join_domain_cat_summarized_dat.R

@@ -1,80 +1,0 @@
-"
-join  unique_domain_cat + 
-summarized by machine, domain
-	: total_page_views, total_duration, n_unique_days_machine_visited_site
-
-"
-
-# Set dir. 
-setwd(basedir)
-
-# Load libs 
-library(data.table)
-library(dplyr)
-
-# 2002 --- we have data starting July  (20020701 20021231)
-# -----------------------------------------------------------
-
-# Read in the data 
-cs2002_machine_domain  <- fread("data/media/comScore/views_duration_by_machine_id_domain/cs2002_by_machine_domain.csv")
-cs2002_domain_cat      <- fread("data/media/comScore/unique_domain_cat/cs2002_unique_domains_shalla_ml1_porn.csv")
-#cs2002_dem <- fread("data/comscore/dem/demographics2002.csv")
-
-cs2002_t <- inner_join(cs2002_machine_domain, cs2002_domain_cat)
-
-cs2002_porn <- 
-cs2002_t %>%
-group_by(machine_id) %>%
-summarise(porn_time = sum(as.numeric(shalla_category=='porn')*as.numeric(total_duration), na.rm=T), porn_views = sum(as.numeric(shalla_category=='porn')*as.numeric(total_pages), na.rm=T))
-
-mean(cs2002_t$shalla_category=='porn', na.rm=T)
-#[1] 0.3929881
-
-median(cs2002_porn$porn_time)
-median(cs2002_porn$porn_views)
-
-
-# Read in the data 
-cs2008_machine_domain  <- fread("data/media/comScore/views_duration_by_machine_id_domain/cs2008_by_machine_domain.csv")
-cs2008_domain_cat      <- fread("data/media/comScore/unique_domain_cat/cs2008_unique_domains_shalla_ml1_porn.csv")
-#cs2002_dem <- fread("data/comscore/dem/demographics2002.csv")
-
-cs2008_t <- inner_join(cs2008_machine_domain, cs2008_domain_cat)
-mean(cs2008_t$shalla_category=='porn', na.rm=T)
-
-cs2008_porn <- 
-cs2008_t %>%
-group_by(machine_id) %>%
-summarise(porn_time = sum(as.numeric(shalla_category=='porn')*as.numeric(total_duration), na.rm=T), porn_views = sum(as.numeric(shalla_category=='porn')*as.numeric(total_pages), na.rm=T))
-
-median(cs2008_porn$porn_time)
[…]

### 2023-10-14 scripts/utils/data_utils.py
Add ind-level data based on vt
Added individual-level data based on the payloads from virustotal. Similar to the baseline data, except that consumption of porn is based on the alternative classifications (from Forcepoint ThreatSeeker, alphaMountain, and Bitdefender)

@@ -1,8 +1,10 @@
 import pandas as pd
 import statsmodels.api as sm
 import statsmodels.formula.api as smf
-from stargazer.stargazer import Stargazer
-
+try:
+    from stargazer.stargazer import Stargazer
+except:
+    pass
 
 def pandas_to_tex(df, texfile, index=False):
     if texfile.split(".")[-1] != ".tex":

### 2023-10-15 scripts/utils/data_utils.py
Update quantile tables
Added tables for traffic as outcome variable.

Shortened variable labels.

@@ -78,7 +78,7 @@ def fit_ols_reg(y, x, df, z=None):
     return ols_results
 
 
-def esttab_ols_quantile(y, x, quantiles, df, z=None):
+def esttab_ols_quantile(y, x, quantiles, df, z=None, significant_digits=2):
     ## Set up regression models (quantile & OLS)
     if z is None:
         quantile_model = smf.quantreg(f"{y} ~ {x}", df)
@@ -104,8 +104,8 @@ def esttab_ols_quantile(y, x, quantiles, df, z=None):
         "rep": "Republican", 
         "C(gender)[T.2]": "Female",
         "C(educ2)[T.2]": "Educ (HS)",
-        "C(educ2)[T.3]": "Educ (some college)",
-        "C(educ2)[T.4]": "Educ (college grad)",
+        "C(educ2)[T.3]": "Educ (some coll.)",
+        "C(educ2)[T.4]": "Educ (coll. grad.)",
         "age": "Age",
         "age2": "Age$^2$",        
         "C(race2)[T.2]": "Race (Black)",
@@ -122,7 +122,7 @@ def esttab_ols_quantile(y, x, quantiles, df, z=None):
         stargazer.covariate_order(["rep", "Intercept"])
     else:
         stargazer.covariate_order(coeflabels.keys())
-    stargazer.significant_digits(2)
+    stargazer.significant_digits(significant_digits)
 
     ## Pare down to get LaTeX *fragment*
     latex_str = stargazer.render_latex()

### 2023-10-15 scripts/utils/data_utils.py
Add timeuse results
E.g. adult consumption vs other types of leisure (entertainment, shopping)

@@ -137,3 +137,38 @@ def esttab_ols_quantile(y, x, quantiles, df, z=None, significant_digits=2):
     latex_fragment_str = latex_fragment_str.replace("$^{**}$", "\sym{b}")
     latex_fragment_str = latex_fragment_str.replace("$^{***}$", "\sym{a}")
     return latex_fragment_str, stargazer
+
+
+import numpy as np
+import statsmodels.api as sm
+lowess = sm.nonparametric.lowess
+
+def lowess_ci(x, y, N=100, conf_interval=0.95, lowess_kw=None, num_points=100):
+    """
+    Perform Lowess regression and determine a confidence interval by bootstrap resampling
+    Source: https://www.statsmodels.org/dev/examples/notebooks/generated/lowess.html
+    """
+    # Automatically generate evaluation points based on the range of x
+    eval_x = np.linspace(min(x), max(x), num_points)
+
+    # Lowess smoothing
+    smoothed = sm.nonparametric.lowess(exog=x, endog=y, xvals=eval_x, **lowess_kw)
+
+    # Perform bootstrap resamplings of the data and evaluate the smoothing at the fixed set of points
+    smoothed_values = np.empty((N, num_points))
+    for i in range(N):
+        sample = np.random.choice(len(x), len(x), replace=True)
+        sampled_x = x[sample]
+        sampled_y = y[sample]
+
+        smoothed_values[i] = sm.nonparametric.lowess(
+            exog=sampled_x, endog=sampled_y, xvals=eval_x, **lowess_kw
+        )
+
+    # Get the confidence interval
+    sorted_values = np.sort(smoothed_values, axis=0)
+    bound = int(N * (1 - conf_interval) / 2)
+    bottom = sorted_values[bound - 1]
+    top = sorted_values[-bound]
+
+    return smoothed, eval_x, bottom, top    

### 2023-10-20 tabs/top10cat_description.tex
Make table for traffic to top ten categories

                                  Business & 720,930 & 13.0 &   720,930 & 13.0 & (decipherinc.com, samplicio.us, privatelink.de) & 4.8 & 10.0 & 0.0 & 0.5 & 1.8 & 5.0 & 11.7 & 18.7 & 140.5 \\
                Search Engines and Portals & 670,710 & 12.1 & 1,391,640 & 25.0 &           (google.com, google.co.uk, yahoo.com) & 4.1 &  8.9 & 0.0 & 0.2 & 1.5 & 4.9 & 10.2 & 15.4 & 139.9 \\
                Chat and Instant Messaging & 613,394 & 11.0 & 2,005,034 & 36.0 &               (google.com, yahoo.com, live.com) & 9.0 & 25.8 & 0.0 & 0.2 & 2.7 & 9.7 & 21.3 & 31.1 & 492.3 \\
               Business, Social Networking & 443,281 &  8.0 & 2,448,315 & 44.0 &        (facebook.com, facebook.co, soocial.com) & 6.4 & 18.6 & 0.0 & 0.1 & 0.6 & 4.5 & 15.4 & 33.0 & 245.5 \\
                                  Shopping & 328,300 &  5.9 & 2,776,615 & 49.9 &             (amazon.com, ebay.com, walmart.com) & 3.6 &  7.3 & 0.0 & 0.2 & 1.2 & 3.8 &  9.0 & 15.9 &  79.0 \\
          Business, Information Technology & 284,428 &  5.1 & 3,061,043 & 55.0 &       (clarity.ms, sentry.io, inboxdollars.com) & 1.8 &  4.9 & 0.0 & 0.1 & 0.5 & 1.8 &  4.1 &  7.0 &  87.8 \\
            Entertainment, Streaming Media & 261,165 &  4.7 & 3,322,208 & 59.7 &            (youtube.com, hulu.com, netflix.com) & 7.2 & 32.7 & 0.0 & 0.1 & 0.3 & 3.0 & 14.8 & 27.8 & 617.5 \\
News and Media, Search Engines and Portals & 231,157 &  4.2 & 3,553,365 & 63.9 &                             (bing.com, att.net) & 3.2 &  6.3 & 0.0 & 0.0 & 0.7 & 3.8 &  9.0 & 16.0 &  61.8 \\
                       Business, Education & 181,106 &  3.3 & 3,734,471 & 67.1 &           (yougov.com, google.com, prolific.co) & 1.8 &  4.9 & 0.0 & 0.2 & 0.7 & 1.8 &  3.8 &  6.5 & 104.5 \\
                        Business, Shopping & 135,431 &  2.4 & 3,869,902 & 69.6 &        (amazon.com, rakuten.com, instacart.com) & 1.5 &  3.2 & 0.0 & 0.1 & 0.4 & 1.3 &  3.5 &  5.9 &  32.2

### 2024-04-15 ms/adult.tex
Updates from Overleaf

--- 2023-01-08 ms/adult.tex
@@
 \usepackage{url}        % Correctly formats URLs with the \url{} tag
+\usepackage{xurl}
 \usepackage{fullpage}   %1-inch margins
@@
 
+% https://tex.stackexchange.com/questions/611786/misplaced-noalign-because-input-before-booktabs-rule
+% I was getting Misplaced \noalign. \bottomrule on my laptop
+% but not on my desktop...
+% Comment out for older LaTeX versions
+%\iffalse
+\ExplSyntaxOn
+\cs_new:Npn \expandableinput #1
+{ \use:c { @@input } { \file_full_name:n {#1} } }
+\AddToHook{env/tabular/begin}
+{ \cs_set_eq:NN \input \expandableinput }
+\ExplSyntaxOff
+%\fi
+
 %\usepackage[T1]{fontenc}
@@
 \usepackage{dcolumn}
+\usepackage{pdflscape}
 
@@
 \renewcommand{\ttdefault}{pcr}
+
+\usepackage[right]{lineno}
 
@@
 
-\title{Holier Than Thou: Partisan Gap in the Consumption\\ of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}}
-
-\author{Lucas Shen\thanks{Lucas is a Research Fellow at Asia Competitiveness Institute, Lee Kuan Yew School of Public Policy, at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
+\title{Holier Than Thou?
+No Large Partisan Gaps in the Consumption of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}
+}
+
+\author{Lucas Shen\thanks{Lucas is a Research Fellow at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
 
@@
 
-\begin{comment}
-
-setwd("~/Documents/Github/adult/ms/")
-tools::texi2dvi("adult.tex", pdf=TRUE, clean=TRUE)
-
-\end{comment}
-
 \thispagestyle{empty}
 \begin{abstract}
-\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture.
+\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of the culture.
 Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online.
@@
 Only about 32 percent of respondents consumed pornography online during the month-long observation period.
-Of the people who consumed pornography, the median consumer spent about three-quarters of an hour consuming pornography and 95 percent of the consumers spent less than five and a half hours.
-Lastly, we find that, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, Republicans consume somewhat more pornography online than Democrats.
-Adjusting for immutable characteristics like age and gender makes the differences go away.
+Of the people who consumed pornography, the median consumer spent about three-quarters of an hour consuming pornography, and 95 percent of the consumers spent less than five and a half hours.
+Lastly, we find, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, that Republicans consume somewhat more pornography online than Democrats.
+Adjusting for immutable characteristics like age and gender makes the differences go away.\\
+
+\emph{Keywords:} Measurement, YouGov, Pornography, Partisanship, Quantile Regression, Online Consumption
 \end{abstract} 
@@
 \doublespace
-
+%\linenumbers
+\section{Introduction}\label{sec:intro}
+Pornography consumption has been rising steadily  \citep{Perry2018-cw, Price2016-sm, Wright2013-gl}.
 Consumption of pornography is associated with a variety of disturbing attitudes, beliefs, emotions, and behaviors.
-Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex, and having extramarital sex \citep{wright2012internet}.
-A lot of popular pornography also contains a healthy dose of violence.
-An analysis of popular pornography revealed that 88.2\% of the scenes contained physical aggression, and 48.7\% verbal aggression \citep{bridges2010aggression}.
-For all these reasons, there are serious concerns about the consumption of pornography.
+Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex and having extramarital sex \citep{wright2012internet}.
+A lot of popular pornography also contains a healthy dose of violence \citep{Vera-Gray2021-qv}.
+An analysis of popular pornography revealed that 88.2\% of the scenes contained physical aggression and 48.7\% verbal aggression \citep{bridges2010aggression}.
+The increased accessibility of online pornography also raises concerns about adolescent sexual development \citep{Peter2016-de, Ybarra2005-id}.
+For all these reasons, there are serious concerns about the consumption of pornography.\footnote{This is despite the fact that the studies cited above do not provide rigorous evidence for the negative impact of pornography consumption \citep{Ferguson2022-fo, Pathmendra2023-fx, Peter2016-de}.}
 
 In this paper, we investigate how much pornography Americans consume online.
-Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
+Using passive tracking data on online browsing from YouGov, we find a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
 About 68 percent of respondents abstained from consuming pornography online during the month-long observation period.
-Of the people who consumed pornography, the median consumer spent about 45 minutes consuming pornography and the 95th percentile consumer spent about five and a half hours.
-
-We also use the data to shed light on an age-old debate---whether Democrats consume more pornography than Republicans or vice versa.
-Both parties claim the higher moral ground.
-And in surveys both parties think consumption of pornography is abhorrent.
-Like previous research, which relied on aggregated data, we find that Republicans consume somewhat more pornography online than Democrats \citep{macinnis2015american, edelman2009markets}.
-Adjusting for background attributes like age, gender etc., makes the differences go away.
-
-\section*{Data}\label{sec:data}
-\addcontentsline{toc}{section}{\nameref{sec:data}}
-We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}.
+Of the people who consumed pornography, the median consumer spent about 45 minutes consuming pornography, and the 95th percentile consumer spent close to 20 hours.
+% (Table SI 1.2)
+
+We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}.
+Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research, using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
+Combining individual-level data on partisanship with directly measured pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa.
+Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats.
+Adjusting for background attributes like age, gender, etc., however, makes the partisan differences go away.
+Our findings relate to \cite{Perry2018-cn}, who find that higher levels of religiosity, also linked to political conservatism, are associated with views of pornography as morally wrong while still having viewed pornography.
+This unexpected finding suggests a discordance between survey responses and reported actions.
+Republicans may be consuming just as much pornography as Democrats; they are just saying otherwise.
+
+\section{Data and Methods}
+\label{sec:data}
+
+\subsection{Online Browsing Data}
+\label{subsec:online_browse_data}
+
+We use data from YouGov to measure the consumption of adult content online.
 YouGov maintains a large panel that it recruits through various methods.
-YouGov uses matched sampling to survey respondents: it draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
-For data on how well YouGov is able to approximate a random sample, see \citet{rivers2009}.
-For our sample, panelists also shared de-identified web browsing data tracked via passive metering software installed voluntarily on their computers.
-The software, called RealityMine, captures online visits independent of the type of browser or browser-specific privacy settings.
-
-The data are from 1,200 respondents for June, 2022.
-We have data on about 6 million visits.
-For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
-The respondents visited about 64,000 unique domains.
-
-Our data also includes characteristics of the respondents.
-We have data on demographic characteristics like birth year, state, gender, race, and education level.
-We also have information on their party identification.
+It uses matched sampling to survey respondents: it draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
+(For data on how well YouGov surveys approximate results from the census and other high-quality government surveys, see \citet{rivers2009, graham2021advantages, foote2021measuring}.) YouGov also collects de-identified web browsing data via passive metering software, RealityMine, which some panelists volunteer to have installed in lieu of rewards.
+RealityMine captures online visits independent of browser type or browser-specific privacy settings.
+
+Specifically, we use data from 1,200 YouGov panelists for June 2022 \citep{data-dataverse}.
+These 1,200 panelists visited the web nearly 6 million times.
+For each visit, we have the anonymized URL, domain (e.g., wikipedia.org), the time of the visit, the length of the visit, and the type of content.
+
+\subsection{Demographics And Partisan Identification}
+\label{subsec:demographics}
+YouGov panel file contains data on demographic characteristics like birth year, state of residence, gender, race, and education level.
+It also contains data on partisan self-identification.
 Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents.
-Of those 1,080 individuals, 82 percent lean either Republican or Democrat.
-The remaining 18 percent identify as independent.
-
-\section*{Measuring Pornographic Content}\label{sec:measuring_porn_content}
-\addcontentsline{toc}{section}{\nameref{sec:measuring_porn_content}}
-
-We code pornographic content at the domain level.
-Our main analysis depends on the domain classifications that come with YouGov data.
-We code domains that YouGov categorizes as ``Adult'' as pornographic.
-These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com).
-Yougov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as `Adult.' Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We cite some of the statistical packages to compute key results \citep{tableone, statsmodels, forestplot, scipy}.}, we manually checked the top adult domains to remove such sites.
-We code a domain as pornographic if there is nudity on the landing page or if the site is some form of erotica.
-
-In \ref{si:alternate_ways}, we leverage the \texttt{piedomains} package, which uses a machine learning model that uses the text of the website to classify the content of domains \citep{Chintalapati_piedomains_Predict_the_2022}.
-We leverage the probability estimates to produce a low false negative and low false positive version.
-The key conclusions remain unchanged.
-
-\section*{Results}\label{sec:results}
-\addcontentsline{toc}{section}{\nameref{sec:results}}
-
-Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
-(In \ref{si:visits}, we analyze similar metrics for visits.
-The upshot is that the key conclusions are unaffected.)
-
-\subsection*{Consumption of Pornography}
-Only about 32 percent of respondents consumed pornography online during the observation period.
-Of the 32\% of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile, nearly 20 hours (see \cref{tab:distribution_duration}).
-You see a similar picture when it comes to the proportion of time spent online consuming pornography-the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).
-
-The consumption of pornography is also highly concentrated among a few sites, with the ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites (approximately 109 minutes vs.
-9 minutes, see \cref{fig:concentration_porn_consumption}).
-Close to 80 percent of the traffic to pornographic sites is to just one pornographic site.
-Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male (see, for instance, Panel B of \cref{tab:characteristics_split_by_porn_consumers}).
-
-\subsection*{Partisan Differences in Consumption of Pornography Online}
-
-Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
-(In \ref{si:visits}, we analyze similar metrics for visits.
-The upshot is that the key conclusions are unaffected.)
-
-Given the skew in the data, we ran a quantile regression, regressing the duration on party.
-As Figures \ref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs.
-For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively.
-In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{
-
-	We analyze the consumption of pornography online among independents in \cref{si:independents}.
-The median independent consumes more pornography than partisans (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
-This pattern reverses somewhat near the right tail of the distribution.}
-
-Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \ref{fig:quantile_regression_prop_duration}).
-The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).
-
-Looking at differences in the percentage of partisans who consume any pornographic content shows muted differences.
-Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June, 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
-
-To what extent are the results "explained" by the confounding demographic differences between the parties?
-To learn that, we control for immutable characteristics like age and gender.
-(\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
-As Figure \ref{fig:quantile_regression_duration} shows, once you adjust for confounders, the partisan differences melt away.
+Of the 1,080 people, 82\% leaned either Republican or Democrat.
+The remaining 18 percent identified as independent.
+(See Panel B of \cref{tab:characteristics_split_by_party} for a summary of socio-demographic data by party.)
+
+\subsection{Measuring Pornographic Content}
+\label{subsec:measuring_porn_content}
+
+Our main analysis uses classifications provided by YouGov.
+Of the 6 million visits to 855,564 unique anonymized URLs, YouGov provides data on the kind of content hosted (e.g., Shopping, Business, Adult) for 727,681 unique URLs (making up 85\% of all visits).
+To illustrate the granularity of the categorization, \url{https://www.google.com/search?ANONYMIZED} is categorized as ``Search Engines and Portals'' while \url{https://mail.google.com/mail/u/0/} is categorized as ``Chat and Instant Messaging.''
+
+To code pornographic content, we start by assuming all content marked ``Adult'' as pornographic.
+This includes ``Adult, Business'' (e.g., onlyfans.com) and ``Adult, Entertainment'' (e.g., hentainfox.com).
+YouGov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as Adult.
+Given the skew in the data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites.
+We code a domain as carrying pornographic content if there is nudity on the landing page or if the site is some form of erotica.
+Domains without a YouGov category are assumed to be missing completely at random.
+
+In \ref{subsec:alternate_porn}, we leverage \texttt{piedomains} and a Google service, Virustotal, to assess whether our results are robust to alternate ways of measuring the kind of content accessed by people.
+\texttt{piedomains} uses open-source domain classification lists to train a neural network that learns the relationship between the kind of content hosted by a domain and the text on the homepage and homepage screenshots of websites \citep{Chintalapati_piedomains_Predict_the_2022}.
+%We leverage the probability estimates to produce inferences from low false negative and low false positive versions. 
+VirusTotal collates domain classification data from different private services.
+Based on their data coverage of our domain data, we use the top three services: Forcepoint ThreatSeeker, Bitdefender, and alphaMountain.\footnote{Forcepoint ThreatSeeker, Bitdefender, and alphaMountain, respectively, cover 47,950, 43,391, and 36,063 of the roughly 64,000 unique domains the panelists visited over the month.}
+
+\section{Results}\label{sec:results}
+\subsection{Most Visits Are to a Few Websites}
+\label{subsec:concentration_media_consumption}
+
+In line with previous research \citep{hindman2009myth, Dewan2004-tt}, we find a considerable skew in online media consumption (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult}).
+As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites.
+The top 5 non-pornographic sites were visited more than 200,000 times by our panelists.
+In comparison, the 99th percentile non-pornographic site was visited only 1,652 times by our panelists during the observation period.
+
+There is a similar concentration of visits in adult content, with a few adult sites attracting a bulk of the total traffic.
+\cref{fig:top25_adult} reports the top 25 pornography sites.
+The top three pornography sites (``\textit{xvideos.com}'', ``\textit{pornhub.com}'', and ``\textit{xnxx.com}'') are visited more than 6,500 times by the people in our sample during the one-month period.
+The most visited site, xvideos.com, clocked 311 hours in total from our participants who visited a pornographic site.
+(Given 361 consumers of online pornography, this translates into an average of 52 minutes of consumption of \textit{xvideos.com} per participant.) Newer platforms such as ``\textit{onlyfans.com}'' are among the most visited pornography sites.
+Nine sites are above the 99th percentile in pornography visits (2,224 visits).
+The average time spent on the ten most frequented pornography sites is 12x the average time on all other pornography sites (approximately 109 minutes vs.
+9 minutes, \cref{fig:concentration_porn_consumption}).
+Our finding is consistent with other analyses of traffic to pornographic sites \cite{webporn}.
+The average time spent on the ten most frequented pornography sites is 12 times the average time spent on all other pornographic sites (approximately 109 minutes vs.
+9 minutes, \cref{fig:concentration_porn_consumption}).
+This finding is consistent with other analyses of traffic to pornographic sites \citep{webporn}.
+
+In all, in line with other studies on online media consumption \citep{Dewan2004-tt, hindman2009myth, webporn}, we find that a few sites attract most of the traffic online.
+
+\subsection{Consumption of Pornography Online}
+\label{subsec:concentration_in_porn}
+
+Only 31.8 percent of the respondents consumed any pornography online during the observation period (see column 3 of \cref{tab:characteristics_split_by_party}).
+Of the 31.8 percent of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography (approximately 42 minutes), while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile almost 20 hours or about 40 minutes per day (see \cref{tab:distribution_duration}).
+A similar picture arises when it comes to the proportion of time spent online consuming pornography--the 50th percentile consumer spent about 3.1 percent of their time on online pornography.
+For the 80th percentile, this is about 14 percent, and for the 95th percentile, this is about 58.5 percent (see \cref{tab:distribution_prop_duration}).
+
+To help contextualize the above figures, we present statistics on time spent consuming content from the top ten non-adult categories in \cref{tab:top10cat_description}. 
+The median pornography consumer spends more hours on adult content than sites from six non-adult categories. 
+Only three categories, ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), ``Business, Social Networking'' (e.g., facebook.com, facebook.co, soocial.com)),  and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile relative to online pornography consumption.
+
+\subsection{Substitution?}
+Are people substituting pornography for other kinds of leisure content?
+To shed light on that, we examine the relationship between the time spent on online pornography vs.
+time spent on other leisure-related online sites (\cref{si:tu_porn_leisure}).
+We fit locally weighted linear regression after removing extreme values (90th percentile) in online consumption.
+At the left tail of online pornography (below 0.5 hours), increases in pornography consumption are associated with fewer hours spent on non-adult-related shopping sites (\cref{fig:tu_prop_entertainment-prop_adult_duration}).
+Otherwise, there are no salient patterns of substitution in time spent on online pornography vs.
+other leisure sites.
+
+\begin{figure}[ht]
+\caption{Time Spent on Online Pornography vs. Non-adult Leisure}
+\label{fig:tu_prop_entertainment-prop_adult_duration}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_adult.pdf}
+         \caption{Entertainment}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_adult.pdf}
+         \caption{Shopping}
+     \end{subfigure}
+\caption*{\footnotesize \emph{Notes:} Lowess between time spent on online pornography and time spent on other non-adult leisure (``entertainment'' and ``shopping'').
+Observations above the 90th percentile for adult content consumption are omitted to prevent the graph from being dominated by these outliers.
+(Given we plot a lowess, such truncation doesn't change the relationship we show.) Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
+Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---the top five such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
+Each estimation in the Lowess uses .3 of the sample data.
+ The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
+Swapping the horizontal axis for adult content excluding adult-related entertainment and shopping sites looks similar (see \cref{fig:tu_prop_entertainment-prop_pure_adult}).
+}
+\end{figure}
+
+\subsection{Partisan Differences}
+\label{subsec:partisan_differences}
+As \cref{tab:characteristics_split_by_party} shows, 31.5\% of Democrats consumed at least some pornography over the month vs.
+29.4\% of Republicans.
+The 2\% difference is not statistically significant.
+Of the partisans who consumed any pornographic content online, \cref{tab:distribution_duration_party} presents the distribution of time spent on pornographic sites by partisan leanings.
+Republicans spent more time consuming online pornography than Democrats.
+The median Republican consumer of pornography consumed 1.4 hours of pornography, while the median Democratic consumer of pornography consumed 0.5 hours.
+A two-sample Kolmogorov-Smirnov test for differences in distribution rejects the null hypothesis (p = .005) (\cref{tab:distribution_duration_party}).
+In \cref{tab:distribution_prop_duration_party}, we observe similar patterns for time spent on pornography sites as for percentage of total time spent on the web.
+The median Republican consumer of pornography consumes 4 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.3 percent.
+
+Given the skew in the data, we quantify differences in online pornography consumption by party using quantile regression.\footnote{\cref{tab:characteristics_split_by_party_medians} presents non-parametric tests for differences in medians in consumption of pornography.} Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+We regress the total time (share of time) spent on pornographic sites on an indicator for Republicans.
 
 %===========================
-
 % Quantile regressions
-
 % Hours spent on adult sites
-
 %===========================
-
 \begin{figure}[t]
-
-	\centering
-
+	\centering
 	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
-
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
-
-	\caption*{\footnotesize \emph{Notes:}
-
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-
 		95\% confidence intervals constructed from standard errors.
-
 		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
-
-	}
-
+        \cref{tab:quantile-estimates-hours} tabulates the estimates.
+	}
 	\label{fig:quantile_regression_duration}
-
 \end{figure}
@@
 %========================================
-
 % Quantile regressions
-
 % Proportion of time spent on adult sites
-
 %========================================
-
 \begin{figure}[t]
-
-	\centering
-
+	\centering
 	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
-
-	\caption*{\footnotesize \emph{Notes:}
-
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-
 		95\% confidence intervals constructed from standard errors.
-
 		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
-
-	}
-
+            %\cref{tab:quantile-estimates-time} tabulates the estimates.
+            \cref{tab:quantile-estimates-time} tabulates the estimates.
+	}
 	\label{fig:quantile_regression_prop_duration}
-
-\end{figure}
-
-\section*{Discussion}\label{sec:discussion}
-\addcontentsline{toc}{section}{\nameref{sec:discussion}}
-Consumption of pornography has been attributed to a variety of ills.
+\end{figure}
+
+As \cref{fig:quantile_regression_duration} shows, the 80th percentile of the difference is close to 0, but from thereon, there is a diverging trend with the 95th percentile difference nearly 1.6 hrs.
+(\cref{tab:quantile-estimates-hours} reports estimates for each quantile.).\footnote{\cref{si:independents} describes the distribution of consumption of pornography online by independents.
+The median independent consumes more pornography than partisans (1.3 hours vs.
+0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.1\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).}
+
+Looking at the share of time spent on pornographic sites reveals a similar pattern to the one we saw for total time spent (see \cref{fig:quantile_regression_prop_duration}).
+The 80th percentile of the partisan difference is nearly 0, and after that, the differences rise sharply with differences of more than 2 hours at the 100th percentile (albeit the number is very imprecisely estimated).
+
+Looking at differences in the percentage of partisans who consume any pornographic content, we find little difference.
+Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
+
+In addition to individual-level demographics, we also have precise timestamps for each visit.
+We use these timestamps to evaluate the extent to which differences in the timing of consumption differ by partisanship.
+Overall, we find some evidence that Republicans consume more online pornography in the morning (see \cref{si:time_of_consumption}).
+
+\subsection{Accounting for Confounders}
+
+Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}).
+For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}).
+Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}).
+How do differences in age and other such demographic differences between the parties ``explain'' the results?
+To find out, we control for the following immutable characteristics that predict pornography consumption: age \citep{Wright2013-an, Woodrum1992-vk}, ethnicity \citep{Wright2013-an}, gender \citep{Woodrum1992-vk}, and education level \citep{Woodrum1992-vk}.
+As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away.
+(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.)
+
+%=====================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (with covariates) 
+%=====================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
+  \cref{tab:quantile-estimates-hours} tabulates the estimates.
+	}
+	\label{fig:quantile_regression_duration_covariates}
+\end{figure}
+
+%================================================================
+% Fig of quantile regression estimates
+% Percentage Time Spent on Adult Sites by Party (with covariates) 
+%================================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
+        \cref{tab:quantile-estimates-time} tabulates the estimates.
+	}
+	\label{fig:quantile_regression_prop_duration_covariates}
+\end{figure}
+
+\subsection{Robustness}
+In \ref{si:visits}, we analyze similar metrics for total number of visits and proportion of visits instead of time.
+The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party}).
+We also replicate our analyses using four alternative classifications of domains (see \nameref{subsec:alternate_porn}) and obtain similar results.
+
+\section{Discussion}
+\label{sec:discussion}
+The consumption of pornography has been attributed to a variety of ills.
 It is also considered problematic from a religious perspective.
 For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}} The Internet has dramatically increased access to pornography.
-This has led to the concern that pornography consumption has become very widespread and extensive.
-Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.
-
-The second contribution of our paper is estimates of partisan differences in consumption of pornography online.
-Both parties claim the higher ground when it comes to women---one's case for morality is steeped in religion, the other's in enduring concern for women.
-Our data suggest that partisan differences are likely small.
+This has led to the concern that pornography consumption has become a ``public health crisis''.
+Our data suggest that pornography consumption online is highly concentrated, with very few people consuming a lot of pornography and most people consuming very little or none.
+
+The paper's primary contribution concerns partisan differences in online pornography consumption.
+Both parties claim the higher ground when it comes to women—one's case for morality is steeped in religion, the other's in enduring concern for women.
+We tested this presentiment using individual-level browsing data.
+The data suggest that partisan differences are likely small.
+
+The key strengths of our unique dataset include having micro-level records of online browsing activities, allowing us to track timestamped visits to multiple online pornography sites.
+Moreover, our dataset also allows us to adjust for partisan differences in fundamental baseline demographics.\footnote{Other studies we cite in this paper lack this combination of ground-truth individual-level consumption of online pornography and individual-level demographics (e.g., \cite{Peek1982-ua, Woodrum1992-vk, Markey2011-xo, Perry2020-cp, Ybarra2005-id, Perry2018-cw, Price2016-sm, webporn, Wright2013-gl}).} \footnote{A more subtle strength of our study is that it is conducted around 2022, by which time differences in online content consumption---including pornography content--- are unlikely to be driven by variations in regional broadband penetration.}
 
@@
 This runs the risk of incurring some ecological fallacy.
-For instance, our classification codes websites like Tumblr as not carrying pornographic content but some of Tumblr's content is pornographic.
+For instance, our classification codes websites like Tumblr as not carrying pornographic content, but some of Tumblr's content is pornographic.
 
 The third concern is that our measures are a point in time.
-We have data from one month in one year - June, 2022.
+We have data from one month in one year - June 2022.
 It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in the preceding or following months.
 
-\clearpage
+% Strengths of our approach
+% Unlike traditional sources like survey or using google searches (like Markey 2011 Pornography-seeking behaviors following midterm political elections in the United States: A replication of the challenge hypothesis), they lack groundtruth AND finegrain info on timing of consumption
+% Unlike pornhub that has IP addresses, has fuller universe of porn consumers, they lack individual level covariates
+% More recent, less susceptible to differences in broadband penetration by area (as opposed to the same study 10 years ago)
+
+%\clearpage
 \bibliographystyle{apsr}
-\bibliography{porn}
+\bibliography{porn,paperpile}
 \clearpage
@@
 \renewcommand{\thesection}{SI \arabic{section}}
-\renewcommand\thetable{\thesection.\arabic{table}}  
-\renewcommand\thefigure{\thesection.\arabic{figure}}
+\setcounter{table}{0}\renewcommand\thetable{\thesection.\arabic{table}}
+\setcounter{figure}{0}\renewcommand\thefigure{\thesection.\arabic{figure}}
 \counterwithin{figure}{section}
@@
 
-\section{Supporting Information}\label{si}
+\begin{center}
+\Large \textbf{Supporting Information}
+\end{center}
+\singlespacing
+\vspace{-.4in}
+\label{si}
 %\begin{center}
@@
 %===============================================================================
-\subsection{Descriptive Analysis}
-
-\subsubsection{Skew in Website Visits}
-%============================
-% Figure of top 25 adultsites
-%============================
-\begin{figure}[ht]
-	\centering
-	\caption{Top 25 Pornography Sites}
-	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 pornographic sites that individuals visit in the sample period.
-		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
-		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
-		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
-	}
-	\label{fig:top25_adult}
-\end{figure}
+\section{Descriptive Analysis}
+
+\subsection{Website Visits Are Highly Skewed}
 
@@
 	\centering
-	\caption{Top 25 (Non-Porn) Domains}
-	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 non-pornographic sites that individuals visit in the sample period.
-		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
-		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
+	\caption{Top 25 Non-Pornographic Sites}
+	\includegraphics[width=\textwidth]{figs/top_25_nonadultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 non-pornographic sites individuals visited in the sample period.
+            All numbers are based on online visits during the one-month period.
+		The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+		The \emph{Visits} column is the total number of visits by individuals in the sample to the site.  			
+		Sites to the right of the vertical dashed are the top 1 percent of non-pornographic sites in visits.
 	}
 	\label{fig:top25_nonadult}
+\end{figure}
+
+%============================
+% Figure of top 25 adultsites
+%============================
+\begin{figure}[ht]
+	\centering
+	\caption{Top 25 Pornography Sites}
+	\includegraphics[width=\textwidth]{figs/top_25_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 pornographic sites that individuals visited in the sample period.
+            All numbers are based on online visits during the one-month period.
+		Pornography sites are categorized by YouGov (see the \nameref{sec:data} section).
+    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.
+            Sites to the right of the vertical dashed are the top 1 percent of pornographic sites in visits.
+	}
+	\label{fig:top25_adult}
 \end{figure}
@@
 	\caption{Traffic to Top 10 Pornographic Sites}
-	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
+	\includegraphics[width=.5\textwidth]{figs/concentration_porn_consumption.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
 		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
-		The Others bar indicates traffic to all other pornographic sites outside of the top 10.
+		The ``Others'' bar indicates traffic to all other pornographic sites outside of the top 10.
 		The y-axis is the total time spent on pornographic sites, averaged across individuals.
-		Time units is hours.
+		Time units are hours.
 		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
 
-%====================================
-% Figure of traffic to top x websites
-%====================================
-\begin{figure}
-	\centering
-	\caption{Traffic to Top x Pornographic Sites by Party}
-	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
-		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:concentration_porn_consumption_topX_by_party}
-\end{figure}
+\begin{landscape}% Landscape page
+    \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{3 pt} \setlength{\defaultaddspace}{0pt}
+    \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+    \caption{Time Spent by the Type of Content}
+    \label{tab:top10cat_description}
+	\begin{adjustbox}{max width=1.325\textwidth}
+            \begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrrrrrrrrrrr@{\hspace{0\tabcolsep}}}
+            \toprule\toprule
+            %\cmidrule(l){2-21}
+            &\multicolumn{5}{c}{\textbf{Panel A.} Top sites based on traffic}&\multicolumn{9}{c}{\textbf{Panel B.}}\\
+            \cmidrule(lr){2-6}
+            &&&\multicolumn{2}{c}{Cumulative}&&\multicolumn{9}{c}{Summary statistics for hours spent on sites}\\
+            \cmidrule(l){4-5}\cmidrule{7-15}
+            &\multicolumn{1}{c}{Traffic}&\multicolumn{1}{c}{\%}&\multicolumn{1}{c}{Traffic}&\multicolumn{1}{c}{\%}&\multicolumn{1}{c}{Examples of websites}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{S.D.}&\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{p25}&\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p75}&\multicolumn{1}{c}{p90}&\multicolumn{1}{c}{p95}&\multicolumn{1}{c}{Max}\\
+            \cmidrule(l){2-5}
+            YouGov category&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)} \\
+            \midrule
+            \input{tabs/top10cat_description}\\       
+            \bottomrule
+        \end{tabular}
+        \end{adjustbox}
+        \caption*{\scriptsize
+        The table enumerates the top ten categories (YouGov) based on the amount of traffic to the corresponding sites from individuals in the sample.
+        Panel A is constructed using the browsing level data (n = 6.3m web browsing records.) Panel B is constructed using the domain-level data (n = 40k).
+        }
+    \end{table}
+\end{landscape}
 
 \FloatBarrier
-\subsubsection{Skew in Consumption of Pornographic Content}
+\subsection{Skew in Consumption of Pornographic Content}
 %====================================================
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online}
+	\caption{Distribution of Consumption of Pornography Online (Conditional on having consumed pornography)}
 	\label{tab:distribution_duration}
@@
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
+			\input{tabs/percentiles_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
 		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
@@
 %=====================================================================
-% Tabulated percentiles of proportion of duration spent on adult sites
+% Tabulated percentiles of the proportion of duration spent on adult sites
 %=====================================================================
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites}
+	\caption{Percentage of Time Spent on Pornographic Sites (Conditional on having consumed pornography)}
 	\label{tab:distribution_prop_duration}
@@
 			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
-		See \cref{tab:distribution_duration} for the distribution in terms of hours.
-		%See \cref{fig:distribution_prop_duration} for the plot.
-	}
+			\input{tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
+The base number is the individual's own total time spent on the web.
+See \cref{tab:distribution_duration} for the distribution of total time spent on pornographic websites.}
 \end{table}
@@
 \clearpage
-\subsection{Partisan Differences}
-\subsubsection{Distribution of Differences}
+\section{Partisan Differences}
+
 %===========================================================================
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party}
+	\caption{Distribution of Consumption of Pornography Online by Party (Conditional on having consumed pornography)}
 	\label{tab:distribution_duration_party}
@@
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+			\input{tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
 		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
-		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
 		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.005, rejecting the null that the Republican and Democrat distributions are the same.
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
+	}
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for the proportion of time spent on adultsites
 %===============================================================================
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party (Conditional on having consumed pornography)}
 	\label{tab:distribution_prop_duration_party}
@@
 			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+			\input{tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+        The base number is the individual's own total time spent on the web.
 		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
-		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
 		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.025, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
 		%See \cref{fig:distribution_prop_duration_party} for the plot.
-	}
-\end{table}
-
-\FloatBarrier
-\clearpage
-\subsubsection{Accounting for Confounders}
-%==============================================================================
-% Table for balance of porn consumption and individual characteristics by party
-%==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
-	\label{tab:characteristics_split_by_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
-			\toprule
-			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_party.tex}\\
-			%-------------------------------------------------------------------
-			\cmidrule{2-8}
-			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_covariates_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
-		Standard deviations and percentages in parentheses.
-		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in consumption of pornography, we also performed tests for difference in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
-	}
-\end{table}
-
-%==============================================================================
-% Table for balance of porn consumption and individual characteristics by party
-%==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
-	\label{tab:characteristics_split_by_porn_consumers}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
-			\toprule
-			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
-			%-------------------------------------------------------------------
-			\cmidrule{2-8}
-			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
-		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
-		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
-		Standard deviations and percentages in parentheses.
-		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
 	}
@@
 			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
+			\input{tabs/balance_outcomes_by_party_medians.tex}\\
 			\bottomrule
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
+		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
 		This table focuses on differences in medians.
@@
 		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles, for the full sample, Democrats, and Republicans.
+		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans.
 		1st and 3rd quartiles in brackets.
@@
 \end{table}
+\FloatBarrier
+\clearpage
+\subsection{Accounting for Confounders}
+
+%==============================================================================
+% Table for balance of porn consumption and individual characteristics by consumer
+%==============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
+	\label{tab:characteristics_split_by_porn_consumers}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
+			\toprule
+			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{tabs/balance_outcomes_by_porn_consumers.tex}\\
+			%-------------------------------------------------------------------
+			\cmidrule{2-8}
+			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{tabs/balance_covariates_by_porn_consumers.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:}
+		The table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
+		65 of the 1,200 individuals did not clock any browsing activity and are in the first panel.
+		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) shows subgroups for categorical variables.
+		Column (2) indicates the count of missing variables, if any.
+		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
+		Standard deviations and percentages are in parentheses.
+		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
+	}
+\end{table}
+
+%==============================================================================
+% Table for balance of porn consumption and individual characteristics by party
+%==============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
+	\label{tab:characteristics_split_by_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
+			\toprule
+			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{tabs/balance_outcomes_by_party.tex}\\
+			%-------------------------------------------------------------------
+			\cmidrule{2-8}
+			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{tabs/balance_covariates_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:}
+		The table shows splits by party for pornographic consumption and for individual characteristics for the 1,200 individuals.
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) shows subgroups for categorical variables.
+		Column (2) indicates the count of missing variables, if any.
+		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables for the full sample, Democratic individuals, and Republican individuals.
+		Standard deviations and percentages are in parentheses.
+		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
+		Given the skew in consumption of pornography, we also performed tests for differences in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
+	}
+\end{table}
+
+\clearpage
+
+\begin{landscape}% Landscape page
+    \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{0 pt} \setlength{\defaultaddspace}{0pt}
+    \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+    \caption{Quantile Estimates--Hours spent on Pornographic Sites by Party }
+    \label{tab:quantile-estimates-hours}
+	\begin{adjustbox}{max width=1.325\textwidth}
+            \begin{tabular}{l*{20}{D{.}{.}{-1}}}
+            \toprule\toprule
+            &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}         &\multicolumn{1}{c}{(7)}         &\multicolumn{1}{c}{(8)}         &\multicolumn{1}{c}{(9)}         &\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}         &\multicolumn{1}{c}{(12)}         &\multicolumn{1}{c}{(13)}         &\multicolumn{1}{c}{(14)}         &\multicolumn{1}{c}{(15)}         &\multicolumn{1}{c}{(16)}         &\multicolumn{1}{c}{(17)}         &\multicolumn{1}{c}{(18)}         &\multicolumn{1}{c}{(19)}         &\multicolumn{1}{c}{(20)}         \\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel A
+            &\multicolumn{20}{c}{\textbf{Panel A. Unconditional quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+            \input{tabs/regtab_quantile_reg_duration_adult.tex}\\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel B            
+            &\multicolumn{20}{c}{\textbf{Panel B. Adjusted quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+             \input{tabs/regtab_quantile_reg_covariates_duration_adult.tex}\\          
+            \bottomrule
+        \end{tabular}
+        \end{adjustbox}
+        \caption*{\scriptsize
+        The outcome variable is the number of hours spent on online pornography sites.
+        Panel A corresponds to \cref{fig:quantile_regression_duration}.
+        Panel B corresponds to \cref{fig:quantile_regression_duration_covariates}.
+        For the adjusted estimates, see \cref{fig:quantile_regression_duration_covariates} for notes on the included covariates.
+        The relevant base/reference categories in Panel B are: Democrats, male, Educ (no HS), Race (White), Region (NE).
+        Sample size: N = 834.
+        Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$0.01.
+        }
+    \end{table}
+\end{landscape}
+
+\begin{landscape}% Landscape page
+    \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{0 pt} \setlength{\defaultaddspace}{0pt}
+    \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+    \caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party}
+    \label{tab:quantile-estimates-time}
+	\begin{adjustbox}{max width=1.325\textwidth}
+            \begin{tabular}{l*{20}{D{.}{.}{-1}}}
+            \toprule\toprule
+            &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}         &\multicolumn{1}{c}{(7)}         &\multicolumn{1}{c}{(8)}         &\multicolumn{1}{c}{(9)}         &\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}         &\multicolumn{1}{c}{(12)}         &\multicolumn{1}{c}{(13)}         &\multicolumn{1}{c}{(14)}         &\multicolumn{1}{c}{(15)}         &\multicolumn{1}{c}{(16)}         &\multicolumn{1}{c}{(17)}         &\multicolumn{1}{c}{(18)}         &\multicolumn{1}{c}{(19)}         &\multicolumn{1}{c}{(20)}         \\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel A
+            &\multicolumn{20}{c}{\textbf{Panel A. Unconditional quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+            \input{tabs/regtab_quantile_reg_proportion_duration_adult}\\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel B            
+            &\multicolumn{20}{c}{\textbf{Panel B. Adjusted quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+             \input{tabs/regtab_quantile_reg_covariates_proportion_duration_adult}\\          
+            \bottomrule
+        \end{tabular}
+        \end{adjustbox}
+        \caption*{\scriptsize
+        The outcome variable is the percentage of time spent on online pornography sites.
+        Panel A corresponds to \cref{fig:quantile_regression_prop_duration}.
+        Panel B corresponds to \cref{fig:quantile_regression_prop_duration_covariates}.
+        For the adjusted estimates, see \cref{fig:quantile_regression_prop_duration_covariates} for notes on the included covariates.
+        The relevant base/reference categories in Panel B are: Democrats, male, Educ (no HS), Race (White), Region (NE).
+        Sample size: N = 834.
+        Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$0.01.
+        }
+    \end{table}
+\end{landscape}
+
+\FloatBarrier
+%===============================================================================
+% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
+%===============================================================================
+\section{Alternate Ways of Measuring Pornography}
+\label{subsec:alternate_porn}
+\subsection{Piedomains}
+%============================
+% Figure of top 25 adultsites
+%============================
+\begin{figure}[ht]
+	\centering
+	\caption{Top 25 Pornography Sites (Piedomains)}
+	\includegraphics[width=\textwidth]{figs/top_25_adultsites_piedomains.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 pornographic sites that individuals visited in the sample period.
+            All numbers are based on online visits during the one-month period.
+		Pornography sites are categorized by Piedomains \citep{Chintalapati_piedomains_Predict_the_2022}.
+            See \cref{fig:top25_adult} for a comparison with our base classification.
+    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
+	}
+	\label{fig:top25_adult_piedomains}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (\texttt{piedomains})}
+	\includegraphics[width=.7\linewidth]{figs/piedomains_quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours people spent on pornographic sites.
+Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+95\% confidence intervals constructed from standard errors.
+See \cref{fig:piedomains_quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:piedomains_quantile_regression_duration}
+\end{figure}
+
 %=====================================================
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, \texttt{piedomains})}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
-	}
-	\label{fig:quantile_regression_duration_covariates}
-\end{figure}
-
-%================================================================
-% Fig of quantile regression estimates
-% Percentage Time Spent on Adult Sites by Party (with covariates) 
-%================================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
-	}
-	\label{fig:quantile_regression_prop_duration_covariates}
-\end{figure}
-\clearpage
-
-\FloatBarrier
-%===============================================================================
-% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
-%===============================================================================
-\subsection{Alternate Ways of Measuring Pornography}
-\label{si:alternate_ways}
-%===========================================================================
-% Tabulated splits by party and by percentiles for hours spent on adultsites
-%===========================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party}
-	\label{tab:piedomains_distribution_duration_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/piedomains_percentiles_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Classificationo of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		See \cref{tab:piedomains_distribution_prop_duration_party} for the corresponding distribution in terms of percentage of time. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.0481, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
-%===============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party}
-	\label{tab:piedomains_distribution_prop_duration_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/piedomains_percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Classificationo of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of percentage of time.
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.19, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
-		%See \cref{fig:distribution_prop_duration_party} for the plot.
-	}
-\end{table}
+		See \cref{fig:piedomains_quantile_regression_duration_covariates} for the same plot without covariates.
+	}
+	\label{fig:piedomains_quantile_regression_duration_covariates}
+\end{figure}
 
@@
 \clearpage
-\subsection{Consumption of Pornography Among Independents}
+\subsection{Forcepoint ThreatSeeker}
+%============================
+% Figure of top 25 adultsites
+%============================
+\begin{figure}[ht]
+	\centering
+	\caption{Top 25 Pornography Sites (Forcepoint ThreatSeeker)}
+	\includegraphics[width=\textwidth]{figs/top_25_adultsites_forcepoint_threatseeker.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 pornographic sites that individuals visited in the sample period.
+            All numbers are based on online visits during the one-month period.
+		Pornography sites are categorized by Forcepoint ThreatSeeker (``Sex'' or ``Adult Content'').
+            See \cref{fig:top25_adult} for a comparison with our base classification.
+    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
+	}
+	\label{fig:top25_adult_forcepoint}
+\end{figure}
+
+%===========================
+
+% Quantile regressions
+
+% Hours spent on adult sites
+
+%===========================
+
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Forcepoint ThreatSeeker)}
+	\includegraphics[width=.7\linewidth]{figs/forcepoint_quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:forcepoint_quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:forcepoint_quantile_regression_duration}
+\end{figure}
+
+%=====================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (with covariates) 
+%=====================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, Forcepoint ThreatSeeker)}
+	\includegraphics[width=.55\linewidth]{figs/forcepoint_quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:forcepoint_quantile_regression_duration_covariates} for the same plot without covariates.
+	}
+	\label{fig:forcepoint_quantile_regression_duration_covariates}
+\end{figure}
+
+\FloatBarrier
+\clearpage
+\subsection{Bitdefender}
+%============================
+% Figure of top 25 adultsites
+%============================
+\begin{figure}[ht]
+	\centering
+	\caption{Top 25 Pornography Sites (Bitdefender)}
+	\includegraphics[width=\textwidth]{figs/top_25_adultsites_bitdefender.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 pornographic sites that individuals visited in the sample period.
+            All numbers are based on online visits during the one-month period.
+		Pornography sites are categorized by Bitdefender.
+            See \cref{fig:top25_adult} for a comparison with our base classification.
+    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
+	}
+	\label{fig:top25_adult_bitdefender}
+\end{figure}
+
+%===========================
+
+% Quantile regressions
+
+% Hours spent on adult sites
+
+%===========================
+
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Bitdefender)}
+	\includegraphics[width=.7\linewidth]{figs/bitdefender_quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:bitdefender_quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:bitdefender_quantile_regression_duration}
+\end{figure}
+
+%=====================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (with covariates) 
+%=====================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, Bitdefender)}
+	\includegraphics[width=.55\linewidth]{figs/bitdefender_quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:bitdefender_quantile_regression_duration_covariates} for the same plot without covariates.
+	}
+	\label{fig:bitdefender_quantile_regression_duration_covariates}
+\end{figure}
+
+\FloatBarrier
+\clearpage
+\subsection{alphaMountain}
+%============================
+% Figure of top 25 adultsites
+%============================
+\begin{figure}[ht]
+	\centering
+	\caption{Top 25 Pornography Sites (alphaMountain)}
+	\includegraphics[width=\textwidth]{figs/top_25_adultsites_alphamountain.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 pornographic sites that individuals visited in the sample period.
+            All numbers are based on online visits during the one-month period.
+		Pornography sites are categorized by alphaMountain (we include any categories mentioning ``porn'', ``adult'' or ``mature'').
+            See \cref{fig:top25_adult} for a comparison with our base classification.
+    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
+	}
+	\label{fig:top25_adult_alphamountain}
+\end{figure}
+
+%===========================
+
+% Quantile regressions
+
+% Hours spent on adult sites
+
+%===========================
+
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (alphaMountain)}
+	\includegraphics[width=.7\linewidth]{figs/alphamountain_quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:alphamountain_quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
+	}
+	\label{fig:alphamountain_quantile_regression_duration}
+\end{figure}
+
+%=====================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (with covariates) 
+%=====================================================
+\begin{figure}[ht]
+	\centering
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, Bitdefender)}
+	\includegraphics[width=.55\linewidth]{figs/alphamountain_quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:alphamountain_quantile_regression_duration_covariates} for the same plot without covariates.
+	}
+	\label{fig:alphamountain_quantile_regression_duration_covariates}
+\end{figure}
+
+\FloatBarrier
+\clearpage
+\section{Consumption of Pornography Among Independents}
 \label{si:independents}
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
-	\caption{Distribution of Consumption of Pornography Online Among Independents}
+	\caption{Time Spent on Pornographic Sites (including Independents)}
 	\label{tab:percentiles_duration_adultsites_by_individuals_independents_partisans}
 	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrr@{\hspace{0\tabcolsep}}}
 			\toprule		
 			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
+            &\multicolumn{3}{c}{\textbf{Partisans}}&\multicolumn{2}{c}{\textbf{Non-partisans}}\\
+            \cmidrule(lr){2-4}\cmidrule(l){5-6}
+			\textbf{Percentile}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\textbf{Independents/DK}\\
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Column (1) includes Democrats (n = 154).
-		Column (2) includes Republicans (n = 95).
-		Column (3) includes both Republicans and Democrats (n = 249).
-		Column (4) includes Independents (n = 67).
-		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
-		%See \cref{fig:distribution_duration_party} for the plot.
+			\input{tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
+            \midrule
+            Observations&\multicolumn{1}{r}{\text{98}}&\multicolumn{1}{r}{\text{158}}&\multicolumn{1}{r}{\text{256}}&\multicolumn{1}{r}{\text{68}}&105\\   
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
 	}
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites Among Independents}
+	\caption{Percentage of Time Spent on Pornographic Sites  (including Independents)}
 	\label{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}
 	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrr@{\hspace{0\tabcolsep}}}
 			\toprule		
 			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
+            &\multicolumn{3}{c}{\textbf{Partisans}}&\multicolumn{2}{c}{\textbf{Non-partisans}}\\
+            \cmidrule(lr){2-4}\cmidrule(l){5-6}
+			\textbf{Percentile}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\textbf{Independents/DK}\\
 			\midrule
-			\input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Column (1) includes Democrats (n = 154).
-		Column (2) includes Republicans (n = 95).
-		Column (3) includes both Republicans and Democrats (n = 249).
-		Column (4) includes Independents (n = 67).
-		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
-		%See \cref{fig:distribution_duration_party} for the plot.
+            \input{tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
+            \midrule
+            Observations&\multicolumn{1}{r}{\text{98}}&\multicolumn{1}{r}{\text{158}}&\multicolumn{1}{r}{\text{256}}&\multicolumn{1}{r}{\text{68}}&105\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
 	}
@@
 \FloatBarrier
-\subsection{Alternate Measures}
-\subsubsection{Proportion of Partisans Who Consumed Any Pornography}
+\section{Alternate Measures}
+\subsection{Proportion of the Group That Consumed Any Pornography}
 %============================================================================
@@
 %============================================================================
-\begin{figure}
+\begin{figure}[ht]
 	\centering
 	\caption{Pornography Consumption by Party}
-	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
+	\includegraphics[width=.5\textwidth]{figs/consume_porn_yes_no.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the proportion of individuals in the sample who consumed pornography in the sample period by party.
 		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
 %===============================================================================
-\subsubsection{Analyses of Visits}
+\subsection{Analyses of Visits}
 \label{si:visits}
@@
 	\caption{Distribution of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{../figs/distribution_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
-		Individuals are split into deciles with each bin containing approximately the same number of individuals.
-		Height of bars indicate mean of each bin.
+	\includegraphics[width=.5\linewidth]{figs/distribution_visits_to_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
+		Individuals are split into deciles, with each bin containing approximately the same number of individuals.
+		The height of the bars indicates the mean of each bin.
 		Capped vertical bars are 95\% confidence intervals.
@@
 	\caption{Percentage of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of visits to pornography sites by individuals who consumed pornography in the sample period.
-		Individuals are split into deciles with each bin containing approximately the same number of individuals.
-		Height of bars indicate mean of each bin.
+	\includegraphics[width=.5\linewidth]{figs/distribution_proportion_visits_to_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the proportion of visits to pornography sites by individuals who consumed pornography in the sample period.
+		Individuals are split into deciles, with each bin containing approximately the same number of individuals.
+		The height of the bars indicates the mean of each bin.
 		Capped vertical bars are 95\% confidence intervals.
@@
 
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Consumption of Pornography Online by Party}
+	\label{tab:distribution_visits_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Traffic}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+		%percentiles_duration_adultsites_by_individuals_by_party
+            \input{tabs/percentiles_visits_adultsites_by_individuals_by_party}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and key percentiles (each of the ten deciles plus quantiles at the right tail) for the visits to pornographic sites.
+		See \cref{tab:distribution_duration_party} for the distribution in terms of time spent. 
+		See \cref{fig:distribution_visits} for the plot.
+	}
+\end{table}
+
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Consumption of Pornography Online by Party}
+	\label{tab:distribution_prop_visits_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% Traffic}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+		%percentiles_duration_adultsites_by_individuals_by_party
+            \input{tabs/percentiles_proportion_visits_adultsites_by_individuals_by_party}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
+		See \cref{fig:distribution_prop_visits} for the plot.
+	}
+\end{table}
+
+\FloatBarrier
 %=======================
@@
 	\caption{Quantile Estimates--Traffic to Pornography Sites by Party}
-	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of visits to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
 		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_visits_covariates} for the same plot controlling for individual characteristics.
+		See \cref{fig:quantile_regression_visits_covariates} for the same plot controlling for individual characteristics.
+            \cref{tab:quantile-estimates-traffic} tabulates the estimates.
 	}
 	\label{fig:quantile_regression_visits}
+\end{figure}
+
+%==================================================
+% Fig of quantile regression estimates
+% Traffic to Adult Sites by Party (with covariates) 
+%==================================================
+\begin{figure}
+	\centering
+	\caption{Quantile Estimates--Traffic to Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of visits to pornographic sites by individuals in our sample.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_visits} for the same plot without covariates.
+            \cref{tab:quantile-estimates-traffic} tabulates the estimates.
+	}
+	\label{fig:quantile_regression_visits_covariates}
 \end{figure}
@@
 	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party}
-	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
 		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot controlling for individual characteristics.
+		See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot controlling for individual characteristics.
+            \cref{tab:quantile-estimates-prop-traffic} tabulates the estimates.
 	}
 	\label{fig:quantile_regression_prop_visits}
-\end{figure}
-
-%==================================================
-% Fig of quantile regression estimates
-% Traffic to Adult Sites by Party (with covariates) 
-%==================================================
-\begin{figure}
-	\centering
-	\caption{Quantile Estimates--Traffic to Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_visits} for the same plot without covariates.
-	}
-	\label{fig:quantile_regression_visits_covariates}
 \end{figure}
@@
 	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_prop_visits} for the same plot without covariates.
+		See \cref{fig:quantile_regression_prop_visits} for the same plot without covariates.
+            \cref{tab:quantile-estimates-prop-traffic} tabulates the estimates.
 	}
@@
 
+\begin{landscape}% Landscape page
+    \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{0 pt} \setlength{\defaultaddspace}{0pt}
+    \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+    \caption{Quantile Estimates--Traffic to Pornographic Sites by Party }
+    \label{tab:quantile-estimates-traffic}
+	\begin{adjustbox}{max width=1.325\textwidth}
+            \begin{tabular}{l*{20}{D{.}{.}{-1}}}
+            \toprule\toprule
+            &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}         &\multicolumn{1}{c}{(7)}         &\multicolumn{1}{c}{(8)}         &\multicolumn{1}{c}{(9)}         &\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}         &\multicolumn{1}{c}{(12)}         &\multicolumn{1}{c}{(13)}         &\multicolumn{1}{c}{(14)}         &\multicolumn{1}{c}{(15)}         &\multicolumn{1}{c}{(16)}         &\multicolumn{1}{c}{(17)}         &\multicolumn{1}{c}{(18)}         &\multicolumn{1}{c}{(19)}         &\multicolumn{1}{c}{(20)}         \\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel A
+            &\multicolumn{20}{c}{\textbf{Panel A. Unconditional quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+            \input{tabs/regtab_quantile_reg_visits_adult}\\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel B            
+            &\multicolumn{20}{c}{\textbf{Panel B. Adjusted quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+             \input{tabs/regtab_quantile_reg_covariates_visits_adult}\\          
+            \bottomrule
+        \end{tabular}
+        \end{adjustbox}
+        \caption*{\scriptsize
+        The outcome variable is the traffic (count) to online pornography sites.
+        Panel A corresponds to \cref{fig:quantile_regression_visits}.
+        Panel B corresponds to \cref{fig:quantile_regression_visits_covariates}.
+        For the adjusted estimates, see \cref{fig:quantile_regression_visits_covariates} for notes on the included covariates.
+        The relevant base/reference categories in Panel B are: Democrats, male, Educ (no HS), Race (White), Region (NE).
+        Sample size: N = 834.
+        Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$0.01.
+        }
+    \end{table}
+\end{landscape}
+
+\begin{landscape}% Landscape page
+    \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{0 pt} \setlength{\defaultaddspace}{0pt}
+    \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+    \caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party }
+    \label{tab:quantile-estimates-prop-traffic}
+	\begin{adjustbox}{max width=1.325\textwidth}
+            \begin{tabular}{l*{20}{D{.}{.}{-1}}}
+            \toprule\toprule
+            &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}         &\multicolumn{1}{c}{(7)}         &\multicolumn{1}{c}{(8)}         &\multicolumn{1}{c}{(9)}         &\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}         &\multicolumn{1}{c}{(12)}         &\multicolumn{1}{c}{(13)}         &\multicolumn{1}{c}{(14)}         &\multicolumn{1}{c}{(15)}         &\multicolumn{1}{c}{(16)}         &\multicolumn{1}{c}{(17)}         &\multicolumn{1}{c}{(18)}         &\multicolumn{1}{c}{(19)}         &\multicolumn{1}{c}{(20)}         \\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel A
+            &\multicolumn{20}{c}{\textbf{Panel A. Unconditional quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+            \input{tabs/regtab_quantile_reg_proportion_visits_adult}\\
+            \cmidrule(l){2-21}
+            % ===================================================================
+            % Panel B            
+            &\multicolumn{20}{c}{\textbf{Panel B. Adjusted quantile estimates}}\\
+            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            \cmidrule(l){2-21}
+             \input{tabs/regtab_quantile_reg_covariates_proportion_visits_adult}\\          
+            \bottomrule
+        \end{tabular}
+        \end{adjustbox}
+        \caption*{\scriptsize
+        The outcome variable is the percentage of traffic to online pornography sites.
+        Panel A corresponds to \cref{fig:quantile_regression_prop_visits}.
+        Panel B corresponds to \cref{fig:quantile_regression_prop_visits_covariates}.
+        For the adjusted estimates, see \cref{fig:quantile_regression_prop_visits_covariates} for notes on the included covariates.
+        The relevant base/reference categories in Panel B are: Democrats, male, Educ (no HS), Race (White), Region (NE).
+        Sample size: N = 834.
+        Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$0.01.
+        }
+    \end{table}
+\end{landscape}
+
+\cleardoublepage
+\FloatBarrier
+%===============================================================================
+%===============================================================================
+% Time use --- substitution
+%===============================================================================
+%===============================================================================
+
+%===============================================================================
+%===============================================================================
+%===============================================================================
+\section{Online Pornography vs. Leisure}\label{si:tu_porn_leisure}
+% adult vs non-adult entertainment
+% adult vs non-adult shopping
+
+% Pure adult vs adult-entertainment
+% Pure adult vs adult shopping
+
+% Pure adult vs nonadult entertainment
+% Pure adult vs nondault shopping
+
+\begin{figure}[ht]
+\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
+\label{fig:tu_prop_entertainment-prop_pure_adult}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_pure_adult.pdf}
+         \caption{Entertainment}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_pure_adult.pdf}
+         \caption{Shopping}
+     \end{subfigure}
+\caption*{\footnotesize \emph{Notes:}
+Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs time spent on other non-adult leisure (``entertainment'' and ``shopping'').
+Observations above the 90th percentile are omitted. 
+Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five of such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
+Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---top five of such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
+Top five pure adult sites are: xvideos.com, pornhub.com, xnxx.com, rule34.xxx, and xhamster.com (see \cref{fig:top25_adult}).
+Each estimation in the Lowess uses .3 of the sample data.
+The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
+Swapping the horizontal axis for any adult content looks similar in \cref{fig:tu_prop_entertainment-prop_adult_duration}. 
+}
+\end{figure}
+
+\FloatBarrier
+\clearpage
+%===============================================================================
+%===============================================================================
+\section{Time of Consumption}
+%===============================================================================
+\label{si:time_of_consumption}
+
+First, we evaluate the density of the timing of visits to online pornography sites using 24-hour bins.
+As anticipated, most visits to online pornography sites occur around midnight.
+We also observe considerable traffic around the midday (1--3 pm, \cref{fig:time-of-day-consumption}).
+Both these observations track with \cite{webporn}'s findings using web session data.
+Second, we repeat the evaluation of the density of the timing of visits but split by partisanship.
+
+The densities suggest that Democratic traffic to pornography sites is concentrated around midnight (11 pm--1 am) while the Republican traffic is concentrated in the early morning (6 am--7 am, \cref{fig:time-of-day-consumption-by-party}).
+
+\begin{figure}[ht]
+\centering
+\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
+    \includegraphics[width=.85\linewidth]{figs/time-of-day-wls-estimates.pdf}
+\caption*{\footnotesize \emph{Notes:} 
+        Estimates of partisan differences in time-of-day visits to online pornography sites.
+        Points represent differences between Republicans relative to Democrats (reference category)---interpreted as proportion differences.
+        The adjusted estimate, which is significant at the 1\% level after Bonferroni correction (at 4 am--8 am), is indicated in the figure.
+        Vertical lines are 95\% confidence intervals.
+        This figure offers an alternative visualization of \cref{tab:regtab_wls_visit_timing_4hrbins}.
+	}
+    \label{fig:time-of-day-wls-estimates}
+\end{figure}
+
+Third, to formally test whether there are differences in time of consumption by partisanship, we begin by dividing traffic to online pornography sites into six 4-hour bins: (a) 4 am--8 am, (b) 8 am--12 pm, (c) 12 pm--4 pm, (d) 4 pm--8 pm, (e) 8 pm--12 am, and (f) 12 am--4 am.
+We code a visit depending on which time interval it occurred and regress that time-of-day window on partisanship, weighted by the dwelling time of the visit.
+Cognizant of the somewhat ad-hoc splits for the time-of-day windows and that we are creating multiple outcome variables, we subject p-values of the partisan point estimate to Bonferroni correction in addition to the adjustments for individual-level demographics.
+
+\cref{fig:time-of-day-wls-estimates} reports a summary of this exercise (\cref{tab:regtab_wls_visit_timing_4hrbins} in \cref{si:time_of_consumption} reports the full set of estimates).
+The unadjusted estimates suggest that Republicans are more likely to consume pornography during midday (the 12 pm--4 pm window), relative to Democrats, which is significant at the 1 percent level after correction.
+Conversely, Republicans are less likely to consume pornography late at night (12 am--4 am).
+These unadjusted findings correspond somewhat to our evaluation of densities of visits by partisanship where Democrat visits to online pornography are concentrated around midnight (\cref{fig:time-of-day-consumption-by-party}).
+
+Once we adjust for the individual-level demographics and for day-of-week fixed effects, Republicans are no longer more (or less) likely to consume pornography during the midday (or late at night).
+However, the adjusted estimates suggest that Republicans are more likely to consume pornography in the early morning (4 am--8 am), specifically five percentage points more likely, which is significant at the 1 percent level even after Bonferroni correction (indicated in \cref{fig:time-of-day-wls-estimates}).
+
+\begin{figure}[ht]
+\centering
+\caption{Time-of-Day Traffic to Online Pornography Sites}
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption.pdf}
+\caption*{\footnotesize \emph{Notes:} 
+        Density plot of traffic to online pornography sites.
+        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 84,289).
+        Each of the 24 bins corresponds to an hour of the day.
+	}
+    \label{fig:time-of-day-consumption}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption-by-party.pdf}
+\caption*{\footnotesize \emph{Notes:} 
+        Density plot of traffic to online pornography sites by partisanship (indicated by colors); bars for Republican consumption are also hatched.
+        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 59,324).
+        Each of the 24 bins corresponds to an hour of the day.
+        See \cref{tab:regtab_wls_visit_timing_4hrbins}, which reports formal tests of differences in time-of-day visits by party.
+	}
+    \label{fig:time-of-day-consumption-by-party}
+\end{figure}
+
+\begin{table}[ht] \centering \footnotesize \setlength\tabcolsep{6 pt} \setlength{\defaultaddspace}{0pt}
+\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+\caption{Time-of-Day Traffic to Pornographic by Party}
+\label{tab:regtab_wls_visit_timing_4hrbins}
+\begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{@{\hspace{0\tabcolsep}}l*{20}{D{.}{.}{-1}}@{\hspace{0\tabcolsep}}}
+        \toprule\toprule
+        &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}\\
+        \cmidrule(l){2-7}
+        &\multicolumn{6}{c}{\textbf{Panel A. WLS estimates}}\\
+        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
+        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
+        \cmidrule(l){2-7}
+        \input{tabs/regtab_wls_visit_timing_4hrbins}\\
+        \cmidrule(l){2-7}
+        &\multicolumn{6}{c}{\textbf{Panel B. Adjusted WLS estimates}}\\
+        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
+        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
+        \cmidrule(l){2-7}
+        \input{tabs/regtab_wls_visit_timing_4hrbins_adjusted}\\
+    \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption*{\scriptsize
+    The table reports weighted least squares estimates from regressing a binary variable based on time-of-day visits to online pornography on the Republican dummy.
+    The unit of observation is at the individual web browsing level for traffic to pornography sites (n = 59,324).
+    Each column represents dummy variables for each of the six 4-hour windows.
+    Weights are the duration of each visit.
+    Models also adjust for day-of-week fixed effects (not reported to conserve space).
+    See also \cref{fig:time-of-day-consumption-by-party}, which provides descriptive evidence that the density in time-of-day traffic is different by party.
+    Significance levels (uncorrected): $^{*}$ 0.05 $^{**}$0.01.
+    P-values are Bonferroni-corrected for six tests---the $^\dagger$ indicates significance at the p = 0.01 level after adjustment.    
+    }
+\end{table}
+
 \end{document}

### 2024-04-15 ms/adult_loi.tex
Updates from Overleaf (#3)
resolving merge conflict...

--- 2023-01-08 ms/adult.tex
@@
 
-\title{Holier Than Thou: Partisan Gap in the Consumption\\ of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}}
+\title{Letter of Inquiry For Holier Than Thou: Partisan Gap in the Consumption of Pornography Online}
 
-\author{Lucas Shen\thanks{Lucas is a Research Fellow at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
-
-\date{\today}
-
+\date{\nodate}
 \begin{document}
@@
 
-\thispagestyle{empty}
-\begin{abstract}
-\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture.
+Dear Editors,\\
+
+Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of the culture.
 Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online.
@@
 Of the people who consumed pornography, the median consumer spent about three-quarters of an hour consuming pornography and 95 percent of the consumers spent less than five and a half hours.
-Lastly, we find that, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, Republicans consume somewhat more pornography online than Democrats.
+Lastly, we find that, in line with previous research, which was based on aggregated data, Republicans consume somewhat more pornography online than Democrats.
 Adjusting for immutable characteristics like age and gender makes the differences go away.
-\end{abstract} 
-\clearpage
-\setcounter{page}{1}
-\doublespace
 
-Consumption of pornography is associated with a variety of disturbing attitudes, beliefs, emotions, and behaviors.
-Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex, and having extramarital sex \citep{wright2012internet}.
-A lot of popular pornography also contains a healthy dose of violence.
-An analysis of popular pornography revealed that 88.2\% of the scenes contained physical aggression, and 48.7\% verbal aggression \citep{bridges2010aggression}.
-For all these reasons, there are serious concerns about the consumption of pornography.
+To answer the precise questions of interest:
 
-In this paper, we investigate how much pornography Americans consume online.
-Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography.
-About 68 percent of respondents abstained from consuming pornography online during the month-long observation period.
-Of the people who consumed pornography, the median consumer spent about 45 minutes consuming pornography and the 95th percentile consumer spent about five and a half hours.
+\begin{itemize}
+\item \textbf{What is your research question, in one sentence?}
 
-We also use the data to shed light on an age-old debate---whether Democrats consume more pornography than Republicans or vice versa.
-Both parties claim the higher moral ground.
-And in surveys both parties think consumption of pornography is abhorrent.
-Like previous research, which relied on aggregated data, we find that Republicans consume somewhat more pornography online than Democrats \citep{macinnis2015american, edelman2009markets}.
-Adjusting for background attributes like age, gender etc., makes the differences go away.
+How much pornography do Americans consume online and are there partisan differences in the consumption of pornography?
 
-\section*{Data}\label{sec:data}
-\addcontentsline{toc}{section}{\nameref{sec:data}}
-We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}.
-YouGov maintains a large panel that it recruits through various methods.
-YouGov uses matched sampling to survey respondents: it draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
-For data on how well YouGov is able to approximate a random sample, see \citet{rivers2009}.
-For our sample, panelists also shared de-identified web browsing data tracked via passive metering software installed voluntarily on their computers.
-The software, called RealityMine, captures online visits independent of the type of browser or browser-specific privacy settings.
+\item \textbf{What is being described?}
 
-The data are from 1,200 respondents for June, 2022.
-We have data on about 6 million visits.
-For each visit, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain.
-The respondents visited about 64,000 unique domains.
+Distribution of pornographic consumption online using passively observed domain level browsing data.
 
-Our data also includes characteristics of the respondents.
-We have data on demographic characteristics like birth year, state, gender, race, and education level.
-We also have information on their party identification.
-Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents.
-Of those 1,080 individuals, 82 percent lean either Republican or Democrat.
-The remaining 18 percent identify as independent.
-Column (3) of \cref{tab:characteristics_split_by_party} reports summary statistics.
+\item \textbf{How is the sample constructed?}
 
-\section*{Measuring Pornographic Content}\label{sec:measuring_porn_content}
-\addcontentsline{toc}{section}{\nameref{sec:measuring_porn_content}}
+We use a 1200 person sample from YouGov. We have profile data and passively observed browsing data for a month on these users.
 
-We code pornographic content at the domain level.
-Our main analysis depends on the domain classifications that come with YouGov data.
-We code domains that YouGov categorizes as ``Adult'' as pornographic.
-These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com).
-Yougov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as `Adult.' Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We cite some of the statistical packages to compute key results \citep{tableone, statsmodels, forestplot, scipy}.}, we manually checked the top adult domains to remove such sites.
-We code a domain as pornographic if there is nudity on the landing page or if the site is some form of erotica.
+\item \textbf{How does it pertain to digital media?}
 
-In \ref{si:alternate_ways}, we leverage the \texttt{piedomains} package, which uses a machine learning model that uses the text of the website to classify the content of domains \citep{Chintalapati_piedomains_Predict_the_2022}.
-We leverage the probability estimates to produce a low false negative and low false positive version.
-The key conclusions remain unchanged.
+We only observe and report on how much digital pornography people consume.
 
-\section*{Results}\label{sec:results}
-\addcontentsline{toc}{section}{\nameref{sec:results}}
-
-Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
-(In \ref{si:visits}, we analyze similar metrics for visits.
-The upshot is that the key conclusions are unaffected.)
-
-\subsection*{Consumption of Pornography}
-Only about 32 percent of respondents consumed pornography online during the observation period.
-Of the 32\% of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile, nearly 20 hours (see \cref{tab:distribution_duration}).
-You see a similar picture when it comes to the proportion of time spent online consuming pornography---the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).
-
-The consumption of pornography is also highly concentrated among a few sites, with the ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites (approximately 109 minutes vs.
-9 minutes, see \cref{fig:concentration_porn_consumption}).
-Close to 80 percent of the traffic to pornographic sites is to just one pornographic site (\cref{fig:concentration_porn_consumption_topX_by_party}).
-
-Looking at the characteristics of consumers of pornography in Panel B of \cref{tab:characteristics_split_by_porn_consumers}, expectedly, consumers of pornography online are younger and are more likely to be male.
-In addition, consumers of pornography are no different in terms of party identification.
-The mean in the 7-point scale in party identification is identical, with a mean of 3.6 and a standard deviation of 2.2, for both consumers and non-consumers of pornography.
-Treating party identification as subgroups (Republicans, Independents, Democrats) does not change this lack of difference in party identification between consumers and non-consumers (see also \cref{fig:consume_porn_yes_no}).
-This foreshadows the systematic lack of partisan differences in consumption of pornography online we find below.
-
-\subsection*{Partisan Differences in Consumption of Pornography Online}
-
-%===========================
-% Quantile regressions
-% Hours spent on adult sites
-%===========================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_quantile_reg_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:quantile_regression_duration}
-\end{figure}
-
-%========================================
-% Quantile regressions
-% Proportion of time spent on adult sites
-%========================================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_quantile_reg_proportion_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:quantile_regression_prop_duration}
-\end{figure}
-
-Given the skew in the data, we ran a quantile regression, regressing the duration on party.
-As \cref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs.
-For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively.
-In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{
-We analyze the consumption of pornography online among independents in \cref{si:independents}.
-The median independent consumes more pornography than partisans (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
-This pattern reverses somewhat near the right tail of the distribution.}
-
-Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \cref{fig:quantile_regression_prop_duration}).
-The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).
-
-Looking at differences in the percentage of partisans who consume any pornographic content shows muted differences.
-Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June, 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
-
-To what extent are the results "explained" by the confounding demographic differences between the parties?
-To learn that, we control for immutable characteristics like age, gender, level of education qualification, race, and region.
-(\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
-As \cref{si:confounders} shows, once you adjust for confounders, the partisan differences melt away.\footnote{Using an alternative machine learning classifier of domains in \cref{si:alternate_ways} and alternative measures of pornography consumption (using traffic to pornographic sites) in \cref{si:visits} does little to change our conclusions.}
-
-\section*{Discussion}\label{sec:discussion}
-\addcontentsline{toc}{section}{\nameref{sec:discussion}}
-Consumption of pornography has been attributed to a variety of ills.
-It is also considered problematic from a religious perspective.
-For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}.} The Internet has dramatically increased access to pornography.
-This has led to the concern that pornography consumption has become very widespread and extensive.
-Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.
-
-The second contribution of our paper is estimates of partisan differences in consumption of pornography online.
-Both parties claim the higher ground when it comes to women---one's case for morality is steeped in religion, the other's in enduring concern for women.
-Our data suggest that partisan differences are likely small.
-
-Our research has three major limitations.
-The first concern with our data is that we may not have all the Internet visitation data of a user.
-If the respondent changes their behavior in response to the knowledge that their data is being collected (even if it is de-identified), for e.g., they may modify their behavior on the machine or figure out ways to evade detection, it may bias our results.
-In fact, we think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified).
-If that is so, our estimates are a lower bound of consumption of online pornography.
-If this bias varies by party, our estimates of partisan differences will also be biased.
-
-The second concern with our measurement is that we code content at a domain level.
-This runs the risk of incurring some ecological fallacy.
-For instance, our classification codes websites like Tumblr as not carrying pornographic content but some of Tumblr's content is pornographic.
-
-The third concern is that our measures are a point in time.
-We have data from one month in one year - June, 2022.
-It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in the preceding or following months.
-
-\clearpage
-\bibliographystyle{apsr}
-\bibliography{porn}
-\clearpage
-
-%===============================================================================
-%===============================================================================
-% Appendix
-%===============================================================================
-%===============================================================================
-\appendix
-\renewcommand{\thesection}{SI \arabic{section}}
-\renewcommand\thetable{\thesection.\arabic{table}}  
-\renewcommand\thefigure{\thesection.\arabic{figure}}
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-
-\section{Supporting Information}\label{si}
-%\begin{center}
-%\Large{Supporting Information}
-%\end{center}
-
-\FloatBarrier
-%===============================================================================
-% Supplementary Descriptives for sense of landscape of porn consumption
-%===============================================================================
-\subsection{Descriptive Analysis}
-
-\subsubsection{Skew in Website Visits}
-%============================
-% Figure of top 25 adultsites
-%============================
-\begin{figure}[ht]
-	\centering
-	\caption{Top 25 Pornography Sites}
-	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
-		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
-		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
-		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
-		See \cref{fig:top25_nonadult} for top non-pornographic domains.
-	}
-	\label{fig:top25_adult}
-\end{figure}
-
-%================================
-% Figure of top 25 non-adultsites
-%================================
-\begin{figure}
-	\centering
-	\caption{Top 25 (Non-Pornographic) Domains}
-	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 non-pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
-		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
-		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
-		See \cref{fig:top25_nonadult} for top non-pornographic domains.
-	}
-	\label{fig:top25_nonadult}
-\end{figure}
-
-%=============================================
-% Figure for concentration of porn consumption
-%=============================================
-\begin{figure}
-	\centering
-	\caption{Traffic to Top 10 Pornographic Sites}
-	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
-		Observations are at the individual-domain level (N = 2,437) for pornography sites and individuals who consume pornography online.
-		The Others bar indicates traffic to all other pornographic sites outside of the top 10.
-		The y-axis is the total time spent on pornographic sites, averaged across individuals.
-		Time units is hours.
-		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:concentration_porn_consumption}
-\end{figure}
-
-%====================================
-% Figure of traffic to top x websites
-%====================================
-\begin{figure}
-	\centering
-	\caption{Traffic to Top x Pornographic Sites by Party}
-	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
-		Observations are from the 256 individuals with party identification (Republicans or Democrats) who consume pornography online.
-		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:concentration_porn_consumption_topX_by_party}
-\end{figure}
-
-\FloatBarrier
-\subsubsection{Skew in Consumption of Pornographic Content}
-%====================================================
-% Tabulated percentiles of hours spent on adult sites
-%====================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online}
-	\label{tab:distribution_duration}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{cr}
-			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
-			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period (n = 353).
-		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
-		%See \cref{fig:distribution_duration} for the plot.
-	}
-\end{table}
-
-%=====================================================================
-% Tabulated percentiles of proportion of duration spent on adult sites
-%=====================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites}
-	\label{tab:distribution_prop_duration}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{cr}
-			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
-			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period (n = 353).
-		See \cref{tab:distribution_duration} for the distribution in terms of hours.
-		%See \cref{fig:distribution_prop_duration} for the plot.
-	}
-\end{table}
-
-\FloatBarrier
-\clearpage
-\subsection{Partisan Differences}
-\subsubsection{Distribution of Differences}
-%===========================================================================
-% Tabulated splits by party and by percentiles for hours spent on adultsites
-%===========================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party}
-	\label{tab:distribution_duration_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
-		See \cref{tab:distribution_duration_party_untruncated} including non-consumers of pornography.
-		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.005, rejecting the null that the Republican and Democrat distributions are the same.
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
-%===============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party}
-	\label{tab:distribution_prop_duration_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
-		See \cref{tab:distribution_prop_duration_party_untruncated} including non-consumers of pornography.
-		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.025, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
-		%See \cref{fig:distribution_prop_duration_party} for the plot.
-	}
-\end{table}
-
-%===========================================================================
-% Tabulated splits by party and by percentiles for hours spent on adultsites
-% Full sample
-%===========================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party\\ (Including non-consumers)}
-	\label{tab:distribution_duration_party_untruncated}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party_untruncated.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Sample includes 834 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
-		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.37, rejecting the null that the Republican and Democrat distributions are the same.
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
-% Full sample
-%===============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party \\(Including non-consumers)}
-	\label{tab:distribution_prop_duration_party_untruncated}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party_untruncated.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Sample includes 834 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
-		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.6, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
-		%See \cref{fig:distribution_prop_duration_party} for the plot.
-	}
-\end{table}
-
-\FloatBarrier
-\clearpage
-\subsubsection{Accounting for Confounders}\label{si:confounders}
-%==============================================================================
-% Table for balance of porn consumption and individual characteristics by party
-%==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
-	\label{tab:characteristics_split_by_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
-			\toprule
-			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_party.tex}\\
-			%-------------------------------------------------------------------
-			\cmidrule{2-8}
-			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_covariates_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
-		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
-		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
-		52 of the 65 are partisans, so in later analyses the sample of partisans drop from the 886 to 834.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
-		Standard deviations and percentages in parentheses.
-		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in consumption of pornography, we also performed tests for difference in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
-	}
-\end{table}
-
-%==============================================================================
-% Table for balance of porn consumption and individual characteristics by party
-%==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
-	\label{tab:characteristics_split_by_porn_consumers}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
-			\toprule
-			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
-			%-------------------------------------------------------------------
-			\cmidrule{2-8}
-			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
-		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel. 
-		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
-		52 of the 65 are partisans, so in later analyses the sample of partisans drop from the 886 to 834.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
-		Standard deviations and percentages in parentheses.
-		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
-	}
-\end{table}
-
-%==============================================================================
-% Table for balance of porn consumption and individual characteristics by party
-% Difference in medians
-%==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences (in Medians) in Pornography Consumption}
-	\label{tab:characteristics_split_by_party_medians}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
-			\toprule
-			&\multicolumn{7}{c}{\underline{Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
-		This table focuses on differences in medians.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles, for the full sample, Democrats, and Republicans.
-		1st and 3rd quartiles in brackets.
-		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
-		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
-	}
-\end{table}
-
-%============================
-% Regression table
-% Dependent variable is hours
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites}
-	\label{tab:regtab_quantile_reg_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_duration} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for estimates controlling for individual characteristics.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\label{tab:regtab_quantile_reg_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_prop_duration} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for estimates controlling for individual characteristics.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%=====================================================
-% Fig of quantile regression estimates
-% Time Spent on Adult Sites by Party (with covariates) 
-%=====================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
-		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:quantile_regression_duration_covariates}
-\end{figure}
-
-%================================================================
-% Fig of quantile regression estimates
-% Percentage Time Spent on Adult Sites by Party (with covariates) 
-%================================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
-		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:quantile_regression_prop_duration_covariates}
-\end{figure}
-
-%============================
-% Regression table
-% Dependent variable is hours
-% w/ covariates
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_quantile_reg_covariates_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_covariates_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_duration_covariates} for a plot of the quantile estimates for the Republican coefficient.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-% w/ covariates
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_quantile_reg_covariates_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_covariates_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_prop_duration_covariates} for a plot of the quantile estimates for the Republican coefficient.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-\FloatBarrier
-%===============================================================================
-% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
-% Piedomains classification
-%===============================================================================
-\subsection{Alternate Ways of Measuring Pornography}
-\label{si:alternate_ways}
-%===========================================================================
-% Tabulated splits by party and by percentiles for hours spent on adultsites
-%===========================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party}
-	\label{tab:piedomains_distribution_duration_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/piedomains_percentiles_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:piedomains_distribution_prop_duration_party} for the corresponding distribution in terms of percentage of time. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.0481, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
-%===============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party}
-	\label{tab:piedomains_distribution_prop_duration_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/piedomains_percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of hours.
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.19, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
-		%See \cref{fig:distribution_prop_duration_party} for the plot.
-	}
-\end{table}
-
-%===========================
-% Quantile regressions
-% Hours spent on adult sites
-% Piedomains
-%===========================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:piedomains_quantile_reg_covariates_duration_adult} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_piedomains_quantile_reg_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_duration_adult}
-\end{figure}
-
-%========================================
-% Quantile regressions
-% Proportion of time spent on adult sites
-% Piedomains
-%========================================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:piedomains_quantile_reg_covariates_proportion_duration_adult} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_piedomains_quantile_reg_proportion_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_proportion_duration_adult}
-\end{figure}
-
-%============================
-% Regression table
-% Dependent variable is hours
-% Piedomains
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites}
-	\label{tab:regtab_piedomains_quantile_reg_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-% Piedomains
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\label{tab:regtab_piedomains_quantile_reg_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_proportion_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_proportion_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-\FloatBarrier
-\subsubsection{Accounting for Confounders}
-%=====================================================
-% Fig of quantile regression estimates
-% Time Spent on Adult Sites by Party (with covariates) 
-% Piedomains
-% w/ covariates
-%=====================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_covariates_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{tab:regtab_piedomains_quantile_reg_covariates_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_covariates_duration_adult}
-\end{figure}
-
-%========================================
-% Quantile regressions
-% Proportion of time spent on adult sites
-% Piedomains
-% w/ covariates
-%========================================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{tab:regtab_piedomains_quantile_reg_covariates_proportion_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_covariates_proportion_duration_adult}
-\end{figure}
-
-%============================
-% Regression table
-% Dependent variable is hours
-% Piedomains
-% \w covariates
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_piedomains_quantile_reg_covariates_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_covariates_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_covariates_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-% Piedomains
-% w/ covariates
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_piedomains_quantile_reg_covariates_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_covariates_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_covariates_proportion_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-\FloatBarrier
-\clearpage
-\subsection{Consumption of Pornography Among Independents}
-\label{si:independents}
-%===========================================================================
-% Tabulated splits by party and by percentiles for hours spent on adultsites
-%===========================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
-	\caption{Distribution of Consumption of Pornography Online Among Independents}
-	\label{tab:percentiles_duration_adultsites_by_individuals_independents_partisans}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
-			\toprule		
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
-			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) includes Republicans (n = 95).		
-		Column (2) includes Democrats (n = 154).
-		Column (3) includes both individuals from columns (1) and (2)---the Republicans and Democrats (n = 249).
-		Column (4) includes Independents (n = 67).
-		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites Among Independents}
-	\label{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
-			\toprule		
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
-			\midrule
-			\input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) includes Republicans (n = 95).
-		Column (2) includes Democrats (n = 154).
-		Column (3) includes both individuals from columns (1) and (2)---the Republicans and Democrats (n = 249).
-		Column (4) includes Independents (n = 67).
-		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-\cleardoublepage
-\FloatBarrier
-\subsection{Alternate Measures}
-\subsubsection{Proportion of Partisans Who Consumed Any Pornography}
-%============================================================================
-% Figure of porn consumption by party
-% Y-axis = proportion of individuals that ever consumed porn in sample period
-%============================================================================
-\begin{figure}
-	\centering
-	\caption{Pornography Consumption by Party}
-	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
-		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
-	}
-	\label{fig:consume_porn_yes_no}
-\end{figure}
-\clearpage
-
-\FloatBarrier
-%===============================================================================
-%===============================================================================
-% Analogous results for visits to adult sites
-%===============================================================================
-%===============================================================================
-\subsubsection{Analyses of Visits}
-\label{si:visits}
-%=================================================
-% Figure for Distribution of visits to adult sites
-%=================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Distribution of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{../figs/distribution_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the number of visits to pornography sites by the 361 individuals who consumed pornography in the sample period.
-		Individuals are split into deciles with each bin containing approximately the same number of individuals.
-		Height of bars indicate mean of each bin.
-		Capped vertical bars are 95\% confidence intervals.
-		%See \cref{tab:distribution_visits} for the more tabulated values.
-	}
-	\label{fig:distribution_visits}
-\end{figure}
-
-%===============================================================
-% Figure for Distribution of proportion of visits to adult sites
-%===============================================================
-\begin{figure}
-	\centering
-	\caption{Percentage of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of visits to pornography sites by the 361 individuals who consumed pornography in the sample period.
-		Individuals are split into deciles with each bin containing approximately the same number of individuals.
-		Height of bars indicate mean of each bin.
-		Capped vertical bars are 95\% confidence intervals.
-		%See \cref{tab:distribution_prop_visits} for the more tabulated values.
-	}
-	\label{fig:distribution_prop_visits}
-\end{figure}
-
-%=======================
-% Quantile regressions
-% Traffic to adult sites
-%=======================
-\begin{figure}
-	\centering
-	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites}
-	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_visits_covariates} for the same plot controlling for individual characteristics.
-	}
-	\label{fig:quantile_regression_visits}
-\end{figure}
-
-%=====================================
-% Quantile regressions
-% Proportion of traffic to adult sites
-%=====================================
-\begin{figure}
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Visits to Pornographic Sites}
-	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_prop_visits_covariates} for the same plot controlling for individual characteristics.
-	}
-	\label{fig:quantile_regression_prop_visits}
-\end{figure}
-
-%==================================================
-% Fig of quantile regression estimates
-% Traffic to Adult Sites by Party (with covariates) 
-%==================================================
-\begin{figure}
-	\centering
-	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_visits} for the same plot without covariates.
-	}
-	\label{fig:quantile_regression_visits_covariates}
-\end{figure}
-
-%=============================================================
-% Fig of quantile regression estimates
-% Percentage Traffic to Adult Sites by Party (with covariates) 
-%=============================================================
-\begin{figure}
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Visits to Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		%See \cref{fig:quantile_regression_prop_visits} for the same plot without covariates.
-	}
-	\label{fig:quantile_regression_prop_visits_covariates}
-\end{figure}
+\end{itemize}
 

### 2024-04-15 ms/lit_review.tex
Updates from Overleaf (#3)
resolving merge conflict...

### Violence in videos

"Of the 304 scenes analyzed, 88.2\% contained physical aggression, principally spanking, gagging, and slapping, while 48.7\% of scenes contained verbal aggression, primarily name-calling. Perpetrators of aggression were usually male, whereas targets of aggression were overwhelmingly female." \citep{bridges2010aggression}
    - Data:  The population of titles for this research was drawn from a compilation of 250 best-selling and 250 most rented video lists published monthly by AVN. The researchers selected the top 30 videos appearing on each list from December 2004 to June 2005. After deleting duplications, the population consisted of 275 titles (AVN, 2005). Fifty titles were randomly selected from this list to comprise the sample, yielding 304 scenes ...

### Correlates of Porn

"Nonetheless, demand for several online services does not appear to be sensitive to income, including chat, credit history, social media, and pornography." \citep{boik2016empirical}

### 2024-04-15 ms/scrap_yard.tex
Updates from Overleaf (#3)
resolving merge conflict...

--- 2023-01-04 ms/scrap_yard.tex
@@
+\subsubsection{Percentage of Time Spent on Top 10 Most Visited }
+
+%===========================================================================
+% Tabulated splits by party and by percentiles for hours spent on adultsites
+%===========================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Distribution of Consumption of Pornography Online by Party (\texttt{piedomains})}
+	\label{tab:piedomains_distribution_duration_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{tabs/piedomains_percentiles_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Classification of pornography sites is based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		See \cref{tab:piedomains_distribution_prop_duration_party} for the corresponding distribution in terms of percentage of time. 
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.0481, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
+		%See \cref{fig:distribution_duration_party} for the plot.
+	}
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
+%===============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party (\texttt{piedomains})}
+	\label{tab:piedomains_distribution_prop_duration_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{tabs/piedomains_percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		Classification of pornography sites is based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of percentage of time.
+		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.19, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
+		%See \cref{fig:distribution_prop_duration_party} for the plot.
+	}
+\end{table}
+
+%====================================
+% Figure of traffic to top x websites
+%====================================
+\begin{figure}[h]
+	\centering
+	\caption{Traffic to Top x Pornographic Sites by Party}
+	\includegraphics[width=.6\textwidth]{figs/concentration_porn_consumption_topX_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the concentration of pornography consumption based on individuals' most frequented pornographic sites.
+            The underlying data is the individual's own most frequented site.
+            We first sort online pornography sites for each individual and compute the percentage of time that individual spent for his/her own top 10 sites before computing and plotting the average (as shown above).
+		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
+	}
+	\label{fig:concentration_porn_consumption_topX_by_party}
+\end{figure}
+
+\begin{figure}[ht]
+\caption{Time Spent on Online Pure Pornography vs. Adult-related Leisure}
+\label{fig:tu_prop_adult_entertainment-prop_pure_adult}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_adult_entertainment-duration_pure_adult.pdf}
+         \caption{Entertainment}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_adult_shop-duration_pure_adult.pdf}
+         \caption{Shopping}
+     \end{subfigure}
+\caption*{\footnotesize \emph{Notes:}
+Lowess for time spent on online pornography (excludes adult entertainment, adult gaming, adult shopping) vs time spent on other adult-related leisure (``adult entertainment'' and ``adult shopping'').
+Observations above the 90th percentile are omitted. 
+Adult-related entertainment sites are those with YouGov categories containing ``adult'' and ``entertainment''---top five of such sites are thechive.com, redgifs.com, 4chan.org, hentairead.com, and hentaifox.com.
+Adult-related shopping sites are those with YouGov categories containing ``adult'' and ``shopping''---top five of such sites are manyvids.com, adameve.com, victoriassecret.com, honeyplaybox.com, and r18.com.
+Each estimation in the Lowess uses half of the sample data.
+The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).}
+\end{figure}
+
 %% given sample size, probably misleading so I propose scraping it for now
@@
 	\label{fig:distribution_prop_duration_party}
+\end{figure}
+
+%====================================
+% Figure of traffic to top x websites
+%====================================
+\begin{figure}
+	\centering
+	\caption{Traffic to Top x Pornographic Sites by Party}
+	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
+		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
+	}
+	\label{fig:concentration_porn_consumption_topX_by_party}
 \end{figure}

### 2024-04-21 ms/main.tex

--- 2024-04-15 ms/adult.tex
@@
-\documentclass[12pt, letterpaper]{article}
-\usepackage[titletoc,title]{appendix}
-\usepackage{color}
-\usepackage{booktabs}
-\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\definecolor{dark-red}{rgb}{0.75,0.10,0.10}
-\definecolor{bluish}{rgb}{0.05,0.05,0.85}
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{naturalnames}{hyperref}
-\usepackage[margin=1in]{geometry}
-\usepackage[linkcolor=blue,
+\documentclass[12pt,twoside]{article}
+\renewcommand{\abstractname}{\vspace{-\baselineskip}}
+\usepackage[dvipsnames]{xcolor}
+\usepackage[
+linkcolor=darkgray,
 colorlinks=true,
-			urlcolor=blue,
+urlcolor=darkgray,
 pdfstartview={XYZ null null 1.00},
 pdfpagemode=UseNone,
-			citecolor={bluish},
-			pdftitle={partisan adult}]{hyperref}
-
-%\newcites{SI}{SI References}
+citecolor={darkgray},
+pdftitle={Holier Than Thou? Partisan Gaps in Pornography}
+]{hyperref}
+\urlstyle{same}
+\usepackage{geometry}
+ \geometry{left=1.25in,top=1.7in}
+\setlength{\parindent}{.5in}
+\renewcommand{\baselinestretch}{1.3}
+\setlength{\parskip}{\baselineskip}
+\usepackage{xcolor}
+\usepackage{fancyhdr}
+\renewcommand{\headrulewidth}{0pt}
+\usepackage[labelfont=bf]{caption}
+\captionsetup[figure]{labelfont={bf},name={Figure},labelsep=period}
 \usepackage{natbib}
-
+\bibliographystyle{apalike}
+\usepackage{graphicx}
 \usepackage{float}
+\usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage{titling}
+\usepackage{amsmath}
 \usepackage{placeins}
-
-\usepackage{geometry}  % see geometry.pdf on how to lay out the page. There's lots.
-\geometry{letterpaper} % This is 8.5x11 paper. Options are a4paper or a5paper or other...
-\usepackage{graphicx}  % Handles inclusion of major graphics formats and allows use of
-\usepackage{amsfonts,amssymb,amsbsy}
-\usepackage{amsxtra}
-\usepackage{verbatim}
-%\setcitestyle{round,semicolon,aysep={},yysep={;}}
-\usepackage{setspace} % Permits line spacing control. Options are:
-%\doublespacing
-%\onehalfspace
-%\usepackage{sectsty}    % Permits control of section header styles
+\usepackage{subcaption}
+\usepackage{lscape}
 \usepackage{pdflscape}
-\usepackage{fancyhdr}   % Permits header customization. See header section below.
-\usepackage{url}        % Correctly formats URLs with the \url{} tag
-\usepackage{xurl}
-\usepackage{fullpage}   %1-inch margins
-\usepackage{multirow}
-\usepackage{verbatim}
-\usepackage{rotating}
-\setlength{\parindent}{3em}
-
-% https://tex.stackexchange.com/questions/611786/misplaced-noalign-because-input-before-booktabs-rule
-% I was getting Misplaced \noalign. \bottomrule on my laptop
-% but not on my desktop...
-% Comment out for older LaTeX versions
-%\iffalse
-\ExplSyntaxOn
-\cs_new:Npn \expandableinput #1
-{ \use:c { @@input } { \file_full_name:n {#1} } }
-\AddToHook{env/tabular/begin}
-{ \cs_set_eq:NN \input \expandableinput }
-\ExplSyntaxOff
-%\fi
-
-%\usepackage[T1]{fontenc}
-%\usepackage[bitstream-charter]{mathdesign}
-
-\usepackage{chngcntr}
-\usepackage{longtable}
 \usepackage{adjustbox}
 \usepackage{dcolumn}
-\usepackage{pdflscape}
-
+\usepackage{moresize}
 \usepackage[nameinlink, capitalize, noabbrev]{cleveref}
-
-\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})}
-
-\makeatother
-
-\usepackage{footmisc}
-\setlength{\footnotesep}{\baselineskip}
-\makeatother
-\renewcommand{\footnotelayout}{\normalsize \doublespacing}
-
-% Colors
-\usepackage{color}
-
-\newcommand{\bch}{\color{blue}\em  }   % begin change
-\newcommand{\ying} {\color{orange}\em  }   % begin change
-\newcommand{\bgcd} {\color{purple}\em }
-\newcommand{\ech}{\color{black}\rm  }    % end change
-
-% Caption
-\usepackage[hang, font=small,skip=0pt, labelfont={bf}]{caption}
-%\captionsetup[subtable]{font=small,skip=0pt}
-\usepackage{subcaption}
-
-% tt font issues
-% \renewcommand*{\ttdefault}{qcr}
-\renewcommand{\ttdefault}{pcr}
-
-\usepackage[right]{lineno}
-
-\usepackage{tocloft}
-
-\usepackage{lscape}
-\renewcommand{\textfraction}{0}
-\renewcommand{\topfraction}{0.95}
-\renewcommand{\bottomfraction}{0.95}
-\renewcommand{\floatpagefraction}{0.40}
-\setcounter{totalnumber}{5}
-\makeatletter
-\providecommand\phantomcaption{\caption@refstepcounter\@captype}
-\makeatother
-
-\title{Holier Than Thou?
-No Large Partisan Gaps in the Consumption of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}
-}
-
-\author{Lucas Shen\thanks{Lucas is a Research Fellow at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
-
-\date{\today}
-
+\settowidth{\thanksmarkwidth}{*}
+\setlength{\thanksmargin}{-\thanksmarkwidth}
+\usepackage{titlesec}
+\setlength{\droptitle}{-5em}
+\setlength\thanksmarkwidth{.5em}
+\setlength\thanksmargin{-\thanksmarkwidth}
+\titleformat{\section}{\normalfont\bfseries\filcenter}{}{0pt}{}
+\titleformat{\subsection}{\normalfont\bfseries\filcenter}{}{0pt}{\itshape}
+\titleformat{\subsubsection}{\normalfont\bfseries\filcenter}{}{0pt}{\itshape}
+\titlespacing*{\section}
+  {0pt}{-.1\baselineskip}{-.1\baselineskip}  
+\titlespacing*{\subsection}
+   {0pt}{-.1\baselineskip}{-.1\baselineskip}
+
+\usepackage[T1]{fontenc}
+\usepackage{fontspec}
+\fontspec{Times New Roman}
+\date{}
+\providecommand{\keywords}[1]
+{
+   \small	
+  \textit{\hspace{-1em} Keywords: } #1
+}
+\newfontfamily\headingfont[]{Arial}
+%Add Author names to headers and footers here:
+\fancypagestyle{firstpage}{
+  \fancyhf{}% clear all fields
+  \fancyfoot[L]{\color{gray} \footnotesize Copyright \copyright 2021 (Author1, Author2, AuthorN).
+Licensed under the Creative Commons Attribution Non-commercial No Derivatives (by-nc-nd).
+Available at: \url{http://journalqd.org}}%
+  \lhead{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021), 1–n}
+\rhead{\color{gray} \footnotesize 10.51685/jqd.2024.011}
+}
+\pagestyle{fancy}
+\fancyhf{}
+\fancyhead[LO]{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021)}
+\fancyhead[RO]{\color{gray} \footnotesize Short Title \thepage}
+\fancyhead[LE]{\color{gray} \footnotesize Author1, Author2, AuthorN}
+\fancyhead[RE]{ \color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021) \thepage}
+% DO NOT MAKE CHANGES ABOVE THIS LINE
+%Article Title goes here
+\title{\normalsize \headingfont \textbf{Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online} \vspace{-1.5em}} 
+%Author names and affiliations go here, any Acknowledgements / authors' note / disclosure statement goes into \thanks{}
+\author{\normalsize FIRST AUTHOR NAME\\ \normalsize Institution, Country 
+\vspace{1em} \\ \normalsize SECOND AUTHOR NAME \\ \normalsize Institution, Country \thanks{Author 1: author1's enail address} \thanks{Author 2: author2's enail address} \thanks{Date submitted: XXXX-XX-XX}}
+\usepackage{lipsum}
+\renewcommand\footnotemark{}
 \begin{document}
 \maketitle
-
-\thispagestyle{empty}
+\thispagestyle{firstpage}
+\vspace{-8em}
+
 \begin{abstract}
-\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of the culture.
+  Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of the culture.
 Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online.
@@
 Lastly, we find, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, that Republicans consume somewhat more pornography online than Democrats.
-Adjusting for immutable characteristics like age and gender makes the differences go away.\\
-
+Adjusting for immutable characteristics like age and gender makes the differences go away.
 \emph{Keywords:} Measurement, YouGov, Pornography, Partisanship, Quantile Regression, Online Consumption
 \end{abstract}
-\clearpage
-\setcounter{page}{1}
-\doublespace
-%\linenumbers
+
+\keywords{\textit{measurement, YouGov, pornography, partisanship, quantile regression, online consumption} \vspace{8ex}}
+
 \section{Introduction}\label{sec:intro}
@@
 This unexpected finding suggests a discordance between survey responses and reported actions.
-Republicans may be consuming just as much pornography as Democrats; they are just saying otherwise.
+Republicans may be consuming just as much pornography as Democrats; they are simply saying otherwise.
 
@@
 
-In \ref{subsec:alternate_porn}, we leverage \texttt{piedomains} and a Google service, Virustotal, to assess whether our results are robust to alternate ways of measuring the kind of content accessed by people.
+In \hyperref[sm:smE]{Appendix E}, we leverage \texttt{piedomains} and a Google service, Virustotal, to assess whether our results are robust to alternate ways of measuring the kind of content accessed by people.
 \texttt{piedomains} uses open-source domain classification lists to train a neural network that learns the relationship between the kind of content hosted by a domain and the text on the homepage and homepage screenshots of websites \citep{Chintalapati_piedomains_Predict_the_2022}.
-%We leverage the probability estimates to produce inferences from low false negative and low false positive versions. 
 VirusTotal collates domain classification data from different private services.
@@
 
-In line with previous research \citep{hindman2009myth, Dewan2004-tt}, we find a considerable skew in online media consumption (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult}).
+In line with previous research \citep{hindman2009myth, Dewan2004-tt}, we find a considerable skew in online media consumption (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult} in \hyperref[sm:smA]{Appendix A}).
 As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites.
@@
 The median pornography consumer spends more hours on adult content than sites from six non-adult categories.
-Only three categories, ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), ``Business, Social Networking'' (e.g., facebook.com, facebook.co, soocial.com)),  and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile relative to online pornography consumption.
+Only three categories, ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), ``Business, Social Networking'' (e.g., facebook.com, soocial.com)),  and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile than online pornography.
 
@@
 To shed light on that, we examine the relationship between the time spent on online pornography vs.
-time spent on other leisure-related online sites (\cref{si:tu_porn_leisure}).
+time spent on other leisure-related online sites.
 We fit locally weighted linear regression after removing extreme values (90th percentile) in online consumption.
@@
 
-\begin{figure}[ht]
+\begin{figure}[!ht]
 \caption{Time Spent on Online Pornography vs. Non-adult Leisure}
@@
  The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
-Swapping the horizontal axis for adult content excluding adult-related entertainment and shopping sites looks similar (see \cref{fig:tu_prop_entertainment-prop_pure_adult}).
+Swapping the horizontal axis for adult content excluding adult-related entertainment and shopping sites looks similar (see \cref{fig:tu_prop_entertainment-prop_pure_adult} in \hyperref[sm:smC]{Appendix C}).
 }
@@
 
-Given the skew in the data, we quantify differences in online pornography consumption by party using quantile regression.\footnote{\cref{tab:characteristics_split_by_party_medians} presents non-parametric tests for differences in medians in consumption of pornography.} Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
-We regress the total time (share of time) spent on pornographic sites on an indicator for Republicans.
-
 %===========================
@@
 		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
-        \cref{tab:quantile-estimates-hours} tabulates the estimates.
+        \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
 	}
@@
             %\cref{tab:quantile-estimates-time} tabulates the estimates.
-            \cref{tab:quantile-estimates-time} tabulates the estimates.
+            \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
 	}
@@
 
+Given the skew in the data, we quantify differences in online pornography consumption by party using quantile regression.\footnote{\cref{tab:characteristics_split_by_party_medians} presents non-parametric tests for differences in medians in consumption of pornography.} Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+We regress the total time (share of time) spent on pornographic sites on an indicator for Republicans.
+
 As \cref{fig:quantile_regression_duration} shows, the 80th percentile of the difference is close to 0, but from thereon, there is a diverging trend with the 95th percentile difference nearly 1.6 hrs.
-(\cref{tab:quantile-estimates-hours} reports estimates for each quantile.).\footnote{\cref{si:independents} describes the distribution of consumption of pornography online by independents.
+(\cref{tab:quantile-estimates-hours} reports estimates for each quantile.).\footnote{\hyperref[sm:smF]{Appendix F} describes the distribution of consumption of pornography online by independents.
 The median independent consumes more pornography than partisans (1.3 hours vs.
@@
 We use these timestamps to evaluate the extent to which differences in the timing of consumption differ by partisanship.
-Overall, we find some evidence that Republicans consume more online pornography in the morning (see \cref{si:time_of_consumption}).
+Overall, we find some evidence that Republicans consume more online pornography in the morning (see \hyperref[sm:smD]{Appendix D}).
 
@@
 %=====================================================
-\begin{figure}[ht]
+\begin{figure}[!ht]
 	\centering
 	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
-  \cref{tab:quantile-estimates-hours} tabulates the estimates.
+  \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
 	}
@@
 %================================================================
-\begin{figure}[ht]
+\begin{figure}[!ht]
 	\centering
 	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
-        \cref{tab:quantile-estimates-time} tabulates the estimates.
+        \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
 	}
@@
 \subsection{Robustness}
-In \ref{si:visits}, we analyze similar metrics for total number of visits and proportion of visits instead of time.
-The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party}).
-We also replicate our analyses using four alternative classifications of domains (see \nameref{subsec:alternate_porn}) and obtain similar results.
+In \ref{si:visits}, we analyze similar metrics for the total number of visits and proportion of visits instead of time.
+The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party} in \hyperref[sm:smG]{Appendix G}).
+We also replicate our analyses using four alternative classifications of domains (see \hyperref[sm:smE]{Appendix E}) and obtain similar results.
 
@@
 
-The key strengths of our unique dataset include having micro-level records of online browsing activities, allowing us to track timestamped visits to multiple online pornography sites.
-Moreover, our dataset also allows us to adjust for partisan differences in fundamental baseline demographics.\footnote{Other studies we cite in this paper lack this combination of ground-truth individual-level consumption of online pornography and individual-level demographics (e.g., \cite{Peek1982-ua, Woodrum1992-vk, Markey2011-xo, Perry2020-cp, Ybarra2005-id, Perry2018-cw, Price2016-sm, webporn, Wright2013-gl}).} \footnote{A more subtle strength of our study is that it is conducted around 2022, by which time differences in online content consumption---including pornography content--- are unlikely to be driven by variations in regional broadband penetration.}
-
-Our research has three major limitations.
+The key strengths of our unique dataset include having micro-level records of online browsing activities, allowing us to track timestamped visits to online pornography.
+Moreover, our dataset also allows us to adjust for partisan differences in fundamental baseline demographics.\footnote{Other studies on the topic lack this combination of ground-truth individual-level consumption of online pornography and individual-level demographics (e.g., \cite{Peek1982-ua, Woodrum1992-vk, Markey2011-xo, Perry2020-cp, Ybarra2005-id, Perry2018-cw, Price2016-sm, webporn, Wright2013-gl}).} \footnote{A more subtle strength of our study is that it was conducted around 2022, by which time differences in online content consumption---including pornography content--- are unlikely to be driven by variations in regional broadband penetration, a point \cite{edelman2009markets} worries about.}
+
+Our research has two major limitations.
 The first concern with our data is that we may not have all the Internet visitation data of a user.
@@
 
-The second concern with our measurement is that we code content at a domain level.
-This runs the risk of incurring some ecological fallacy.
-For instance, our classification codes websites like Tumblr as not carrying pornographic content, but some of Tumblr's content is pornographic.
-
-The third concern is that our measures are a point in time.
+The second concern is that our measures are a point in time.
 We have data from one month in one year - June 2022.
@@
 
-% Strengths of our approach
-% Unlike traditional sources like survey or using google searches (like Markey 2011 Pornography-seeking behaviors following midterm political elections in the United States: A replication of the challenge hypothesis), they lack groundtruth AND finegrain info on timing of consumption
-% Unlike pornhub that has IP addresses, has fuller universe of porn consumers, they lack individual level covariates
-% More recent, less susceptible to differences in broadband penetration by area (as opposed to the same study 10 years ago)
-
-%\clearpage
-\bibliographystyle{apsr}
+\section{Acknowledgments}
+Acknowledgements/ Author's disclosure/ funding statement.
+
 \bibliography{porn,paperpile}
+\addcontentsline{toc}{section}{References}
+
 \clearpage
-
-%===============================================================================
-%===============================================================================
+% =============================================================================
 % 	Appendix
-%===============================================================================
-%===============================================================================
-\appendix
-\renewcommand{\thesection}{SI \arabic{section}}
-\setcounter{table}{0}\renewcommand\thetable{\thesection.\arabic{table}}
-\setcounter{figure}{0}\renewcommand\thefigure{\thesection.\arabic{figure}}
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-
-\begin{center}
-\Large \textbf{Supporting Information}
-\end{center}
-\singlespacing
-\vspace{-.4in}
-\label{si}
-%\begin{center}
-%\Large{Supporting Information}
-%\end{center}
-
+% =============================================================================
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+
+\setcounter{secnumdepth}{0}
+\section[Supplementary Information]{\large Supplementary Information (Authors here \today)}\label{sec:sm}
+%\onehalfspacing
+\normalsize
+
+\newcommand{\smATitle}{Descriptive Analyses}
+\newcommand{\smBTitle}{Partisan Differences}
+\newcommand{\smCTitle}{Online Pornography vs. Leisure}
+\newcommand{\smDTitle}{Time of Consumption}
+\newcommand{\smETitle}{Alternate Classifications of Pornography Sites}
+\newcommand{\smFTitle}{Consumption of Pornography Among Independents}
+\newcommand{\smGTitle}{Alternate Measures of Pornography}
+
+%\noindent 
+\textbf{\hphantom{aaa}Table of Contents}\\
+\hyperref[sm:smA]{\indent \textcolor{magenta}{\S A:}} \smATitle{}\\
+\hyperref[sm:smB]{\indent \textcolor{magenta}{\S B:}} \smBTitle{}\\
+\hyperref[sm:smC]{\indent \textcolor{magenta}{\S C:}} \smCTitle{}\\
+\hyperref[sm:smD]{\indent \textcolor{magenta}{\S D:}} \smDTitle{}\\
+\hyperref[sm:smE]{\indent \textcolor{magenta}{\S E:}} \smETitle{}\\
+\hyperref[sm:smF]{\indent \textcolor{magenta}{\S F:}} \smFTitle{}\\
+\hyperref[sm:smG]{\indent \textcolor{magenta}{\S G:}} \smGTitle{}\\
+
+\clearpage
+% =============================================================================
 \FloatBarrier
-%===============================================================================
-% Supplementary Descriptives for sense of landscape of porn consumption
-%===============================================================================
-\section{Descriptive Analysis}
-
-\subsection{Website Visits Are Highly Skewed}
+\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thefigure}{A\arabic{figure}}
+\renewcommand{\theequation}{A\arabic{equation}}
+\subsection{A. \smATitle{}}\label{sm:smA}
+% =============================================================================
+
+\subsubsection{Website Visits Are Highly Skewed}
 
@@
 %================================
-\begin{figure}
+\begin{figure}[h]
 	\centering
@@
 \begin{landscape}% Landscape page
-    \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{3 pt} \setlength{\defaultaddspace}{0pt}
+    \begin{table}[ht] \centering \small \setlength\tabcolsep{3 pt} \setlength{\defaultaddspace}{0pt}
     \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
@@
 
+\clearpage
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
 \FloatBarrier
-\clearpage
-\section{Partisan Differences}
+\renewcommand{\thetable}{B\arabic{table}}
+\renewcommand{\thefigure}{B\arabic{figure}}
+\renewcommand{\theequation}{B\arabic{equation}}
+\subsection{B. \smBTitle{}}\label{sm:smB}
+% =============================================================================
 
@@
 \clearpage
-\subsection{Accounting for Confounders}
+\subsubsection{Accounting for Confounders}
+
+%==============================================================================
+% Table for balance of porn consumption and individual characteristics by party
+%==============================================================================
+\begin{table}[!ht] \centering \ssmall \setlength\tabcolsep{9 pt}
+	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
+	\label{tab:characteristics_split_by_party}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
+			\toprule
+			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{tabs/balance_outcomes_by_party.tex}\\
+			%-------------------------------------------------------------------
+			\cmidrule{2-8}
+			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
+			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-8}
+			\input{tabs/balance_covariates_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:}
+		The table shows splits by party for pornographic consumption and for individual characteristics for the 1,200 individuals.
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) shows subgroups for categorical variables.
+		Column (2) indicates the count of missing variables, if any.
+		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables for the full sample, Democratic individuals, and Republican individuals.
+		Standard deviations and percentages are in parentheses.
+		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
+		Given the skew in consumption of pornography, we also performed tests for differences in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
+	}
+\end{table}
 
@@
 %==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+\begin{table}[ht] \centering \scriptsize \setlength\tabcolsep{6 pt}
 	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
@@
 
-%==============================================================================
-% Table for balance of porn consumption and individual characteristics by party
-%==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
-	\label{tab:characteristics_split_by_party}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
-			\toprule
-			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{tabs/balance_outcomes_by_party.tex}\\
-			%-------------------------------------------------------------------
-			\cmidrule{2-8}
-			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
-			\input{tabs/balance_covariates_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
-		The table shows splits by party for pornographic consumption and for individual characteristics for the 1,200 individuals.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables for the full sample, Democratic individuals, and Republican individuals.
-		Standard deviations and percentages are in parentheses.
-		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in consumption of pornography, we also performed tests for differences in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
-	}
-\end{table}
-
 \clearpage
@@
 \begin{landscape}% Landscape page
-    \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{0 pt} \setlength{\defaultaddspace}{0pt}
+    \begin{table}[ht] \centering \ssmall \setlength\tabcolsep{0 pt} \setlength{\defaultaddspace}{0pt}
     \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
@@
 
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
 \FloatBarrier
-%===============================================================================
-% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
-%===============================================================================
-\section{Alternate Ways of Measuring Pornography}
-\label{subsec:alternate_porn}
-\subsection{Piedomains}
+\renewcommand{\thetable}{C\arabic{table}}
+\renewcommand{\thefigure}{C\arabic{figure}}
+\renewcommand{\theequation}{C\arabic{equation}}
+\subsection{C. \smCTitle{}}\label{sm:smC}
+% =============================================================================
+
+\begin{figure}[!h]
+\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
+\label{fig:tu_prop_entertainment-prop_pure_adult}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_pure_adult.pdf}
+         \caption{Entertainment}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_pure_adult.pdf}
+         \caption{Shopping}
+     \end{subfigure}
+\caption*{\footnotesize \emph{Notes:}
+Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs time spent on other non-adult leisure (``entertainment'' and ``shopping'').
+Observations above the 90th percentile are omitted. 
+Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five of such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
+Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---top five of such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
+Top five pure adult sites are: xvideos.com, pornhub.com, xnxx.com, rule34.xxx, and xhamster.com (see \cref{fig:top25_adult}).
+Each estimation in the Lowess uses .3 of the sample data.
+The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
+Swapping the horizontal axis for any adult content looks similar in \cref{fig:tu_prop_entertainment-prop_adult_duration}. 
+}
+\end{figure}
+
+\clearpage
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
+\FloatBarrier
+\renewcommand{\thetable}{D\arabic{table}}
+\renewcommand{\thefigure}{D\arabic{figure}}
+\renewcommand{\theequation}{D\arabic{equation}}
+\subsection{D. \smDTitle{}}\label{sm:smD}
+% =============================================================================
+
+First, we evaluate the density of the timing of visits to online pornography sites using 24-hour bins.
+As anticipated, most visits to online pornography sites occur around midnight.
+We also observe considerable traffic around the midday (1--3 pm, \cref{fig:time-of-day-consumption}).
+Both these observations track with \cite{webporn}'s findings using web session data.
+Second, we repeat the evaluation of the density of the timing of visits but split by partisanship.
+
+The densities suggest that Democratic traffic to pornography sites is concentrated around midnight (11 pm--1 am) while the Republican traffic is concentrated in the early morning (6 am--7 am, \cref{fig:time-of-day-consumption-by-party}).
+
+Third, to formally test whether there are differences in time of consumption by partisanship, we begin by dividing traffic to online pornography sites into six 4-hour bins: (a) 4 am--8 am, (b) 8 am--12 pm, (c) 12 pm--4 pm, (d) 4 pm--8 pm, (e) 8 pm--12 am, and (f) 12 am--4 am.
+We code a visit depending on which time interval it occurred and regress that time-of-day window on partisanship, weighted by the dwelling time of the visit.
+Cognizant of the somewhat ad-hoc splits for the time-of-day windows and that we are creating multiple outcome variables, we subject p-values of the partisan point estimate to Bonferroni correction in addition to the adjustments for individual-level demographics.
+
+\begin{figure}[ht]
+\centering
+\caption{Time-of-Day Traffic to Online Pornography Sites}
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption.pdf}
+\caption*{\footnotesize \emph{Notes:} 
+        Density plot of traffic to online pornography sites.
+        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 84,289).
+        Each of the 24 bins corresponds to an hour of the day.
+	}
+    \label{fig:time-of-day-consumption}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption-by-party.pdf}
+\caption*{\footnotesize \emph{Notes:} 
+        Density plot of traffic to online pornography sites by partisanship (indicated by colors); bars for Republican consumption are also hatched.
+        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 59,324).
+        Each of the 24 bins corresponds to an hour of the day.
+        See \cref{tab:regtab_wls_visit_timing_4hrbins}, which reports formal tests of differences in time-of-day visits by party.
+	}
+    \label{fig:time-of-day-consumption-by-party}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
+    \includegraphics[width=.85\linewidth]{figs/time-of-day-wls-estimates.pdf}
+\caption*{\footnotesize \emph{Notes:} 
+        Estimates of partisan differences in time-of-day visits to online pornography sites.
+        Points represent differences between Republicans relative to Democrats (reference category)---interpreted as proportion differences.
+        The adjusted estimate, which is significant at the 1\% level after Bonferroni correction (at 4 am--8 am), is indicated in the figure.
+        Vertical lines are 95\% confidence intervals.
+        This figure offers an alternative visualization of \cref{tab:regtab_wls_visit_timing_4hrbins}.
+	}
+    \label{fig:time-of-day-wls-estimates}
+\end{figure}
+
+\cref{fig:time-of-day-wls-estimates} reports a summary of this exercise (\cref{tab:regtab_wls_visit_timing_4hrbins} reports the full set of estimates).
+The unadjusted estimates suggest that Republicans are more likely to consume pornography during midday (the 12 pm--4 pm window), relative to Democrats, which is significant at the 1 percent level after correction.
+Conversely, Republicans are less likely to consume pornography late at night (12 am--4 am).
+These unadjusted findings correspond somewhat to our evaluation of densities of visits by partisanship where Democrat visits to online pornography are concentrated around midnight (\cref{fig:time-of-day-consumption-by-party}).
+
+Once we adjust for the individual-level demographics and for day-of-week fixed effects, Republicans are no longer more (or less) likely to consume pornography during the midday (or late at night).
+However, the adjusted estimates suggest that Republicans are more likely to consume pornography in the early morning (4 am--8 am), specifically five percentage points more likely, which is significant at the 1 percent level even after Bonferroni correction (indicated in \cref{fig:time-of-day-wls-estimates}).
+
+\begin{table}[!ht] \centering \scriptsize \setlength\tabcolsep{9 pt} \setlength{\defaultaddspace}{0pt}
+\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+\caption{Time-of-Day Traffic to Pornographic by Party}
+\label{tab:regtab_wls_visit_timing_4hrbins}
+\begin{adjustbox}{max width=\textwidth}
+        \begin{tabular}{@{\hspace{0\tabcolsep}}l*{6}{D{.}{.}{-1}}@{\hspace{0\tabcolsep}}}
+        \toprule\toprule
+        &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}\\
+        \cmidrule(l){2-7}
+        &\multicolumn{6}{c}{\textbf{Panel A. WLS estimates}}\\
+        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
+        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
+        \cmidrule(l){2-7}
+        \input{tabs/regtab_wls_visit_timing_4hrbins}\\
+        \cmidrule(l){2-7}
+        &\multicolumn{6}{c}{\textbf{Panel B. Adjusted WLS estimates}}\\
+        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
+        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
+        \cmidrule(l){2-7}
+        \input{tabs/regtab_wls_visit_timing_4hrbins_adjusted}\\
+    \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption*{\scriptsize
+    The table reports weighted least squares estimates from regressing a binary variable based on time-of-day visits to online pornography on the Republican dummy.
+    The unit of observation is at the individual web browsing level for traffic to pornography sites (n = 59,324).
+    Each column represents dummy variables for each of the six 4-hour windows.
+    Weights are the duration of each visit.
+    Models also adjust for day-of-week fixed effects (not reported to conserve space).
+    See also \cref{fig:time-of-day-consumption-by-party}, which provides descriptive evidence that the density in time-of-day traffic is different by party.
+    Significance levels (uncorrected): $^{*}$ 0.05 $^{**}$0.01.
+    P-values are Bonferroni-corrected for six tests---the $^\dagger$ indicates significance at the p = 0.01 level after adjustment.    
+    }
+\end{table}
+
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
+\FloatBarrier
+\renewcommand{\thetable}{E\arabic{table}}
+\renewcommand{\thefigure}{E\arabic{figure}}
+\renewcommand{\theequation}{E\arabic{equation}}
+\subsection{E. \smETitle{}}\label{sm:smE}
+% =============================================================================
+\subsubsection{Piedomains}
 %============================
@@
 \clearpage
-\subsection{Forcepoint ThreatSeeker}
+\subsubsection{Forcepoint ThreatSeeker}
 %============================
@@
 %============================
-\begin{figure}[ht]
+\begin{figure}[!ht]
 	\centering
@@
 \clearpage
-\subsection{Bitdefender}
+\subsubsection{Bitdefender}
 %============================
@@
 \clearpage
-\subsection{alphaMountain}
+\subsubsection{alphaMountain}
 %============================
@@
 
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
 \FloatBarrier
-\clearpage
-\section{Consumption of Pornography Among Independents}
-\label{si:independents}
+\renewcommand{\thetable}{F\arabic{table}}
+\renewcommand{\thefigure}{F\arabic{figure}}
+\renewcommand{\theequation}{F\arabic{equation}}
+\subsection{F. \smFTitle{}}\label{sm:smF}
+% =============================================================================
 %===========================================================================
@@
 %===========================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
+\begin{table}[!ht] \centering \small \setlength\tabcolsep{6 pt}
 	\caption{Time Spent on Pornographic Sites (including Independents)}
@@
 
-\cleardoublepage
+\clearpage
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
 \FloatBarrier
-\section{Alternate Measures}
-\subsection{Proportion of the Group That Consumed Any Pornography}
+\renewcommand{\thetable}{G\arabic{table}}
+\renewcommand{\thefigure}{G\arabic{figure}}
+\renewcommand{\theequation}{G\arabic{equation}}
+\subsection{G. \smGTitle{}}\label{sm:smG}
+% =============================================================================
+\subsubsection{Proportion of the Group That Consumed Any Pornography}
 %============================================================================
@@
 
-\cleardoublepage
-\FloatBarrier
-%===============================================================================
-%===============================================================================
-% Time use --- substitution
-%===============================================================================
-%===============================================================================
-
-%===============================================================================
-%===============================================================================
-%===============================================================================
-\section{Online Pornography vs. Leisure}\label{si:tu_porn_leisure}
-% adult vs non-adult entertainment
-% adult vs non-adult shopping
-
-% Pure adult vs adult-entertainment
-% Pure adult vs adult shopping
-
-% Pure adult vs nonadult entertainment
-% Pure adult vs nondault shopping
-
-\begin{figure}[ht]
-\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
-\label{fig:tu_prop_entertainment-prop_pure_adult}
-     \centering
-     \begin{subfigure}[b]{0.495\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_pure_adult.pdf}
-         \caption{Entertainment}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.495\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_pure_adult.pdf}
-         \caption{Shopping}
-     \end{subfigure}
-\caption*{\footnotesize \emph{Notes:}
-Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs time spent on other non-adult leisure (``entertainment'' and ``shopping'').
-Observations above the 90th percentile are omitted. 
-Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five of such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
-Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---top five of such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
-Top five pure adult sites are: xvideos.com, pornhub.com, xnxx.com, rule34.xxx, and xhamster.com (see \cref{fig:top25_adult}).
-Each estimation in the Lowess uses .3 of the sample data.
-The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
-Swapping the horizontal axis for any adult content looks similar in \cref{fig:tu_prop_entertainment-prop_adult_duration}. 
-}
-\end{figure}
-
-\FloatBarrier
-\clearpage
-%===============================================================================
-%===============================================================================
-\section{Time of Consumption}
-%===============================================================================
-\label{si:time_of_consumption}
-
-First, we evaluate the density of the timing of visits to online pornography sites using 24-hour bins.
-As anticipated, most visits to online pornography sites occur around midnight.
-We also observe considerable traffic around the midday (1--3 pm, \cref{fig:time-of-day-consumption}).
-Both these observations track with \cite{webporn}'s findings using web session data.
-Second, we repeat the evaluation of the density of the timing of visits but split by partisanship.
-
-The densities suggest that Democratic traffic to pornography sites is concentrated around midnight (11 pm--1 am) while the Republican traffic is concentrated in the early morning (6 am--7 am, \cref{fig:time-of-day-consumption-by-party}).
-
-\begin{figure}[ht]
-\centering
-\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
-    \includegraphics[width=.85\linewidth]{figs/time-of-day-wls-estimates.pdf}
-\caption*{\footnotesize \emph{Notes:} 
-        Estimates of partisan differences in time-of-day visits to online pornography sites.
-        Points represent differences between Republicans relative to Democrats (reference category)---interpreted as proportion differences.
-        The adjusted estimate, which is significant at the 1\% level after Bonferroni correction (at 4 am--8 am), is indicated in the figure.
-        Vertical lines are 95\% confidence intervals.
-        This figure offers an alternative visualization of \cref{tab:regtab_wls_visit_timing_4hrbins}.
-	}
-    \label{fig:time-of-day-wls-estimates}
-\end{figure}
-
-Third, to formally test whether there are differences in time of consumption by partisanship, we begin by dividing traffic to online pornography sites into six 4-hour bins: (a) 4 am--8 am, (b) 8 am--12 pm, (c) 12 pm--4 pm, (d) 4 pm--8 pm, (e) 8 pm--12 am, and (f) 12 am--4 am.
-We code a visit depending on which time interval it occurred and regress that time-of-day window on partisanship, weighted by the dwelling time of the visit.
-Cognizant of the somewhat ad-hoc splits for the time-of-day windows and that we are creating multiple outcome variables, we subject p-values of the partisan point estimate to Bonferroni correction in addition to the adjustments for individual-level demographics.
-
-\cref{fig:time-of-day-wls-estimates} reports a summary of this exercise (\cref{tab:regtab_wls_visit_timing_4hrbins} in \cref{si:time_of_consumption} reports the full set of estimates).
-The unadjusted estimates suggest that Republicans are more likely to consume pornography during midday (the 12 pm--4 pm window), relative to Democrats, which is significant at the 1 percent level after correction.
-Conversely, Republicans are less likely to consume pornography late at night (12 am--4 am).
-These unadjusted findings correspond somewhat to our evaluation of densities of visits by partisanship where Democrat visits to online pornography are concentrated around midnight (\cref{fig:time-of-day-consumption-by-party}).
-
-Once we adjust for the individual-level demographics and for day-of-week fixed effects, Republicans are no longer more (or less) likely to consume pornography during the midday (or late at night).
-However, the adjusted estimates suggest that Republicans are more likely to consume pornography in the early morning (4 am--8 am), specifically five percentage points more likely, which is significant at the 1 percent level even after Bonferroni correction (indicated in \cref{fig:time-of-day-wls-estimates}).
-
-\begin{figure}[ht]
-\centering
-\caption{Time-of-Day Traffic to Online Pornography Sites}
-    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption.pdf}
-\caption*{\footnotesize \emph{Notes:} 
-        Density plot of traffic to online pornography sites.
-        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 84,289).
-        Each of the 24 bins corresponds to an hour of the day.
-	}
-    \label{fig:time-of-day-consumption}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
-    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption-by-party.pdf}
-\caption*{\footnotesize \emph{Notes:} 
-        Density plot of traffic to online pornography sites by partisanship (indicated by colors); bars for Republican consumption are also hatched.
-        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 59,324).
-        Each of the 24 bins corresponds to an hour of the day.
-        See \cref{tab:regtab_wls_visit_timing_4hrbins}, which reports formal tests of differences in time-of-day visits by party.
-	}
-    \label{fig:time-of-day-consumption-by-party}
-\end{figure}
-
-\begin{table}[ht] \centering \footnotesize \setlength\tabcolsep{6 pt} \setlength{\defaultaddspace}{0pt}
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-\caption{Time-of-Day Traffic to Pornographic by Party}
-\label{tab:regtab_wls_visit_timing_4hrbins}
-\begin{adjustbox}{max width=\textwidth}
-        \begin{tabular}{@{\hspace{0\tabcolsep}}l*{20}{D{.}{.}{-1}}@{\hspace{0\tabcolsep}}}
-        \toprule\toprule
-        &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}\\
-        \cmidrule(l){2-7}
-        &\multicolumn{6}{c}{\textbf{Panel A. WLS estimates}}\\
-        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
-        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
-        \cmidrule(l){2-7}
-        \input{tabs/regtab_wls_visit_timing_4hrbins}\\
-        \cmidrule(l){2-7}
-        &\multicolumn{6}{c}{\textbf{Panel B. Adjusted WLS estimates}}\\
-        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
-        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
-        \cmidrule(l){2-7}
-        \input{tabs/regtab_wls_visit_timing_4hrbins_adjusted}\\
-    \bottomrule
-    \end{tabular}
-    \end{adjustbox}
-    \caption*{\scriptsize
-    The table reports weighted least squares estimates from regressing a binary variable based on time-of-day visits to online pornography on the Republican dummy.
-    The unit of observation is at the individual web browsing level for traffic to pornography sites (n = 59,324).
-    Each column represents dummy variables for each of the six 4-hour windows.
-    Weights are the duration of each visit.
-    Models also adjust for day-of-week fixed effects (not reported to conserve space).
-    See also \cref{fig:time-of-day-consumption-by-party}, which provides descriptive evidence that the density in time-of-day traffic is different by party.
-    Significance levels (uncorrected): $^{*}$ 0.05 $^{**}$0.01.
-    P-values are Bonferroni-corrected for six tests---the $^\dagger$ indicates significance at the p = 0.01 level after adjustment.    
-    }
-\end{table}
-
 \end{document}

### 2024-04-21 tabs/predict_pid.tex

\begin{table}
\small
    \begin{tabular}{lllll}
    \textbf{Reg Model}  & \textbf{Hyperparams}                             & \textbf{Predictors}                                        & \textbf{Accuracy (in sample)} & \textbf{Accuracy (o.o.s.)} \\
    CV penalized & $\alpha = 1$, $\lambda = 0.03$ & Demographics only                                 & 0.617                & 0.601                    \\
    CV penalized & $\alpha = 0.5$, $\lambda = 0.07$ &  Web visits only (counts)                          & 0.703                & 0.407                    \\
    CV penalized & $\alpha = 0.5$, $\lambda = 0.05$ &  Political site visits (counts), demographics      & 0.687                & 0.584                    \\
    CV penalized & $\alpha = 0.5$, $\lambda = 0.03$ &  Political site visits (proportions), demographics & 0.671                & 0.567                    \\
    CV penalized & $\alpha = 1$, $\lambda = 0.05$ &  Web visits (counts), demographics                 & 0.92                 & 0.576                    \\
    CV penalized & $\alpha = 1$, $\lambda = 0.05$ &  Web visits (proportions), demographics            & 0.391                & 0.556                    \\
    \end{tabular}
\end{table}

### 2024-04-25 ms/adult.tex
Updates from Overleaf

@@
 We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}.
-Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research, using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
+Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
 Combining individual-level data on partisanship with directly measured pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa.
@@
 \subsection{Robustness}
-In \ref{si:visits}, we analyze similar metrics for total number of visits and proportion of visits instead of time.
+In \ref{si:visits}, we analyze similar metrics for the total number of visits and proportion of visits instead of time.
 The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party}).
@@
 
-The key strengths of our unique dataset include having micro-level records of online browsing activities, allowing us to track timestamped visits to multiple online pornography sites.
-Moreover, our dataset also allows us to adjust for partisan differences in fundamental baseline demographics.\footnote{Other studies we cite in this paper lack this combination of ground-truth individual-level consumption of online pornography and individual-level demographics (e.g., \cite{Peek1982-ua, Woodrum1992-vk, Markey2011-xo, Perry2020-cp, Ybarra2005-id, Perry2018-cw, Price2016-sm, webporn, Wright2013-gl}).} \footnote{A more subtle strength of our study is that it is conducted around 2022, by which time differences in online content consumption---including pornography content--- are unlikely to be driven by variations in regional broadband penetration.}
-
-Our research has three major limitations.
+The key strengths of our unique dataset include having micro-level records of online browsing activities, allowing us to track timestamped visits to online pornography.
+Moreover, our dataset also allows us to adjust for partisan differences in fundamental baseline demographics.\footnote{Other studies on the topic lack this combination of ground-truth individual-level consumption of online pornography and individual-level demographics (e.g., \cite{Peek1982-ua, Woodrum1992-vk, Markey2011-xo, Perry2020-cp, Ybarra2005-id, Perry2018-cw, Price2016-sm, webporn, Wright2013-gl}).}\footnote{A more subtle strength of our study is that it was conducted around 2022, by which time differences in online content consumption---including pornography content--- are unlikely to be driven by variations in regional broadband penetration, a point \cite{edelman2009markets} worries about.}
+
+Our research has two major limitations.
 The first concern with our data is that we may not have all the Internet visitation data of a user.
@@
 
-The second concern with our measurement is that we code content at a domain level.
+%The second concern with our measurement is that we code content at a domain level.
 This runs the risk of incurring some ecological fallacy.
@@
 
-The third concern is that our measures are a point in time.
+The second concern is that our measures are a point in time.
 We have data from one month in one year - June 2022.
@@
 
-% Strengths of our approach
-% Unlike traditional sources like survey or using google searches (like Markey 2011 Pornography-seeking behaviors following midterm political elections in the United States: A replication of the challenge hypothesis), they lack groundtruth AND finegrain info on timing of consumption
-% Unlike pornhub that has IP addresses, has fuller universe of porn consumers, they lack individual level covariates
-% More recent, less susceptible to differences in broadband penetration by area (as opposed to the same study 10 years ago)
-
-%\clearpage
+\clearpage
 \bibliographystyle{apsr}
@@
 \section{Online Pornography vs. Leisure}\label{si:tu_porn_leisure}
-% adult vs non-adult entertainment
-% adult vs non-adult shopping
-
-% Pure adult vs adult-entertainment
-% Pure adult vs adult shopping
-
-% Pure adult vs nonadult entertainment
-% Pure adult vs nondault shopping
 

### 2024-04-25 ms/main.tex
Updates from Overleaf

@@
 citecolor={darkgray},
-pdftitle={Holier Than Thou? Partisan Gaps in Pornography}
+pdftitle={Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online}
 ]{hyperref}
@@
   \fancyhf{}% clear all fields
-  \fancyfoot[L]{\color{gray} \footnotesize Copyright \copyright 2021 (Author1, Author2, AuthorN).
+  \fancyfoot[L]{\color{gray} \footnotesize Copyright \copyright 2024 Lucas Shen and Gaurav Sood.
 Licensed under the Creative Commons Attribution Non-commercial No Derivatives (by-nc-nd).
@@
 \fancyhf{}
-\fancyhead[LO]{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021)}
-\fancyhead[RO]{\color{gray} \footnotesize Short Title \thepage}
-\fancyhead[LE]{\color{gray} \footnotesize Author1, Author2, AuthorN}
+\fancyhead[LO]{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024)}
+\fancyhead[RO]{\color{gray} \footnotesize Consumption of Pornography Online \thepage}
+\fancyhead[LE]{\color{gray} \footnotesize Lucas Shen and Gaurav Sood}
 \fancyhead[RE]{ \color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021) \thepage}
@@
 %Author names and affiliations go here, any Acknowledgements / authors' note / disclosure statement goes into \thanks{}
-\author{\normalsize FIRST AUTHOR NAME\\ \normalsize Institution, Country 
-\vspace{1em} \\ \normalsize SECOND AUTHOR NAME \\ \normalsize Institution, Country \thanks{Author 1: author1's enail address} \thanks{Author 2: author2's enail address} \thanks{Date submitted: XXXX-XX-XX}}
+\author{\normalsize Lucas Shen\\ \normalsize National University of Singapore, Singapore
+\vspace{1em} \\ \normalsize Gaurav Sood \\ \normalsize Independent Researcher, USA \thanks{Lucas Shen: \href{mailto:lucas@lucasshen.com}{lucas@lucasshen.com}}\thanks{Gaurav Sood: \href{mailto:gsood07@gmail.com}{gsood07@gmail.com}}\thanks{Date submitted: 2023-03-13}}
 \usepackage{lipsum}
@@
 
+\begin{figure}[!ht]
+\caption{Hours Spent on Online Pornography and All Other Online Content}
+\label{fig:distribution_duration_on_adultsites_fullsample}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/distribution_duration_on_adultsites_fullsample.pdf}
+         \caption{Online pornography}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/distribution_duration_on_nonadultsites_fullsample.pdf}
+         \caption{Other online content}
+     \end{subfigure}
+\caption*{\footnotesize \emph{Notes:} 
+    Each panel shows the total number of hours for the sample period.
+    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
+    The height of the bars indicates the mean of each bin. 
+    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
+    %textbf{FIG??} shows the same figures but only for consumers of pornography.
+}
+\end{figure}
+
+\cref{fig:distribution_duration_on_adultsites_fullsample} plots hours spent on pornography sites and all other online content for the entire sample.
+Consumption of online pornography pales in comparison to all other online content.
 Only 31.8 percent of the respondents consumed any pornography online during the observation period (see column 3 of \cref{tab:characteristics_split_by_party}).
@@
 
-Given the skew in the data, we quantify differences in online pornography consumption by party using quantile regression.\footnote{\cref{tab:characteristics_split_by_party_medians} presents non-parametric tests for differences in medians in consumption of pornography.} Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+Given the skew in the data, we quantify differences in online pornography consumption by party using quantile regression.\footnote{\cref{tab:characteristics_split_by_party_medians} presents non-parametric tests for differences in medians in the consumption of pornography.} Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
 We regress the total time (share of time) spent on pornographic sites on an indicator for Republicans.
@@
 
-\section{Acknowledgments}
-Acknowledgements/ Author's disclosure/ funding statement.
+%\section{Acknowledgments}
+%Acknowledgments/ Author's disclosure/ funding statement.
 
@@
 \setcounter{secnumdepth}{0}
-\section[Supplementary Information]{\large Supplementary Information (Authors here \today)}\label{sec:sm}
+\section[Supplementary Information]{\large Supplementary Information}\label{sec:sm}
 %\onehalfspacing
@@
 \newcommand{\smATitle}{Descriptive Analyses}
+\newcommand{\smCTitle}{Online Pornography vs. Leisure}
 \newcommand{\smBTitle}{Partisan Differences}
-\newcommand{\smCTitle}{Online Pornography vs. Leisure}
+\newcommand{\smETitle}{Alternate Classifications of Pornography Sites}
+\newcommand{\smGTitle}{Alternate Measures of Pornography}
+\newcommand{\smFTitle}{Consumption of Pornography Among Independents}
 \newcommand{\smDTitle}{Time of Consumption}
-\newcommand{\smETitle}{Alternate Classifications of Pornography Sites}
-\newcommand{\smFTitle}{Consumption of Pornography Among Independents}
-\newcommand{\smGTitle}{Alternate Measures of Pornography}
 
@@
             All numbers are based on online visits during the one-month period.
-		The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+		The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
 		The \emph{Visits} column is the total number of visits by individuals in the sample to the site.  			
@@
 		Pornography sites are categorized by YouGov (see the \nameref{sec:data} section).
-    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
     	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		Covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
@@
             See \cref{fig:top25_adult} for a comparison with our base classification.
-    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
     	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
@@
 Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+Covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 95\% confidence intervals constructed from standard errors.

### 2024-04-25 ms/misc/anon_adult.tex
Updates from Overleaf

--- 2023-01-08 ms/adult.tex
@@
 
-\title{Holier Than Thou: Partisan Gap in the Consumption\\ of Pornography Online\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}}
-
-\author{Lucas Shen\thanks{Lucas is a Research Fellow at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
+\title{Holier Than Thou: Partisan Gap in the Consumption\\ of Pornography Online}%\thanks{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.}}
+
+%\author{Lucas Shen\thanks{Lucas is a Research Fellow at Asia Competitiveness Institute, Lee Kuan Yew School of Public Policy, at the National University of Singapore, \href{mailto:lucas@lucasshen.com}{\footnotesize{\texttt{lucas@lucasshen.com}}}} \and Gaurav Sood\thanks{Gaurav can be reached at \href{mailto:gsood07@gmail.com}{\footnotesize{\texttt{gsood07@gmail.com}}}}\vspace{.5cm}}
 
@@
 \begin{abstract}
-\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture.
+\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of the culture.
 Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online.
@@
 Of the people who consumed pornography, the median consumer spent about three-quarters of an hour consuming pornography and 95 percent of the consumers spent less than five and a half hours.
-Lastly, we find that, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, Republicans consume somewhat more pornography online than Democrats.
+Lastly, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, we find that Republicans consume slightly more pornography online than Democrats.
 Adjusting for immutable characteristics like age and gender makes the differences go away.
@@
 Consumption of pornography is associated with a variety of disturbing attitudes, beliefs, emotions, and behaviors.
-Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex, and having extramarital sex \citep{wright2012internet}.
+Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex and having extramarital sex \citep{wright2012internet}.
 A lot of popular pornography also contains a healthy dose of violence.
@@
 Both parties claim the higher moral ground.
-And in surveys both parties think consumption of pornography is abhorrent.
+And in surveys, both parties think the consumption of pornography is abhorrent.
 Like previous research, which relied on aggregated data, we find that Republicans consume somewhat more pornography online than Democrats \citep{macinnis2015american, edelman2009markets}.
-Adjusting for background attributes like age, gender etc., makes the differences go away.
+Adjusting for background attributes like age, gender, etc., makes the differences go away.
 
@@
 
-The data are from 1,200 respondents for June, 2022.
+The data are from 1,200 respondents for June 2022.
 We have data on about 6 million visits.
@@
 
-Our data also includes characteristics of the respondents.
+Our data also includes the characteristics of the respondents.
 We have data on demographic characteristics like birth year, state, gender, race, and education level.
@@
 The remaining 18 percent identify as independent.
-Column (3) of \cref{tab:characteristics_split_by_party} reports summary statistics.
 
@@
 
-Our primary dependent variables of interest are total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
 (In \ref{si:visits}, we analyze similar metrics for visits.
@@
 Of the 32\% of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile, nearly 20 hours (see \cref{tab:distribution_duration}).
-You see a similar picture when it comes to the proportion of time spent online consuming pornography---the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).
+You see a similar picture when it comes to the proportion of time spent online consuming pornography-the 50th percentile is nearly 3\%, the 80th percentile is about 14\%, and the 95th percentile is about 58\% (see \ref{tab:distribution_prop_duration}).
 
@@
 9 minutes, see \cref{fig:concentration_porn_consumption}).
-Close to 80 percent of the traffic to pornographic sites is to just one pornographic site (\cref{fig:concentration_porn_consumption_topX_by_party}).
-
-Looking at the characteristics of consumers of pornography in Panel B of \cref{tab:characteristics_split_by_porn_consumers}, expectedly, consumers of pornography online are younger and are more likely to be male.
-In addition, consumers of pornography are no different in terms of party identification.
-The mean in the 7-point scale in party identification is identical, with a mean of 3.6 and a standard deviation of 2.2, for both consumers and non-consumers of pornography.
-Treating party identification as subgroups (Republicans, Independents, Democrats) does not change this lack of difference in party identification between consumers and non-consumers (see also \cref{fig:consume_porn_yes_no}).
-This foreshadows the systematic lack of partisan differences in consumption of pornography online we find below.
+Close to 80 percent of the traffic to pornographic sites is to just one pornographic site.
+Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male (see, for instance, Panel B of \cref{tab:characteristics_split_by_porn_consumers}).
 
 \subsection*{Partisan Differences in Consumption of Pornography Online}
+
+Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+(In \ref{si:visits}, we analyze similar metrics for visits.
+The upshot is that the key conclusions are unaffected.)
+
+Given the skew in the data, we ran a quantile regression, regressing the duration on party.
+As Figure \ref{fig:quantile_regression_duration} shows, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs.
+For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively.
+In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{
+
+	We analyze the consumption of pornography online among independents in \cref{si:independents}.
+The median independent consumes more pornography than partisans (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
+This pattern reverses somewhat near the right tail of the distribution.}
+
+Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \ref{fig:quantile_regression_prop_duration}).
+The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences of nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).
+
+Looking at differences in the percentage of partisans who consume any pornographic content shows muted differences.
+Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
+
+To what extent are the results "explained" by the confounding demographic differences between the parties?
+To learn that, we control for immutable characteristics like age and gender.
+(\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
+As Figure \ref{fig:quantile_regression_duration} shows, once you adjust for confounders, the partisan differences melt away.
 
@@
 	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
 		95\% confidence intervals constructed from standard errors.
 		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_quantile_reg_duration_adult} for a numerical report of the estimates.
 	}
@@
 	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
+
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
         Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
 		95\% confidence intervals constructed from standard errors.
 		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_quantile_reg_proportion_duration_adult} for a numerical report of the estimates.
 	}
 	\label{fig:quantile_regression_prop_duration}
-\end{figure}
-
-Given the skew in the data, we ran a quantile regression, regressing the duration on party.
-As \cref{fig:quantile_regression_duration}, the 80th percentile of the difference is close to 0 but from thereon, there is a sharp diverging trend with the 95th percentile difference nearly 1.5 hrs.
-For context, the 80th and 95th percentile of time spent on pornographic sites online among Republicans is nearly .3 hours and 6.2 hours respectively.
-In contrast, the corresponding numbers are .2 hours and 4.5 hours for Democrats.\footnote{
-We analyze the consumption of pornography online among independents in \cref{si:independents}.
-The median independent consumes more pornography than partisans (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
-This pattern reverses somewhat near the right tail of the distribution.}
-
-Looking at the percentage of time spent on pornographic sites reveals a similar trend to the trend in total time spent on pornographic sites (see \cref{fig:quantile_regression_prop_duration}).
-The 80th percentile of the partisan difference is nearly 0 and then there is a sharply rising line with differences nearly 10\% at the 100th percentile (albeit the number is very imprecisely estimated).
-
-Looking at differences in the percentage of partisans who consume any pornographic content shows muted differences.
-Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June, 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
-
-To what extent are the results "explained" by the confounding demographic differences between the parties?
-To learn that, we control for immutable characteristics like age, gender, level of education qualification, race, and region.
-(\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below.
-As \cref{si:confounders} shows, once you adjust for confounders, the partisan differences melt away.\footnote{Using an alternative machine learning classifier of domains in \cref{si:alternate_ways} and alternative measures of pornography consumption (using traffic to pornographic sites) in \cref{si:visits} does little to change our conclusions.}
+
+\end{figure}
 
@@
 \addcontentsline{toc}{section}{\nameref{sec:discussion}}
-Consumption of pornography has been attributed to a variety of ills.
+The consumption of pornography has been attributed to a variety of ills.
 It is also considered problematic from a religious perspective.
-For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}.} The Internet has dramatically increased access to pornography.
+For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}} The Internet has dramatically increased access to pornography.
 This has led to the concern that pornography consumption has become very widespread and extensive.
@@
 
-The second contribution of our paper is estimates of partisan differences in consumption of pornography online.
+The second contribution of our paper is estimates of partisan differences in the consumption of pornography online.
 Both parties claim the higher ground when it comes to women---one's case for morality is steeped in religion, the other's in enduring concern for women.
@@
 The third concern is that our measures are a point in time.
-We have data from one month in one year - June, 2022.
+We have data from one month in one year - June 2022.
 It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in the preceding or following months.
@@
 	\caption{Top 25 Pornography Sites}
-	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
+	\includegraphics[width=\textwidth]{figs/top_25_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 pornographic sites that individuals visit in the sample period.
 		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
-		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
+		The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+		The \emph{Visits} column is the total number of visits by individuals in the sample to the site.  
 		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
-		See \cref{fig:top25_nonadult} for top non-pornographic domains.
 	}
@@
 	\centering
-	\caption{Top 25 (Non-Pornographic) Domains}
-	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows the top 25 non-pornographic sites that individuals visit in the sample period using over 6 million internet browsing logs.
-		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
-		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
+	\caption{Top 25 (Non-Porn) Domains}
+	\includegraphics[width=\textwidth]{figs/top_25_nonadultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows the top 25 non-pornographic sites that individuals visit in the sample period.
+		The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+		The \emph{Visits} column is the total number of visits by individuals in the sample to the site.  			
 		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
-		See \cref{fig:top25_nonadult} for top non-pornographic domains.
 	}
@@
 	\caption{Traffic to Top 10 Pornographic Sites}
-	\includegraphics[width=.5\textwidth]{../figs/concentration_porn_consumption.pdf}
+	\includegraphics[width=.5\textwidth]{figs/concentration_porn_consumption.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
 		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
-		Observations are at the individual-domain level (N = 2,437) for pornography sites and individuals who consume pornography online.
 		The Others bar indicates traffic to all other pornographic sites outside of the top 10.
 		The y-axis is the total time spent on pornographic sites, averaged across individuals.
-		Time units is hours.
+		Time units are hours.
 		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
 	\caption{Traffic to Top x Pornographic Sites by Party}
-	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
-		Observations are from the 256 individuals with party identification (Republicans or Democrats) who consume pornography online.
+	\includegraphics[width=.6\textwidth]{figs/concentration_porn_consumption_topX_by_party.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the concentration of pornography consumption based on individuals' most frequented pornographic sites.
 		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period (n = 353).
+			\input{tabs/percentiles_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
 		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
@@
 			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period (n = 353).
+			\input{tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
 		See \cref{tab:distribution_duration} for the distribution in terms of hours.
@@
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
+			\input{tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
 		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
-		See \cref{tab:distribution_duration_party_untruncated} including non-consumers of pornography.
 		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
@@
 			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
+			\input{tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
 		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
-		See \cref{tab:distribution_prop_duration_party_untruncated} including non-consumers of pornography.
 		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
@@
 
-%===========================================================================
-% Tabulated splits by party and by percentiles for hours spent on adultsites
-% Full sample
-%===========================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party\\ (Including non-consumers)}
-	\label{tab:distribution_duration_party_untruncated}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party_untruncated.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Sample includes 834 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:distribution_prop_duration_party} for the distribution in terms of percentage of time. 
-		See \cref{tab:piedomains_distribution_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.37, failing to reject the null that the Republican and Democrat distributions are the same.
-		%See \cref{fig:distribution_duration_party} for the plot.
-	}
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
-% Full sample
-%===============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party \\(Including non-consumers)}
-	\label{tab:distribution_prop_duration_party_untruncated}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party_untruncated.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Sample includes 834 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
-		See \cref{tab:piedomains_distribution_prop_duration_party} for the distribution using an alternate machine learning classifier of pornographic sites. 
-		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.6, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
-		%See \cref{fig:distribution_prop_duration_party} for the plot.
-	}
-\end{table}
-
 \FloatBarrier
 \clearpage
-\subsubsection{Accounting for Confounders}\label{si:confounders}
+\subsubsection{Accounting for Confounders}
 %==============================================================================
@@
 			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_party.tex}\\
+			\input{tabs/balance_outcomes_by_party.tex}\\
 			%-------------------------------------------------------------------
@@
 			\cmidrule{2-8}
-			\input{../tabs/balance_covariates_by_party.tex}\\
+			\input{tabs/balance_covariates_by_party.tex}\\
 			\bottomrule
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
-		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel.
-		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
-		52 of the 65 are partisans, so in later analyses the sample of partisans drop from the 886 to 834.
+		The table shows splits by party for pornographic consumption and for individual characteristics for the 1,200 individuals.
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in consumption of pornography, we also performed tests for difference in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
+		Given the skew in consumption of pornography, we also performed tests for differences in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
 	}
@@
 			\cmidrule{2-8}
-			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
+			\input{tabs/balance_outcomes_by_porn_consumers.tex}\\
 			%-------------------------------------------------------------------
@@
 			\cmidrule{2-8}
-			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
+			\input{tabs/balance_covariates_by_porn_consumers.tex}\\
 			\bottomrule
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by consumers of pornography for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
-		65 of the 1,200 individuals did not clocked any browsing activity and are in the first panel. 
+		The table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
+		65 of the 1,200 individuals did not clock any browsing activity and are in the first panel.
 		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
-		52 of the 65 are partisans, so in later analyses the sample of partisans drop from the 886 to 834.
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
@@
 	\caption*{\scriptsize \emph{Notes:}
-		Table shows splits by party for pornography consumption and for individual characteristics for all 1,200 individuals in the sample.
+		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
 		This table focuses on differences in medians.
@@
 \end{table}
-
-%============================
-% Regression table
-% Dependent variable is hours
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites}
-	\label{tab:regtab_quantile_reg_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_duration} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for estimates controlling for individual characteristics.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\label{tab:regtab_quantile_reg_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_prop_duration} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for estimates controlling for individual characteristics.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
 %=====================================================
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
 		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
-		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for a numerical report of the estimates.
 	}
@@
 	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
 		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
-		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for a numerical report of the estimates.
 	}
@@
 \end{figure}
-
-%============================
-% Regression table
-% Dependent variable is hours
-% w/ covariates
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_quantile_reg_covariates_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_covariates_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_duration_covariates} for a plot of the quantile estimates for the Republican coefficient.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-% w/ covariates
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_quantile_reg_covariates_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_quantile_reg_covariates_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions. 
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:quantile_regression_prop_duration_covariates} for a plot of the quantile estimates for the Republican coefficient.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
+\clearpage
 
@@
 % Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
-% Piedomains classification
 %===============================================================================
@@
 			\midrule
-			\input{../tabs/piedomains_percentiles_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
+			\input{tabs/piedomains_percentiles_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Classification of pornography sites is based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
 		See \cref{tab:piedomains_distribution_prop_duration_party} for the corresponding distribution in terms of percentage of time. 
@@
 			\midrule
-			\input{../tabs/piedomains_percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Sample includes 256 Republicans and Democrats (see \cref{tab:characteristics_split_by_porn_consumers}).
-		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of hours.
+			\input{tabs/piedomains_percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		Classification of pornography sites is based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
+		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of percentage of time.
 		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.19, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
 		%See \cref{fig:distribution_prop_duration_party} for the plot.
-	}
-\end{table}
-
-%===========================
-% Quantile regressions
-% Hours spent on adult sites
-% Piedomains
-%===========================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:piedomains_quantile_reg_covariates_duration_adult} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_piedomains_quantile_reg_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_duration_adult}
-\end{figure}
-
-%========================================
-% Quantile regressions
-% Proportion of time spent on adult sites
-% Piedomains
-%========================================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:piedomains_quantile_reg_covariates_proportion_duration_adult} for the same plot controlling for individual characteristics.
-		See \cref{tab:regtab_piedomains_quantile_reg_proportion_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_proportion_duration_adult}
-\end{figure}
-
-%============================
-% Regression table
-% Dependent variable is hours
-% Piedomains
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites}
-	\label{tab:regtab_piedomains_quantile_reg_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-% Piedomains
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
-	\label{tab:regtab_piedomains_quantile_reg_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_proportion_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_proportion_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-\FloatBarrier
-\subsubsection{Accounting for Confounders}
-%=====================================================
-% Fig of quantile regression estimates
-% Time Spent on Adult Sites by Party (with covariates) 
-% Piedomains
-% w/ covariates
-%=====================================================
-\begin{figure}[ht]
-	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_covariates_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{tab:regtab_piedomains_quantile_reg_covariates_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_covariates_duration_adult}
-\end{figure}
-
-%========================================
-% Quantile regressions
-% Proportion of time spent on adult sites
-% Piedomains
-% w/ covariates
-%========================================
-\begin{figure}[t]
-	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/piedomains_quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Classification of pornography sites are based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{tab:regtab_piedomains_quantile_reg_covariates_proportion_duration_adult} for a numerical report of the estimates.
-	}
-	\label{fig:piedomains_quantile_reg_covariates_proportion_duration_adult}
-\end{figure}
-
-%============================
-% Regression table
-% Dependent variable is hours
-% Piedomains
-% \w covariates
-%============================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in Hours Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_piedomains_quantile_reg_covariates_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_covariates_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the number of hours of pornography consumption online by individuals.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_covariates_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
-	}
-\end{table}
-
-%======================================
-% Regression table
-% Dependent variable is percentage time
-% Piedomains
-% w/ covariates
-%======================================
-\begin{table} \centering \small \setlength\tabcolsep{0 pt}
-	\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornographic Sites (Conditional on Covariates)}
-	\label{tab:regtab_piedomains_quantile_reg_covariates_proportion_duration_adult}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{l*{20}{D{.}{.}{-1}}}
-			\toprule
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{c}{(7)}&\multicolumn{1}{c}{(8)}&\multicolumn{1}{c}{(9)}&\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}&\multicolumn{1}{c}{(12)}&\multicolumn{1}{c}{(13)}&\multicolumn{1}{c}{(14)}&\multicolumn{1}{c}{(15)}&\multicolumn{1}{c}{(16)}&\multicolumn{1}{c}{(17)}&\multicolumn{1}{c}{(18)}&\multicolumn{1}{c}{(19)}&\multicolumn{1}{c}{(20)}\\
-			\cmidrule{3-21}
-			&&\multicolumn{19}{c}{Quantile regressions}\\
-			&\multicolumn{1}{c}{OLS}&\multicolumn{1}{c}{$q5$}&\multicolumn{1}{c}{$q10$}&\multicolumn{1}{c}{$q15$}&\multicolumn{1}{c}{$q20$}&\multicolumn{1}{c}{$q25$}&\multicolumn{1}{c}{$q30$}&\multicolumn{1}{c}{$q35$}&\multicolumn{1}{c}{$q40$}&\multicolumn{1}{c}{$q45$}&\multicolumn{1}{c}{$q50$}&\multicolumn{1}{c}{$q55$}&\multicolumn{1}{c}{$q60$}&\multicolumn{1}{c}{$q65$}&\multicolumn{1}{c}{$q70$}&\multicolumn{1}{c}{$q75$}&\multicolumn{1}{c}{$q80$}&\multicolumn{1}{c}{$q85$}&\multicolumn{1}{c}{$q90$}&\multicolumn{1}{c}{$q95$}\\
-			\cmidrule(l){2-21}
-			\input{../tabs/regtab_piedomains_quantile_reg_covariates_proportion_duration_adult.tex}\\
-			\bottomrule
-		\end{tabular}{\tiny }
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:} 
-		Table reports estimates from OLS and quantile regressions using the classification of pornographic sites using a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
-		Dependent variable is the percentage of time individuals spend on pornography consumption online.
-		All models have N = 834; only partisans are included in the sample.
-		Baseline category is Democrats.
-		See \cref{fig:piedomains_quantile_reg_covariates_proportion_duration_adult} for a plot of the quantile estimates for the Republican coefficient.
-		See \cref{tab:regtab_quantile_reg_covariates_proportion_duration_adult} for estimates using the YouGov classification.
-		Standard errors in parentheses.
-		Significance levels: $^c$ 0.1 $^b$ 0.05 $^a$ 0.01.
 	}
@@
 			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) includes Republicans (n = 95).		
-		Column (2) includes Democrats (n = 154).
-		Column (3) includes both individuals from columns (1) and (2)---the Republicans and Democrats (n = 249).
+			\input{tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		Column (1) includes Democrats (n = 154).
+		Column (2) includes Republicans (n = 95).
+		Column (3) includes both Republicans and Democrats (n = 249).
 		Column (4) includes Independents (n = 67).
@@
 			\midrule
-			\input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) includes Republicans (n = 95).
-		Column (2) includes Democrats (n = 154).
-		Column (3) includes both individuals from columns (1) and (2)---the Republicans and Democrats (n = 249).
+			\input{tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+		Column (1) includes Democrats (n = 154).
+		Column (2) includes Republicans (n = 95).
+		Column (3) includes both Republicans and Democrats (n = 249).
 		Column (4) includes Independents (n = 67).
@@
 	\caption{Pornography Consumption by Party}
-	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
+	\includegraphics[width=.5\textwidth]{figs/consume_porn_yes_no.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the proportion of individuals in the sample who consumed pornography in the sample period by party.
 		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
 	\caption{Distribution of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{../figs/distribution_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the number of visits to pornography sites by the 361 individuals who consumed pornography in the sample period.
+	\includegraphics[width=.5\linewidth]{figs/distribution_visits_to_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
-		Height of bars indicate mean of each bin.
+		The height of the bars indicates the mean of each bin.
 		Capped vertical bars are 95\% confidence intervals.
@@
 	\caption{Percentage of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{../figs/distribution_proportion_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Figure shows the proportion of visits to pornography sites by the 361 individuals who consumed pornography in the sample period.
+	\includegraphics[width=.5\linewidth]{figs/distribution_proportion_visits_to_adultsites.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The figure shows the proportion of visits to pornography sites by individuals who consumed pornography in the sample period.
 		Individuals are split into deciles with each bin containing approximately the same number of individuals.
-		Height of bars indicate mean of each bin.
+		The height of the bars indicates the mean of each bin.
 		Capped vertical bars are 95\% confidence intervals.
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites}
-	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
+	\caption{Quantile Estimates--Traffic to Pornography Sites by Party}
+	\includegraphics[width=.6\linewidth]{figs/quantile_reg_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of visits to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
 		95\% confidence intervals constructed from standard errors.
@@
 	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Visits to Pornographic Sites}
-	\includegraphics[width=.6\linewidth]{../figs/quantile_reg_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
+	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party}
+	\includegraphics[width=.6\linewidth]{figs/quantile_reg_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
 		95\% confidence intervals constructed from standard errors.
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the number of visits to pornographic sites by individuals in our sample.
+	\caption{Quantile Estimates--Traffic to Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of visits to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
@@
 	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Visits to Pornographic Sites (Conditional on Covariates)}
-	\includegraphics[width=.55\linewidth]{../figs/quantile_reg_covariates_proportion_visits_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		Dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
+	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_proportion_visits_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Sample includes 834 individuals identified as either Republicans or Democrats.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.

### 2024-04-27 ms/main.tex
Updates from Overleaf

@@
 \documentclass[12pt,twoside]{article}
+\usepackage{silence}
+\WarningsOff*
 \renewcommand{\abstractname}{\vspace{-\baselineskip}}
@@
 \usepackage{graphicx}
+\graphicspath{{../}}
 \usepackage{float}
@@
 \fancyhead[LE]{\color{gray} \footnotesize Lucas Shen and Gaurav Sood}
-\fancyhead[RE]{ \color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021) \thepage}
+\fancyhead[RE]{ \color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024) \thepage}
 % DO NOT MAKE CHANGES ABOVE THIS LINE
@@
             \midrule
-            \input{tabs/top10cat_description}\\       
+            \input{../tabs/top10cat_description}\\       
             \bottomrule
@@
 			\midrule
-			\input{tabs/percentiles_duration_adultsites_by_individuals.tex}\\
+			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
 			\bottomrule
@@
 			\midrule
-			\input{tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
+			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
 			\bottomrule
@@
 			\midrule
-			\input{tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
+			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
 			\bottomrule
@@
 			\midrule
-			\input{tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
 			\bottomrule
@@
 			\cmidrule{2-8}
-			\input{tabs/balance_outcomes_by_party_medians.tex}\\
+			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
 			\bottomrule
@@
 			\cmidrule{2-8}
-			\input{tabs/balance_outcomes_by_party.tex}\\
+			\input{../tabs/balance_outcomes_by_party.tex}\\
 			%-------------------------------------------------------------------
@@
 			\cmidrule{2-8}
-			\input{tabs/balance_covariates_by_party.tex}\\
+			\input{../tabs/balance_covariates_by_party.tex}\\
 			\bottomrule
@@
 			\cmidrule{2-8}
-			\input{tabs/balance_outcomes_by_porn_consumers.tex}\\
+			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
 			%-------------------------------------------------------------------
@@
 			\cmidrule{2-8}
-			\input{tabs/balance_covariates_by_porn_consumers.tex}\\
+			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
 			\bottomrule
@@
             \cmidrule(l){2-21}
-            \input{tabs/regtab_quantile_reg_duration_adult.tex}\\
+            \input{../tabs/regtab_quantile_reg_duration_adult.tex}\\
             \cmidrule(l){2-21}
@@
             \cmidrule(l){2-21}
-             \input{tabs/regtab_quantile_reg_covariates_duration_adult.tex}\\          
+             \input{../tabs/regtab_quantile_reg_covariates_duration_adult.tex}\\          
             \bottomrule
@@
             \cmidrule(l){2-21}
-            \input{tabs/regtab_quantile_reg_proportion_duration_adult}\\
+            \input{../tabs/regtab_quantile_reg_proportion_duration_adult}\\
             \cmidrule(l){2-21}
@@
             \cmidrule(l){2-21}
-             \input{tabs/regtab_quantile_reg_covariates_proportion_duration_adult}\\          
+             \input{../tabs/regtab_quantile_reg_covariates_proportion_duration_adult}\\          
             \bottomrule
@@
         \cmidrule(l){2-7}
-        \input{tabs/regtab_wls_visit_timing_4hrbins}\\
+        \input{../tabs/regtab_wls_visit_timing_4hrbins}\\
         \cmidrule(l){2-7}
@@
         \cmidrule(l){2-7}
-        \input{tabs/regtab_wls_visit_timing_4hrbins_adjusted}\\
+        \input{../tabs/regtab_wls_visit_timing_4hrbins_adjusted}\\
     \bottomrule
@@
 			\midrule
-			\input{tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
+			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
             \midrule
@@
 			\midrule
-            \input{tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
+            \input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
             \midrule
@@
 		%percentiles_duration_adultsites_by_individuals_by_party
-            \input{tabs/percentiles_visits_adultsites_by_individuals_by_party}\\
+            \input{../tabs/percentiles_visits_adultsites_by_individuals_by_party}\\
 			\bottomrule
@@
 		%percentiles_duration_adultsites_by_individuals_by_party
-            \input{tabs/percentiles_proportion_visits_adultsites_by_individuals_by_party}\\
+            \input{../tabs/percentiles_proportion_visits_adultsites_by_individuals_by_party}\\
 			\bottomrule
@@
             \cmidrule(l){2-21}
-            \input{tabs/regtab_quantile_reg_visits_adult}\\
+            \input{../tabs/regtab_quantile_reg_visits_adult}\\
             \cmidrule(l){2-21}
@@
             \cmidrule(l){2-21}
-             \input{tabs/regtab_quantile_reg_covariates_visits_adult}\\          
+             \input{../tabs/regtab_quantile_reg_covariates_visits_adult}\\          
             \bottomrule
@@
             \cmidrule(l){2-21}
-            \input{tabs/regtab_quantile_reg_proportion_visits_adult}\\
+            \input{../tabs/regtab_quantile_reg_proportion_visits_adult}\\
             \cmidrule(l){2-21}
@@
             \cmidrule(l){2-21}
-             \input{tabs/regtab_quantile_reg_covariates_proportion_visits_adult}\\          
+             \input{../tabs/regtab_quantile_reg_covariates_proportion_visits_adult}\\          
             \bottomrule

### 2024-04-27 ms/main.tex
Updates from Overleaf

@@
 \newcommand{\smATitle}{Descriptive Analyses}
+\newcommand{\smBTitle}{Partisan Differences}
 \newcommand{\smCTitle}{Online Pornography vs. Leisure}
-\newcommand{\smBTitle}{Partisan Differences}
+\newcommand{\smDTitle}{Time of Consumption}
 \newcommand{\smETitle}{Alternate Classifications of Pornography Sites}
+\newcommand{\smFTitle}{Consumption of Pornography Among Independents}
 \newcommand{\smGTitle}{Alternate Measures of Pornography}
-\newcommand{\smFTitle}{Consumption of Pornography Among Independents}
-\newcommand{\smDTitle}{Time of Consumption}
+\newcommand{\smHTitle}{Missing at Random}
 
@@
 \hyperref[sm:smG]{\indent \textcolor{magenta}{\S G:}} \smGTitle{}\\
+\hyperref[sm:smH]{\indent \textcolor{magenta}{\S H:}} \smHTitle{}\\
 
@@
 
+\clearpage
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
+\FloatBarrier
+\renewcommand{\thetable}{H\arabic{table}}
+\renewcommand{\thefigure}{H\arabic{figure}}
+\renewcommand{\theequation}{H\arabic{equation}}
+\subsection{H. \smHTitle{}}\label{sm:smH}
+% =============================================================================
+\begin{figure}[!ht]
+\caption{Hours Spent on Online Pornography and All Other Online Content}
+\label{fig:distribution_duration_on_adultsites_fullsample_mar}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/mar/distribution_duration_on_adultsites_fullsample.pdf}
+         \caption{Online pornography}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/mar/distribution_duration_on_nonadultsites_fullsample.pdf}
+         \caption{Other online content}
+     \end{subfigure}
+\caption*{\footnotesize \emph{Notes:} 
+    Each panel shows the total number of hours for the sample period.
+    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
+    The height of the bars indicates the mean of each bin. 
+    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
+    \cref{fig:distribution_duration_on_adultsites_fullsample} in main body.
+
+}
+\end{figure}
+
+%========================================
+% Quantile regressions
+% Proportion of time spent on adult sites
+%========================================
+\begin{figure}[t]
+	\centering
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
+	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration_covariates_mar} for the same plot controlling for individual characteristics.
+            \cref{fig:quantile_regression_prop_duration} in main body.
+	}
+	\label{fig:quantile_regression_prop_duration_mar}
+\end{figure}
+
+%================================================================
+% Fig of quantile regression estimates
+% Percentage Time Spent on Adult Sites by Party (with covariates) 
+%================================================================
+\begin{figure}[!ht]
+	\centering
+	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
+	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration_mar} for the same plot without covariates.
+            \cref{fig:quantile_regression_prop_duration_covariates} in main body.
+	}
+	\label{fig:quantile_regression_prop_duration_covariates_mar}
+\end{figure}
+
+%=====================================================================
+% Tabulated percentiles of the proportion of duration spent on adult sites
+%=====================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites (Conditional on having consumed pornography)}
+	\label{tab:distribution_prop_duration}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{cr}
+			\toprule
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
+			\midrule
+			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
+The base number is the individual's own total time spent on the web.
+See \cref{tab:distribution_duration} for the distribution of total time spent on pornographic websites.}
+\end{table}
+
 \end{document}

### 2024-04-27 ms/main.tex

@@
 	\caption{Percentage of Time Spent on Pornographic Sites (Conditional on having consumed pornography)}
-	\label{tab:distribution_prop_duration}
+	\label{tab:distribution_prop_duration_mar}
 	\begin{adjustbox}{max width=\textwidth}
@@
 			\midrule
-			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
+			\input{../tabs/mar/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
 			\bottomrule
@@
 The base number is the individual's own total time spent on the web.
-See \cref{tab:distribution_duration} for the distribution of total time spent on pornographic websites.}
+See \cref{tab:distribution_duration} for the distribution of total time spent on pornographic websites.
+    See also \cref{tab:distribution_prop_duration}.
+ }
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for the proportion of time spent on adultsites
+%===============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party (Conditional on having consumed pornography)}
+	\label{tab:distribution_prop_duration_party_mar}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/mar/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+        The base number is the individual's own total time spent on the web.
+		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
+          See also \cref{tab:distribution_prop_duration_party}.
+	}
 \end{table}

### 2024-04-28 ms/main.tex
Updates from Overleaf

@@
 \usepackage{graphicx}
+\setlength{\abovecaptionskip}{0pt}
 \graphicspath{{../}}
@@
 Available at: \url{http://journalqd.org}}%
-  \lhead{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2021), 1–n}
+  \lhead{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024), 1–n}
 \rhead{\color{gray} \footnotesize 10.51685/jqd.2024.011}
@@
 We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}.
-Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research, using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
+Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
 Combining individual-level data on partisanship with directly measured pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa.
 Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats.
-Adjusting for background attributes like age, gender, etc., however, makes the partisan differences go away.
+Adjusting for background attributes (e.g., age, gender, race, education), however, makes the partisan differences go away.
 Our findings relate to \cite{Perry2018-cn}, who find that higher levels of religiosity, also linked to political conservatism, are associated with views of pornography as morally wrong while still having viewed pornography.
@@
 The remaining 18 percent identified as independent.
-(See Panel B of \cref{tab:characteristics_split_by_party} for a summary of socio-demographic data by party.)
+(See Panel B of \cref{tab:characteristics_split_by_party} and \cref{tab:characteristics_split_by_porn_consumers} for a summary of socio-demographic data by party.)
 
@@
 YouGov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as Adult.
-Given the skew in the data (see \cref{fig:top25_adult} and \cref{fig:top25_nonadult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites.
+Given the skew in the data (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites.
 We code a domain as carrying pornographic content if there is nudity on the landing page or if the site is some form of erotica.
-Domains without a YouGov category are assumed to be missing completely at random.
+Domains without a YouGov category are assumed to be non-pornographic sites.\footnote{
+    We replicate key findings by dropping observations on all sites without YouGov category instead of assuming that only non-pornographic sites have absent YouGov categories. 
+    This difference in assumption only affects results on proportion-based measures of consumption through the baseline on total duration. 
+    We find a similar skew in pornographic consumption. 
+    We also find that partisan differences disappear once we adjust for the baseline characteristics. 
+    \hyperref[sm:smH]{Appendix H} reports these results.
+}
 
@@
 As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites.
-The top 5 non-pornographic sites were visited more than 200,000 times by our panelists.
+Each of the top 5 non-pornographic sites were visited more than 200,000 times by our panelists.
 In comparison, the 99th percentile non-pornographic site was visited only 1,652 times by our panelists during the observation period.
@@
 \cref{fig:top25_adult} reports the top 25 pornography sites.
-The top three pornography sites (``\textit{xvideos.com}'', ``\textit{pornhub.com}'', and ``\textit{xnxx.com}'') are visited more than 6,500 times by the people in our sample during the one-month period.
+The top three pornography sites (``\textit{xvideos.com}'', ``\textit{pornhub.com}'', and ``\textit{xnxx.com}'') are each visited more than 6,500 times by the people in our sample during the one-month period.
 The most visited site, xvideos.com, clocked 311 hours in total from our participants who visited a pornographic site.
@@
 Nine sites are above the 99th percentile in pornography visits (2,224 visits).
-The average time spent on the ten most frequented pornography sites is 12x the average time on all other pornography sites (approximately 109 minutes vs.
+The average time spent on the ten most frequented pornography sites is 12 times the average time on all other pornography sites (approximately 109 minutes vs.
 9 minutes, \cref{fig:concentration_porn_consumption}).
 Our finding is consistent with other analyses of traffic to pornographic sites \cite{webporn}.
-The average time spent on the ten most frequented pornography sites is 12 times the average time spent on all other pornographic sites (approximately 109 minutes vs.
-9 minutes, \cref{fig:concentration_porn_consumption}).
-This finding is consistent with other analyses of traffic to pornographic sites \citep{webporn}.
 
@@
 \begin{figure}[!ht]
-\caption{Hours Spent on Online Pornography and All Other Online Content}
-\label{fig:distribution_duration_on_adultsites_fullsample}
      \centering
@@
      \end{subfigure}
-\caption*{\footnotesize \emph{Notes:} 
-    Each panel shows the total number of hours for the sample period.
+\caption{Hours Spent on Online Pornography and All Other Online Content}
+\label{fig:distribution_duration_on_adultsites_fullsample}
+\caption*{\footnotesize \emph{Notes:} 
+    Each panel shows the average hours per decile for the sample period.
     Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
@@
 To help contextualize the above figures, we present statistics on time spent consuming content from the top ten non-adult categories in \cref{tab:top10cat_description}. 
-The median pornography consumer spends more hours on adult content than sites from six non-adult categories.
-Only three categories, ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), ``Business, Social Networking'' (e.g., facebook.com, soocial.com)),  and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile than online pornography.
+The median pornography consumer (\cref{tab:distribution_duration}) spends at least as many hours on adult content as the median online user on sites from six non-adult categories. 
+Only three categories, ``Business, Social Networking'' (e.g., facebook.com, soocial.com)), ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile than online pornography.
 
@@
 \begin{figure}[!ht]
-\caption{Time Spent on Online Pornography vs. Non-adult Leisure}
 \label{fig:tu_prop_entertainment-prop_adult_duration}
@@
      \end{subfigure}
+\caption{Time Spent on Online Pornography vs. Non-adult Leisure}
 \caption*{\footnotesize \emph{Notes:} Lowess between time spent on online pornography and time spent on other non-adult leisure (``entertainment'' and ``shopping'').
@@
 29.4\% of Republicans.
-The 2\% difference is not statistically significant.
+The 2\% difference is not statistically significant (p = .57).
 Of the partisans who consumed any pornographic content online, \cref{tab:distribution_duration_party} presents the distribution of time spent on pornographic sites by partisan leanings.
@@
 In \cref{tab:distribution_prop_duration_party}, we observe similar patterns for time spent on pornography sites as for percentage of total time spent on the web.
-The median Republican consumer of pornography consumes 4 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.3 percent.
+The median Republican consumer of pornography consumes 4 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.3 percent.\footnote{
+    With the missing at-random assumption, the Republican consumer of pornography consumes 4.2 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.5 percent (\cref{tab:distribution_prop_duration_party_mar}).
+}
 
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites}
 	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
 	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 
-Looking at differences in the percentage of partisans who consume any pornographic content, we find little difference.
+Looking at differences in the percentage of partisans who consume any pornographic content, we find little difference as well.
 Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
@@
 \subsection{Accounting for Confounders}
+
+%=====================================================
+% Fig of quantile regression estimates
+% Time Spent on Adult Sites by Party (with covariates) 
+%=====================================================
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates)}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
+  \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
+	}
+	\label{fig:quantile_regression_duration_covariates}
+\end{figure}
+
+%================================================================
+% Fig of quantile regression estimates
+% Percentage Time Spent on Adult Sites by Party (with covariates) 
+%================================================================
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornographic Sites (with covariates)}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
+        \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
+	}
+	\label{fig:quantile_regression_prop_duration_covariates}
+\end{figure}
 
@@
 As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away.
-(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.)
-
-%=====================================================
-% Fig of quantile regression estimates
-% Time Spent on Adult Sites by Party (with covariates) 
-%=====================================================
-\begin{figure}[!ht]
-	\centering
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
-  \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
-	}
-	\label{fig:quantile_regression_duration_covariates}
-\end{figure}
-
-%================================================================
-% Fig of quantile regression estimates
-% Percentage Time Spent on Adult Sites by Party (with covariates) 
-%================================================================
-\begin{figure}[!ht]
-	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
-	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
-        \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
-	}
-	\label{fig:quantile_regression_prop_duration_covariates}
-\end{figure}
-
-\subsection{Robustness}
-In \ref{si:visits}, we analyze similar metrics for the total number of visits and proportion of visits instead of time.
-The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party} in \hyperref[sm:smG]{Appendix G}).
-We also replicate our analyses using four alternative classifications of domains (see \hyperref[sm:smE]{Appendix E}) and obtain similar results.
+%(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.) 
+%Using alternative classifications of pornography sites led to similar conclusions (\cref{sec:robustness}).
+
+\subsection{Robustness}\label{sec:robustness}
+We replicate our analyses using four alternative classifications of domains and obtain similar results (see \hyperref[sm:smE]{Appendix E}).  
+In \hyperref[sm:smG]{Appendix G}, we also analyze similar metrics for the total number of visits and proportion of visits instead of time. 
+The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party}). 
+\hyperref[sm:smH]{Appendix H} replicates key findings by dropping domains with missing YouGov domain category.
 
@@
 %\noindent 
-\textbf{\hphantom{aaa}Table of Contents}\\
+\textbf{\hphantom{aaaaa}Table of Contents}\\
 \hyperref[sm:smA]{\indent \textcolor{magenta}{\S A:}} \smATitle{}\\
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The table shows the top 25 non-pornographic sites individuals visited in the sample period.
-            All numbers are based on online visits during the one-month period.
+		The table shows the top 25 non-pornographic sites individuals visited during the observation period.
 		The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
@@
 		The table shows the top 25 pornographic sites that individuals visited in the sample period.
-            All numbers are based on online visits during the one-month period.
 		Pornography sites are categorized by YouGov (see the \nameref{sec:data} section).
@@
 	\centering
-	\caption{Traffic to Top 10 Pornographic Sites}
 	\includegraphics[width=.5\textwidth]{figs/concentration_porn_consumption.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		The Top 10 bar indicates traffic to the top 10 pornographic sites in the data (see \cref{fig:top25_adult}).
-		The ``Others'' bar indicates traffic to all other pornographic sites outside of the top 10.
-		The y-axis is the total time spent on pornographic sites, averaged across individuals.
-		Time units are hours.
+	\caption{Top 10 Pornographic Sites vs. Other Pornographic Sites}
+	\caption*{\footnotesize \emph{Notes:} 
+            The average number of hours spent on the top 10 pornographic sites by total time spent vs. all other pornographic sites.
 		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
             &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}         &\multicolumn{1}{c}{(7)}         &\multicolumn{1}{c}{(8)}         &\multicolumn{1}{c}{(9)}         &\multicolumn{1}{c}{(10)}&\multicolumn{1}{c}{(11)}         &\multicolumn{1}{c}{(12)}         &\multicolumn{1}{c}{(13)}         &\multicolumn{1}{c}{(14)}         &\multicolumn{1}{c}{(15)}         &\multicolumn{1}{c}{(16)}         &\multicolumn{1}{c}{(17)}         &\multicolumn{1}{c}{(18)}         &\multicolumn{1}{c}{(19)}         &\multicolumn{1}{c}{(20)}         \\
+            &\multicolumn{19}{c}{Quantile regressions}\\
+            \cmidrule(l){3-21}
+            &\multicolumn{1}{c}{OLS} &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}           \\
             \cmidrule(l){2-21}
@@
             &\multicolumn{20}{c}{\textbf{Panel A. Unconditional quantile estimates}}\\
-            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
             \cmidrule(l){2-21}
@@
             &\multicolumn{20}{c}{\textbf{Panel B. Adjusted quantile estimates}}\\
-            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
             \cmidrule(l){2-21}
@@
         Panel B corresponds to \cref{fig:quantile_regression_duration_covariates}.
+        Column (1) reports Ordinary Least Squares (OLS) estimates.
         For the adjusted estimates, see \cref{fig:quantile_regression_duration_covariates} for notes on the included covariates.
@@
             &\multicolumn{20}{c}{\textbf{Panel B. Adjusted quantile estimates}}\\
-            &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}         &\multicolumn{1}{c}{p100}         \\
+            %&\multicolumn{1}{c}{OLS} &\multicolumn{1}{c}{p5}         &\multicolumn{1}{c}{p10}         &\multicolumn{1}{c}{p15}         &\multicolumn{1}{c}{p20}         &\multicolumn{1}{c}{p25}         &\multicolumn{1}{c}{p30}         &\multicolumn{1}{c}{p35}         &\multicolumn{1}{c}{p40}         &\multicolumn{1}{c}{p45}         &\multicolumn{1}{c}{p50}&\multicolumn{1}{c}{p55}         &\multicolumn{1}{c}{p60}         &\multicolumn{1}{c}{p65}         &\multicolumn{1}{c}{p70}         &\multicolumn{1}{c}{p75}         &\multicolumn{1}{c}{p80}         &\multicolumn{1}{c}{p85}         &\multicolumn{1}{c}{p90}         &\multicolumn{1}{c}{p95}           \\
             \cmidrule(l){2-21}
@@
         Panel B corresponds to \cref{fig:quantile_regression_prop_duration_covariates}.
+        Column (1) reports Ordinary Least Squares (OLS) estimates.
         For the adjusted estimates, see \cref{fig:quantile_regression_prop_duration_covariates} for notes on the included covariates.
@@
 \begin{figure}[!h]
-\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
 \label{fig:tu_prop_entertainment-prop_pure_adult}
@@
      \end{subfigure}
+\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
 \caption*{\footnotesize \emph{Notes:}
@@
 \centering
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption.pdf}
 \caption{Time-of-Day Traffic to Online Pornography Sites}
-    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption.pdf}
 \caption*{\footnotesize \emph{Notes:} 
@@
 \centering
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption-by-party.pdf}
 \caption{Time-of-Day Traffic to Online Pornography Sites by Party}
-    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption-by-party.pdf}
 \caption*{\footnotesize \emph{Notes:} 
@@
 \centering
+    \includegraphics[width=.85\linewidth]{figs/time-of-day-wls-estimates.pdf}
 \caption{Time-of-Day Traffic to Online Pornography Sites by Party}
-    \includegraphics[width=.85\linewidth]{figs/time-of-day-wls-estimates.pdf}
 \caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (\texttt{piedomains})}
 	\includegraphics[width=.7\linewidth]{figs/piedomains_quantile_reg_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (\texttt{piedomains})}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, \texttt{piedomains})}
 	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, \texttt{piedomains})}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Forcepoint ThreatSeeker)}
 	\includegraphics[width=.7\linewidth]{figs/forcepoint_quantile_reg_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (Forcepoint ThreatSeeker)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, Forcepoint ThreatSeeker)}
 	\includegraphics[width=.55\linewidth]{figs/forcepoint_quantile_reg_covariates_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, Forcepoint ThreatSeeker)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (Bitdefender)}
 	\includegraphics[width=.7\linewidth]{figs/bitdefender_quantile_reg_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (Bitdefender)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, Bitdefender)}
 	\includegraphics[width=.55\linewidth]{figs/bitdefender_quantile_reg_covariates_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, Bitdefender)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Distribution of Partisan Differences in Hours Spent on Pornographic Sites (alphaMountain)}
 	\includegraphics[width=.7\linewidth]{figs/alphamountain_quantile_reg_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (alphaMountain)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party (with covariates, Bitdefender)}
 	\includegraphics[width=.55\linewidth]{figs/alphamountain_quantile_reg_covariates_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, Bitdefender)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
+	\includegraphics[width=.5\textwidth]{figs/consume_porn_yes_no.pdf}
 	\caption{Pornography Consumption by Party}
-	\includegraphics[width=.5\textwidth]{figs/consume_porn_yes_no.pdf}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
+	\includegraphics[width=.5\linewidth]{figs/distribution_visits_to_adultsites.pdf}
 	\caption{Distribution of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{figs/distribution_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		The figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
+	\caption*{\footnotesize \emph{Notes:} 
+            Each bar shows the mean number of visits to pornography sites per decile.
 		Individuals are split into deciles, with each bin containing approximately the same number of individuals.
-		The height of the bars indicates the mean of each bin.
 		Capped vertical bars are 95\% confidence intervals.
@@
 	\centering
+	\includegraphics[width=.5\linewidth]{figs/distribution_proportion_visits_to_adultsites.pdf}
 	\caption{Percentage of Traffic to Pornography Online}
-	\includegraphics[width=.5\linewidth]{figs/distribution_proportion_visits_to_adultsites.pdf}
-	\caption*{\footnotesize \emph{Notes:} 
-		The figure shows the proportion of visits to pornography sites by individuals who consumed pornography in the sample period.
+	\caption*{\footnotesize \emph{Notes:} 
+             Each bar shows the mean percentage of total visits that are to pornography sites per decile.
 		Individuals are split into deciles, with each bin containing approximately the same number of individuals.
-		The height of the bars indicates the mean of each bin.
 		Capped vertical bars are 95\% confidence intervals.
@@
 	\centering
-	\caption{Quantile Estimates--Traffic to Pornography Sites by Party}
 	\includegraphics[width=.55\linewidth]{figs/quantile_reg_visits_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Traffic to Pornography Sites}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Traffic to Pornographic Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_visits_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in Traffic to Pornography Sites (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party}
 	\includegraphics[width=.55\linewidth]{figs/quantile_reg_proportion_visits_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in the Percentage of Traffic to Pornography Sites}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party (with covariates)}
 	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_proportion_visits_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in the Percentage of Traffic to Pornography Sites (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
         Panel B corresponds to \cref{fig:quantile_regression_visits_covariates}.
+        Column (1) reports Ordinary Least Squares (OLS) estimates.
         For the adjusted estimates, see \cref{fig:quantile_regression_visits_covariates} for notes on the included covariates.
@@
         Panel B corresponds to \cref{fig:quantile_regression_prop_visits_covariates}.
+        Column (1) reports Ordinary Least Squares (OLS) estimates.
         For the adjusted estimates, see \cref{fig:quantile_regression_prop_visits_covariates} for notes on the included covariates.
@@
 \begin{figure}[!ht]
-\caption{Hours Spent on Online Pornography and All Other Online Content}
 \label{fig:distribution_duration_on_adultsites_fullsample_mar}
@@
      \end{subfigure}
-\caption*{\footnotesize \emph{Notes:} 
-    Each panel shows the total number of hours for the sample period.
+\caption{Hours Spent on Online Pornography and All Other Online Content}
+\caption*{\footnotesize \emph{Notes:} 
+    Each panel shows the average hours per decile for the sample period.
     Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
@@
 	\centering
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
 	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_proportion_duration_adult.pdf}
+	\caption{Partisan Differences in the Percentage of Time Spent on Pornography Sites}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party (with covariates)}
 	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornography Sites (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 

### 2024-04-28 ms/main.tex

@@
 	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+            Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
 		95\% confidence intervals constructed from standard errors.
@@
 	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornographic Sites}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
 		95\% confidence intervals constructed from standard errors.
@@
 	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates)}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
 		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornographic Sites (with covariates)}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
 		Covariates included: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-            The average number of hours spent on the top 10 pornographic sites by total time spent vs. all other pornographic sites.
+            The average number of minutes spent on the top 10 pornographic sites vs. all other pornographic sites.
+            Top 10 pornographic sites are determined by the total amount of time spent on each site by all individuals over the sample period.
+            Data is at the individual-domain level (n = 2.4k).
 		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
@@
         The table enumerates the top ten categories (YouGov) based on the amount of traffic to the corresponding sites from individuals in the sample.
-        Panel A is constructed using the browsing level data (n = 6.3m web browsing records.) Panel B is constructed using the domain-level data (n = 40k).
+        Panel A is constructed using the browsing level data (n = 6.3m web browsing records.) Panel B is constructed using the individual-category-level data (n = 40k).
         }
@@
 \end{table}
+
+\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+	\caption{Median Differences in Pornography Consumption}
+	\label{tab:characteristics_split_by_party_medians}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}lrcccrr@{\hspace{0\tabcolsep}}}
+			\toprule
+			&\multicolumn{6}{c}{\underline{Measures of pornography consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}\\			
+			&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-7}
+        			n                            &            & 1200          & 530           & 356            &                  \\
+         Minutes, median [Q1,Q3]      &  65        & 0.0 [0.0,4.8] & 0.0 [0.0,3.1] & 0.0 [0.0,3.6] & 0.981     & 0.056           \\
+         \% of time, median [Q1,Q3]    &  65        & 0.0 [0.0,0.1] & 0.0 [0.0,0.1] & 0.0 [0.0,0.1] & 0.842     & 0.049           \\
+         Visits, median [Q1,Q3]       &  65        & 0.0 [0.0,8.0] & 0.0 [0.0,6.0] & 0.0 [0.0,8.0] & 0.933     & 0.048           \\
+         \% of visits, median [Q1,Q3]  &  65        & 0.0 [0.0,0.2] & 0.0 [0.0,0.1] & 0.0 [0.0,0.2] & 0.916     & 0.085         \\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\scriptsize \emph{Notes:}
+		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
+		This table focuses on differences in medians.
+		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
+		Column (1) indicates the count of missing variables.
+		Columns (2)--(4) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans, respectively.
+		1st and 3rd quartiles in brackets.
+		Column (5) and column (6) report the p-values and standardized median differences for Democrats vs Republicans.
+		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
+	}
+\end{table}
+
 \FloatBarrier
@@
     \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-    \caption{Quantile Estimates--Hours spent on Pornographic Sites by Party }
+    \caption{Distribution of Partisan Differences in Hours Spent on Pornography}
     \label{tab:quantile-estimates-hours}
@@
     \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-    \caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party}
+    \caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
     \label{tab:quantile-estimates-time}
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{figs/piedomains_quantile_reg_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (\texttt{piedomains})}
+	\includegraphics[width=.6\linewidth]{figs/piedomains_quantile_reg_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (\texttt{piedomains})}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
 95\% confidence intervals constructed from standard errors.
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, \texttt{piedomains})}
+	\includegraphics[width=.6\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (with covariates, \texttt{piedomains})}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
 		Covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{figs/forcepoint_quantile_reg_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (Forcepoint ThreatSeeker)}
+	\includegraphics[width=.6\linewidth]{figs/forcepoint_quantile_reg_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (Forcepoint ThreatSeeker)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/forcepoint_quantile_reg_covariates_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, Forcepoint ThreatSeeker)}
+	\includegraphics[width=.6\linewidth]{figs/forcepoint_quantile_reg_covariates_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (with covariates, Forcepoint ThreatSeeker)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{figs/bitdefender_quantile_reg_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (Bitdefender)}
+	\includegraphics[width=.6\linewidth]{figs/bitdefender_quantile_reg_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (Bitdefender)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/bitdefender_quantile_reg_covariates_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, Bitdefender)}
+	\includegraphics[width=.6\linewidth]{figs/bitdefender_quantile_reg_covariates_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (with covariates, Bitdefender)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.7\linewidth]{figs/alphamountain_quantile_reg_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (alphaMountain)}
+	\includegraphics[width=.6\linewidth]{figs/alphamountain_quantile_reg_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (alphaMountain)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/alphamountain_quantile_reg_covariates_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Hours Spent on Pornographic Sites (with covariates, Bitdefender)}
+	\includegraphics[width=.6\linewidth]{figs/alphamountain_quantile_reg_covariates_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (with covariates, Bitdefender)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
 Covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/quantile_reg_visits_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Traffic to Pornography Sites}
+	\includegraphics[width=.6\linewidth]{figs/quantile_reg_visits_adult.pdf}
+	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_visits_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in Traffic to Pornography Sites (with covariates)}
+	\includegraphics[width=.6\linewidth]{figs/quantile_reg_covariates_visits_adult.pdf}
+	\caption{Distribution of Partisan Differences in Visits to Pornographic Sites (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/quantile_reg_proportion_visits_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in the Percentage of Traffic to Pornography Sites}
+	\includegraphics[width=.6\linewidth]{figs/quantile_reg_proportion_visits_adult.pdf}
+	\caption{Distribution of Partisan Differences in Percentage of Total Visits to Pornographic Sites}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\centering
-	\includegraphics[width=.55\linewidth]{figs/quantile_reg_covariates_proportion_visits_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in the Percentage of Traffic to Pornography Sites (with covariates)}
+	\includegraphics[width=.6\linewidth]{figs/quantile_reg_covariates_proportion_visits_adult.pdf}
+	\caption{Distribution of Partisan Differences in Percentage of Total Visits to Pornographic Sites (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 
@@
     \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-    \caption{Quantile Estimates--Traffic to Pornographic Sites by Party }
+    \caption{Distribution of Partisan Differences in Visits to Pornographic Sites}
     \label{tab:quantile-estimates-traffic}
@@
     \def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-    \caption{Quantile Estimates--Percentage of Traffic to Pornographic Sites by Party }
+    \caption{Distribution of Partisan Differences in Percentage of Total Visits to Pornographic Sites}
     \label{tab:quantile-estimates-prop-traffic}
@@
 	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_proportion_duration_adult.pdf}
-	\caption{Partisan Differences in the Percentage of Time Spent on Pornography Sites}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
 	\caption*{\footnotesize \emph{Notes:} 
@@
 	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption{Quantile Estimates--Partisan Differences in the Percentage of Time Spent on Pornography Sites (with covariates)}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
 	\caption*{\footnotesize \emph{Notes:} 

### 2024-04-28 ms/main.tex
Updates from Overleaf

@@
 The remaining 18 percent identified as independent.
-(See Panel B of \cref{tab:characteristics_split_by_party} and \cref{tab:characteristics_split_by_porn_consumers} for a summary of socio-demographic data by party.)
+(See Panel B of \cref{tab:characteristics_split_by_party} for a summary of socio-demographic data by party.)
 
@@
 
-Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}).
-For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}).
-Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}).
+Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). 
+%Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}). 
 How do differences in age and other such demographic differences between the parties ``explain'' the results?
@@
 %==============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
+\begin{table}[ht] \centering \normalsize \setlength\tabcolsep{5 pt}
 	\caption{Differences (in Medians) in Pornography Consumption}
@@
 			\toprule
-			&\multicolumn{7}{c}{\underline{Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
-			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-8}
+			&\multicolumn{6}{c}{\underline{Measures of pornography consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}\\			
+			&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
+			\cmidrule{2-7}
 			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
@@
 	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
+	\caption*{\footnotesize \emph{Notes:}
 		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
@@
 		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
-		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
-	}
-\end{table}
-
-\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
-	\caption{Median Differences in Pornography Consumption}
-	\label{tab:characteristics_split_by_party_medians}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}lrcccrr@{\hspace{0\tabcolsep}}}
-			\toprule
-			&\multicolumn{6}{c}{\underline{Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}\\			
-			&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-7}
-        			n                            &            & 1200          & 530           & 356            &                  \\
-         Minutes, median [Q1,Q3]      &  65        & 0.0 [0.0,4.8] & 0.0 [0.0,3.1] & 0.0 [0.0,3.6] & 0.981     & 0.056           \\
-         \% of time, median [Q1,Q3]    &  65        & 0.0 [0.0,0.1] & 0.0 [0.0,0.1] & 0.0 [0.0,0.1] & 0.842     & 0.049           \\
-         Visits, median [Q1,Q3]       &  65        & 0.0 [0.0,8.0] & 0.0 [0.0,6.0] & 0.0 [0.0,8.0] & 0.933     & 0.048           \\
-         \% of visits, median [Q1,Q3]  &  65        & 0.0 [0.0,0.2] & 0.0 [0.0,0.1] & 0.0 [0.0,0.2] & 0.916     & 0.085         \\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\scriptsize \emph{Notes:}
-		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
-		This table focuses on differences in medians.
-		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) indicates the count of missing variables.
-		Columns (2)--(4) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans, respectively.
-		1st and 3rd quartiles in brackets.
-		Column (5) and column (6) report the p-values and standardized median differences for Democrats vs Republicans.
 		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
@@
 	\caption*{\scriptsize \emph{Notes:}
-		The table shows splits by party for pornographic consumption and for individual characteristics for the 1,200 individuals.
+		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
+		This table focuses on differences in medians.
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables for the full sample, Democratic individuals, and Republican individuals.
-		Standard deviations and percentages are in parentheses.
-		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
-		Given the skew in consumption of pornography, we also performed tests for differences in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
-	}
-\end{table}
-
+		Column (1) indicates the count of missing variables.
+		Columns (2)--(4) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans, respectively.
+		1st and 3rd quartiles in brackets.
+		Column (5) and column (6) report the p-values and standardized median differences for Democrats vs Republicans.
+		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
+	}
+\end{table}
+
+\iffalse
 %==============================================================================
@@
 \end{table}
+\fi
 

### 2024-04-29 ms/main.tex

@@
 We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts.
-Only about 32 percent of respondents consumed pornography online during the month-long observation period.
-Of the people who consumed pornography, the median consumer spent about three-quarters of an hour consuming pornography, and 95 percent of the consumers spent less than five and a half hours.
-Lastly, we find, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, that Republicans consume somewhat more pornography online than Democrats.
-Adjusting for immutable characteristics like age and gender makes the differences go away.
+Only about a third of the respondents consumed pornography online during the month-long observation period.
+Of the people who consumed pornography, the median consumer spent about three-quarters of an hour consuming pornography.
+Lastly, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, we find that Republicans likely consume somewhat more pornography online than Democrats.
+Adjusting for immutable characteristics like age and gender makes the small differences go away.
 \emph{Keywords:} Measurement, YouGov, Pornography, Partisanship, Quantile Regression, Online Consumption
@@
 \section{Introduction}\label{sec:intro}
-Pornography consumption has been rising steadily  \citep{Perry2018-cw, Price2016-sm, Wright2013-gl}.
 Consumption of pornography is associated with a variety of disturbing attitudes, beliefs, emotions, and behaviors.
-Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex and having extramarital sex \citep{wright2012internet}.
-A lot of popular pornography also contains a healthy dose of violence \citep{Vera-Gray2021-qv}.
+Consuming pornography is associated with support for violence against women \citep{hald2010pornography, malamuth2012pornography, donnerstein1984pornography}, belief in rape myths \citep{foubert2011pornography}, increased gender role conflict, lesser sexual satisfaction \citep{szymanski2014psychological, stewart2012young}, poorer relationship quality \citep{szymanski2014psychological, szymanski2015male}, and sexually risky behaviors such as engaging in paid sex and having extramarital sex \citep{wright2012internet}.\footnote{The cited studies do not provide rigorous evidence for the effect of consuming pornography \citep{Ferguson2022-fo, Pathmendra2023-fx, Peter2016-de}.} A lot of popular pornography also contains a healthy dose of violence \citep{Vera-Gray2021-qv}.
 An analysis of popular pornography revealed that 88.2\% of the scenes contained physical aggression and 48.7\% verbal aggression \citep{bridges2010aggression}.
-The increased accessibility of online pornography also raises concerns about adolescent sexual development \citep{Peter2016-de, Ybarra2005-id}.
-For all these reasons, there are serious concerns about the consumption of pornography.\footnote{This is despite the fact that the studies cited above do not provide rigorous evidence for the negative impact of pornography consumption \citep{Ferguson2022-fo, Pathmendra2023-fx, Peter2016-de}.}
+For all these reasons, there are concerns about the consumption of pornography.
 
@@
 We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}.
-Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that politically conservative states search for pornography more often and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
-Combining individual-level data on partisanship with directly measured pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa.
+Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that people in politically conservative states search for pornography and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
+Combining individual-level data on partisanship with direct passive individual level measures of pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa.
 Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats.
-Adjusting for background attributes (e.g., age, gender, race, education), however, makes the partisan differences go away.
-Our findings relate to \cite{Perry2018-cn}, who find that higher levels of religiosity, also linked to political conservatism, are associated with views of pornography as morally wrong while still having viewed pornography.
-This unexpected finding suggests a discordance between survey responses and reported actions.
-Republicans may be consuming just as much pornography as Democrats; they are simply saying otherwise.
+Adjusting for background attributes such as age, gender, race, and education, however, make the partisan differences go away.
+Our findings relate to \cite{Perry2018-cn}, which finds that more religious people are more likely to think of pornography as morally wrong while still consuming pornography.
 
@@
 
-We use data from YouGov to measure the consumption of adult content online.
+We use data from YouGov to measure the consumption of pornographic content online.
 YouGov maintains a large panel that it recruits through various methods.
 It uses matched sampling to survey respondents: it draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey.
-(For data on how well YouGov surveys approximate results from the census and other high-quality government surveys, see \citet{rivers2009, graham2021advantages, foote2021measuring}.) YouGov also collects de-identified web browsing data via passive metering software, RealityMine, which some panelists volunteer to have installed in lieu of rewards.
+(For data on how well YouGov surveys approximate results from the census and other high-quality government surveys, see \citet{rivers2009, graham2021advantages, foote2021measuring}.) YouGov also collects de-identified web browsing data via RealityMine, which some panelists volunteer to have installed in lieu of rewards.
 RealityMine captures online visits independent of browser type or browser-specific privacy settings.
@@
 These 1,200 panelists visited the web nearly 6 million times.
-For each visit, we have the anonymized URL, domain (e.g., wikipedia.org), the time of the visit, the length of the visit, and the type of content.
+For each visit, we have the anonymized URL, domain, e.g., \texttt{wikipedia.org}, the time of the visit, the length of the visit, and the type of content.
+Of the 1,200 panelists, 65 panelists apparently did not visit the web even once during the month.
+We assume these data to be missing completely at random as we think it unlikely that these data reflect true zeroes.
+We redo our analysis assuming these respondents did not visit the web even once to test the robustness of our results and find that key substantive conclusions remain unaffected.
 
@@
 YouGov panel file contains data on demographic characteristics like birth year, state of residence, gender, race, and education level.
-It also contains data on partisan self-identification.
+It also includes data on partisan self-identification.
 Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents.
@@
 
-Our main analysis uses classifications provided by YouGov.
-Of the 6 million visits to 855,564 unique anonymized URLs, YouGov provides data on the kind of content hosted (e.g., Shopping, Business, Adult) for 727,681 unique URLs (making up 85\% of all visits).
-To illustrate the granularity of the categorization, \url{https://www.google.com/search?ANONYMIZED} is categorized as ``Search Engines and Portals'' while \url{https://mail.google.com/mail/u/0/} is categorized as ``Chat and Instant Messaging.''
+YouGov provides data on the kind of content hosted (e.g., Shopping, Business, Adult). 
+Of the 6 million visits to 855,564 unique anonymized URLs, YouGov provides classifications for 727,681 URLs (making up 85\% of all visits).
+To illustrate the granularity of the categorization, \url{https://www.google.com/search?ANONYMIZED} is categorized as ``Search Engines and Portals'' while \url{https://mail.google.com/mail/u/0/} is categorized as ``Chat and Instant Messaging.'' Our main analysis uses these YouGov classifications.
 
@@
 We code a domain as carrying pornographic content if there is nudity on the landing page or if the site is some form of erotica.
-Domains without a YouGov category are assumed to be non-pornographic sites.\footnote{
-    We replicate key findings by dropping observations on all sites without YouGov category instead of assuming that only non-pornographic sites have absent YouGov categories. 
-    This difference in assumption only affects results on proportion-based measures of consumption through the baseline on total duration. 
-    We find a similar skew in pornographic consumption. 
-    We also find that partisan differences disappear once we adjust for the baseline characteristics. 
-    \hyperref[sm:smH]{Appendix H} reports these results.
-}
-
-In \hyperref[sm:smE]{Appendix E}, we leverage \texttt{piedomains} and a Google service, Virustotal, to assess whether our results are robust to alternate ways of measuring the kind of content accessed by people.
+Domains without a YouGov category are assumed to be non-pornographic sites.
+In \hyperref[sm:smD]{Appendix D}, we test whether replacing this assumption with the more usual missing-completely-at-random assumption changes the key substantive conclusions.
+It doesn't.
+
+To further explore the robustness of our findings, we test if the results change if we use different measures of pornographic content.
+In \hyperref[sm:smE]{Appendix E},  \texttt{piedomains} and a Google service, Virustotal, to measure the kind of content accessed by people.
 \texttt{piedomains} uses open-source domain classification lists to train a neural network that learns the relationship between the kind of content hosted by a domain and the text on the homepage and homepage screenshots of websites \citep{Chintalapati_piedomains_Predict_the_2022}.
 VirusTotal collates domain classification data from different private services.
-Based on their data coverage of our domain data, we use the top three services: Forcepoint ThreatSeeker, Bitdefender, and alphaMountain.\footnote{Forcepoint ThreatSeeker, Bitdefender, and alphaMountain, respectively, cover 47,950, 43,391, and 36,063 of the roughly 64,000 unique domains the panelists visited over the month.}
+Based on their coverage of our domain data, we use the top three services: Forcepoint ThreatSeeker, Bitdefender, and alphaMountain.\footnote{Forcepoint ThreatSeeker, Bitdefender, and alphaMountain, respectively, cover 47,950, 43,391, and 36,063 of the roughly 64,000 unique domains the panelists visited over the month.}
 
@@
 The top three pornography sites (``\textit{xvideos.com}'', ``\textit{pornhub.com}'', and ``\textit{xnxx.com}'') are each visited more than 6,500 times by the people in our sample during the one-month period.
-The most visited site, xvideos.com, clocked 311 hours in total from our participants who visited a pornographic site.
-(Given 361 consumers of online pornography, this translates into an average of 52 minutes of consumption of \textit{xvideos.com} per participant.) Newer platforms such as ``\textit{onlyfans.com}'' are among the most visited pornography sites.
+The most visited site, xvideos.com, clocked 311 hours in total.
+(Given 361 consumers of online pornography, this translates into an average of 52 minutes of consumption of \textit{xvideos.com} per participant.) Newer platforms such as ``\textit{onlyfans.com}'' are also among the most visited pornography sites.
 Nine sites are above the 99th percentile in pornography visits (2,224 visits).
@@
 \caption*{\footnotesize \emph{Notes:} 
-    Each panel shows the average hours per decile for the sample period.
+    Each panel shows the average number of hours spent consuming respective kind of content during the observation period per decile.
     Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
-    The height of the bars indicates the mean of each bin. 
     Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
@@
 Of the 31.8 percent of the respondents who consumed any pornography during the month, the median consumer consumed less than an hour of pornography (approximately 42 minutes), while the 80th percentile consumer consumed nearly 4.5 hours and the 95th percentile almost 20 hours or about 40 minutes per day (see \cref{tab:distribution_duration}).
-A similar picture arises when it comes to the proportion of time spent online consuming pornography--the 50th percentile consumer spent about 3.1 percent of their time on online pornography.
+A similar picture arises when it comes to the percentage of time spent online consuming pornography--the 50th percentile consumer spent about 3.1 percent of their time on online pornography.
 For the 80th percentile, this is about 14 percent, and for the 95th percentile, this is about 58.5 percent (see \cref{tab:distribution_prop_duration}).
@@
 To help contextualize the above figures, we present statistics on time spent consuming content from the top ten non-adult categories in \cref{tab:top10cat_description}. 
-The median pornography consumer (\cref{tab:distribution_duration}) spends at least as many hours on adult content as the median online user on sites from six non-adult categories. 
-Only three categories, ``Business, Social Networking'' (e.g., facebook.com, soocial.com)), ``Chat and Instant Messaging'' (e.g., google.com, yahoo.com, live.com), and ``Entertainment, Streaming Media'' (e.g., youtube.com, hulu.com, netflix.com), have higher levels of consumption at the 95th percentile than online pornography.
+The median pornography consumer (\cref{tab:distribution_duration}) spends at least as much time on adult content as the median user on sites from six non-adult categories.
+Only three categories, ``Business, Social Networking,'' e.g., \texttt{facebook.com}, etc., ``Chat and Instant Messaging,'' e.g., \texttt{google.com}, \texttt{live.com}, and ``Entertainment, Streaming Media,'' e.g., \texttt{youtube.com}, \texttt{hulu.com}, \texttt{netflix.com}, have higher levels of consumption at the 95th percentile than online pornography.
 
@@
 Are people substituting pornography for other kinds of leisure content?
-To shed light on that, we examine the relationship between the time spent on online pornography vs.
-time spent on other leisure-related online sites.
-We fit locally weighted linear regression after removing extreme values (90th percentile) in online consumption.
-At the left tail of online pornography (below 0.5 hours), increases in pornography consumption are associated with fewer hours spent on non-adult-related shopping sites (\cref{fig:tu_prop_entertainment-prop_adult_duration}).
-Otherwise, there are no salient patterns of substitution in time spent on online pornography vs.
-other leisure sites.
+To shed light on that, we examine the relationship between the time spent on online pornography and time spent on other leisure-related online sites.
+We fit a locally weighted linear regression after removing extreme values (90th percentile) (for visualization or else the graph is dominated by the tail on which we have the least data) in online consumption.
+We see no evidence of substitution.
 
@@
 \caption{Time Spent on Online Pornography vs. Non-adult Leisure}
-\caption*{\footnotesize \emph{Notes:} Lowess between time spent on online pornography and time spent on other non-adult leisure (``entertainment'' and ``shopping'').
+\caption*{\footnotesize \emph{Notes:} Lowess between time spent on online pornography and time spent on other non-adult leisure (``entertainment'' and ``shopping'') with a bandwidth of .3.
 Observations above the 90th percentile for adult content consumption are omitted to prevent the graph from being dominated by these outliers.
-(Given we plot a lowess, such truncation doesn't change the relationship we show.) Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
-Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---the top five such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
-Each estimation in the Lowess uses .3 of the sample data.
+(Given we plot a lowess, such truncation doesn't change the relationship we show.) Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five such sites are \texttt{youtube.com}, \texttt{hideout.co}, \texttt{hulu.com}, \texttt{netflix.com}, and \texttt{yahoo.com}.
+Non-adult shopping sites are those with YouGov categories containing ``shopping,'' e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.---the top five such sites are \texttt{amazon.com}, \texttt{ebay.com}, \texttt{walmart.com}, \texttt{etsy.com}, \texttt{capitaloneshopping.com}, and \texttt{craigslist.org}.
 The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
-Swapping the horizontal axis for adult content excluding adult-related entertainment and shopping sites looks similar (see \cref{fig:tu_prop_entertainment-prop_pure_adult} in \hyperref[sm:smC]{Appendix C}).
+Swapping the horizontal axis for adult content excluding adult-related entertainment and shopping sites looks similar (see \cref{fig:tu_prop_entertainment-prop_pure_adult} in \hyperref[sm:smB]{Appendix B}).
 }
@@
 The median Republican consumer of pornography consumes 4 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.3 percent.\footnote{
-    With the missing at-random assumption, the Republican consumer of pornography consumes 4.2 percent of their online time on pornography, while the median Democratic consumer of pornography consumes 1.5 percent (\cref{tab:distribution_prop_duration_party_mar}).
+    With the missing at-random assumption, the Republican consumer of pornography spends 4.2 percent of their online time on pornography, while the median Democratic consumer of pornography spends 1.5 percent (\cref{tab:distribution_prop_duration_party_mar}).
 }
@@
 		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
-        \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
+        \cref{tab:quantile-estimates-hours} tabulates the estimates.
 	}
@@
 		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
-            %\cref{tab:quantile-estimates-time} tabulates the estimates.
-            \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
+            \cref{tab:quantile-estimates-time} tabulates the estimates.
 	}
@@
 
-Given the skew in the data, we quantify differences in online pornography consumption by party using quantile regression.\footnote{\cref{tab:characteristics_split_by_party_medians} presents non-parametric tests for differences in medians in the consumption of pornography.} Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
+Given the skew in the data, we quantify differences in online pornography consumption by party using quantile regression.
+(\cref{tab:characteristics_split_by_party_medians} presents non-parametric tests for differences in medians in pornography consumption; the median differences on time spent, share of time spent, etc., are all 0.) Our primary dependent variables of interest are the total time spent on pornographic sites and the proportion of time spent on pornographic sites.
 We regress the total time (share of time) spent on pornographic sites on an indicator for Republicans.
@@
 As \cref{fig:quantile_regression_duration} shows, the 80th percentile of the difference is close to 0, but from thereon, there is a diverging trend with the 95th percentile difference nearly 1.6 hrs.
-(\cref{tab:quantile-estimates-hours} reports estimates for each quantile.).\footnote{\hyperref[sm:smF]{Appendix F} describes the distribution of consumption of pornography online by independents.
+(\cref{tab:quantile-estimates-hours} reports estimates for each quantile.).\footnote{\hyperref[sm:smG]{Appendix G} describes the distribution of consumption of pornography online by independents.
 The median independent consumes more pornography than partisans (1.3 hours vs.
@@
 We use these timestamps to evaluate the extent to which differences in the timing of consumption differ by partisanship.
-Overall, we find some evidence that Republicans consume more online pornography in the morning (see \hyperref[sm:smD]{Appendix D}).
+Overall, we find some evidence that Republicans consume more pornography in the morning than Democrats (see \hyperref[sm:smH]{Appendix H}).
 
@@
 \newcommand{\smATitle}{Descriptive Analyses}
-\newcommand{\smBTitle}{Partisan Differences}
-\newcommand{\smCTitle}{Online Pornography vs. Leisure}
-\newcommand{\smDTitle}{Time of Consumption}
+\newcommand{\smBTitle}{Online Pornography vs. Leisure}
+\newcommand{\smCTitle}{Partisan Differences}
+\newcommand{\smDTitle}{Missing at Random}
 \newcommand{\smETitle}{Alternate Classifications of Pornography Sites}
-\newcommand{\smFTitle}{Consumption of Pornography Among Independents}
-\newcommand{\smGTitle}{Alternate Measures of Pornography}
-\newcommand{\smHTitle}{Missing at Random}
+\newcommand{\smFTitle}{Alternate Measures of Pornography Consumption}
+\newcommand{\smGTitle}{Consumption of Pornography Among Independents}
+\newcommand{\smHTitle}{Time of Consumption}
 
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The table shows the top 25 non-pornographic sites individuals visited during the observation period.
+		The table shows the top 25 non-pornographic sites visited by the sample.
 		The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
@@
 	\caption*{\footnotesize \emph{Notes:} 
-            The average number of minutes spent on the top 10 pornographic sites vs. all other pornographic sites.
-            Top 10 pornographic sites are determined by the total amount of time spent on each site by all individuals over the sample period.
+            The average minutes spent on the top 10 pornographic sites vs. all other pornographic sites.
+            The top 10 pornographic sites are determined by the total amount of time spent on each site by all individuals over the sample period.
             Data is at the individual-domain level (n = 2.4k).
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online (Conditional on having consumed pornography)}
+	\caption{Distribution of Consumption of Pornography Online Among People Who Consumed Any Pornography}
 	\label{tab:distribution_duration}
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites (Conditional on having consumed pornography)}
+	\caption{Percentage of Time Spent on Pornographic Sites Among People Who Consumed Any Pornography}
 	\label{tab:distribution_prop_duration}
@@
 \end{table}
-
 \clearpage
@@
 
+\begin{figure}[!h]
+\label{fig:tu_prop_entertainment-prop_pure_adult}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_pure_adult.pdf}
+         \caption{Entertainment}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_pure_adult.pdf}
+         \caption{Shopping}
+     \end{subfigure}
+\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
+\caption*{\footnotesize \emph{Notes:}
+Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs time spent on other non-adult leisure (``entertainment'' and ``shopping'').
+Observations above the 90th percentile are omitted. 
+Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five of such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
+Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---top five of such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
+Top five pure adult sites are: xvideos.com, pornhub.com, xnxx.com, rule34.xxx, and xhamster.com (see \cref{fig:top25_adult}).
+Each estimation in the Lowess uses .3 of the sample data.
+The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
+Swapping the horizontal axis for any adult content looks similar in \cref{fig:tu_prop_entertainment-prop_adult_duration}. 
+}
+\end{figure}
+
+\clearpage
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
+\FloatBarrier
+\renewcommand{\thetable}{C\arabic{table}}
+\renewcommand{\thefigure}{C\arabic{figure}}
+\renewcommand{\theequation}{C\arabic{equation}}
+\subsection{C. \smCTitle{}}\label{sm:smC}
+% =============================================================================
+
 %===========================================================================
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party (Conditional on having consumed pornography)}
+	\caption{Distribution of Consumption of Pornography Online by Party Among People Who Consumed Any Pornography}
 	\label{tab:distribution_duration_party}
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party (Conditional on having consumed pornography)}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party Among People Who Consumed Any Pornography}
 	\label{tab:distribution_prop_duration_party}
@@
 \begin{table}[ht] \centering \normalsize \setlength\tabcolsep{5 pt}
-	\caption{Differences (in Medians) in Pornography Consumption}
+	\caption{Median Differences in Pornography Consumption}
 	\label{tab:characteristics_split_by_party_medians}
@@
 		1st and 3rd quartiles in brackets.
-		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
+		Column (6) and column (7) report the p-values and Standardized Median Differences (SMD) for Democrats vs Republicans.
 		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
@@
 
-\setcounter{table}{0}
-\setcounter{figure}{0}
-\setcounter{equation}{0}
-% =============================================================================
-\FloatBarrier
-\renewcommand{\thetable}{C\arabic{table}}
-\renewcommand{\thefigure}{C\arabic{figure}}
-\renewcommand{\theequation}{C\arabic{equation}}
-\subsection{C. \smCTitle{}}\label{sm:smC}
-% =============================================================================
-
-\begin{figure}[!h]
-\label{fig:tu_prop_entertainment-prop_pure_adult}
-     \centering
-     \begin{subfigure}[b]{0.495\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_pure_adult.pdf}
-         \caption{Entertainment}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.495\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_pure_adult.pdf}
-         \caption{Shopping}
-     \end{subfigure}
-\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
-\caption*{\footnotesize \emph{Notes:}
-Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs time spent on other non-adult leisure (``entertainment'' and ``shopping'').
-Observations above the 90th percentile are omitted. 
-Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five of such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
-Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---top five of such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
-Top five pure adult sites are: xvideos.com, pornhub.com, xnxx.com, rule34.xxx, and xhamster.com (see \cref{fig:top25_adult}).
-Each estimation in the Lowess uses .3 of the sample data.
-The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
-Swapping the horizontal axis for any adult content looks similar in \cref{fig:tu_prop_entertainment-prop_adult_duration}. 
-}
-\end{figure}
-
 \clearpage
@@
 % =============================================================================
-
-First, we evaluate the density of the timing of visits to online pornography sites using 24-hour bins.
-As anticipated, most visits to online pornography sites occur around midnight.
-We also observe considerable traffic around the midday (1--3 pm, \cref{fig:time-of-day-consumption}).
-Both these observations track with \cite{webporn}'s findings using web session data.
-Second, we repeat the evaluation of the density of the timing of visits but split by partisanship.
-
-The densities suggest that Democratic traffic to pornography sites is concentrated around midnight (11 pm--1 am) while the Republican traffic is concentrated in the early morning (6 am--7 am, \cref{fig:time-of-day-consumption-by-party}).
-
-Third, to formally test whether there are differences in time of consumption by partisanship, we begin by dividing traffic to online pornography sites into six 4-hour bins: (a) 4 am--8 am, (b) 8 am--12 pm, (c) 12 pm--4 pm, (d) 4 pm--8 pm, (e) 8 pm--12 am, and (f) 12 am--4 am.
-We code a visit depending on which time interval it occurred and regress that time-of-day window on partisanship, weighted by the dwelling time of the visit.
-Cognizant of the somewhat ad-hoc splits for the time-of-day windows and that we are creating multiple outcome variables, we subject p-values of the partisan point estimate to Bonferroni correction in addition to the adjustments for individual-level demographics.
-
-\begin{figure}[ht]
-\centering
-    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption.pdf}
-\caption{Time-of-Day Traffic to Online Pornography Sites}
-\caption*{\footnotesize \emph{Notes:} 
-        Density plot of traffic to online pornography sites.
-        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 84,289).
-        Each of the 24 bins corresponds to an hour of the day.
-	}
-    \label{fig:time-of-day-consumption}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption-by-party.pdf}
-\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
-\caption*{\footnotesize \emph{Notes:} 
-        Density plot of traffic to online pornography sites by partisanship (indicated by colors); bars for Republican consumption are also hatched.
-        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 59,324).
-        Each of the 24 bins corresponds to an hour of the day.
-        See \cref{tab:regtab_wls_visit_timing_4hrbins}, which reports formal tests of differences in time-of-day visits by party.
-	}
-    \label{fig:time-of-day-consumption-by-party}
-\end{figure}
-
 \begin{figure}[!ht]
-\centering
-    \includegraphics[width=.85\linewidth]{figs/time-of-day-wls-estimates.pdf}
-\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
-\caption*{\footnotesize \emph{Notes:} 
-        Estimates of partisan differences in time-of-day visits to online pornography sites.
-        Points represent differences between Republicans relative to Democrats (reference category)---interpreted as proportion differences.
-        The adjusted estimate, which is significant at the 1\% level after Bonferroni correction (at 4 am--8 am), is indicated in the figure.
-        Vertical lines are 95\% confidence intervals.
-        This figure offers an alternative visualization of \cref{tab:regtab_wls_visit_timing_4hrbins}.
-	}
-    \label{fig:time-of-day-wls-estimates}
-\end{figure}
-
-\cref{fig:time-of-day-wls-estimates} reports a summary of this exercise (\cref{tab:regtab_wls_visit_timing_4hrbins} reports the full set of estimates).
-The unadjusted estimates suggest that Republicans are more likely to consume pornography during midday (the 12 pm--4 pm window), relative to Democrats, which is significant at the 1 percent level after correction.
-Conversely, Republicans are less likely to consume pornography late at night (12 am--4 am).
-These unadjusted findings correspond somewhat to our evaluation of densities of visits by partisanship where Democrat visits to online pornography are concentrated around midnight (\cref{fig:time-of-day-consumption-by-party}).
-
-Once we adjust for the individual-level demographics and for day-of-week fixed effects, Republicans are no longer more (or less) likely to consume pornography during the midday (or late at night).
-However, the adjusted estimates suggest that Republicans are more likely to consume pornography in the early morning (4 am--8 am), specifically five percentage points more likely, which is significant at the 1 percent level even after Bonferroni correction (indicated in \cref{fig:time-of-day-wls-estimates}).
-
-\begin{table}[!ht] \centering \scriptsize \setlength\tabcolsep{9 pt} \setlength{\defaultaddspace}{0pt}
-\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
-\caption{Time-of-Day Traffic to Pornographic by Party}
-\label{tab:regtab_wls_visit_timing_4hrbins}
+\label{fig:distribution_duration_on_adultsites_fullsample_mar}
+     \centering
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/mar/distribution_duration_on_adultsites_fullsample.pdf}
+         \caption{Online pornography}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.495\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{figs/mar/distribution_duration_on_nonadultsites_fullsample.pdf}
+         \caption{Other online content}
+     \end{subfigure}
+\caption{Hours Spent on Online Pornography and All Other Online Content}
+\caption*{\footnotesize \emph{Notes:} 
+    Each panel shows the average hours per decile for the sample period.
+    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
+    The height of the bars indicates the mean of each bin. 
+    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
+    \cref{fig:distribution_duration_on_adultsites_fullsample} in main body.
+
+}
+\end{figure}
+
+%========================================
+% Quantile regressions
+% Proportion of time spent on adult sites
+%========================================
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_proportion_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration_covariates_mar} for the same plot controlling for individual characteristics.
+            \cref{fig:quantile_regression_prop_duration} in main body.
+	}
+	\label{fig:quantile_regression_prop_duration_mar}
+\end{figure}
+
+%================================================================
+% Fig of quantile regression estimates
+% Percentage Time Spent on Adult Sites by Party (with covariates) 
+%================================================================
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_covariates_proportion_duration_adult.pdf}
+	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
+	\caption*{\footnotesize \emph{Notes:} 
+		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		95\% confidence intervals constructed from standard errors.
+		See \cref{fig:quantile_regression_prop_duration_mar} for the same plot without covariates.
+            \cref{fig:quantile_regression_prop_duration_covariates} in main body.
+	}
+	\label{fig:quantile_regression_prop_duration_covariates_mar}
+\end{figure}
+
+%=====================================================================
+% Tabulated percentiles of the proportion of duration spent on adult sites
+%=====================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites Among People Who Consumed Any Pornography}
+	\label{tab:distribution_prop_duration_mar}
 	\begin{adjustbox}{max width=\textwidth}
-        \begin{tabular}{@{\hspace{0\tabcolsep}}l*{6}{D{.}{.}{-1}}@{\hspace{0\tabcolsep}}}
-        \toprule\toprule
-        &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}\\
-        \cmidrule(l){2-7}
-        &\multicolumn{6}{c}{\textbf{Panel A. WLS estimates}}\\
-        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
-        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
-        \cmidrule(l){2-7}
-        \input{../tabs/regtab_wls_visit_timing_4hrbins}\\
-        \cmidrule(l){2-7}
-        &\multicolumn{6}{c}{\textbf{Panel B. Adjusted WLS estimates}}\\
-        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
-        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
-        \cmidrule(l){2-7}
-        \input{../tabs/regtab_wls_visit_timing_4hrbins_adjusted}\\
-    \bottomrule
-    \end{tabular}
-    \end{adjustbox}
-    \caption*{\scriptsize
-    The table reports weighted least squares estimates from regressing a binary variable based on time-of-day visits to online pornography on the Republican dummy.
-    The unit of observation is at the individual web browsing level for traffic to pornography sites (n = 59,324).
-    Each column represents dummy variables for each of the six 4-hour windows.
-    Weights are the duration of each visit.
-    Models also adjust for day-of-week fixed effects (not reported to conserve space).
-    See also \cref{fig:time-of-day-consumption-by-party}, which provides descriptive evidence that the density in time-of-day traffic is different by party.
-    Significance levels (uncorrected): $^{*}$ 0.05 $^{**}$0.01.
-    P-values are Bonferroni-corrected for six tests---the $^\dagger$ indicates significance at the p = 0.01 level after adjustment.    
+		\begin{tabular}{cr}
+			\toprule
+			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
+			\midrule
+			\input{../tabs/mar/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
+The base number is the individual's own total time spent on the web.
+See \cref{tab:distribution_duration} for the distribution of total time spent on pornographic websites.
+    See also \cref{tab:distribution_prop_duration}.
+ }
+\end{table}
+
+%===============================================================================
+% Tabulated splits by party and by percentiles for the proportion of time spent on adultsites
+%===============================================================================
+\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites by Party Among People Who Consumed Any Pornography}
+	\label{tab:distribution_prop_duration_party_mar}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{crr}
+			\toprule
+			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
+			\cmidrule(l){2-3}
+			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
+			\midrule
+			\input{../tabs/mar/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+        The base number is the individual's own total time spent on the web.
+		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
+          See also \cref{tab:distribution_prop_duration_party}.
 	}
@@
 \setcounter{equation}{0}
+
 % =============================================================================
@@
 
+\clearpage
 \setcounter{table}{0}
@@
 \subsection{F. \smFTitle{}}\label{sm:smF}
-% =============================================================================
-%===========================================================================
-% Tabulated splits by party and by percentiles for hours spent on adultsites
-%===========================================================================
-\begin{table}[!ht] \centering \small \setlength\tabcolsep{6 pt}
-	\caption{Time Spent on Pornographic Sites (including Independents)}
-	\label{tab:percentiles_duration_adultsites_by_individuals_independents_partisans}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrr@{\hspace{0\tabcolsep}}}
-			\toprule		
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
-            &\multicolumn{3}{c}{\textbf{Partisans}}&\multicolumn{2}{c}{\textbf{Non-partisans}}\\
-            \cmidrule(lr){2-4}\cmidrule(l){5-6}
-			\textbf{Percentile}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\textbf{Independents/DK}\\
-			\midrule
-			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
-            \midrule
-            Observations&\multicolumn{1}{r}{\text{98}}&\multicolumn{1}{r}{\text{158}}&\multicolumn{1}{r}{\text{256}}&\multicolumn{1}{r}{\text{68}}&105\\   
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
-	}
-\end{table}
-
-\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites  (including Independents)}
-	\label{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrr@{\hspace{0\tabcolsep}}}
-			\toprule		
-			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
-            &\multicolumn{3}{c}{\textbf{Partisans}}&\multicolumn{2}{c}{\textbf{Non-partisans}}\\
-            \cmidrule(lr){2-4}\cmidrule(l){5-6}
-			\textbf{Percentile}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\textbf{Independents/DK}\\
-			\midrule
-            \input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
-            \midrule
-            Observations&\multicolumn{1}{r}{\text{98}}&\multicolumn{1}{r}{\text{158}}&\multicolumn{1}{r}{\text{256}}&\multicolumn{1}{r}{\text{68}}&105\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-	}
-\end{table}
-
-\clearpage
-\setcounter{table}{0}
-\setcounter{figure}{0}
-\setcounter{equation}{0}
-% =============================================================================
-\FloatBarrier
-\renewcommand{\thetable}{G\arabic{table}}
-\renewcommand{\thefigure}{G\arabic{figure}}
-\renewcommand{\theequation}{G\arabic{equation}}
-\subsection{G. \smGTitle{}}\label{sm:smG}
 % =============================================================================
@@
 	\centering
-	\includegraphics[width=.5\linewidth]{figs/distribution_visits_to_adultsites.pdf}
+	\includegraphics[width=.65\linewidth]{figs/distribution_visits_to_adultsites.pdf}
 	\caption{Distribution of Traffic to Pornography Online}
@@
 	\centering
-	\includegraphics[width=.5\linewidth]{figs/distribution_proportion_visits_to_adultsites.pdf}
+	\includegraphics[width=.65\linewidth]{figs/distribution_proportion_visits_to_adultsites.pdf}
 	\caption{Percentage of Traffic to Pornography Online}
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party}
+	\caption{Distribution of Consumption of Pornography Online by Party Among People Who Consumed Any Pornography}
 	\label{tab:distribution_visits_party}
@@
 \begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Distribution of Consumption of Pornography Online by Party}
+	\caption{Distribution of Consumption of Pornography Online by Party Among People Who Consumed Any Pornography}
 	\label{tab:distribution_prop_visits_party}
@@
 \FloatBarrier
+\renewcommand{\thetable}{G\arabic{table}}
+\renewcommand{\thefigure}{G\arabic{figure}}
+\renewcommand{\theequation}{G\arabic{equation}}
+\subsection{G. \smGTitle{}}\label{sm:smG}
+% =============================================================================
+%===========================================================================
+% Tabulated splits by party and by percentiles for hours spent on adultsites
+%===========================================================================
+\begin{table}[!ht] \centering \small \setlength\tabcolsep{6 pt}
+	\caption{Time Spent on Pornographic Sites by Partisanship Among People Who Consumed Any Pornography}
+	\label{tab:percentiles_duration_adultsites_by_individuals_independents_partisans}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrr@{\hspace{0\tabcolsep}}}
+			\toprule		
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
+            &\multicolumn{3}{c}{\textbf{Partisans}}&\multicolumn{2}{c}{\textbf{Non-partisans}}\\
+            \cmidrule(lr){2-4}\cmidrule(l){5-6}
+			\textbf{Percentile}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\textbf{Independents/DK}\\
+			\midrule
+			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
+            \midrule
+            Observations&\multicolumn{1}{r}{\text{98}}&\multicolumn{1}{r}{\text{158}}&\multicolumn{1}{r}{\text{256}}&\multicolumn{1}{r}{\text{68}}&105\\   
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} 
+		The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period.
+	}
+\end{table}
+
+\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
+	\caption{Percentage of Time Spent on Pornographic Sites by Partisanship Among People Who Consumed Any Pornography}
+	\label{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}
+	\begin{adjustbox}{max width=\textwidth}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrr@{\hspace{0\tabcolsep}}}
+			\toprule		
+			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
+            &\multicolumn{3}{c}{\textbf{Partisans}}&\multicolumn{2}{c}{\textbf{Non-partisans}}\\
+            \cmidrule(lr){2-4}\cmidrule(l){5-6}
+			\textbf{Percentile}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\textbf{Independents/DK}\\
+			\midrule
+            \input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
+            \midrule
+            Observations&\multicolumn{1}{r}{\text{98}}&\multicolumn{1}{r}{\text{158}}&\multicolumn{1}{r}{\text{256}}&\multicolumn{1}{r}{\text{68}}&105\\
+			\bottomrule
+		\end{tabular}
+	\end{adjustbox}
+	\caption*{\footnotesize \emph{Notes:} The table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
+	}
+\end{table}
+
+\clearpage
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{equation}{0}
+% =============================================================================
+\FloatBarrier
 \renewcommand{\thetable}{H\arabic{table}}
@@
 % =============================================================================
+
+First, we evaluate the density of the timing of visits to online pornography sites using 24-hour bins.
+As anticipated, most visits to online pornography sites occur around midnight.
+We also observe considerable traffic around the midday (1--3 pm, \cref{fig:time-of-day-consumption}).
+Both these observations track with \cite{webporn}'s findings using web session data.
+Second, we repeat the evaluation of the density of the timing of visits but split by partisanship.
+
+The densities suggest that Democratic traffic to pornography sites is concentrated around midnight (11 pm--1 am) while the Republican traffic is concentrated in the early morning (6 am--7 am, \cref{fig:time-of-day-consumption-by-party}).
+
+Third, to formally test whether there are differences in time of consumption by partisanship, we begin by dividing traffic to online pornography sites into six 4-hour bins: (a) 4 am--8 am, (b) 8 am--12 pm, (c) 12 pm--4 pm, (d) 4 pm--8 pm, (e) 8 pm--12 am, and (f) 12 am--4 am.
+We code a visit depending on which time interval it occurred and regress that time-of-day window on partisanship, weighted by the dwelling time of the visit.
+Cognizant of the somewhat ad-hoc splits for the time-of-day windows and that we are creating multiple outcome variables, we subject p-values of the partisan point estimate to Bonferroni correction in addition to the adjustments for individual-level demographics.
+
+\begin{figure}[ht]
+\centering
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption.pdf}
+\caption{Time-of-Day Traffic to Online Pornography Sites}
+\caption*{\footnotesize \emph{Notes:} 
+        Density plot of traffic to online pornography sites.
+        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 84,289).
+        Each of the 24 bins corresponds to an hour of the day.
+	}
+    \label{fig:time-of-day-consumption}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+    \includegraphics[width=.75\linewidth]{figs/time-of-day-consumption-by-party.pdf}
+\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
+\caption*{\footnotesize \emph{Notes:} 
+        Density plot of traffic to online pornography sites by partisanship (indicated by colors); bars for Republican consumption are also hatched.
+        Data is at the individual-browsing level with timestamped visits to pornography sites (individual-browsing n = 59,324).
+        Each of the 24 bins corresponds to an hour of the day.
+        See \cref{tab:regtab_wls_visit_timing_4hrbins}, which reports formal tests of differences in time-of-day visits by party.
+	}
+    \label{fig:time-of-day-consumption-by-party}
+\end{figure}
+
 \begin{figure}[!ht]
-\label{fig:distribution_duration_on_adultsites_fullsample_mar}
-     \centering
-     \begin{subfigure}[b]{0.495\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{figs/mar/distribution_duration_on_adultsites_fullsample.pdf}
-         \caption{Online pornography}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.495\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{figs/mar/distribution_duration_on_nonadultsites_fullsample.pdf}
-         \caption{Other online content}
-     \end{subfigure}
-\caption{Hours Spent on Online Pornography and All Other Online Content}
-\caption*{\footnotesize \emph{Notes:} 
-    Each panel shows the average hours per decile for the sample period.
-    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
-    The height of the bars indicates the mean of each bin. 
-    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
-    \cref{fig:distribution_duration_on_adultsites_fullsample} in main body.
-
-}
-\end{figure}
-
-%========================================
-% Quantile regressions
-% Proportion of time spent on adult sites
-%========================================
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_proportion_duration_adult.pdf}
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
-	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_prop_duration_covariates_mar} for the same plot controlling for individual characteristics.
-            \cref{fig:quantile_regression_prop_duration} in main body.
-	}
-	\label{fig:quantile_regression_prop_duration_mar}
-\end{figure}
-
-%================================================================
-% Fig of quantile regression estimates
-% Percentage Time Spent on Adult Sites by Party (with covariates) 
-%================================================================
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_covariates_proportion_duration_adult.pdf}
-	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
-	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
-		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_prop_duration_mar} for the same plot without covariates.
-            \cref{fig:quantile_regression_prop_duration_covariates} in main body.
-	}
-	\label{fig:quantile_regression_prop_duration_covariates_mar}
-\end{figure}
-
-%=====================================================================
-% Tabulated percentiles of the proportion of duration spent on adult sites
-%=====================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites (Conditional on having consumed pornography)}
-	\label{tab:distribution_prop_duration_mar}
+\centering
+    \includegraphics[width=.85\linewidth]{figs/time-of-day-wls-estimates.pdf}
+\caption{Time-of-Day Traffic to Online Pornography Sites by Party}
+\caption*{\footnotesize \emph{Notes:} 
+        Estimates of partisan differences in time-of-day visits to online pornography sites.
+        Points represent differences between Republicans relative to Democrats (reference category)---interpreted as proportion differences.
+        The adjusted estimate, which is significant at the 1\% level after Bonferroni correction (at 4 am--8 am), is indicated in the figure.
+        Vertical lines are 95\% confidence intervals.
+        This figure offers an alternative visualization of \cref{tab:regtab_wls_visit_timing_4hrbins}.
+	}
+    \label{fig:time-of-day-wls-estimates}
+\end{figure}
+
+\cref{fig:time-of-day-wls-estimates} reports a summary of this exercise (\cref{tab:regtab_wls_visit_timing_4hrbins} reports the full set of estimates).
+The unadjusted estimates suggest that Republicans are more likely to consume pornography during midday (the 12 pm--4 pm window), relative to Democrats, which is significant at the 1 percent level after correction.
+Conversely, Republicans are less likely to consume pornography late at night (12 am--4 am).
+These unadjusted findings correspond somewhat to our evaluation of densities of visits by partisanship where Democrat visits to online pornography are concentrated around midnight (\cref{fig:time-of-day-consumption-by-party}).
+
+Once we adjust for the individual-level demographics and for day-of-week fixed effects, Republicans are no longer more (or less) likely to consume pornography during the midday (or late at night).
+However, the adjusted estimates suggest that Republicans are more likely to consume pornography in the early morning (4 am--8 am), specifically five percentage points more likely, which is significant at the 1 percent level even after Bonferroni correction (indicated in \cref{fig:time-of-day-wls-estimates}).
+
+\begin{table}[!ht] \centering \scriptsize \setlength\tabcolsep{9 pt} \setlength{\defaultaddspace}{0pt}
+\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
+\caption{Time-of-Day Traffic to Pornographic by Party}
+\label{tab:regtab_wls_visit_timing_4hrbins}
 \begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{cr}
-			\toprule
-			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{\% time}}\\
-			\midrule
-			\input{../tabs/mar/percentiles_proportion_duration_adultsites_by_individuals.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the percentage of time on pornography sites spent by individuals who consumed pornography in the sample period.
-The base number is the individual's own total time spent on the web.
-See \cref{tab:distribution_duration} for the distribution of total time spent on pornographic websites.
-    See also \cref{tab:distribution_prop_duration}.
- }
-\end{table}
-
-%===============================================================================
-% Tabulated splits by party and by percentiles for the proportion of time spent on adultsites
-%===============================================================================
-\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
-	\caption{Percentage of Time Spent on Pornographic Sites by Party (Conditional on having consumed pornography)}
-	\label{tab:distribution_prop_duration_party_mar}
-	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{crr}
-			\toprule
-			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
-			\cmidrule(l){2-3}
-			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
-			\midrule
-			\input{../tabs/mar/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
-			\bottomrule
-		\end{tabular}
-	\end{adjustbox}
-	\caption*{\footnotesize \emph{Notes:} 
-		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period.
-        The base number is the individual's own total time spent on the web.
-		See \cref{tab:distribution_duration_party} for the distribution in terms of percentage of time.
-          See also \cref{tab:distribution_prop_duration_party}.
+        \begin{tabular}{@{\hspace{0\tabcolsep}}l*{6}{D{.}{.}{-1}}@{\hspace{0\tabcolsep}}}
+        \toprule\toprule
+        &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         &\multicolumn{1}{c}{(5)}         &\multicolumn{1}{c}{(6)}\\
+        \cmidrule(l){2-7}
+        &\multicolumn{6}{c}{\textbf{Panel A. WLS estimates}}\\
+        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
+        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
+        \cmidrule(l){2-7}
+        \input{../tabs/regtab_wls_visit_timing_4hrbins}\\
+        \cmidrule(l){2-7}
+        &\multicolumn{6}{c}{\textbf{Panel B. Adjusted WLS estimates}}\\
+        &\multicolumn{6}{c}{Outcome variable is a binary variable based on time-of-day visit:}\\
+        &\multicolumn{1}{c}{4am--8am}&\multicolumn{1}{c}{8am--12pm}&\multicolumn{1}{c}{12pm--4pm}&\multicolumn{1}{c}{4pm--8pm}&\multicolumn{1}{c}{8pm--12am}&\multicolumn{1}{c}{12am--4am}\\
+        \cmidrule(l){2-7}
+        \input{../tabs/regtab_wls_visit_timing_4hrbins_adjusted}\\
+    \bottomrule
+    \end{tabular}
+    \end{adjustbox}
+    \caption*{\scriptsize
+    The table reports weighted least squares estimates from regressing a binary variable based on time-of-day visits to online pornography on the Republican dummy.
+    The unit of observation is at the individual web browsing level for traffic to pornography sites (n = 59,324).
+    Each column represents dummy variables for each of the six 4-hour windows.
+    Weights are the duration of each visit.
+    Models also adjust for day-of-week fixed effects (not reported to conserve space).
+    See also \cref{fig:time-of-day-consumption-by-party}, which provides descriptive evidence that the density in time-of-day traffic is different by party.
+    Significance levels (uncorrected): $^{*}$ 0.05 $^{**}$0.01.
+    P-values are Bonferroni-corrected for six tests---the $^\dagger$ indicates significance at the p = 0.01 level after adjustment.    
     }

### 2024-04-29 tabs/top10cat_description.tex
Fixing Tab A1
Imputing 0s for categories with no visits across individuals

@@
-                                  Business & 720,930 & 13.0 &   720,930 & 13.0 & (decipherinc.com, samplicio.us, privatelink.de) & 4.8 & 10.0 & 0.0 & 0.5 & 1.8 & 5.0 & 11.7 & 18.7 & 140.5 \\
-                Search Engines and Portals & 670,710 & 12.1 & 1,391,640 & 25.0 &           (google.com, google.co.uk, yahoo.com) & 4.1 &  8.9 & 0.0 & 0.2 & 1.5 & 4.9 & 10.2 & 15.4 & 139.9 \\
-                Chat and Instant Messaging & 613,394 & 11.0 & 2,005,034 & 36.0 &               (google.com, yahoo.com, live.com) & 9.0 & 25.8 & 0.0 & 0.2 & 2.7 & 9.7 & 21.3 & 31.1 & 492.3 \\
-               Business, Social Networking & 443,281 &  8.0 & 2,448,315 & 44.0 &        (facebook.com, facebook.co, soocial.com) & 6.4 & 18.6 & 0.0 & 0.1 & 0.6 & 4.5 & 15.4 & 33.0 & 245.5 \\
-                                  Shopping & 328,300 &  5.9 & 2,776,615 & 49.9 &             (amazon.com, ebay.com, walmart.com) & 3.6 &  7.3 & 0.0 & 0.2 & 1.2 & 3.8 &  9.0 & 15.9 &  79.0 \\
-          Business, Information Technology & 284,428 &  5.1 & 3,061,043 & 55.0 &       (clarity.ms, sentry.io, inboxdollars.com) & 1.8 &  4.9 & 0.0 & 0.1 & 0.5 & 1.8 &  4.1 &  7.0 &  87.8 \\
-            Entertainment, Streaming Media & 261,165 &  4.7 & 3,322,208 & 59.7 &            (youtube.com, hulu.com, netflix.com) & 7.2 & 32.7 & 0.0 & 0.1 & 0.3 & 3.0 & 14.8 & 27.8 & 617.5 \\
-News and Media, Search Engines and Portals & 231,157 &  4.2 & 3,553,365 & 63.9 &                             (bing.com, att.net) & 3.2 &  6.3 & 0.0 & 0.0 & 0.7 & 3.8 &  9.0 & 16.0 &  61.8 \\
-                       Business, Education & 181,106 &  3.3 & 3,734,471 & 67.1 &           (yougov.com, google.com, prolific.co) & 1.8 &  4.9 & 0.0 & 0.2 & 0.7 & 1.8 &  3.8 &  6.5 & 104.5 \\
-                        Business, Shopping & 135,431 &  2.4 & 3,869,902 & 69.6 &        (amazon.com, rakuten.com, instacart.com) & 1.5 &  3.2 & 0.0 & 0.1 & 0.4 & 1.3 &  3.5 &  5.9 &  32.2
+                                  Business & 720,930 & 13.0 &   720,930 & 13.0 & (decipherinc.com, samplicio.us, privatelink.de) & 4.6 &  9.9 & 0.0 & 0.4 & 1.6 & 4.8 & 11.3 & 18.6 & 140.5 \\
+                Search Engines and Portals & 670,710 & 12.1 & 1,391,640 & 25.0 &           (google.com, google.co.uk, yahoo.com) & 4.0 &  8.7 & 0.0 & 0.2 & 1.3 & 4.5 & 10.0 & 15.2 & 139.9 \\
+                Chat and Instant Messaging & 613,394 & 11.0 & 2,005,034 & 36.0 &               (google.com, yahoo.com, live.com) & 5.9 & 21.3 & 0.0 & 0.0 & 0.2 & 5.3 & 16.4 & 25.1 & 492.3 \\
+               Business, Social Networking & 443,281 &  8.0 & 2,448,315 & 44.0 &        (facebook.com, facebook.co, soocial.com) & 5.0 & 16.6 & 0.0 & 0.0 & 0.2 & 2.5 & 11.4 & 23.2 & 245.5 \\
+                                  Shopping & 328,300 &  5.9 & 2,776,615 & 49.9 &             (amazon.com, ebay.com, walmart.com) & 3.2 &  7.0 & 0.0 & 0.1 & 0.8 & 3.2 &  8.2 & 14.4 &  79.0 \\
+          Business, Information Technology & 284,428 &  5.1 & 3,061,043 & 55.0 &       (clarity.ms, sentry.io, inboxdollars.com) & 1.7 &  4.7 & 0.0 & 0.1 & 0.4 & 1.6 &  3.9 &  6.4 &  87.8 \\
+            Entertainment, Streaming Media & 261,165 &  4.7 & 3,322,208 & 59.7 &            (youtube.com, hulu.com, netflix.com) & 5.5 & 28.7 & 0.0 & 0.0 & 0.1 & 1.4 &  9.6 & 20.5 & 617.5 \\
+News and Media, Search Engines and Portals & 231,157 &  4.2 & 3,553,365 & 63.9 &                             (bing.com, att.net) & 1.3 &  4.3 & 0.0 & 0.0 & 0.0 & 0.2 &  3.9 &  6.9 &  61.8 \\
+                       Business, Education & 181,106 &  3.3 & 3,734,471 & 67.1 &           (yougov.com, google.com, prolific.co) & 1.7 &  4.7 & 0.0 & 0.1 & 0.6 & 1.7 &  3.5 &  6.3 & 104.5 \\
+                        Business, Shopping & 135,431 &  2.4 & 3,869,902 & 69.6 &        (amazon.com, rakuten.com, instacart.com) & 1.2 &  3.0 & 0.0 & 0.0 & 0.3 & 1.1 &  3.0 &  5.1 &  32.2

### 2024-04-29 ms/main.tex
Updates from Overleaf

@@
 Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that people in politically conservative states search for pornography and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}.
-Combining individual-level data on partisanship with direct passive individual level measures of pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa.
+Combining individual-level data on partisanship with direct passive individual-level measures of pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa.
 Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats.
-Adjusting for background attributes such as age, gender, race, and education, however, make the partisan differences go away.
+Adjusting for background attributes such as age, gender, race, and education, however, makes the partisan differences go away.
 Our findings relate to \cite{Perry2018-cn}, which finds that more religious people are more likely to think of pornography as morally wrong while still consuming pornography.
@@
 To code pornographic content, we start by assuming all content marked ``Adult'' as pornographic.
-This includes ``Adult, Business'' (e.g., onlyfans.com) and ``Adult, Entertainment'' (e.g., hentainfox.com).
-YouGov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as Adult.
+This includes ``Adult, Business'' (e.g., onlyfans.com) and ``Adult, Entertainment,'' e.g., \texttt{hentainfox.com}.
+YouGov classifies some domains that do not primarily carry pornographic content, e.g., \texttt{urbandictionary.com} and \texttt{4chan.org}, as Adult.
 Given the skew in the data (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites.
@@
 As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites.
-Each of the top 5 non-pornographic sites were visited more than 200,000 times by our panelists.
+Each of the top 5 non-pornographic sites was visited more than 200,000 times by our panelists.
 In comparison, the 99th percentile non-pornographic site was visited only 1,652 times by our panelists during the observation period.
@@
 \caption*{\footnotesize \emph{Notes:} 
-    Each panel shows the average number of hours spent consuming respective kind of content during the observation period per decile.
+    Each panel shows the average number of hours spent consuming the respective kind of content during the observation period per decile.
     Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
@@
 To shed light on that, we examine the relationship between the time spent on online pornography and time spent on other leisure-related online sites.
-We fit a locally weighted linear regression after removing extreme values (90th percentile) (for visualization or else the graph is dominated by the tail on which we have the least data) in online consumption.
+We fit a locally weighted linear regression after removing extreme values (90th percentile) (for visualization, or else the graph is dominated by the tail on which we have the least data) in online consumption.
 We see no evidence of substitution.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		The dependent variable is the number of hours spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-	The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+	The dependent variable is the percentage of time spent on pornographic sites.
 Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 
-Looking at differences in the percentage of partisans who consume any pornographic content, we find little difference as well.
+Differences in the percentage of partisans who consume any pornographic content reveal little difference as well.
 Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).
@@
 		95\% confidence intervals constructed from standard errors.
-		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
-  \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
+		See \cref{fig:quantile_regression_duration} for the same plot without covariates. \cref{tab:quantile-estimates-hours} tabulates the estimates.
 	}
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		The dependent variable is the percentage of time spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
   Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
-		Covariates included: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
 		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
-        \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
+        \cref{tab:quantile-estimates-time} tabulates the estimates.
 	}
@@
 
-Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). 
-%Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}). 
+Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}).
+For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}).
 How do differences in age and other such demographic differences between the parties ``explain'' the results?
@@
 \subsection{Robustness}\label{sec:robustness}
-We replicate our analyses using four alternative classifications of domains and obtain similar results (see \hyperref[sm:smE]{Appendix E}).  
-In \hyperref[sm:smG]{Appendix G}, we also analyze similar metrics for the total number of visits and proportion of visits instead of time. 
+\hyperref[sm:smD]{Appendix D} replicates key findings by dropping domains with missing YouGov domain categories.
+We also replicate our analyses using four alternative classifications of domains and obtain similar results (see \hyperref[sm:smE]{Appendix E}).
+In \hyperref[sm:smF]{Appendix F}, we analyze the impact on the total number of visits and the percentage of visits instead of time.
 The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party}).
-\hyperref[sm:smH]{Appendix H} replicates key findings by dropping domains with missing YouGov domain category.
 
@@
 The second concern is that our measures are a point in time.
-We have data from one month in one year - June 2022.
+We have data from one month in one year---June 2022.
 It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in the preceding or following months.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The table shows the top 25 non-pornographic sites visited by the sample.
-		The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
-		The \emph{Visits} column is the total number of visits by individuals in the sample to the site.  			
+		The table shows the top 25 non-pornographic sites visited by respondents in the sample period.
+		The \emph{Hours} column is the total number of hours spent by all the respondents in the sample period.
+    	The \emph{Visits} column is the total number of visits by all the respondents in the sample period.			
 		Sites to the right of the vertical dashed are the top 1 percent of non-pornographic sites in visits.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The table shows the top 25 pornographic sites that individuals visited in the sample period.
-		Pornography sites are categorized by YouGov (see the \nameref{sec:data} section).
-    	The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
-    	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.
+		The table shows the top 25 pornographic sites visited by respondents in the sample period. Pornography sites are categorized by YouGov (see the \nameref{sec:data} section).
+    	The \emph{Hours} column is the total number of hours spent by all the respondents in the sample period.
+    	The \emph{Visits} column is the total number of visits by all the respondents in the sample period.
             Sites to the right of the vertical dashed are the top 1 percent of pornographic sites in visits.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-            The average minutes spent on the top 10 pornographic sites vs. all other pornographic sites.
-            The top 10 pornographic sites are determined by the total amount of time spent on each site by all individuals over the sample period.
+            The average number of minutes spent on the top 10 pornographic sites vs. all other pornographic sites.
+            The top 10 pornographic sites are determined by the total amount of time spent on each site by all the respondents during the sample period.
             Data is at the individual-domain level (n = 2.4k).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period.
+		The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the number of hours spent by individuals who consumed pornography in the sample period.
 		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
@@
 \caption*{\footnotesize \emph{Notes:}
-Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs time spent on other non-adult leisure (``entertainment'' and ``shopping'').
+Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs.
+time spent on other non-adult leisure (``entertainment'' and ``shopping'') with a bandwidth of .3.
 Observations above the 90th percentile are omitted.
-Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five of such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
-Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---top five of such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
-Top five pure adult sites are: xvideos.com, pornhub.com, xnxx.com, rule34.xxx, and xhamster.com (see \cref{fig:top25_adult}).
-Each estimation in the Lowess uses .3 of the sample data.
+Non-adult entertainment sites are those with YouGov categories containing ``entertainment,'' e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.---top five such sites are \texttt{youtube.com}, \texttt{hideout.co}, \texttt{hulu.com}, \texttt{netflix.com}, and \texttt{yahoo.com}.
+Non-adult shopping sites are those with YouGov categories containing ``shopping,'' e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.---top five of such sites are \texttt{amazon.com}, \texttt{ebay.com}, \texttt{walmart.com}, \texttt{etsy.com}, \texttt{capitaloneshopping.com}, and \texttt{craigslist.org}.
+Top five pure adult sites are: \texttt{xvideos.com}, \texttt{pornhub.com}, \texttt{xnxx.com}, \texttt{rule34.xxx}, and \texttt{xhamster.com} (see \cref{fig:top25_adult}).
 The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
+		The dependent variable is the percentage of time a person spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
-		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
-		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		The dependent variable is the percentage of time a person spent on pornographic sites.
+		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
+		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
@@
             See \cref{fig:top25_adult} for a comparison with our base classification.
-    	The \emph{Hours} column is the total number of hours that individuals in the sample spent on the site. 
+    	The \emph{Hours} column is the total number of hours that individuals in the sample cumulatively spent on the site. 
     	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of hours people spent on pornographic sites.
+		The dependent variable is the number of hours a person spent on pornographic sites.
 Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		The dependent variable is the number of hours a person spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
   Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
-		Covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
@@
             All numbers are based on online visits during the one-month period.
-		Pornography sites are categorized by Forcepoint ThreatSeeker (``Sex'' or ``Adult Content'').
+		Pornography sites are categorized by Forcepoint ThreatSeeker (``Sex'').
             See \cref{fig:top25_adult} for a comparison with our base classification.
-    	The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
+    	The \emph{Hours} column is the total number of hours individuals in the sample cumulatively spent on the site. 
     	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		The dependent variable is the number of hours a person spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		The dependent variable is the number of hours a person spent on pornographic sites.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
   Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
-		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
@@
             All numbers are based on online visits during the one-month period.
-		Pornography sites are categorized by alphaMountain (we include any categories mentioning ``porn'', ``adult'' or ``mature'').
+		Pornography sites are categorized by alphaMountain (``Pornography'').
             See \cref{fig:top25_adult} for a comparison with our base classification.
-    	The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
+    	The \emph{Hours} column is the total number of hours individuals in the sample cumulatively spent on the site. 
     	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.            
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
+		The dependent variable is the number of hours a person spent on pornographic sites.
 Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
 Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
-Covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 95\% confidence intervals constructed from standard errors.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of visits to pornographic sites by individuals in our sample.
+		The dependent variable is the number of visits to pornographic sites by a person.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the number of visits to pornographic sites by individuals in our sample.
+		The dependent variable is the number of visits to pornographic sites by a person.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
   Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
-		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
+		The dependent variable is the percentage of traffic to pornographic sites by a person.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
@@
 	\caption*{\footnotesize \emph{Notes:} 
-		The dependent variable is the percentage of traffic to pornographic sites by individuals in our sample.
+		The dependent variable is the percentage of traffic to pornographic sites by a person.
 		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
   Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
-		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
+		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
 		95\% confidence intervals constructed from standard errors.
@@
 
-First, we evaluate the density of the timing of visits to online pornography sites using 24-hour bins.
+We analyze whether partisans view pornography at different times during the day.
+We begin by evaluating the density of the timing of visits to online pornography sites using 24-hour bins.
 As anticipated, most visits to online pornography sites occur around midnight.
@@
 Second, we repeat the evaluation of the density of the timing of visits but split by partisanship.
-
-The densities suggest that Democratic traffic to pornography sites is concentrated around midnight (11 pm--1 am) while the Republican traffic is concentrated in the early morning (6 am--7 am, \cref{fig:time-of-day-consumption-by-party}).
-
-Third, to formally test whether there are differences in time of consumption by partisanship, we begin by dividing traffic to online pornography sites into six 4-hour bins: (a) 4 am--8 am, (b) 8 am--12 pm, (c) 12 pm--4 pm, (d) 4 pm--8 pm, (e) 8 pm--12 am, and (f) 12 am--4 am.
+The data suggest that Democratic traffic to pornography sites is concentrated around midnight (11 pm--1 am) while the Republican traffic is concentrated in the early morning (6 am--7 am, \cref{fig:time-of-day-consumption-by-party}).
+
+To formally test whether there are differences in time of consumption by partisanship, we begin by dividing traffic to online pornography sites into six 4-hour bins: (a) 4 am--8 am, (b) 8 am--12 pm, (c) 12 pm--4 pm, (d) 4 pm--8 pm, (e) 8 pm--12 am, and (f) 12 am--4 am.
 We code a visit depending on which time interval it occurred and regress that time-of-day window on partisanship, weighted by the dwelling time of the visit.

### 2024-04-29 ms/main.tex

@@
 Adjusting for immutable characteristics like age and gender makes the small differences go away.
-\emph{Keywords:} Measurement, YouGov, Pornography, Partisanship, Quantile Regression, Online Consumption
 \end{abstract}
@@
 
-To help contextualize the above figures, we present statistics on time spent consuming content from the top ten non-adult categories in \cref{tab:top10cat_description}.
-The median pornography consumer (\cref{tab:distribution_duration}) spends at least as much time on adult content as the median user on sites from six non-adult categories.
+To help contextualize the above figures, we present statistics on time spent consuming content from the top ten non-adult categories by traffic in \cref{tab:top10cat_description}.
+For each of these ten categories, we summarize statistics on hours spent in total.
+The median individual consumes less than 0.7 hours in seven of these categories.
+The three categories in which the median individual consumes more than 0.7 hours are: ''Business'', ``Search Engines and Portals'', and ``Shopping''.
+At the 95th percentile, only three of the top ten non-adult categories have more than 20 hours spent: ``Chat and Instant Messaging'', ``Business, Social Networking'', and ``Entertainment, Streaming Media''.
+
+%In comparison, the median pornography consumer spends 0.7 hours on pornography (\cref{tab:distribution_duration}).
+%The median pornography consumer (\cref{tab:distribution_duration}) spends at least as much time on adult content as the median user on sites from six non-adult categories.
 Only three categories, ``Business, Social Networking,'' e.g., \texttt{facebook.com}, etc., ``Chat and Instant Messaging,'' e.g., \texttt{google.com}, \texttt{live.com}, and ``Entertainment, Streaming Media,'' e.g., \texttt{youtube.com}, \texttt{hulu.com}, \texttt{netflix.com}, have higher levels of consumption at the 95th percentile than online pornography.
@@
         The table enumerates the top ten categories (YouGov) based on the amount of traffic to the corresponding sites from individuals in the sample.
-        Panel A is constructed using the browsing level data (n = 6.3m web browsing records.) Panel B is constructed using the individual-category-level data (n = 40k).
+        Panel A is constructed using the browsing level data (n = 6.3m web browsing records.) 
+        Panel B presents summary statistics at the individual-category level.
         }

### 2024-05-02 ms/main.tex
Updates from Overleaf

@@
 \renewcommand{\abstractname}{\vspace{-\baselineskip}}
-\usepackage[dvipsnames]{xcolor}
-\usepackage[
-linkcolor=darkgray,
-colorlinks=true,
-urlcolor=darkgray,
-pdfstartview={XYZ null null 1.00},
-pdfpagemode=UseNone,
-citecolor={darkgray},
-pdftitle={Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online}
-]{hyperref}
-\urlstyle{same}
+
 \usepackage{geometry}
@@
 \setlength{\parskip}{\baselineskip}
-\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 \usepackage{fancyhdr}
@@
 \usepackage[labelfont=bf]{caption}
+\usepackage{amsmath}
 \captionsetup[figure]{labelfont={bf},name={Figure},labelsep=period}
@@
 \usepackage{titling}
-\usepackage{amsmath}
 \usepackage{placeins}
@@
 \usepackage{moresize}
-\usepackage[nameinlink, capitalize, noabbrev]{cleveref}
 \settowidth{\thanksmarkwidth}{*}
@@
 Available at: \url{http://journalqd.org}}%
-  \lhead{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024), 1–n}
+  \lhead{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024), 1–67}
 \rhead{\color{gray} \footnotesize 10.51685/jqd.2024.011}
@@
 \fancyhf{}
-\fancyhead[LO]{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 1(2024)}
+\fancyhead[LO]{\color{gray} \footnotesize Journal of Quantitative Description: Digital Media 4(2024)}
 \fancyhead[RO]{\color{gray} \footnotesize Consumption of Pornography Online \thepage}
@@
 %Author names and affiliations go here, any Acknowledgements / authors' note / disclosure statement goes into \thanks{}
-\author{\normalsize Lucas Shen\\ \normalsize National University of Singapore, Singapore
+\author{\normalsize Lucas Shen\\ \normalsize Singapore Institute for Clinical Sciences, Singapore
 \vspace{1em} \\ \normalsize Gaurav Sood \\ \normalsize Independent Researcher, USA \thanks{Lucas Shen: \href{mailto:lucas@lucasshen.com}{lucas@lucasshen.com}}\thanks{Gaurav Sood: \href{mailto:gsood07@gmail.com}{gsood07@gmail.com}}\thanks{Date submitted: 2023-03-13}}
-\usepackage{lipsum}
+
+\usepackage[
+linkcolor=darkgray,
+colorlinks=true,
+urlcolor=darkgray,
+pdfstartview={XYZ null null 1.00},
+pdfpagemode=UseNone,
+citecolor={darkgray},
+pdftitle={Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online}
+]{hyperref}
+\usepackage[nameinlink, capitalize, noabbrev]{cleveref}
+\urlstyle{same}
+
 \renewcommand\footnotemark{}
@@
 Lastly, in line with previous research \citep{macinnis2015american, edelman2009markets}, which was based on aggregated data, we find that Republicans likely consume somewhat more pornography online than Democrats.
-Adjusting for immutable characteristics like age and gender makes the small differences go away.
+Adjusting for immutable characteristics like age and gender makes the small differences go away.\\
+
+  \noindent\keywords{\textit{measurement, YouGov, pornography, partisanship, quantile regression, online consumption} \vspace{8ex}}  
 \end{abstract}
-
-\keywords{\textit{measurement, YouGov, pornography, partisanship, quantile regression, online consumption} \vspace{8ex}}
 
@@
 \cref{fig:top25_adult} reports the top 25 pornography sites.
-The top three pornography sites (``\textit{xvideos.com}'', ``\textit{pornhub.com}'', and ``\textit{xnxx.com}'') are each visited more than 6,500 times by the people in our sample during the one-month period.
-The most visited site, xvideos.com, clocked 311 hours in total.
-(Given 361 consumers of online pornography, this translates into an average of 52 minutes of consumption of \textit{xvideos.com} per participant.) Newer platforms such as ``\textit{onlyfans.com}'' are also among the most visited pornography sites.
+The top three pornography sites (\texttt{xvideos.com}, \texttt{pornhub.com}, and \texttt{xnxx.com}) are each visited more than 6,500 times by the people in our sample during the one-month period.
+The most visited site, \texttt{xvideos.com}, clocked 311 hours in total.
+(Given 361 consumers of online pornography, this translates into an average of 52 minutes of consumption of \texttt{xvideos.com} per participant.) Newer platforms such as \texttt{onlyfans.com} are also among the most visited pornography sites.
 Nine sites are above the 99th percentile in pornography visits (2,224 visits).
@@
 \caption{Hours Spent on Online Pornography and All Other Online Content}
-\label{fig:distribution_duration_on_adultsites_fullsample}
 \caption*{\footnotesize \emph{Notes:} 
@@
 }
+\label{fig:distribution_duration_on_adultsites_fullsample}
 \end{figure}
@@
 The median individual consumes less than 0.7 hours in seven of these categories.
-The three categories in which the median individual consumes more than 0.7 hours are: ''Business'', ``Search Engines and Portals'', and ``Shopping''.
-At the 95th percentile, only three of the top ten non-adult categories have more than 20 hours spent: ``Chat and Instant Messaging'', ``Business, Social Networking'', and ``Entertainment, Streaming Media''.
+The three categories in which the median individual consumes more than 0.7 hours are: Business, Search Engines and Portals, and Shopping.
+At the 95th percentile, only three of the top ten non-adult categories have more than 20 hours spent: Chat and Instant Messaging, Business/Social Networking, and Entertainment/Streaming Media.
 
@@
 \begin{figure}[!ht]
-\label{fig:tu_prop_entertainment-prop_adult_duration}
      \centering
@@
 (Given we plot a lowess, such truncation doesn't change the relationship we show.) Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five such sites are \texttt{youtube.com}, \texttt{hideout.co}, \texttt{hulu.com}, \texttt{netflix.com}, and \texttt{yahoo.com}.
-Non-adult shopping sites are those with YouGov categories containing ``shopping,'' e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.---the top five such sites are \texttt{amazon.com}, \texttt{ebay.com}, \texttt{walmart.com}, \texttt{etsy.com}, \texttt{capitaloneshopping.com}, and \texttt{craigslist.org}.
+Non-adult shopping sites are those with YouGov categories containing shopping, e.g., ``Business,Shopping,'' ``Messageboards and Forums, Shopping'', etc.---the top five such sites are \texttt{amazon.com}, \texttt{ebay.com}, \texttt{walmart.com}, \texttt{etsy.com}, \texttt{capitaloneshopping.com}, and \texttt{craigslist.org}.
 The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
@@
 }
+\label{fig:tu_prop_entertainment-prop_adult_duration}
 \end{figure}
@@
 %Acknowledgments/ Author's disclosure/ funding statement.
-
+\clearpage
+\phantomsection
 \bibliography{porn,paperpile}
@@
 
+\newpage
 \clearpage
@@
     \label{tab:top10cat_description}
-	\begin{adjustbox}{max width=1.325\textwidth}
+	\begin{adjustbox}{max width=1.28\textwidth}
             \begin{tabular}{@{\hspace{0\tabcolsep}}lrrrrrrrrrrrrrr@{\hspace{0\tabcolsep}}}
@@
 \begin{figure}[!h]
-\label{fig:tu_prop_entertainment-prop_pure_adult}
      \centering
@@
 }
+\label{fig:tu_prop_entertainment-prop_pure_adult}
 \end{figure}
@@
 %==============================================================================
-\begin{table}[ht] \centering \normalsize \setlength\tabcolsep{5 pt}
+\begin{table}[ht] \centering \normalsize \setlength\tabcolsep{7 pt}
 	\caption{Median Differences in Pornography Consumption}
@@
 	\begin{adjustbox}{max width=\textwidth}
-		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
+		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccr@{\hspace{0\tabcolsep}}}
 			\toprule
-			&\multicolumn{6}{c}{\underline{Measures of pornography consumption}}\\
-			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}\\			
-			&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
-			\cmidrule{2-7}
+			&\multicolumn{5}{c}{\underline{Measures of pornography consumption}}\\
+			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\			
+			&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}\\
+			\cmidrule{2-6}
 			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
@@
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) shows subgroups for categorical variables.
-		Column (2) indicates the count of missing variables, if any.
-		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans.
+		Column (1) indicates the count of missing variables, if any.
+		Columns (2)--(4) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans.
 		1st and 3rd quartiles in brackets.
-		Column (6) and column (7) report the p-values and Standardized Median Differences (SMD) for Democrats vs Republicans.
-		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
+		Column (5) reports p-values for the difference between Democrats and Republicans.
+		See Panel A of \cref{tab:characteristics_split_by_party} for mean differences.
 	}
@@
 		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
-		Column (1) indicates the count of missing variables.
-		Columns (2)--(4) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans, respectively.
-		1st and 3rd quartiles in brackets.
-		Column (5) and column (6) report the p-values and standardized median differences for Democrats vs Republicans.
-		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
+            Column (1) indicate subgroups.
+		Column (2) indicates the count of missing variables.
+		Columns (3)--(5) show the mean (standard deviation) for the overall sample, Democrats, and Republicans, respectively.
+		Column (6) and column (7) report the p-values and Standardized Median Differences (SMD) for Democrats vs Republicans.
+		See \cref{tab:characteristics_split_by_party_medians} for median differences in pornography consumption.
 	}
@@
     \label{tab:quantile-estimates-hours}
-	\begin{adjustbox}{max width=1.325\textwidth}
+	\begin{adjustbox}{max width=1.28\textwidth}
             \begin{tabular}{l*{20}{D{.}{.}{-1}}}
@@
     \label{tab:quantile-estimates-time}
-	\begin{adjustbox}{max width=1.325\textwidth}
+	\begin{adjustbox}{max width=1.28\textwidth}
             \begin{tabular}{l*{20}{D{.}{.}{-1}}}
@@
 \begin{figure}[!ht]
-\label{fig:distribution_duration_on_adultsites_fullsample_mar}
      \centering
@@
 }
+\label{fig:distribution_duration_on_adultsites_fullsample_mar}
 \end{figure}
@@
     \label{tab:quantile-estimates-traffic}
-	\begin{adjustbox}{max width=1.325\textwidth}
+	\begin{adjustbox}{max width=1.28\textwidth}
             \begin{tabular}{l*{20}{D{.}{.}{-1}}}
@@
     \label{tab:quantile-estimates-prop-traffic}
-	\begin{adjustbox}{max width=1.325\textwidth}
+	\begin{adjustbox}{max width=1.28\textwidth}
             \begin{tabular}{l*{20}{D{.}{.}{-1}}}
